\chapter{Pandora's Actor}

As it turned out, nothing turned up to greet them as they crested the top of the ridge. No pastoral vistas; no bustling town arrayed before them on the other side. What they found on the other side was actually the edge of a deep gully, and only the frayed ends of a broken rope bridge remained on their side of the gap. Far below, hidden by the trees and brush laid bare by the brief passing of winter, he heard the trickling of water and little else but wind through the branches. No sign of the old road remained far away on the opposite side, but a rough path branched from the opening of the trail down a rocky course before disappearing into the trees below.

 

Pandora’s Actor debated whether he should simply leap across and try to find the remains of the road, as the Hanzos did not specify which route had led to their discovery. After a moment, he decided to descend down the rocky trail that seemed to have at least seen recent use. Swinging off of his mount, he unsummoned it as he landed lightly on his feet.

 

“Let’s head down,” he said. “Did the Hanzo report anything else about what lies ahead?”

 

Narberal shook her head as she followed suit, dismissing her own steed and taking a moment to straighten out her attire.

 

Pandora’s Actor turned his attention towards the trail again after receiving her negative response. Perhaps he should have had the Hanzo report to him directly; at least it would have been able to offer its thoughts to him so he would have a better idea of what lay ahead. Then again, hierarchy was important – he did not wish to deprive Narberal of her cherished role in their duty.

 

In the end, he felt that it was fine as long as he did not lose the trail and leapt down several dozen metres at a time. The manner by which he alighted on outcroppings of rock on the way to the bottom of the gully was greatly at odds with the apparent weight of his full plate armour and twin greatswords. Narberal cast Fly on herself and floated down after him. Within a few breaths, he landed with a shallow splash in the creek that he had heard from far above.

 

The rugged trail followed alongside the clear rush of water downstream, where daylight filled an opening in the distance. Narberal had gone ahead and her silhouette could be seen floating over the water where the creek left the trees, body slowly pivoting in midair as she surveyed her surroundings.

 

He joined her a minute later, casually striding out from under the branches and into the open air. The stream’s course continued a short distance before cascading sharply down a series of falls until it joined with a broad river. The trail that they had been following crossed the creek a few metres before the first dropoff. Some old, mismatched planks were laid across the shallows there to provide footing for travellers, held in place by large stones.

 

Now clear of obscuring forest, the trail offered a commanding vantage over the vista that lay before them. The river below cut deeply through the foot of the Southern Border Ranges, carving sheer, rugged cliffs several hundred metres high that towered over the far shore. Entering from between the cliffs to the southwest, it rounded a small, rocky hill at the head of the valley, flowing northwards until it passed where they currently stood. The river disappeared into a steep canyon to continue its journey towards the fertile lowlands.

 

A thick veil of morning mist shrouded the bottom of most of the wide vale that stretched up the river’s course, with only the crown of the distant hill visible in the far end. The forested slopes on the western side of the valley were not as imposing as the cliffs along the far shore, but still rose steeply enough to be considered impassable to the average Human. Beyond the river vale, the wilderness ranges rose in stark relief to the layer of fog over the valley floor, laced with fresh spring snows.

 

It was not surprising that Narberal had stopped to look around at this point – there was a wealth of information to take in instantly upon leaving the trees. Combined with the exposed nature of the trail, it was a perfect location to lay an ambush for the unprepared. Yet beyond the tumult of the falls and the rush of the wind that whistled past them on its way south through the valley, no challenge appeared.

 

His companion appeared to be unwilling to stand down from her vigil so he took the lead instead, following the narrow path down into the fog. It led the rest of the way down to the valley floor, where it joined with the riverbank. Though the trail they had been following saw signs of recent use, there was no trace of tracks leading through the wet sand.

 

The mist slowly dissipated as the morning advanced, though not yet to the point where he could see much beyond their immediate surroundings. The sound of the river current and the odor of damp vegetation filled his senses. The moisture hanging heavily in the air seemed to cling to his cloak and work its way into the joints of his armour. He did not particularly mind the conditions, but he couldn't imagine humans wanting to live in such an environment.

 

As he pondered this, Narberal soundlessly floated down beside him, wordlessly ending her enchantment. She shook her head as he looked to her questioningly.

 

“Only the hill ahead stands out in this fog,” she said. “I could make out little else.”

 

Her face held a neutral expression as she spoke. Even when with other denizens of Nazarick, she was ever succinct in her dialogue. He motioned for her to lead the way and followed her up along the shore of the river.

 

As their destination loomed into view, they slowed their rapid pace to take in the features of the rocky mound that rose before them.

 

The settlement reported by the Hanzo was little more than what it sounded. A bare handful of what were unmistakably hovels constructed of soil, wooden panels and loose stone were built into narrow terraces cut from the hillside. There were few proper buildings that could be seen: aside from the crude manor built halfway up the ascent, which also seemed to be built into the hill like the rest of the homes that could be seen, there was another that looked to be a small warehouse below it. An unremarkable stone shrine stood at the top of the hill and a simple pathway laced haphazardly with rocks of various sizes wove its way down from the shrine, through the buildings and onwards towards the pebbled beaches of the riverbank below.

 

From the manor halfway up the hill, a wisp of blue-grey smoke rose lazily into the air. Pandora’s Actor spotted a person’s face in the window looking straight down at them, but before he could raise his hand in greeting, it vanished behind thin curtains.

 

“Tsk.” Narberal clicked her tongue in annoyance to his side – the first-hand confirmation of the settlement being inhabited had visibly soured her mood.

 

As the pair approached the point where the path from the settlement disappeared into coarse sand, the door of the manor swung inwards. From their vantage at the bottom of the hill, they could see the head of a spear appear from the shadow of the doorway. Before it could clear the entrance, however, it jerked unexpectedly and fell to the floor with a clatter. He pondered whether Momon would have stepped forward to assist this apparently troubled individual, but, unable to see what he was dealing with, he decided to stay beside Narberal at the edge of the village.

 

Eventually, the spear rose again, its head wobbling in the air as it was lifted back up. It finally left the doorway, carried by what appeared to be a giant bolt of fabric. Any remaining semblance of tension slowly turned into impatience as the caricature took several minutes to descend the path down to where they stood.

 

As it turned out, the curious figure was the same person that they had seen in the manor window upon their arrival: an adolescent human girl who could be no older than her mid-teens. Perhaps older? Unlike the concretely-defined existences created by the Supreme Beings, these strange peoples were so variable that he and the others often found it difficult to discern their qualities from outward appearance alone.

 

She was wearing a gambeson that was most certainly meant for a much larger man, which resulted in the thick, padded layers giving her the odd appearance he had noted as she made her way down. Its hem hung down past her knees and the absence of a belt caused the entire weight of the suit to hang heavily upon her shoulders. Loose strands of dark chestnut hair poked out from under a simple leather cap that was strapped onto her head. The girl slowed to an unsteady stop before them; the panicked trek down the hillside in the ill-fitting and oversized equipment having taken its toll on her slender frame.

 

However, as her gaze passed over them, the spear came up. Raised to her shoulder, the blade of her polearm was leveled directly at them.

 

To his side, Narberal bristled at the action and Pandora’s Actor quickly raised his hands in a disarming manner.

 

“We are Momon and Nabe of Darkness,” he announced in a calm and confident tone. “You may have heard of us.”

 

The fame of Darkness had spread far and wide; many people throughout this land could even recognize them on sight. But far out on the isolated frontier of what was formerly the Kingdom of Re-Estize, it was possible that they were entirely unheard of. In that case, they were simply a pair of dangerously armed and imposing strangers that had suddenly appeared out of the mist with no prior invitation or warning.

 

Seeing that the girl did not lower her guard, he cleared his throat and shifted into a less aggressive stance to continue.

 

“As you may know,” he said, “this duchy has come under the dominion of the Sorcerous Kingdom as a result of the battle at Katze Plains. We have come to deliver a missive from the capital to all landed nobles of E-Rantel. Is Bar…”

 

The voice of Momon trailed off in the midst of his delivery. Pandora’s Actor sensed that something was off.

 

Throughout what he gauged to be a relaxed and casual introduction, the waves of alarm and fear coming off of the girl had not subsided. He quickly reviewed the scenario in his mind, seeking out faults in his own performance. Then, with a start, he realized that he had let down his guard.

 

As he had shifted his body, the girl had maintained her crude stance. Yet the head of the spear did not follow him – the much larger and more threatening in appearance between the two Adventurers – as he moved. It remained leveled at the source of her fear.

 

At Narberal.

 

Als Tiger gesprungen und als Bettvorleger gelandet!

 

The idiom came to his mind unbidden and it took substantial effort to not blurt it out aloud.

 

When he had initially received his role as Momon, he believed it to be the perfect opportunity to employ his skills in the service of his creator – the perfect casting. Thrust onto a stage where he was showered with the praise and adoration of the citizens, he had employed his natural abilities as a Doppelganger to draw from the hopes and expectations of the people. By doing so, he was able to enhance his performance and drive the already legendary image of The Dark Warrior to ever greater heights. It was a simple task by his own estimation, yet at the same time supremely gratifying to fulfil a role that he had been seemingly born for.

 

As they entered lands that were increasingly abandoned, however, he had lapsed in the use of these powers with no audience to witness his performance. The result of this misstep was that an irregularity had slowly approached them in plain view, coming within striking range without him even being aware of the threat that she represented. He counted it fortunate that the witnesses to his mortifying oversight were few.

 

Resolving to salvage this unacceptable development, he immediately reached into the mind of the girl standing before them to skim her thoughts with his abilities. While he believed that there was little chance this young human presented any direct physical threat to either Narberal or himself, there was still the matter of what was causing her distress and how it could lead to affect some imperceptible future.

 

It did not take long to recognize the initial sensation; he had felt this fear before. Just a few days ago, after weeks of practice on the field, he had teleported back to E-Rantel to play his part in his Master’s triumphal entry into the city. It was the same emotion that rode through the Human onlookers when the Sorcerer King first entered E-Rantel. A fear born of horror; a terror that either paralyzed one where they stood, or drove them to act. To fight; flee – do anything to survive. A primal fear reserved for the monsters and inhuman enemies that lurked beyond the safety of their cities and villages.

 

Yet Narberal did not hold such an appearance. By Human measure, she was a woman whose sharp manner and exotic features exuded a cold beauty that drew the admiration and envy of all who encountered her.

 

Pandora’s Actor frowned at the incongruity as he navigated the waves of the girl’s overpowering emotions back into her mind until he could finally look out from her thoughts. Normally, it would be a challenge to read anything beyond surface thoughts, but in her distressed state the girl was laying her mind bare to psionic intrusion: the undisciplined mind of a low level individual, broadcasting her fear-ridden thoughts to any who would care to peruse them.

 

His field of vision lowered; he saw the haft of a spear and the gloved hand that held it fearfully directed at its target. Ragged, heavy breathing caused the tarnished blade to rise and fall unsteadily. Beyond his own figure, standing slightly to the side, the weapon was pointed directly at his companion.

 

Above the simple traveller’s garb covered by the plain-looking brown cloak was a smooth, pale visage that looked directly back at her with empty eyes. Despite being devoid of features, a withering aura of hostility could be felt coming from her. After lingering for a moment, he noticed what should have been Narberal's Human appearance faintly superimposed over her natural face. A quick note of Narberal’s hand showed that she still had her Ring of Non-Detection equipped…

 

Pandora’s Actor withdrew from the girl’s thoughts and gathered his own. Enchantments that allowed the recipient to pierce through illusions, defeat magical concealment and even see through abilities that changed one’s form were not unheard of – many casters within Nazarick were capable of the spell which replicated the effects of this sense. As part of his preparations in assuming the role of Momon, he had pored over the information collected since their arrival in this strange new world for any threats that could foil his guise.

 

Amongst the Humans of this world that they knew of, there were scant few. The closest, according to the reports, was a Cleric based hundreds of kilometres away in the royal capital of Re-Estize. Even then, the frightened girl standing before them did not match her description. No matter which way he looked at her, this young girl in ill-fitting armour had neither the bearing of a bold Adventurer, nor the vestments of a distinguished member of a priesthood, nor the appearance of a powerful – by the standards of this world – mage.

 

If anything, this girl resembled nothing more than an ordinary Human: one they could have encountered anywhere along their travels. It was a thought that sent a cold tendril of anxiety down his back over what could have been.

 

There were many mysteries in this world that they had suddenly found themselves in; things unheard of in Yggdrasil. This girl appeared to be one of them: something the Humans in the surrounding regions referred to as a 'Talent Holder'. They were exceedingly uncommon and usually never completely identical to one another. In fact, an individual that manifested such an ability was not guaranteed that it would ever be applicable in their ordinary lives. She may even have gone her entire life without realizing her own Talent; Re-Estize as a nation was, to be nice about it, not very advanced in terms of magic – her daily interactions would not have had her see very much more than her fellow Humans.

 

However, that would no longer be the case. The machinations of his Master would soon give rise to a nation of unprecedented mystical might; a nation filled with a multitude of peoples that would quickly render her Talent self-apparent. That this girl ended up with an ability that she could make immediate practical use out of meant that she was a proverbial diamond in the rough. Whether she could be used to forward his Master’s goals, however, was yet to be seen.


A rare item indeed, thought Pandora’s Actor as he raised a gauntleted hand to his helmet.
