\chapter{Albedo}

Gathering the documents that lay scattered in a loose pile before her, Albedo mentally reviewed the events of the day’s meeting. Beyond the matter of Baroness Zahradnik, it had been much the same as the ones that had preceded it. Shalltear, having mostly regained her composure, excused herself from the chamber as soon as the session had run out of topics to cover: effectively adjourning the gathering. With the collected articles arranged to her satisfaction, Albedo lightly tapped the papers on the desk to align them before slipping them into a dark folder and placing them into her inventory. She did not rise to leave; instead watching as the others slowly left the chamber through various means. After Shalltear left through the main doors, Cocytus teleported away with Entoma while Pandora’s Actor and Sebas were discussing something as they left through the service entrance.

 

Following Momon’s figure with her gaze until he disappeared around the curtain obscuring the side door, she thought back to Pandora’s Actor’s unexpected actions. Not only had Albedo been caught completely unaware, she had been completely defenceless against his motion to create a place for a seemingly problematic Human noblewoman. With how smoothly the entire discourse had gone in his favour, she suspected that he had carefully calculated the trajectory of the discussion long before the subject was even broached. As the one who was created to oversee and manage the Great Tomb of Nazarick, she did not enjoy the fact that matters had been wrested out of her control. In her mind, this was a right reserved for her Master alone.

 

Previously, her experiences with the Doppelganger had been limited to their brief introduction in the Guild Treasury and a few other interactions. Despite his usually flamboyant and exaggerated character, she held the vague understanding that Momonga-sama’s creation possessed an intellect that rivaled both that of Demiurge and her own, though in what manner she had not been even remotely aware of until now. It was reassuring to have another eminently capable individual to serve with, yet at the same time he would be an implacable thorn in her side should he ever choose to oppose her. Fortunately, she had come to this realization before any attempt to incorporate him into her side project.

 

He had laid out a compelling case to allow the Baroness’ continued existence and Albedo’s pride as a supremely capable administrator would not allow her to deny any of his observations regarding the state of E-Rantel and its duchy. Shortly after the Baharuth Emperor’s audience in Nazarick and the plans to annex E-Rantel through the seasonal conflict between the two nations had been laid out, Albedo had started her own preparations for the inevitable outcome. Through the weeks leading up to the conflict, she had made a great study of the city and its surrounding lands in order to ensure a seamless transition to Nazarick’s rule. She had even taken it upon herself to requisition and personally train suitable Undead servitors to act as assistants for the initial phases of the takeover.

 

All of her advance effort had seemingly been for naught, however, as many of the surviving nobles and the officials who served under Lord Rettenmeier had fled to Re-Estize while the formalities of the annexation were still being observed. So complete was their loyalty to the man – who at the time had served as the city’s Mayor and Ramposa’s Provost in the duchy at large – that when he had returned to his own territories in the west, all of his administrative staff in the city had chosen to follow him rather than stay to continue their service in E-Rantel. As loyal vassals of Momonga-sama themselves, the act of solidarity by Rettenmeier and his associates in loyalty to their own liege had earned them the tiniest modicum of respect by the NPCs, but there was no denying the problems they had caused in their wake.

 

The result was that the Sorcerous Kingdom had inherited a district of hastily abandoned government buildings, destroyed archives and the shattered remains of E-Rantel’s aristocracy. She had predicted that it would take several weeks for the Elder Liches to learn how to adapt their training to these vacant offices, but it turned out that they would not even get a chance to do that: trade had ceased entirely, the remaining nobles were still recovering from their bereavement and it was not even known whether those that were left were capable of running their own fiefs. With no data available, and none being collected and filed to process, no projections could be made and no amendments to laws or new policies could be responsibly enacted; thus the entire administrative framework of the Sorcerous Kingdom had run into an unyielding wall from day one.

 

Their only saving grace was that the vast stores of E-Rantel, filled with supplies originally meant for the armies of Re-Estize, would serve as a lifeline for the city’s population for several months. However, If regular operations and commerce could not be restored by that point, the citizens would run out of vital supplies. While it was possible to use Dagda’s Cauldron to supplement food to an extent, it did not solve any of the other shortages, and went against the idea that the duchy was supposed to be a productive source of income for Nazarick. It was a small thing to provide some food to a single village or town, like they had done with Carne Village and the consolidated Lizardman tribes, but feeding the hundreds of thousands of Humans remaining in the duchy of E-Rantel was another matter entirely.

 

One might argue that Pandora’s Actor had made a rather unfair argument in light of the circumstances, but Albedo also knew that his points were irrevocably true. Excuses had no place in Nazarick, and E-Rantel’s continued state of paralysis was absolutely unacceptable. The arrangement orchestrated by the Doppelganger was acceptable for the time being; she would stay apprised of the Baroness’ activities and take advantage of any developments that occurred as a result of them. She did not even care overly much that any of the noble’s accomplishments might be accredited to Shalltear – it was imperative that the Sorcerous Kingdom achieve a semblance of function as quickly as possible.

 

And if Baroness Zahradnik met with too much success, Albedo could always act to suppress her.

 

Satisfied that the situation was well in hand, the Guardian Overseer looked up from her thoughts to see that nearly all of the NPCs had vacated the chamber. The sole occupant other than herself was Narberal, still standing along the wall where she had attended the entire council session.

 

While all of Nazarick’s creations were unified in their purpose to serve the Supreme Beings, the months that had passed in this new world had seen the rise of several ‘factions’ from within its ranks. Rather than any particular agenda, they had formed out of the general attitudes carried by the various denizens of the Great Tomb of Nazarick. There were three main groups: two were led by Albedo and Shalltear, which could be loosely categorized by whether their members saw outsiders as either vermin or food. Those who saw vermin as food, such as Entoma, did not belong to either side. Their members also supported their respective heads in the ongoing bid for Momonga’s attentions.

 

The final group consisted of those denizens that had a more benevolent outlook towards outsiders. It actually had a fair number of prominent members, though none of them held active roles in the direct leadership of Nazarick. In addition, many of the other NPCs: Demiurge, Cocytus, Aura and Mare, to name a handful, either purposely stayed out of these divisions or remained blithely unaware of them.

 

The Pleiades – the formation of battle maids who included Yuri Alpha, Narberal Gamma and Entoma Vassilisa Zeta as a part of their number – were divided in their support for each group, but Narberal was firmly in Albedo’s camp. After taking one last look around the empty room, Albedo focused her attention on Narberal.

 

“Truesight is the nemesis of Doppelgangers,” Albedo’s voice was soft, but still carried clearly across the room to where Narberal stood. “I’m surprised you didn’t dispose of her immediately.”

 

Narberal’s lips drew into a thin line. Though Albedo had taken a conversational tone with the battle maid, the Doppelganger battle maid bowed in apology before speaking.

 

“As soon as I found out,” she said, “I attacked with enough force to kill her several times over…but Pandora’s Actor intercepted my spell.”

 

“Where was this?”

 

“…in the gardens near the front of the Royal Villa,” Narberal replied. “We had just stepped off the gazebo cordoned off for teleportation when he informed me of her Talent.”

 

“I see.”

 

Albedo tapped a finger idly on her desk. Once again, she was made to realize that Pandora’s Actor had already been several steps ahead of her by the time he made his entrance to the council chamber.

 

Narberal’s appearance as an Adventurer left her reliant on her shapeshifting ability – in combination with the Ring of Non-Detection – to conceal her true nature, so Pandora’s Actor must have immediately perceived the Human’s reaction to the Doppelganger’s inhuman appearance. But rather than informing Narberal, whose single racial level in Doppelganger meant that she had no ability to sense the thoughts of those around her, he had purposely withheld the information while continuing to test Baroness Zahradnik’s character and discern her value to the Sorcerous Kingdom.

 

It was only after they had arrived in the central courtyard of E-Rantel that her Talent was disclosed to Narberal, who had in turn reacted appropriately to end the threat. By standing in defence of the Baroness, Pandora’s Actor had demonstrated to her the dangers of revealing her ability, wordlessly declared to anyone that might be watching that she was under his protection and reminded the denizens of Nazarick that potential threats could still be lurking right under their noses, reinforcing their vigilance.

 

The fact that he had done so without even waiting for the outcome of the council meeting was particularly irksome: it suggested that he had plotted out the course of events and that the result was inevitable. His scheme was annoyingly well-crafted – perhaps he had acted on some secret impetus from their Master.

 

Albedo sighed; there was no use in wasting energy thinking about it. Instead, she inquired further as to the Baroness’ circumstances.

 

“Human aristocrats do not exist without people to lord over,” she said. “Was anyone else present to witness this…episode in her territory?”

 

Narberal shook her head in response.

 

“She was alone in her home when we arrived,” she replied. “The village and surroundings were empty. The Baroness informed us that the commoners had fled south to the Slane Theocracy upon hearing about the rout at Katze Plains, abandoning their liege.”

 

The maid’s lips thinned in disgust as the last of the words left her mouth. Albedo blinked as the words registered in her head. They had abandoned their master? The reprehensible thought caused bile to rise in her throat.

 

Stepping out from behind her desk, Albedo made her way down to the central area of the council chamber, where the large oak table filled most of the floor. A giant map of the lands surrounding E-Rantel, far superior to those which they had procured from the remains of the city archive, was spread out over most of its surface. Albedo circled around it until she stood over the southwestern corner, tracing her fingers from where Warden’s Vale lay, through the wilderness and over the border of the Theocracy along the fastest probable route.

 

Nearly half of the population of Humans amongst the rural population of the Duchy of E-Rantel had fled after news of their Kingdom’s catastrophic defeat at Katze; waves of fear and panic swept across the lands, often emptying rural communities wholesale. Since the people had mostly fled west to Re-Estize, Nazarick’s hands had been tied as their Master’s orders forbade them from applying forceful methods to the regions held by neighboring nations. Deploying Momon to try and curb the massive outflow of refugees had been their most effective course of action, but even as he sped from village to village to assuage the fears of the citizens, more had slipped across the border like so many grains of sand through their fingers.

 

Fleeing south, however, was a different story entirely. The eastern extremes of the Abelion Wilderness occupied the space between the southwestern border of the Sorcerous Kingdom and the northern border of the Slane Theocracy. The wildlands were unclaimed by any nation, with next to no development and occupied only by small pockets of Demihuman tribes. A simple calculation led to the conclusion that a refugee caravan filled with Humans of all ages could not possibly have crossed the wilderness yet – even if they had started their journey shortly after receiving news of the Kingdom’s defeat.

 

“There is no forgiveness for betrayal,” Albedo’s icy decree required no interpretation.

 

With a sharp affirmative and a respectful bow, Narberal Gamma strode to the main exit of the council chamber, the sound of her armoured heels echoing in grim cadence.

 

The pristine smile returned to Albedo’s lips: perhaps there was some satisfaction to be had at the end of this, after all.