\chapter{Ludmila Zahradnik}

Following her statement, the trio rode on in silence. Was Momon taking the time to review their exchange, or had he become disinterested in the discussion? Being perpetually encased in that black armour didn’t help with any attempted reading of him. She peered into the overgrown tangle of the forest and wondered how he could ride at such a blistering pace through the neglected road – marred by all manner of hazards – with his visor down.

 

The forest thinned out, and intermittent meadows filled with shrubs and tall grass appeared along the road. The sky remained overcast in the hour or so it had taken for the golem horses to make their way through the woods. The road showed little sign of improvement: the unpaved clay was a patchwork of grass and exposed rocks, with puddles of mud filling the dips and trenches over its eroded course. Ludmila knew to expect this deterioration at the fringes of the inner territories, but directly witnessing the sheer amount of wildland well inside the duchy’s borders was still astonishing.

 

Not a half hour later, Momon broke the silence between them, guiding his mount closer once again to speak to her. To Ludmila’s relief, he appeared to harbour no ill will over their previous discussion.

 

“When we received this request,” he said, “we were given several maps to help us navigate the countryside. Beyond the immediate area around E-Rantel, however, the map for the regions south of the western highway was highly inaccurate.”

 

Reaching into a saddlebag, he produced a roll of crisp parchment and offered it to her. Ludmila received the map and unfurled it, using Nabe’s back as a windbreak while Momon continued to speak.

 

“We would have dismissed it as a fabrication had we not personally seen the remains of many of the features it had marked down. Finding your village after crisscrossing so much of the area was quite a surprise, considering all of the abandoned territories we encountered beforehand.”

 

Indeed, the map was old. As Ludmila held it in front of her and examined the details, she recognized it as a land survey that the Kingdom used for administrative and tax purposes. There was a similar map in her home, and this appeared to be the original: unaltered with the passing of many generations.

 

“This is...a very old map,” she said. “How did you come by it?”

 

“The mayor of E-Rantel fled the city with his administrative staff – along with many of the local nobles,” Momon replied. “Before they left, they took with them or destroyed any documents that might have been used against Re-Estize in the future. This map is the best that the new administration could find in the aftermath: it was stored in the corner of an old archive, which I suppose is how it was missed. Is anything on the map familiar to you? I noticed that the Zahradnik Barony is marked on it.”

 

Using Warden’s Vale as a point of reference, she traced the road north, attempting to discern their location. The forest that they were riding through was once the land of another Baron, which had been carefully managed for lumber, game and forage. On the map, a small village was placed near the edge of the woodlands. They had come across the occasional old, sunken homestead in the meadows that they rode through, but she couldn't tell whether any of those had been a part of the settlement marked on old survey.

 

Ludmila shook her head in response.

 

“Aside from our barony and the duchy capital, no,” she said. “The river as well, of course. Even the borders of many fiefs have changed since this map was made.”

 

“Speaking of which,” Momon asked, “what is that river near your village called? It seemed to have no name on the map. I found it strange with it being so large.”

 

Ludmila looked back at the map. The only place that the river appeared to be marked was as it passed by her home. There was a large valley marked to the south of E-Rantel as well. Perhaps it had not been fully explored at the time it was drawn.

 

“It’s the Katze River,” she said.

 

“The Katze River…” Momon said thoughtfully, “the same river that passes some distance south of E-Rantel into the haunted plains beyond?”

 

“Yes, the very same.”

 

“I see. This is why your territory continues to exist to this day.”

 

Ludmila nodded. Despite being an Adventurer whose expertise should lie elsewhere, he seemed to be intelligent enough to immediately make this particular connection.

 

After its founding, the Kingdom of Re-Estize quickly expanded from its heartlands far to the west. There were two major rivers in its eastern territories: the first flowed down from the great ranges of the Azerlisia Mountains, through the Great Forest of Tob, then onwards into the idyllic heartlands of the Kingdom past E-Libera. The second came out of the border ranges to the south, forming in a high wilderness basin before flowing through Warden’s Vale; eventually running its course past E-Rantel before disappearing into the Katze Plains beyond. The Katze River was the only large waterway in the duchy, thus E-Rantel mostly relied on a network of rural roads to service its landlocked territories.

 

A river was basically a free road that required relatively little effort to transport cargo compared to overland routes. As times grew harder, other fiefs buckled under the cost of maintaining infrastructure and protecting their merchant traffic. It was her family’s ambition to reclaim these lost lands and add them to their own holdings as Warden’s Vale developed, but even with the advantage that the river conferred, their barony barely managed to stay afloat financially.

 

“That doesn’t explain how this area ended up in such a state, though,” Momon said, gesturing to the landscape beyond them. “The map seems to suggest that all of this used to be a prosperous land.”

 

Ludmila thought on how to answer. Considering the two Adventurers appeared to be foreigners, she thought it prudent to ensure that they understood the history of the region.

 

“House Vaiself claimed these lands when Re-Estize was still expanding, then offered titles to those who could tame and hold it. Wealthy families – both of new cadet branches and merchant stock – quickly took advantage of this, claiming the areas closest to the main routes of travel and trade. Over time, successful Adventurers would settle the fringes to retire and establish a legacy for their families. With a dwindling number of landless scions available in such a short period of time, the King extended his offer to them as well.”

 

“So your family was descended from past Adventurers,” Momon inferred from her recital.

 

“House Zahradnik was founded by an Adventurer, yes,” she nodded. “He was a Ranger who fell in love with the pristine valley nestled in the highlands. He took the name of our house with the dream that our family’s home would one day become a verdant jewel, far from the crowded cities that our ancestors came from. With powerful Adventurers serving as Frontier Lords, the borders were quickly secured; the monsters and Demihuman tribes driven away. For his service, Andrei Zahradnik was granted his title of Baron and the royal family encouraged migration from the west to help grow his fledgling fief and those of others like him.”

 

Ludmila glanced towards Momon. She had lost herself in her own recounting of history, which she had learned alongside her siblings. Rather than appearing uninterested like her brothers had been, however, the dark warrior seemed to be listening intently. Taking advantage of her silence, he asked a question.

 

“The Kingdom of the past seems to have been far more progressive than what it has become today,” he said. “This would explain the promising picture portrayed on the map…but with a powerful legacy, how could this reversal in development happen so quickly? The sight you see around you right now isn’t that much different than many of the places that Nabe and I travelled through before arriving at your territory.”

 

The trio had passed out of what could properly be called a woodland. All around, the land was fallow and had grown wild after decades of neglect. Small groves of Aspen and Birch dotted the gently rolling landscape. Ludmila returned her gaze to Momon.

 

“Not all families are as fortunate as House Aindra.” Ludmila replied, referring to the famous noble house that had produced powerful Adventurers over consecutive generations, “While we are, on average, notably stronger than the people inland, children born to powerful Adventurers are not guaranteed to inherit the full strength of their parents. Of the succeeding generation after the first, out of all the southern Frontier Nobles, not a single man or woman had the individual power of their parents. Once in a while a generation will produce a scion that could come close to comparing to their founders, but it is unrealistic to expect a consistent line of strong descendants.”

 

The seemingly capricious Adventurer bloodlines of the Frontier Lords had, over the generations, become regarded as a curse of sorts by nearly all of the border houses. Without the same wealth, influence or connections of the merchants and nobles that had settled the interior had access to, the Adventurers-turned-Aristocrats had relied on personal strength to secure their lands and protect their people, as well as subsidize their fiefs through guild commissions. When succeeding generations had proven incapable of following in their founders’ footsteps, resources needed for development would be set aside for security instead – to hire Adventurers to assist in clearing their lands of bandits and monsters alike.

 

This irony of this was not lost on the Frontier Lords, and it weighed bitterly on their hearts. Ladies would be ashamed that they were unable to produce promising heirs, the question of their fidelity floating in malicious whispers beyond their hearing. Lords were left feeling inadequate and undeserving of their station, ever in the shadow cast by their ancestors. Left mired by their inheritance, they were chained down by the obligations and the duties that came with their titles even more so than their tenants were to the land.

 

Of her own immediate family, neither of her brothers displayed any outstanding qualities; nor did their mother or father – her parents were both Gold-ranked. Her maternal grandfather was said to be about as strong as a Platinum-ranked adventurer. No one that she was aware of in her ancestry came even close to matching the first Lord Zahradnik, who was an Adamantite-rank Ranger in his own right.

 

“I see,” Momon replied: as an Adventurer, he should have been well aware of this. “So the Frontier Lords leveraged their personal strength to offset the remoteness and undeveloped nature of their fiefs, but a generation was not enough time to secure enough wealth to sufficiently develop their lands. Then, as security broke down, the lands that depended on their protection were caught up in their problems as well.”

 

Once again, the Adamantite Adventurer displayed his expertise in matters beyond simple adventuring. Ludmila nodded in response to his words.

 

“It is as you say,” she said. “Once the borderlands lost their strong, unified resistance to the threats of the frontier, Demihumans and monsters started to encroach upon the lands on a regular basis. The Frontier Lords have been on the back foot ever since, until nearly all of the territories along the border ranges became too hostile for Humans to inhabit.”

 

Momon returned to the original topic from when they had left her home, seemingly satisfied that his understanding of the state of the southern frontier was adequate.

 

“That doesn’t explain why your territory was abandoned, though,” he said. “Your barony has held for over a century with its highly defensible position and access to the Katze River. This change seems to have occurred recently as well…what happened?”

 

“They fled south to the Theocracy about a week before you arrived,” Ludmila answered. “When we heard about what had happened at Katze, the decision was made to evacuate the village before the Empire could move on from E-Rantel. I dispatched Rangers to investigate the farmlands beyond this area: they all reported that the lands had been similarly abandoned.”

 

Their journey had brought them out to a fork in the muddy trail. There was what appeared to be the remains of a sign, but the placard had long since fallen off and only the aged, wooden pole it had been attached to remained. The pair of Adventurers slowed their mounts and stopped at the split in their path.

 

“That seems to be an all too common tale recently.” Momon’s voice seemed even, but there seemed to be something else to his words. “Tell me, Baroness. Was it your desire that they evacuate to the Theocracy?”

 

The conversation had taken an odd turn, but Ludmila answered anyway.

 

“I thought it best to wait until we were certain that there were forces coming to attack the village,” she said, “but I did not feel that the people would have done so, even if I had ordered it. The tale that the survivors returned with was so surreal and horrifying that a few villagers had already fled on their own – our ship was stolen the same night that they arrived. The least I thought I could do was ensure that everyone could make it safely through the wilderness which, at the same time, would minimize the damage to the village. Even so, I was secretly hoping that my lord father would return during our preparations and resolve the situation. In the end, however, they left...and I stayed.”

 

For a long moment, the air between them was only filled with the winds blowing across the plains from the north.

 

“So despite your wishes, your vassals abandoned you – they left their liege alone to save themselves.”

 

The sudden change in his tone was jarring. No – his steady tone remained the same, but the atmosphere that had surrounded their conversation developed a dark undercurrent of simmering anger. She felt Nabe go rigid in front of her. The woman raised a gloved hand to cover her mouth, but Ludmila could not see her expression from behind. Turning to stare at Momon, she couldn’t understand what was going on. It was as if her response had meant something else entirely to the two Adamantite Adventurers, and she alone remained ignorant of it. Ludmila was left shifting uncomfortably as the oppressive silence dragged on.

 

There was a sound of metal plates shifting against one another as Momon dismounted and the golem horse vanished into thin air. He walked over to Nabe’s mount, stopping near to where Ludmila was seated behind her.

 

“You mentioned that the other border territories were long abandoned?”

 

Momon held his hand out to her as he once again resumed speaking. The feeling about him had lightened considerably, but the grim aftertaste of what she had felt before still lingered in her mind.

 

“For several decades now, yes,” Ludmila replied.

 

She looked to the horizon, then back to Momon’s offered hand. Were they stopping here to camp overnight? The skies were clearing in the north, and the sun would still be out for a couple of hours yet.

 

“Then our work is done,” he told her. “We will travel directly to E-Rantel from here.”

 

Momon prompted Ludmila once again with his outstretched hand and assisted her off of the tall mount. Ludmila took her pack and waited beside him as Nabe dismounted and her horse vanished like its twin. The young noblewoman looked around them for a hole in the air, recalling the way her cargo was delivered earlier in the day.

 

“Nabe will be teleporting us to the city,” Momon explained. “You may feel some disorientation, but please try to relax.”

 

Momon adjusted the position of her other bag as Nabe stepped forward. She reached out with her hands and lightly laid them on Ludmila and Momon’s arms.

 

“「 Greater Teleportation 」.”

 

The air seemed to shift as Nabe completed casting her spell. The wide open meadows of the countryside were replaced by a large but secluded urban garden. Rows of buildings around them cast their shadows over the ground as the evening sun sank towards the city walls. The three of them were standing inside a large gazebo and, after looking around carefully, Ludmila saw that the buildings were the lavish guest houses of the city: she was in the administrative district of E-Rantel. To her left, the Royal Villa loomed over the surrounding area.

 

One by one, they stepped out of the gazebo onto the pavement of the garden lane, and Momon returned Ludmila’s other bag to her.

 

“This is where we must part ways,” he said. “Nabe and I need to report our findings to the central administration. I believe several guest houses have been prepared to receive the nobles that have come to answer their summons.”

 

They started to head in their separate directions, then Ludmila heard Momon’s voice behind her.

 

“By the way, Baroness Zahradnik,” his calm voice floated over her shoulder.

 

“Yes?” Ludmila stopped to look around at Momon again.

 

“I believe it would be prudent to limit the number of people that know about your Talent.”

 

“Talent?” Both Ludmila and Nabe asked after Momon curiously.

 

“Ah...I neglected to mention it to you, Nabe,” Momon said offhandedly. “Baroness Zahradnik has Truesight.”

 

Nabe’s eyes widened in shock, head turning to quickly look back and forth between the two. Then, all at once, the air was filled with overwhelming murderous intent.

 

“「Maximize Magic – Shocking Grasp」!”

 

Roiling arcs of azure current formed around Nabe’s outstretched arm, rolling down towards her hand as she shot forward with blinding speed towards the startled young noble.

 

Before Nabe could reach her, Momon’s arm came across Ludmila's vision. She saw the electricity jump to the dark warrior with a sharp crackling sound. Even though Nabe’s hand had impacted solidly with the full momentum of her body behind it, his arm did not budge. In the brief silence that followed, Momon’s crimson cloak floated back down to the ground after his sudden movement.

 

“Momon!” Nabe shouted in surprise after realizing that her spell had been thwarted.

 

“It’s fine, Nabe,” he told her calmly. “Leave her be.”

 

After a tense moment, Nabe finally withdrew her arm and relaxed from her aggressive stance. Momon turned to Ludmila.

 

“As you can see,” he said, “some people may react quite poorly to the realization that you have this ability. As a noble of the Sorcerous Kingdom, please refrain from causing panic amongst the citizenry with your gift.”

 

With his last cautionary note, Momon turned away to walk towards the Royal Villa with Nabe. As the pair receded into the distance, she saw Momon touch the nape of Nabe’s neck with his index finger. There was the sharp snick of static, and his partner jumped and stumbled forward with a squeak. Rubbing the back of her neck, she shot a hurt look at Momon, then directed a glare towards Ludmila who had been watching from a distance. Picking up her pace, Nabe walked far ahead of Momon and disappeared into the villa entrance.