\chapter{Pandora's Actor}

The measured tread of metal sabatons echoed through the empty halls of E-Rantel’s Royal Villa. Remaining equipped in Momon’s armour, Pandora’s Actor strode past the displays of exquisite art and luxurious furniture without even so much as a disinterested glance: he had already come down these halls on multiple occasions, and there was nothing new or interesting of note in the first place. The magical lighting lining the walls had been kept purposely dim and reflected weakly off of his dark armour and the polished marble floors. After catching up with Narberal, his mind became preoccupied with other things as he made his way through the corridors – none of their details went much beyond a simple registration of his surroundings.

 

Albedo, the Guardian Overseer, insisted on convening at least twice a week. Out on the field, he and Narberal needed to regularly interrupt their journey and return to E-Rantel via teleportation magic to attend. The meetings had originally been twice per day, until several of the other NPCs had appealed for changes; the frequent interruptions interfered with their personal duties and assigned tasks. In truth, Albedo’s obsessive perfectionism when it came to administrative matters would have probably had them constantly conferring with one another if she could somehow make it possible.

 

Though Pandora’s Actor was well aware of her nature, he could still hardly fault her. Before the advent of their Master’s new realm, information regarding the state of the lands surrounding Nazarick had been treated as little more than a tiny part of the threat assessment taken of the regions nearby when they had initially arrived. However, now that Nazarick had come into its ownership, its denizens – Albedo and himself in particular – felt compelled to learn more of its history and peoples to discover the means to most effectively influence and govern them. The Guardian Overseer had taken to the task of overseeing the administration of the newly acquired territory as a natural extension of her role in the Great Tomb of Nazarick.

 

Unlike Nazarick, however, this world was an alien place and Albedo lacked the tools and resources that she needed to perform what she considered her duties. She had neither the information to run the Sorcerous Kingdom to her exacting standards, nor the means to collect that information at a level of detail which would satisfy her. There were no automated systems or status screens that would quickly deliver accurate and comprehensive data to one’s fingertips so, with the expectations of their Master on her shoulders, she could hardly be held accountable for not being able to act with much confidence. It wouldn’t be a stretch to say that, in his immediate role as Momon, he was also in the best position to acquire a feel for the territory and assist her. Unfortunately, to their vexed frustration, they had worked tirelessly to achieve only a simple, incomplete picture regarding the state of the realm since it’s annexation.

 

The cooperation of the remaining nobles in the territory had been their best hope for a smooth transition, but the aristocracy was still reeling from the results of Katze Plains. As their own lands were being directly contested, every fief had answered fully when King Ramposa III called his banners; by the end of the massacre, every fief had suffered catastrophic losses. Those that survived had fled or otherwise disappeared, leaving a confused group of aristocrats that had no previous expectations of inheritance and thus no thorough preparations to assume the management of their titles. While many were still the recipients of a noble’s education, it was simply no substitute for long years of being groomed for the role.

 

Unlike Baroness Zahradnik, whom they had just returned with, it would be fair to say that none of the other nobles were in any condition to manage their lands; the past week was simply insufficient for them to come to terms with their new reality. It was as if the girl had been cut from an entirely different cloth and, going by her account of history, this was actually the case: the resilient nature of her frontier heritage and strong bloodline had allowed her to land on her feet, so to speak – or at least maintain function to a workable degree.

 

As he mused over the unexpected gem that they had discovered, the two doppelgangers reached the doors to the audience chamber. Though nearly five metres high, the thick Ironwood offered little resistance as he made his entrance. He crossed the threshold, walked through the short antechamber and into the main space, where a feminine voice greeted him from the shadows beyond.

 

“Thank you for your hard work, Momon.”

 

Seated behind the desk at the head of the room was the Guardian Overseer. Despite working without rest for weeks, she maintained her pristine smile and spotless appearance: the diaphanous dress of pure white that was her main article of clothing remained spotless and unwrinkled; her black hair and feathered wings well-groomed. The Demon’s amber eyes followed them as they made their way into the chamber. If she had any feelings of stress or fatigue, not a hint of it could be sensed out of the austere image that she projected.

 

The large audience hall had been converted into a council chamber shortly after their acquisition of E-Rantel. Albedo’s desk was placed to the right of the throne on its raised dais – they were still debating over what would be an appropriate replacement for the shabby wooden one that the previous ruler used. Two rows of tables, lined with short benches facing inwards, had been placed on low platforms along the walls. The arrangement gave all who attended a clear view of the large rectangular table that occupied the centre of the room. Tall windows occupied one wall from floor to ceiling, but thick drapes had been drawn tightly over them, completely preventing any light from creeping inside. As with the halls on the way through the Royal Villa, the magical lighting here was kept purposely dim: save for a spotlight that spilled over the centre of the chamber.

 

It appeared that several of the others were already present: Sebas was seated at the table to Albedo's right; seated across the chamber from Sebas were Cocytus and Shalltear, with Entoma behind them. Narberal had taken to the wall behind Sebas, and she had already donned her uniform as a member of the Pleiades. Pandora’s Actor elected to stay in Momon’s armour and moved to tastefully complete the balance in the room, taking a seat on the bench beside Sebas’ own.

 

Demiurge was attending to his projects far to the southwest in the Abelion Hills and only appeared at their meetings occasionally. This also meant that Aura and Mare would be watching over Nazarick while the other guardians were present here. Their Master, Ainz Ooal Gown, had withdrawn from the public eye: shutting himself away for some purpose beyond their understanding.

 

After Pandora’s Actor settled into his seat, Albedo broke the silence.

 

“Report.”

 

“The city and it’s people remain at peace.”

 

“No unexpected developments. At. The. Lake.”

 

“Absolutely nothing new~”

 

A vein popped up on Albedo's temple as the last response was punctuated by a bored yawn. Her slitted, glowing eyes stabbed in the direction of Pandora’s Actor – the annoyance at the lack of anything useful from the others was clearly evident. Folding his gauntleted hands over the table, he leaned back on his seat and looked at each of the assembled members in turn before settling on his presentation.

 

“We completed our sweep of the southwestern region of the Duchy,” his bold voice filled the chamber. “Development of the lands has deteriorated as much as the preliminary reports by Aura suggested. Little remains of the Human expansion indicated by the records we discovered left in the city; it wouldn’t be an exaggeration to say that the lands have become mostly feral beyond the main arteries of trade. Though it’s regrettable that we’re unable to take advantage of past developments, this also means we’ll have a free hand in reshaping the region to suit our Master’s purposes.”

 

Keeping his report simple, he laid out a cue for Albedo’s usual lament, one that she had expressed in one form or another recently.

 

“And how do you propose we do this?” Her fuming was barely contained, “There are barely enough farmers to help direct the cultivation of the lands nearest to the city – if we can even get them to stop cowering and start working. These nobles are similarly useless: I had some tiny expectation of their being able to handle at least minor administrative tasks, but they're all still preoccupied with wailing into each other’s skirts!”

 

Albedo was furious when they first discovered just how perilous the condition of E-Rantel had become after the occupation of the duchy. While the losses from the Battle of Katze Plains were factored in, the state of its inhabitants was beyond their expectations. Before the territory was formally handed over, over half the population had fled – nearly all of this number from the rural areas. Every one of the surviving nobles that was present to witness the one-sided massacre had uprooted themselves as well, leaving a hodgepodge of widows and orphans to inherit the shambles of the aftermath.

 

Most of the citizens of the urban areas had nowhere to go, so they remained to fearfully await their fate. With Momon being dispatched to the rural territories to keep everything from falling apart entirely, the city folk lost their sense of safety and hid themselves away in their homes: only briefly appearing once in a while to secure provisions. Though their fears were unfounded – that there was no grim fate that awaited them at the hands of some sort of Undead abomination – it did not remedy the fact that nothing was happening. E-Rantel served as the duchy capital and a major hub of inland trade, but with no active rural populations to service and commerce suddenly nonexistent, the city’s economy was effectively frozen. Pandora’s Actor had initially played this tug-of-war between keeping the people of the city confident enough to leave their homes and going out into the territories to do the same but, in the end, decided that the city would have to wait since it could not serve its primary function anyways until the territories were returned to normal.

 

Albedo had originally expressed a great amount of anticipation: the prospect of having new lands to administer was a means to advertise her quality to their Master, but it quickly turned into helpless frustration when it was apparent that the duchy had effectively broken down. Still, though, she had figuratively rolled up her sleeves and dug in for the long battle to get things up and running again. This was certainly admirable, but the fact of the matter was that she could not do everything herself.

 

“Ah, on that note, we did find someone of value while we were out there,” Pandora’s Actor slid smoothly into the wake of her exasperation, “there was still one frontier holding that was still populated.”

 

Frowning at the realization that she had been used as a segue, Albedo snatched a large sheet of paper out from between the piles of books and documents on her desk: it was the same map of the duchy that he and Narberal both had, with amendments made to it as new information from their travels became available.

 

“Which territory?” She said as she placed the map before her.

 

“Zahradnik,” he replied. “Guardian of the upper reaches of the Katze River, on the southwestern border with the wilderness.”

 

Albedo’s eyes flashed towards him as though in reprimand for his applying the term Guardian to such a lowly creature. However, Warden’s Vale was the gateway between the Duchy of E-Rantel and the vast wilderness beyond, so the purpose of this noble house was clearly to be the first line of defence against invaders. As her eyes scanned the map and applied the new information to the overall portrait in her mind, he knew that the strategic value of this location would further reinforce the notion of a role that they were all well acquainted with.

 

“So you believe that this Baron will be useful?” She asked.

 

“Baroness, actually. I–”

 

“Another orphaned girl, you mean?” Albedo rolled her eyes as she cut him short, “We have more than enough of those useless sops weeping their days away in the city already.”

 

“On the contrary,” Pandora’s Actor raised a hand to stay her disdain, “she appears to have several years of experience administering her own fief already. If I may say so myself, she is far more competent than her age would suggest – though her worldview appears to be mostly limited to matters pertaining to her immediate duties. In addition, she comes from a strong Adventurer bloodline and possesses one of the so-called Talents that these natives have. Her value is far greater than the average citizen here.”

 

“I’ve had my fill of those so-called Talents,” Albedo sneered. “You were present yourself the last time they were demonstrated, I believe. It had better not be something utterly pointless like that vermin with the ability to divine one’s undergarments.”

 

Their Master was present at the demonstration as well, and Albedo had been mortified. Pandora’s Actor wondered if the man with the ‘Legendary Talent’ was still alive.

 

“I suppose that, in a way, they are somewhat similar…” he mused.

 

There was a sharp expulsion of frozen air from Cocytus, who was sitting across from him, and a snick sound as the pen Albedo had been using to take notes snapped in half.

 

“The girl has what appears to be Truesight,” Pandora’s Actor said lightly.

 

The already quiet room grew quieter still. The air seemed to grow ever colder, and Albedo loomed malevolent over her desk – as if she could use her glare to pin Pandora’s Actor to his seat.

 

Truesight was an ability that existed in Yggdrasil as well. While he was not absolutely certain that the girl’s Talent was exactly the same, what he had seen of it seemed close enough as to not matter. Truesight granted its wielder a powerful visual perception that foiled any and all forms of mystical and supernatural deception arrayed before it. This meant that anything from simple magical illusions to high-tier spells like Perfect Unknowable were powerless against her ability. Attacks that attempted to fool the target into believing that they were being injured, drowned or subjected to various debilitating effects would similarly be rendered useless if what was projected onto them did not match the reality that they saw. The true form of shapeshifters such as Doppelgangers, as well as all other similarly disguised Heteromorphs, were instantly laid bare.

 

The effects of this sense were emulated by the mid-tier spell True Seeing and was part of the repertoire of many of Nazarick’s casters; its utility for the role played by its wielders abundantly clear. As a spell, it could be countered or nullified by magical effects that protected against divination – such as Narberal’s Ring of Non-Detection – but if it was simply a part of one’s natural perception, there was no passive supernatural countermeasure against an ability that effortlessly defeated such countermeasures. Indeed, every floor of Nazarick had at least a handful of patrols that combined Truesight with high natural perception to defeat attempts by invaders to sneak by undetected through a combination of various means.

 

Baroness Zahradnik was much like one of these sentries: though nowhere near as powerful in combat, she could call to attention anything magically concealed or supernaturally altered and potentially create an endless amount of problems.

 

“Pandora’s Actor, you…”

 

“Hm? Ah, of course I was wearing Momon’s full plate armor, so she doesn’t know,” He chuckled. “It’s quite humbling to realize that Ainz-sama took my then-future role into consideration from the outset of this persona.”

 

The tension in the room lessened visibly.

 

“Baroness Zahradnik saw Narberal, though,” he added nonchalantly.

 

All of the heads in the room immediately snapped around to face Narberal. Ever since the young noblewoman had been brought up as a topic of discussion, the battle maid had been trying to inconspicuously blend into the shadowed wall. She glanced back and forth nervously, unsure how to respond.

 

Albedo spoke first, however.

 

“I find it difficult to believe that you of all people do not understand the ramifications of this.”

 

“Indeed,” he nodded gravely. “It is because of who I am that I understand perhaps better than anyone else.”

 

The cavalier tone of Pandora’s Actor became deadly serious as he parried the Guardian Overseer’s accusatory statement. The uncharacteristic shift caused all eyes in the room to once again be riveted onto him.

 

While he had had some interactions with the other members of Nazarick, Pandora’s Actor was by and large only known as the mysterious NPC that defended and managed the Guild Treasury. While they also knew that he possessed the same degree of intellect as Demiurge and Albedo, most did not treat him as seriously due to his relatively carefree and quirky attitude – he was an existence that was merely a fact and not much else. As he emerged from the shadows and received more responsibilities, however, he had come to understand one more thing: that his being the creation of Momonga – Ainz Ooal Gown – subtly influenced the way the others weighed and measured his words and actions.

 

Upon broaching the subject of Baroness Zahradnik, the die was cast and he now brought his considerable abilities to bear. For the first time, the other NPCs understood what it meant when Pandora’s Actor took the stage. With a single sentence hanging in the air, the shadow of his presence emanated intangible tendrils into the silence that latched onto the hearts and minds of his audience and refused to let go. Their postures straightened; tongues stilled. They were pressed into the backs of their chairs by his sheer force of personality and simply watched and waited, holding their breaths; awaiting the next line of his performance.