\chapter{Pandora's Actor}

Pandora’s Actor had thrown himself wholeheartedly into his assignment as liaison to the citizens of the Sorcerous Kingdom. The days and weeks passed, his experiences accumulated and, in his guise as Momon, he had been provided the opportunity to learn a great many things about the people over whom their Master ruled, as well as his fellow denizens of Nazarick who assisted in that rule.

 

The vast majority of the natives that had come under Nazarick’s dominion were Humans: formerly of the Kingdom of Re-Estize. There were also varied populations of nonhumans that lived to the north in the Great Forest of Tob. The relatively small and simple tribes of the Demihumans and scattered Heteromorphs were relatively easy to manage – they had mostly straightforward traditions, respected strength, and as long as that strength led to provision and security, falling in line was a matter of course.

 

The hundreds of thousands of Humans living in the Duchy of E-Rantel, however, were another matter altogether. A complex snarl of politics, culture and commerce came with their civilization and reshaping their society would not be as simple as a decisive conquest and the promise of continued existence. Even as Momon, who was a heroic figure who had won their trust and acclaim, his reassurances and bravado came second to their uncertainty and fear. The task was uniquely challenging to the denizens of Nazarick, whose whole existence previously revolved around maintaining and defending the home of the Supreme Beings – either they would keep unwelcome guests out, or they would die trying.

 

Even with the overwhelming might of their new sovereign made plain to see, the Humans could still not be coaxed out of their fearful state and, with the restrictions their Master had placed on the denizens of Nazarick, unjustified measures against them were not an option. Beyond cleaning up the city and clearing out bandits and other harmful elements from the lands, little progress had been made with the Humans as a whole. Carne Village, which had seen the personal intervention of Ainz Ooal Gown and his servants on multiple occasions was the sole exception, but they were a single point of data where many thousands more were required – not to mention it was not so much a Human village than a Demihuman town, now.

 

If the King will not lead, his nobles will not follow.

 

Baroness Zahradnik’s matter-of-fact statement from their discussion on the way back from the border had struck him in its profound simplicity. She had perhaps handed him a piece of the far greater puzzle that had been confounding the NPCs of Nazarick ever since their arrival in this strange new world.

 

Their Master had gone to great lengths to perform seemingly menial tasks and went about establishing ploys so simple that they made many believe there was some other scheme in play. Rather than ordering a swift and easy conquest of the laughably weak peoples that inhabited the region, every scenario had numerous conditions – a plethora of stipulations which left his servants in a quandary: at times even having them experience the bitter taste of failure. They had been purposely placed in roles that they were ill-equipped to face and Ainz Ooal Gown only spoke at length about their actions and experiences after the fact. Even in the face of what the NPCs themselves considered unacceptable, he ultimately offered forgiveness and personally shouldered all of the responsibility.

 

The NPCs had been left in a mentally tentative state after each episode, their pride often kicked out from under them; perception and expectation overturned in equal measure. But...had Ainz Ooal Gown actually been acting to lead them? Was everything up to this point a series of exercises devised by their Master to prepare them for the challenges ahead?

 

And, if this was true, was their lack of progress and resulting inaction as his subordinates essentially the same as vassals failing to follow after their King?

 

Pandora’s Actor considered the discussion that had accompanied the young noblewoman’s statement; it did indeed basically describe their current situation. As the noble houses of Re-Estize simply continued to function independently without recognizable guidance from King Ramposa III, the denizens of Nazarick within the Sorcerous Kingdom even now continued their regular modes of operation. Undead sentinels stood silent vigil at every street corner; those assigned to maintenance kept the city orderly and clean. Even Albedo, eminently qualified to serve as the central executive of the realm, sat impotently behind a desk waiting for work to do; for information to analyze and act upon. They were all simply holding to their respective duties, waiting for invaders to defend against or preparing for future problems that they were better suited to deal with. It was as if they had all collectively considered the Sorcerous Kingdom to be a much larger version of Nazarick, but clearly this approach was not working.

 

If everything Ainz Ooal Gown had done so far pointed in the direction that he wished for his servants to go, then they were all unknowingly failing him by not taking his example and lessons to heart. If all his carefully laid efforts went to waste, how would he react? Would he keep trying, or would he simply give up and abandon them like the other Supreme Beings?

 

Pandora’s Actor’s heart quaked at the mere shadow of that thought.

 

In the end, he concluded that the situation had become untenable and he would need to set things into motion to prevent that most dreaded of ends. The fact that the pieces that were required to enact his plan had come together all at once made him feel that his role was part of some unknowable grand design; his Creator once again its masterful architect. With this reassuring thought, he leaned back into his chair, crossing his arms while he resumed speaking.

 

“I had the opportunity to speak at length with the young lady about a great many matters before our return,” he said, “and I believe we stand to gain by enlisting her cooperation.”

 

Contrary to the dramatic stand he had taken just before, his voice returned to its carefully modulated tone. With the invisible pressure released from the room, Albedo quickly recovered and immediately responded.

 

“How can you be so sure of this?” Her voice was laced with disbelief, “A casual afternoon chat on the road is hardly–”

 

She immediately swallowed her words as Pandora’s Actor raised his left hand, tapping a finger against his temple.

 

“Of course I can be sure,” he replied. “I am a Doppelganger, after all – the greatest of my kind in Nazarick. The Baroness had no means to resist my power to read her thoughts as she spoke…never mind that, she didn’t even realize that her mind was being read; her responses carefully measured.”

 

Seeing the Guardian Overseer’s eyes narrow as she sought to find a crack in his defences, he pressed his attack.

 

“It has been nearly a week since we were fully entrusted with the stewardship of our Master’s new realm. A week with no progress towards restoring nominal operations in this territory. You should know more than any of us what is ultimately required to have the citizens of this nation take the first steps towards their new lives as subjects of the Sorcerous Kingdom. You bemoan the dysfunctional nature of its aristocracy – who serve as its administrative machinery beyond the city walls – and how they are useless in the wake of their recent losses.

 

I have identified an asset in the form of this individual that can be employed to help begin the process that has eluded us thus far, yet you continue to wallow in your embittered frustrations. Demiurge has stated that the ultimate goal of our Master is World Domination, and we all know that we have taken but a tiny first step towards the future our Master has envisioned. For the time being, Ainz-sama has minimized his interactions with us, keeping mostly to himself…but sooner or later, he will take action again.

 

When that time comes, what accomplishments will we have to display to him in the span he has graciously allotted to us? When he proceeds onwards and reveals to us the next stage of his plans, what will your response be?

 

‘Ainz-sama, wait! Please give us more time!’?”

 

The last, plaintive line was delivered in Albedo’s own voice, and she visibly recoiled. Her eyes widened, and her fingers unconsciously moved to press against her lips – as if she could prevent more shameful words from leaving a mouth that was not even her own. The other NPCs turned their attention to the Guardian Overseer with worried expressions; without exception, their greatest fear was to fail in their service to the last of the Supreme Beings that remained with them. This, in addition to the relentless advance by Pandora’s Actor, had mercilessly driven her into a corner.

 

With her pride on the line and little room to maneuver, she turned to the only avenue that would enact the ends that she sought.

 

“Very well, then,” she said. “Let us decide the fate of Baroness Zahradnik.”

 

With the subject framed in the manner that it was by Pandora’s Actor, Albedo could not arbitrarily decide to remove what she perceived as an unnecessary complication without losing face in front of the others. Instead, she decided to leverage the opinions of those seated around the audience chamber. In short, it had become a vote.

 

Hidden behind the dark metal visor, the corners of Momon’s mouth turned upwards. In truth, the commands of the Guardian Overseer could not normally be opposed by the denizens of Nazarick – she had been created to hold authority over them, after all – but by exploiting her pride, he had achieved his objective.

 

Sebas was the first to speak, rising to present his views.

 

“I believe there is much to be gained by working with the citizens of this nation,” he said in a stiff, formal voice. “In my own travels, I have seen that these Humans can range widely in character…but to preemptively remove one without investigating their potential would be to squander the fruits of Ainz-sama’s efforts.”

 

His response was to be expected, given his benevolent nature. With nothing more to say, he once again took his seat.

 

“These Humans have bowed, yet they still do not serve. No leniency should be granted to threats from their kind, no matter how insignificant.”

 

Cocytus’ stern response once again tied the vote. In his own rule, over the region surrounding the Great Lake, he had been forbidden from using fear as a motivator, but it was still a rather straightforward power relationship – his view on the matter was equally so.

 

All eyes turned to the final Guardian seated in the hall.

 

“It should be fine to see if she proves useful,” Shalltear’s voice chimed lightly through the chamber, “should it not, de-arinsuka?”

 

The triumphant smile that was slowly forming on Albedo’s face vanished. She had obviously expected a ruthless response from the most powerful of the Floor Guardians. Seeing her reaction, Shalltear Bloodfallen quickly continued to speak.

 

“Securing the entire area and its borders barely took our forces a day,” she reasoned. “Beyond that, we’ve basically just been sitting around, arinsu. We should have something to show for our time when Ainz-sama moves again. If this Human is a way to do this, then we should use her.”

 

“A Human with Truesight is too great of a liability,” Albedo said. “She would pose a risk on so many levels that I don’t even want to consider what she could inadvertently unravel with her ability.”

 

“Then I shall take personal responsibility for this child,” Shalltear replied. “If she causes any major problems, I can just immediately dispose of her.”

 

“You?” Albedo responded suspiciously as her eyes narrowed, clearly skeptical of the Vampire’s uncharacteristic interest.

 

“Yes,” Shalltear confirmed. “Besides, Ainz-sama may still be interested in the unique and strange abilities used by the people of this world. If she is of a strong bloodline, she may be able to perform those ‘Martial Arts’ as well at some point, yes? I believe I was tasked to collect these sorts.”

 

“...shame.” Albedo’s low voice was barely audible.

 

“Hm?”

 

“Have you no shame?” The Demon’s words rose in volume, until they lashed out in accusation, “You, who has not produced any of your own results. Desperately clinging to past duties in some reprehensible, selfish desire to absolve yourself of your own failure!”

 

The NPCs around the chamber collectively flinched. Though the event in question had occurred many months ago, its fearful spectre still lurked in the dark corners of each one of their thoughts. Shalltear’s fatal blunder had been dealt with personally by Ainz Ooal Gown. Though he had absolved her of guilt and personally held himself accountable, Albedo’s assault had shaken even the most stalwart of those in the room. The word failure struck like the sound of a gavel landing before a soul condemned.

 

While the others shifted uncomfortably in their seats, Shalltear’s entire profile crumbled – her veil of relaxed composure falling away all at once. Cringing away from the Guardian Overseer’s reprimand, her face became tearful, cheeks flushed; mouth working silently in shock. Her slim, delicate hands rose; making motions as if to touch her face or cradle her head, but she seemed so disgusted with herself that she could not bear to do so.

 

“I…” her voice choked as she struggled to find the words to defend herself. “I’m–”

 

Pandora’s Actor held out his palms in a placating gesture as he spoke in a calm voice to intercede on behalf of the Guardian who was wrestling with her own shame and self-loathing.

 

“Mah – don’t be like this, Albedo,” he said in mollifying tones. “Frustrations have understandably mounted over the lack of progress with the Humans, but again you have my reassurances that Baroness Zahradnik will be of tangible benefit in at least a few areas. She has a character that appears to value duty and order above all else: she will carry out her noble obligations to both land and liege, regardless of who it may be. If we place her safely under Shalltear’s authority, I believe the young noblewoman will be able to serve faithfully even as she adjusts to her new reality.”

 

He had expectations for additional fruit to be borne out of this arrangement, but kept those thoughts to himself out of fear of altering the momentum of the discussion. There would be the chance to nurture future outcomes at a later point in time; for now he needed to ensure that the current resolution made it out of the door of the council chamber. He messaged Yuri Alpha – whom he had preemptively stationed to be nearby to the young noblewoman after their arrival – to retrieve Baroness Zahradnik.

 

“Very well then,” Albedo spoke once again; her voice had regained its calm, imperious tone. “If that is what you wish for, then we’ll see just how far you can go with this Human.”

 

Turning towards Shalltear, who was still drying her tears, the Guardian Overseer spoke down from the raised dais.

 

“Shalltear Bloodfallen,” she declared, “responsibility for Baroness Zahradnik lies solely with you. Any assistance she requires: be it in regards to resources, labour or advice in her civil duties, rests squarely upon your shoulders. Similarly, any problems that arise from your new charge will reflect equally on you. Pray that she does nothing to bring shame to the name of the Supreme One.”

 

The Guardian Overseer had probably chosen to wash her hands clean of the entire affair, preferring to withdraw from the discussion rather than pursue the matter and fall into whatever other traps Pandora’s Actor had laid out in advance. Shalltear, cast adrift with her new acquisition, sat deep in thought while biting her thumb. One could almost imagine the steam rising off of her head as she attempted to figure out what to do with the young noblewoman she had yet to even meet.

 

“We’ve wasted enough time on this,” Albedo had returned entirely to the pristine, unruffled appearance from the beginning of the meeting, “let us proceed on to other matters.”