\chapter{Ludmila Zahradnik}

Ludmila stood alone on the cobblestones after the doors of the Royal Villa closed behind Momon. The violent lesson that had accompanied his words left an unforgettable impression, but she still pondered the rest of what was said. She recalled Nabe’s inhuman form and thought that this ‘Sorcerer King’ perhaps ruled over many beings like her, or those even more bizarre. With this in mind, she could not help but peer about the empty district…but it seemed to be just that: empty.

 

Momon had informed her that she had a Talent – Truesight? – and thinking back on the day’s events, she supposed that it must be true. Beyond being able to see Nabe’s true appearance, however, she had no idea what exactly it did. Her entire life had been spent in the duchy’s lands surrounded by other Humans so there was nothing really out of the ordinary to notice, not even during her previous visits to E-Rantel. The world around her looked much the same as always. She had no recollection of anyone in her family having any sort of Talent, and her studies were similarly lacking when it came to the many mysteries of the world that had no impact on her generally mundane life.

 

She decided that there was no point in standing around agonizing over it. Uncertain about when she would be summoned to present herself before the Royal Court, Ludmila started making her way towards a certain area within the guest houses that occupied half of the central district. Arranged in a rough circuit lining the innermost wall of the city, the luxurious buildings were meant to offer hospitality to visiting aristocrats and dignitaries, as well as to provide permanent residences for the duchy’s nobles that preferred to conduct their affairs out of E-Rantel.

 

Ludmila’s family stayed in this part of the city during their usual winter visit. It was her lord father’s single major expenditure for the year: used both as a window to show his children the standards that wealthier nobles enjoyed, and a way to provide them with the most exposure to the other members of nobility to make connections with others in their limited time away from the border. The latter part was something that none of her family ever seemed to succeed in.

 

She easily oriented herself once she identified a few familiar landmarks. The street that encircled the entire district was normally quiet unless someone was hosting their guests outdoors, but the eerie atmosphere that hung in the air was decidedly unnatural. There were no servants going about their tasks, no sign of officials or dignitaries travelling to and fro on business. The lanes and buildings had been scoured clean; yards and gardens left perfectly groomed. The immaculate, polished appearance of her surroundings combined with the deathly silence gave everything a sterile feeling: much like that of a well-kept cemetery.

 

After following the street over its circular route for several minutes, she reached the building that was her destination: a large, single-story structure that served as a sort of clubhouse for both the district’s residents and it’s visitors. She thought that she would be able to find some of the staff servicing the district here and have them direct her to available accommodations. The stone path leading through the yard to the building was unattended, so she had to juggle her bags around in order to open the ornately fashioned entrance. The door whispered open on oiled hinges, and Ludmila slipped in on one side. Thankfully, the inner entrance of the landing was propped open, so she did not need to awkwardly maneuver herself in between to open the second set of doors. She stepped forward over onto the lush, crimson carpet to the front desk, setting her bags on the floor as she waited for the reception staff.

 

The motion in the foyer caused several of those inside to turn in her direction, which then prompted others to also face her way as well. Ludmila scanned the people that occupied the lounge just inside the clubhouse; she recognized many as nobles or members of noble families that held titles in the duchy.

 

As she looked over the group to identify each in turn, a familiar woman’s voice spoke from behind her.

 

“...Ludmila?”

 

It was tentative at first, but when Ludmila turned around to face the person who called her out to her, it overflowed with relieved certainty.

 

“Ludmila, it is you!”

 

A young woman close to her own age had come from the hallway leading to the more private areas of the building. She stepped forward excitedly, initially holding up her long cobalt skirts to run to her, until she remembered herself partway and assumed a more dignified pace.

 

“It has been a while, Clara.”

 

Ludmila smiled politely and made a warm greeting in return. Seeing the familiar face fanned the embers of her own hopes.

 

Clara was the daughter of Baron Corelyn, her name styled in the manner of the western nobility. House Corelyn administered the only other port on the Katze River, which lay several hours down the rise from where E-Rantel overlooked the surrounding lands. As trading partners, House Corelyn maintained a close relationship with House Zahradnik – Clara was betrothed to Ludmila’s eldest brother. She had a cheerful disposition which shone as brightly as the waves of her golden hair, and he had received the engagement happily. However, Ludmila saw no sign of her brother amongst the other nobles in the lounge.

 

“Lord Zahradnik and your brothers, are they well?” Clara took Ludmila’s hands in hers as she asked after her family.

 

Ludmila’s smile froze at the question. Because of Clara’s relationship to her brother she was about to ask the very same thing, but Clara’s question left her own hanging unspoken. Her close friend did not miss her reaction, and her warm hands grew as cold as Ludmila’s own.

 

“...but after the chaos,” Clara’s voice shook, “your ship was gone from the harbour – we thought that surely this meant they had returned home.”

 

Ludmila shook her head.

 

“The ship returned,” she replied, “but with only a handful of men. My lord father and my brothers were not amongst them. A part of why I came here was to see if I could find anyone.”

 

The exclusive location made it the natural place for nobles to gather in large groups, as was the case before her. She had hopes that even if her family wasn’t here, there would at least be someone with information on their whereabouts…or knew their fate. Encountering a familiar face had immediately raised her hopes, but they were dashed as surely as Clara's crestfallen expression. The almond eyes that she always remembered sparkling with life welled with tears, and Ludmila had to look away to avoid following suit.

 

There were maids spaced out evenly in the room, presumably to attend to the needs of their guests, but none came forward to the aid of the young noblewoman who had begun quietly sobbing. If anything, they seemed blissfully unaware of their responsibilities. The others in the lounge stood about murmuring to one another while observing the exchange – sound carried quite clearly by design in the open spaces of the clubhouse – they were probably digesting the new information. With some consternation, Ludmila searched for a place where she could take Clara that wouldn’t disturb the other guests.

 

A tired sigh turned her attention towards the lounge again as a figure rose from one of the chairs.

 

“Really, have you all forgotten how to conduct yourselves?”

 

A stern voice seemed to push aside the conversation from the younger nobles around her. She was a severe looking woman with steel grey hair that hung over her shoulder in a large braid, dressed in a conservative russet gown with little in the way of highlights or flourishes. Radiating the air of a noble matron who brooked little nonsense, Ludmila recognized her as Dowager Countess Vilette Jezne. Her deceased husband’s title had passed on to her son who had long since married, but she was still active and influential amongst the ladies of the ducal court.

 

As she made her way towards the pair in the foyer from the lounge, she continued in a reprimand that seemed to be addressing everyone within earshot.

 

“With everything that’s happened,” she said, “the last thing we need is you lot continuing to mope around like a bunch of invalids. Just how long must this go on for?”

 

While she spoke, the sharp clicking of heels from a different hallway could be heard that drew everyone’s attention away from her.

 

Another maid had emerged from the corridor that Clara had appeared from. She was quite tall – a bit taller than Ludmila – with a measured stride exuding confidence and grace. Pale, almost translucent skin emphasized a picturesque beauty that made her wonder if this woman was not actually some impossibly fine statue carved from the purest marble. The generous curves of her figure amply filled out the lines of her outfit, but unlike many young women who would surely flaunt such an advantage, she held a strictly formal posture while her immaculate uniform retained its crisp and conservative appearance. Light from the entryway gave a rich sheen to her jet black hair, which was made up into a tall bun. The glow of the evening glimmered off of the black frames of her spectacles as she stepped forward.

 

As the nobles in the room stood entranced by the beautiful maid, she walked up to the pair at the front desk and lightly placed her hand around Clara’s shoulder.

 

“Baroness Corelyn, you must stay strong,” the maid gently admonished the sniffling noblewoman. “Come, let’s find you a place to rest.”

 

She slowly led Clara away from the gaze of the onlookers in the lounge, speaking in soothing tones. Ludmila suddenly realized that Clara had also been addressed by her father’s title – her father and brothers must have gone missing as well.

 

Up until that point, Ludmila thought the maid bore some sort of similarity to the guise of Nabe of Darkness, but her care for the distraught Lady Corelyn gave her a much warmer impression – much like what Ludmila imagined an older sister might feel. She was so captivating that even the previously unresponsive maids that were supposed to be attending the room were paying close attention to her.

 

“Hmph,” a grunt from the side caused Ludmila to start. “At least someone has their head on straight.”

 

Vilette Jezne spoke as the maid slowly led Baroness Corelyn out of the building. She had walked the rest of the way from the lounge area while the scene between Clara and the maid had drawn everyone else’s attention – Ludmila suspected that the old noblewoman had purposely moved close before speaking to startle her.

 

“I always thought that you were one of the more grounded kids in the batch,” the aged woman told her, “but it seems like you’re just about as helpless as the rest.”

 

Though Ludmila did not particularly enjoy being the target of the Dowager Countess’ criticisms, she felt slightly relieved that the old woman seemed none the worse for wear. The irritable matron was actually a driving force amongst the noblewomen of the duchy, often haranguing even married ladies over their behaviour and actions, or lack thereof. Given the situation that they had now all found themselves in, having Vilette Jezne around was a greatly reassuring thing.

 

“And what about you, hm?” Vilette Jezne went on, “How long are you going to stand in the doorway like some sort of lost page?”

 

Her voice shot over Ludmila's shoulder, stabbing into its unsuspecting target. Ludmila turned at the sound of a boy gasping as the words found their mark.

 

He was perhaps twelve years of age…no, maybe not even that. Dressed in the finery of a noble that hung loosely in several places, it seemed that he still had yet to fully grow into his clothing. By his general appearance and lack of visible attendants, he had neither the care nor attention of any servants. What looked to be a failed attempt at taming his sandy hair topped off the unkempt, rascally image. In a more normal situation, his insecure appearance and nervous manner might have tickled some urge to tease or protect him by a gaggle of older girls, but for the time being Ludmila snatched his arm and led him to the lounge where the other nobles awaited before the ornery old lady could lash out at him again.

 

Several long couches, as well as an assortment of plush chairs, were loosely organized in a circle around the centre of the open space. A huge, midnight blue rug lay over most of the floor, cushioning the steps of those who traversed the room. Standing in groups between three or four people, the nobles in attendance had divided themselves up in a conspicuous manner that Ludmila could not quite put her finger on. Before she could ponder the arrangement for long, Vilette Jezne had made her way to the centre of the room, clapping her hands to gain everyone’s attention.

 

“This is as many as we’re bound to get, I suppose.” She began after enough heads had turned to face her, “It is high time we get our affairs in order.”