\chapter{Ludmila Zahradnik}

Ludmila did not want to get up.

 

Huddled in the small nest of blankets that she had gathered about herself before drifting off to sleep the previous evening, she lay on the floor propped up against a satchel half-filled with winter provisions. Only her head poked out of the covers; her eyes were still closed, but an annoyed look crossed her face. The ravens gathering outside had, for some time, been rudely informing her of the coming dawn: cawing between themselves and hopping all over the thin roof of the manor hall, creating a clamour that she could not doze through. The logs in the fireplace before her had burned away during the night and the stone floor no longer radiated any warmth.

 

What day was it? How long was it since she had been left alone in Warden’s Vale? Her memory sharpened as wakefulness asserted itself.

 

After returning to the village, Ludmila had scrounged around to both prepare for the coming days and distract herself from her worries, looking for anything useful that might help with her lonely vigil. The warehouse still contained a fair number of crates and unpacked goods, left behind on account of being too heavy or unwieldy to transport without a wagon. The shelves were lined with valuable timber and extra staples, mostly. She found an old militia uniform, meant for a man much larger than herself, stuffed in a corner beside an old spear that she had also carried into the manor.

 

Without administrative matters to handle or outstanding issues to address, life had greyed out into a mostly uninteresting blur of daily routines. She would perform a few minor chores, then occasionally make her rounds with spear in hand. She had plenty of time to practice with the weapon or spend her free time rereading her small collection of old books, but life had in general become insufferably dreary.

 

Though spring had already officially begun in Re-Estize, the weather in the southern highlands had taken a turn for the worse. The air cooled sharply and, though it did not snow, she spent most of her days bundled up at her desk to stay warm and conserve her energy, looking out to the north from the manor window. Throughout her idle watchfulness, the ship never returned, nor did anyone appear on the sandy path that followed the river.

 

She had also become keenly aware of just how much she hated being alone. For all of her life, there had always been other people around – whether they be her family or just the vague presence of the neighboring villagers – and she never realized the lack of these things would have such a telling effect on her. It had gotten to the point where she even thought of the wildlife that came to visit the now curiously inactive Human settlement as welcome guests to help stave off her loneliness.

 

As the birds outside continued their play over and around the manor, Ludmila shifted to look towards the heavily curtained window on the other side of the hall and instantly regretted her action. A tendril of frigid morning air slipped into the blankets and licked at her calves. She fished around with her toes in an attempt to close the breach in her defences, but it only caused more cold air to flow in. With her precious warmth being rapidly stolen away, she gave up and jumped out from the blanket with an irritated shout.

 

Not two steps into making her way towards the militia outfit airing out over a chair nearby, gooseflesh was raised all over her body. The thin linen shift that she was accustomed to sleeping in offered little protection against the freezing spring morning. Usually, one of the early risers in the family would have the fire going by the time she left her bed. Sophia had come to do this while her family was away. Despite several mornings in a row experiencing this, it was difficult to break her long standing habits.

 

Ludmila put on the oversized militia gambeson to insulate against the cold, her fingers shaking with the chill as they quickly worked the straps of the coat. As it was tailored for a taller individual, it did not fit very well. She had to fold the sleeves to free her hands and the hem of the suit hung past her knees. Even if she could find a belt for it, the loops at its waist hung part way down her thighs. She was half frozen by the time she was done, and the cold coarse fabric seemed to enhance her misery as it brushed over her skin.

 

The desire for warmth drove her forward. Returning to the fireplace and taking a pair of tongs hanging from a peg on the wall nearby, she sifted through the ashes, searching the charred remains until she located a dimly glowing ember. After clearing debris away from the space under the pot hanging over the ashes, she placed it on the floor of the fireplace, then grabbed a handful of shavings from the tinderbox. After placing the shavings and several split logs over the ember, she coaxed the fire back to life. It sparked and caught on the shavings, eagerly spreading to the fuel that she had offered.

 

Satisfied that the new flames would not die out, she worked the iron ladle out of the pot, using it to break up the layer of ice and oil that had formed over the surface of the stew. As she was loath to go outside and draw water in the freezing weather, all that was left was to wait for breakfast. After neatly folding the blankets strewn the floor and putting them away, she sat down to bask in the warmth of the fire. Hugging her knees, her eyes unfocused as she brooded in the shadows of the manor.

 

It was only after she had settled down again that she realized that it was unnaturally quiet. The ravens had gone silent, leaving only the chill winds and the distant sounds of the river in the air if one strained to hear. The idea that someone might be approaching the village caused her to jump back to her feet. Making her way to the window, she drew the curtain aside cautiously to take a look around.

 

Her eyes were instantly drawn to the base of the hill, where a dark figure strode out of the morning mist. The spark of hope that came to life within her faded as she made out his appearance – the man was heavily armed and armoured with a full helm that prevented her from seeing his face: he was clearly not anyone that she was familiar with. He slowed his pace and raised his head to face towards her. She quickly backed away from the window, and the curtains fell as she withdrew.

 

In a rush to prepare, she headed to where the remainder of the militia outfit lay draped over the chair. She hopped up and down as she pulled on the long woolen pants, tightening the cord at her waist as she moved to the entrance of the house. The metal-shod boots that she had found with the uniform were far too large for her, so she used her own. After pulling them on and tying the outfit’s leather cap to her head, she stuffed the overly long legs of the pants into her boots to keep them from tripping her up. A pair of hardened leather gloves came last – they were stiff and uncomfortable, but it was better than nothing.

 

Ludmila was dimly aware of how ridiculous she must have looked, but didn’t spare any thought for it. She unbolted the door and pulled it open, reaching out for the spear propped up against the wall near the doorframe. It was two-and-a-half metres in length, and she needed to tilt the polearm forward to get it through the door. As she did so, the base of the spear bumped into something behind her, and the impact jarred it out of her gloved grip. The weapon fell with a noisome clatter. With an exasperated breath, she leaned forward to pick it back up again and headed out the door.

 

The manor was built on the broad central terrace that generations long past had cut into the hill. It was too high to simply jump down from, so she followed the long and winding village path down to reach the man standing outside the entrance of the settlement. On the way down, she noticed that a second figure had appeared and quickened her pace, not knowing how many more would come behind them. The militia armour weighed heavily over her shoulders, jostling her awkwardly as she made her way down and she felt slightly winded as she finally made it to the base of the hill to approach the strangers.

 

As Ludmila came closer, anxiety washed over her as she saw what she was up against as he loomed ever larger. Sheathed in jet-black plate armour, a man stood as tall as the haft of the spear that she carried. The two massive blades crossed over his shoulders could not rightly be called greatswords – they were nearly as wide and tall as she was. Their weight must have been such that when swung, her own weapon would splinter from the impact if she tried to deflect the blow. She was at a loss on how to confront him; there was probably nothing she could do to resist if he had come as an adversary. The man seemed to be sizing her up in return, but she was unable to discern his intentions through the closed visor of his helmet.

 

Ludmila turned her gaze from the imposing armoured figure, scanning around for the second person she had noticed on the way down. Her heart leapt into her throat when she found her, and the spear came up in her panic.

 

The woman had no face – or rather, the woman had an empty face.

 

Over the shorter, feminine figure in traveller’s garb was a smooth, pale head devoid of features: save for a pair of empty eyes and a round, lipless mouth. The woman emitted an aura of hostility that made Ludmila brace herself for an imminent attack.

 

To the side, she heard a man’s voice, but she couldn’t turn her attention away from the woman with the empty face. After a moment she noticed the ghostly image of a second face superimposed over the empty one: its sharp, exotic features scowling at her: expressing what the other could not. Ludmila blinked several times, yet her vision did not change. Though what appeared before her seemed alien and unfamiliar, she somehow instinctively knew that the pale, featureless face was real and the sharp human one was some other appearance. She continued to maintain her stance, spearhead leveled at the woman not three metres away from her. The woman did not make any movement; she only directed her vehement glare against her in return.

 

The man’s voice sounded once again to their side. Clearing his throat, he raised his voice to break their silent standoff.

 

“Nabe, ensure the area is secure,” he said. “Report back if you find anything.”

 

With a curt affirmative and a softly spoken word, she slowly rose into the air. Ludmila tracked her ascent until Nabe suddenly shot over her shoulder. By the time Ludmila pivoted around and located her again, she was flying past the village and rounding the hill.

 

The deep voice of the armoured man prompted Ludmila to turn her attention back to him.

 

“Now then,” he said. “Allow me to introduce myself once again.”

 

Up to this point he had his hand raised to his helmet, posing as if he could cradle his chin thoughtfully through the black metal. The man now straightened his posture, pressing gauntleted fingers to his chest.

 

“My name is Momon,” his words were half declaration, half bold introduction. “My companion that just flew off to inspect the surrounding area was Nabe. Together, we are the Adamantite Adventurer team Darkness. Have you perhaps heard of us?”

 

Ludmila mulled over his statement as he spoke. This far out on the frontier, little beyond official business of the realm ever arrived.

 

As far as she knew, of the Adamantite adventurers of the Kingdom of Re-Estize, there was the acclaimed Red Drop and Blue Rose – a recent entry composed solely of women. Both of these Adamantite teams were based to the northwest, far beyond the Duchy of E-Rantel. Blue Rose had made the Royal Capital their home, while Red Drop worked even further afield between the Kingdom of Re-Estize and the Argland Confederation.

 

She had never heard of Darkness, but she supposed that it didn’t matter. As he introduced himself, Momon used his thumb to hold out a small tag made of some dark metal which clasped a chain that hung over his armour. Though she had never seen the precious metal herself, she thought it must be proof of his identity. Adventurers lived and died by their reputations, so she couldn’t imagine one pretending to be something that they were not.

 

Ludmila silently shook her head in reply to his question.

 

“Is that so…”

 

Releasing the tag, he resumed speaking.

 

“At any rate, we’ve been sent by the administration in E-Rantel to deliver a missive to those holding titles within its borders,” Momon gestured in a somewhat exaggerated manner as he spoke; he seemed to be accustomed to retaining the attention of an audience. “The records in the capital have Baron Zahradnik registered as the lord of this holding. Is it possible for you to lead us to him?”

 

Ludmila had not yet found an answer to his next question herself, so silence hung in the air for a short while before she fashioned her response.

 

“Baron Zahradnik has not yet returned from E-Rantel,” she replied softly and swallowed after she began. “Only a handful of men came home, around three weeks ago. Dozens went with him when the King called for his banners. We…I have not seen or heard anything since.”

 

Momon’s posture relaxed somewhat as he received her answer, his voice softening into a more comforting tone.

 

“...I see. My condolences if you have lost anyone in the recent conflict. Did the Baron leave any sons to inherit after him?”

 

There was a rush of heat as she bristled over the stranger’s immediate conclusion over her father’s fate, but Ludmila kept her voice measured and she shook her head again.

 

“My brothers did not return either,” she said.

 

“Your brothers...?”

 

“Baron Zahradnik is my lord father.”

 

Following her reply, Momon straightened and once again brought a gauntleted hand to his chin.

 

“By the succession laws of Re-Estize, that would make you Baroness, would it not?”

 

Ludmila knew this to be the case, but the thought only stoked the bitter feelings growing in her heart. As if sensing that the conversation had taken a sour turn, Momon went straight to the point.

 

“In that case, the order has been issued: all landed nobles of the duchy are to present themselves at E-Rantel to pay their respects to their new sovereign, the Sorcerer King. There are several administrative tasks to perform following this, but I’ll leave those details to the officials in the capital. Please prepare for the journey: we should depart by the afternoon.”

 

Sorcerer King? Not the Emperor?

 

The unfamiliar title raised several questions in Ludmila’s mind, but the Adventurer seemed to have nothing further to say. Having received the order, Ludmila lifted her spear and turned back towards the settlement; an intangible sense of duty nudging at her to comply. However, as she stepped forward to ascend the hill back to her home, Momon spoke once again.

 

“By the way, Baroness Zahradnik,” his voice sounded clearly from behind her, “you seem to have taken issue with my companion. Is there something I should know?”

 

The unexpected question froze Ludmila in her tracks. She wondered how she should respond. Did he know? Was it a secret? Momon spoke of her as a companion…perhaps they were lovers. Recalling the woman’s unsettling visage, she shook that thought quickly from her mind. Maybe this ‘Nabe’ was deceiving him? It was impossible for Ludmila to tell from their brief encounter.

 

Making up her mind, she drew a deep breath and released it. She turned back around to face the man in black armour.

 

“Your companion – Nabe. She was dressed in traveler’s garb, but her head…it was as pale and smooth as a goose’s egg. She had no hair, no nose: only a pair of empty eyes and a round, lipless mouth.”

 

Ludmila watched Momon carefully as she spoke, but she could sense no reaction to her description.

 

In the stillness that followed, Ludmila thought she could feel Momon’s gaze through the visor of his helm. Leather creaked as her hands tightened their grip on her spear with his silence stretching on. The Adamantite Adventurer’s massive figure loomed over her like some dark spectre; it was as if she was being judged, and her execution by one of the ludicrously huge blades on Momon’s back was imminent.

 

Then, all at once, the feeling subsided.

 

“Is that so…” Momon’s voice trailed off quietly as he turned away from her, looking up towards the sombre skies.