\chapter{Ludmila Zahradnik}
Having returned to the manor to prepare for the journey to E-Rantel, Ludmila took an inventory of her surroundings. The activity of the past few days had cleared away most of the loose odds and ends in her family’s home as she neatly organized what little that remained in her boredom. The stew lazily simmering over the cooking fire filled the hall with its appetizing aroma, but now there was no time to sit down to savour a meal.

 

She looked over the row of baggage lined against the wall which had been prepared for the flight to the Theocracy. Though they had been packed for an exodus, the contents were in truth not much different than what they would have brought with them for their trip to E-Rantel for the winter markets. They all contained an adult’s share of food and sundries, as well as a few sets of clothing and a handful of personal articles. Looking down at their contents, divided up over the floor, she decided to take some spare changes of clothing for her father and brothers just in case she found them in the city. She quickly consolidated everything into two larger packs that she could carry, leaving the excess supplies meant for weeks of travel. Throwing one over her shoulder and carrying the other in her arms, Ludmila waddled back out the door.

 

As she carefully picked her way back down through the trail to the bottom of the hill, her mind turned to the other cargo that would usually be brought with them on a trip to the city. Taxes were delivered as a lump sum during her family’s winter visit; the village warehouse was still one-thirds full with the year’s production, out of which the majority of their taxes could be drawn out of the proceeds from sales to the wholesalers in the city. Unfortunately, the bulky remainder of the village’s goods was something that required the efforts of many to bring down to the pier for delivery. Ludmila certainly could not carry it all down on her own.

 

She wondered if she could convince Momon to help. His language suggested he wanted to be on his way as soon as possible, so his assistance as a powerful Adventurer would surely speed things along. Upon arriving back at the entrance of the settlement, she found that Nabe had returned from her flight.

 

The female adventurer still had her two appearances; the Human face had an impatient expression on it. The pair looked towards her as she approached, eyeing the baggage that she had overburdened herself with. She carefully laid her things down on the driest patch of gravel she could find, and Momon spoke.

 

“The journey should not be a long one…but just how much did you plan on bringing with you?”

 

Ludmila bit her lip, trying to devise some sort of acceptable reasoning that she could enlist his help with. Momon, it would seem, had read the situation before she could even broach the subject.

 

“My personal belongings are only one of these bags,” she explained. “The rest are products from the barony and some extra things just in case. During the winter, we sell them in the city; the proceeds go towards paying our taxes and purchasing supplies that cannot be acquired here. There is not as much this year because of what happened, but it will all go to waste if it is not delivered…”

 

Her voice trailed off uncomfortably. She had been piecing her case together in her head as she made her way down the hill, but his sudden prompting had caused most of it to spill out in what felt like an unconvincing babble. Nabe’s eyebrows drew together and the impatient expression transformed into an inconvenienced one.

 

Subjected to her glower, Ludmila quickly picked up where she had trailed off.

 

“Again, there isn’t much!” She continued hurriedly and gestured towards the river, “I’m not sure what you’ve arrived in, but even a smaller ship should be able to carry it all.”

 

The two adventurers exchanged looks before turning their heads back to stare at her blankly. It was only when Ludmila turned her head towards the shore that she realized what the problem was. Her arm was extended towards the jetty of piled stone that extended a short distance into the river. The makeshift harbour it created was where travellers would moor their boats or bring them ashore if they were small enough…but it appeared that her visitors had not used one in the first place. The morning’s mist had been obscuring the pier, so she had mistakenly assumed that they had come by way of the river.

 

After seeing this, she looked over to the Adventurers again.

 

“Don’t tell me...you travelled all the way here on foot?”

 

This complicated matters greatly. The bridge that the old road ran over had broken down in decades past, and since travel over water was so much easier, the routes that led to the farmlands of the interior were not maintained as they had been an unnecessary expense – not that they could afford to, anyways. Delivering the fief’s goods, and thus it’s taxes, went from a simple task to an impossible one upon this realization. Arms hanging despondently at her sides, she imagined the three of them limping all the way to E-Rantel with what little they could carry; her body already felt like it wanted to scream out in protest at the thought.

 

Her mind made invariably futile efforts at solutions as she stood at a loss. Momon stepped forward, effortlessly picking up both of her bags from the ground and tucking them under one arm.

 

“Your worries are unfounded,” His confident words caused her to look up at him in confusion. “Take me to the rest of your cargo.”

 

In her continued bewilderment, Ludmila led Momon back up the hill to the warehouse. Along the way, she kept looking back at him, growing ever more embarrassed by her situation. The Adamantite-class Adventurer’s appearance stood in stark contrast to the humble construction of the village. If it was enchanted, his armour alone was probably worth more than the entire settlement; she cringed internally every time the squishing sound of his footfalls on the muddy path could be heard over the wind. She had a great deal of pride in her home, but at the same time an Adventurer of Momon’s standing cast a long shadow over their surroundings.

 

When they reached the door, Ludmila produced a set of keys and turned the old, tarnished lock that held the crossbar in place. The building was sealed tight to prevent vermin and moisture from entering so, when she pulled open the warehouse door, the odor of preserved meats, dried fruit and aromatic timber wafted over them. Ludmila scraped the mud off of her boots before entering, looking around to ensure everything was where she remembered it was. Momon stepped in after her and set down the bags he had carried back up the hill. He scanned the interior, looking over the shelves, crates and barrels.

 

“These over here, then?” Momon pointed to the crates stacked up on the floor.

 

“Everything in the building, actually,” Ludmila replied sheepishly. “Save for the items in this corner here.”

 

She motioned towards the corner of the warehouse near the door. There was a rack of venison jerky and a barrel of dried fruit, along with a small number of parts and supplies needed to maintain the buildings of the village. A few nets hung on the front wall that could be cast into the river for fish. Though the warehouse was nowhere as full as it should have been, she felt keenly aware of just how much it was to transport without a ship.

 

If Momon had any opinions on the matter, however, he did not express them. The Adventurer simply stood in place, arms crossed as he examined the contents of the warehouse arrayed before him. The awkward silence continued for several minutes, at which point Ludmila felt compelled to apologize for the hassle and for treating him like some sort of common labourer. He had been commissioned to deliver important orders to the lords of the realm, not to act as some sort of cargo hauler.

 

As she was about to give voice to her thoughts, something at the edge of her vision caught her attention. In an empty space near the back wall of the warehouse, a hole silently opened in the air.

 

“Momon!” She shouted out in startled warning.

 

Momon held up his armoured gauntlet, as if to stave away her alarm.

 

“I’ve arranged transport for your goods,” he said. “This corridor leads to a warehouse, where they will be securely stored until you are available to manage them on the other end.”

 

With his brief explanation out of the way, he began moving through the building, methodically making his way down the aisle and casually tossing everything into the hole in the air. Any doubts she had about the man being able to wield the giant blades at his back vanished as he effortlessly snatched crates and barrels with a single hand – grown men would usually work in pairs to move them – even great trunks of timber were tossed over his shoulder with a flick of his wrist, straight into the hole in the air. He never even turned to see if his aim was true as he quickly cleared out the shelves. She thought she heard children’s voices coming out of the hole, crying out in panicked complaint as the stream of cargo flew through the air and disappeared.

 

Ludmila shut her eyes tightly, pinching the bridge of her nose. It was barely midday, yet the events of the morning must have been wearing her thin. Before she realized it the warehouse had been emptied of everything, save for the corner she had indicated earlier. Seeing this, Momon turned back towards her and stepped forward. The thought of being unceremoniously flung over his shoulder into the hole after the rest of her goods filled her mind, and she involuntarily stepped backwards.

 

“Was there anything else you wished to send?” Momon asked as he came to a stop in front of her.

 

Ludmila shook her head and braced herself for an undignified flight. Instead, Momon walked out of the door, addressing her as she left.

 

“In that case,” he said, “we should get going. Join us when you are ready to leave.”

 

The hole in the air closed as soundlessly as it had opened, leaving Ludmila standing alone in the emptied warehouse. Caught off balance with the sudden acceleration of her schedule, she stumbled out of the building in her hurry to not delay the Adventurers any further, quickly making her way back home.

 

Back in the manor, she fished out the set of clothing she had prepared to wear for her eventual trip to E-Rantel. She had expected to depart when the spring weather had finally settled down, so she spent a few futile minutes trying to straighten creases in the fabric and brush away the lint. They were plain and simple garments that she thought suitable for travel on the dusty roads of the countryside: a short sleeved kirtle made of layered, blue-grey linen worn over a white smock and tan woolen hose. A heavy mantle treated for inclement weather covered her body while her hair was tied up and pinned in place under a grey scarf which protected her head and shoulders from the elements. She took one last pass over her outfit before deciding that it would have to do and pulled her boots back on, walking out of the manor door and securing the door behind her.

 

Momon had long since rejoined Nabe at the bottom of the path. He had one of Ludmila’s bags slung over his shoulder, while the other lay on the gravel where she had placed it earlier. She walked over and picked it up: it was the lighter of the two, containing several of her changes of clothing and other necessities for the stay in the city. After testing its weight over her shoulder one last time, she moved to join the two Adventurers waiting beyond the threshold of the settlement.

 

As she made her way towards them, a wave of trepidation swept over her. She turned once more to look back over the village amidst the anxiety that roiled within her. Behind her, she heard Nabe sigh in exasperation at the additional delay.

 

“Is something the matter?” Momon called out upon seeing her falter.

 

“That’s…it’s just that…”

 

Ludmila struggled to express what she was feeling. She took a deep breath and tried again, turning back to face the two Adventurers.

 

“Ever since it was settled,” she said, “this place has always had people defending it. This village; these lands are the lands of House Zahradnik. My lands. My responsibility. It is my duty to protect its people and guard its borders. Yet even as this is my duty, I leave it empty and undefended.”

 

She swept gaze over the valley. Since the arrival of the two Adventurers, the day had lifted away most of the morning’s mist. Her eyes traced over the empty buildings of the village on the hill and the empty harbour below. Beyond the marshy floodplain that ran along the river, long rows of empty terraced fields scaled the lower slopes of the valley. As the seasons passed, there would be no one to work them and the fief would fall to ruin soon after. The last territory of the southern frontier, lost at the end of generations of decline.

 

The sight of it all opened a crack in Ludmila’s stoic composure, and the frustrated helplessness that was building up inside her since news of the doom at Katze had reached the village began to leak out.

 

“I need to fix this,” she spoke quietly to the pair of Adventurers awaiting her, “but where do I even start? My people are gone; I don’t even know if my family is alive or not. I’m not a powerful Adventurer like my ancestors, nor do I have wealth and connections like the nobles of the interior. How can I even call myself a noble as my lands lay destitute and crumbling to ruin? Even my new liege will lose his confidence upon seeing such a hopeless failure of a vassal and cast me away in disgust!”

 

Ludmila’s resistance gave in to self-pity and frustration. Her voice broke, and tears came unbidden. Amidst restrained sobs, she hid her face behind sleeves turning bitter with moisture. From a corner of her mind a fragment of her pride protested, demanding that she maintain her dignity, but it was drowned out and washed away by the flood of fear and uncertainty that had steadily built up over the days and weeks.

 

It took several minutes before she could collect herself but, when she finally stifled her tears, it felt like something had changed. Neither Adventurer had interrupted her, but their tangible sense of aloofness had seemingly vanished. When she looked up, they still remained standing where they had been, with the pair facing her. She expected her embarrassing display to have drawn even more scorn from Nabe, but her Human face no longer held its sharp expression and had become as unreadable as the one beneath it. Momon’s posture had visibly changed. Arms hanging at his sides, the air of brash confidence no longer emanated from him – even his grand crimson cloak seemed to hang limply in the wind.

 

Surely they were aghast with disappointment – they were just polite enough not to say anything about her pitiful outburst. These Adamantite Adventurers had come to the former frontier of Re-Estize in search of the brave nobles that stood as a shield between humanity’s intrepid pioneers and the savage wilds beyond. Instead they found a girl, an adult who might more rightfully be called a child, wallowing in the empty shell of a run-down village. Her immature display had probably worn away what little had remained of their expectations. Coloured with shame, she looked to the ground, unable to face them.

 

The crunch of metal on gravel barely registered in her mind. The dark sabatons of Momon appeared in her downcast gaze as the Adventurer came back to stand before her. She wondered whether he had come to chastise her for her unseemly behaviour or just simply drag her away. Instead, he spoke.

 

“You may not believe me when I say this,” Momon said gently, “but we can empathize with your feelings. Rest assured, Baroness Zahradnik: this realm belongs to the Sorcerer King, now. He is not so petty as to callously forsake his servants for their flaws and failures.”

 

Had he not been standing in front of her, Ludmila would not have believed it was the same man that she had been speaking with earlier that morning. The bravado and sense of showmanship had all but disappeared, replaced by a quiet sincerity that more than anything before made her want to trust in his words. She lifted her head to look up at him, and the towering figure leaned forward.

 

“Let us be on our way, my lady,” Momon extended a gauntleted hand, “and perhaps you can tell us what happened here while we journey."

 

Stepping forward across the threshold of the village, Ludmila placed her hand in his.