\chapter{Ludmila Zahradnik}
Their path led them north, following the river, using an old raised trail that was little more than a sandbar accompanying the river as it bent northwards. Ludmila had released Momon’s hand shortly after regaining most of her composure, feeling that it would probably interfere with his work as her escort. Besides, it would take over a week to reach E-Rantel using the land routes and the idea that she would be daintily led around by the hand for the entire way felt awkward, to say the least. Instead, she fell in line a few metres behind him, their steps retracing the trail in the wet sand that he had left on his approach to the village. Nabe had flown off somewhere again as soon as they had departed, and there was no sign of her in the skies as they made their way along the riverbank.

 

Although Momon previously expressed his curiosity over just how she had been discovered in her sorry state, the pair silently continued on with the sounds of life in the marsh and the river current as their only accompaniment. She wasn’t sure if he was being considerate of her recent episode or if he simply wanted her to keep up with his rapid pace and discuss things after they made camp, but she appreciated the opportunity to sort herself out in the meanwhile.

 

The sun, heavily obscured by overcast skies, had already dipped below the western ridge of the valley by the time they approached the northern end. Here, the river cut ever deeper until the valley had become a deep gorge which could no longer be followed along its shores. The trail turned uphill at this point, following a large stream that fed into the river over a series of cascades. Ludmila turned to look over her home from the crest of the falls. A gloomy shadow had fallen across the valley as light waned and dark clouds rolled in overhead. The end of winter would often be accompanied by its final gasps – bouts of snowfall that made access to the highland valley nearly impossible over the hills until warmer weather finally set in.

 

With a sigh, she hoped that she could secure a way back by way of the river when she returned from the capital. She prayed that Bohdan, too, would be able to cross the high passes into the Theocracy safely with the villagers: they should have come close to that point in their journey already, if they had not already entered it.

 

When she turned back to the trail leading into the narrow gully, Momon stood a short distance away, patiently observing their surroundings.

 

“I apologize for having you wait on me,” Ludmila said as she approached him.

 

Rather than continuing on their way, Momon turned to stand and face her. Ludmila slowed in confusion before stopping in front of him.

 

“The top of the trail is several hundred metres above us,” he answered the unspoken question forming on her face. “If you don't mind, I would like to save us some time.”

 

“I do not mind,” Ludmila’s confusion only increased after he spoke, “but what do you mean?”

 

Momon fixed the satchel that he was carrying for her securely over one shoulder.

 

“...well, it would be faster to demonstrate,” he said. “Please hold your bag in front of you.”

 

Unslinging her own satchel off of her shoulder, she held it in front of her using both arms.

 

“Like thi–eyh?!”

 

Ludmila had no time to react as she was swept off her feet, finding herself suddenly cradled in Momon’s arms. Before she could utter anything further in her surprise, he launched himself from the trail and exploded through the tangle of branches overhead. Her breath caught in her throat and her mind whirled as it tried to make sense out of what was going on. The scenery blurred as they made their rapid ascent, briefly coming into focus whenever he alighted on the ground – only to become a blur again as he made another leap half a heartbeat later, throwing her senses into chaos. Not a minute passed before she found herself being gently set back down onto her feet, far above where they had started.

 

She wavered unsteadily for a moment before her legs gave out and she fell onto her back, staring dizzily at the sky. It took her several seconds to remember how to breathe.

 

“Umu,” Momon let out a satisfied sound.

 

Is that even a word? She wondered as the Adamantite Adventurer stepped away from where she lay.

 

Ludmila vaguely heard a woman’s voice in the direction that Momon had walked off in. Turning her head to look through the dead grass, she saw Nabe conversing with Momon and realized this was the first time she had actually heard her converse. With her heart still trying to explode out of her ears, however, she couldn’t make out what they were saying.

 

Some distance beyond where they stood, there were a pair of fine mounts. They must have left them here to descend into the gully, but it seemed like a terribly risky decision to leave horses in the wilderness like this. Her baggage was already strapped onto them by the time she found her feet again and wobbled over. Taking in the sight of the mount nearest to her, something seemed decidedly odd. Beyond the appearance of a beautiful stallion, the jet-black warhorse did not seem to react to her presence. Or breathe. As she edged closer to inspect the strange beast, she couldn’t feel any body heat, either.

 

“These are golem horses,” Momon said, “summoned mounts, just in case you were wondering.”

 

Momon stepped in behind her while Nabe lifted herself onto the horse before her in a single graceful motion.

 

“You’ll ride with Nabe, Baroness. We’ll be able to make good time from here.”

 

Momon helped Ludmila up into her seat behind Nabe, who seemed to pay no attention to them. After ensuring his charge was securely in place and comfortable, he strode over to his own horse. The two Adventurers urged their mounts up the remainder of the trail towards the forest and Ludmila readjusted her disheveled scarf and mantle as they assumed a brisk trot until the trail joined the old road where it stopped at the broken bridge. Here, the trot accelerated into a gallop, and together the golem horses sped through the undergrowth.

 

With Nabe so close, Ludmila couldn't help but gawk at the sight in front of her. The long, lustrous ponytail moved slightly as they rode, yet beneath that, she saw that the back of her head was as bald and featureless as her face: she didn’t even seem to have ears. Just as Ludmila was about to reach out to try to lightly touch what she saw, Momon cleared his throat to the side.

 

She quickly withdrew her hand. Maybe it wasn’t such a good idea.

 

“I take it from what you said earlier,” Momon said, “things are not as they once were in Re-Estize?”

 

The dark warrior had brought his mount alongside Nabe's, close enough that his voice could be heard clearly through the headwind. Ludmila shook her head in response to his query.

 

“I cannot speak for the other territories,” she said, “but our fief has always been small. It has never been empty like this, however.”

 

Despite their rapid progress along the forest trail, it was not difficult to converse. The strange horse golems moved with a smooth, unnatural gait – more stable than any wagon or carriage in her limited experience.

 

“Then the cause must be…”

 

“Katze, yes,” she said.

 

She did not cherish the memory, but felt obliged to share her story with the man who had shown her so much patience.

 

“My lord father departed with his levy over a month ago,” she said, settling more comfortably onto the saddle, “after the King called for his banners to face the Empire for the annual skirmish. Usually, after a few weeks on the field, our men would return without incident.”

 

Momon remained silent as she related her account and even Nabe appeared to be paying attention, turning her head slightly.

 

“Any noble familiar with the workings of their own demesne had by now figured out that this meant that the Empire simply wanted to harass us without losing too many of their own forces,” Ludmila continued. “Their objective in previous years was to tie up our labour and interfere with the activities surrounding the autumn harvest season.”

 

“You knew this,” Momon interjected, “yet you played into their scheme?”

 

“It is not a matter of being played: an army at your border cannot be ignored,” Ludmila shrugged. “If their goal was to hamper our seasonal activities…then without opposition, they could move on to raze our fields or worse – these standoffs do come after a formal declaration of war, after all. Even the strongest retinues of Re-Estize cannot hope to match the might of the Imperial Legions, so our best course of action was to pool our forces into an army just large enough to threaten them with unacceptable losses should they be ignored. E-Rantel stands over the lowlands that mark the easiest route into the Kingdom, so the stage for the confrontation would naturally be in the nearby Katze Plains.”

 

Now that their discussion revolved around matters familiar to her, Ludmila spoke more fluently, mechanically drawing from her personal knowledge, education and experience.

 

“What of raids, then?” Momon asked, “With all your forces concentrated in one area, wouldn’t it be a simple matter to send detached forces to attack your undefended lands rather than face off against a mass of levied troops?”

 

Ludmila frowned. At this point, it felt very much like she was being tested. Reminding herself that she was speaking not to another noble, but a strong and free-willed Adventurer, she responded in a carefully modulated tone.

 

“Why, it would result in chaos,” she replied. “No one wants that.”

 

She paused for a moment to find words to describe the scenario to him.

 

“The Empire could certainly do what you say, but it would have escalated the conflict and pushed it in an undesirable direction. The Kingdom would respond in kind – there would be roving bands of soldiers everywhere. The Empire’s Legions are primarily composed of heavy cavalry supporting the main body of heavy infantry, all at least trained to a moderate degree with experienced officers set over them. The downside to this is the cost of maintaining an outstanding professional military – it is such that each Legion is relatively small.”

 

This was how her father had related the disposition of troops every year, at least. It had been a question from several years ago, asking why the Empire did not do exactly as Momon suggested.

 

“The levy mustered for this annual skirmish is composed of mostly unseasoned tenants and scutage in the form of mercenary companies,” Ludmila continued her explanation, “depending on the resources of each individual lord. If the skirmish escalated into a full conflict, the levy would expand to a far greater size and noble retinues would be called into war. In fact, since the elite of the Kingdom’s retinues are heavily invested in light cavalry, the Empire is actually at a disadvantage trying to both contain the levy and outmaneuver the retinues if they were deployed. The war would spiral out of control: trade would slow to a crawl, other parties would be drawn into the conflict and both sides would receive a senseless amount of damage to their lands.

 

Ultimately, however, no raid by the Empire can get past E-Rantel anyways. Any sortie into our territory by an army past that point would be intercepted by a response that has a much shorter distance to travel – castles and other fortified positions exist for this very reason. It would amount to a foolish move, and no one that rises to a position of leadership would be such a fool for very long and expect to retain their position. The goal of territorial conflict is to force concessions, not pointlessly devastate the very lands that one is trying to take.”

 

Ludmila paused to take a flask of water from her bag strapped to the side of the horse. As she took a sip to clear her dry throat, Momon asked an unexpected question.

 

“Are you really a teenage girl?”

 

A fit of coughing gripped her, and she turned her head away from Nabe’s back while nearly dropping her flask. She would have been pondering over whether to be offended or not, had she not been fighting for breath.

 

“What do you mean by this?” She finally managed politely through teary eyes.

 

“Hmm...how should I say this,” Momon paused in consideration. “Most young women around your age seem to be interested in...other things. They certainly haven’t spoken of state and military affairs as you do.”

 

Nabe sniffed dismissively at his words and Ludmila pondered them, absently looking out at the dense undergrowth of the forest while she wiped her face with a handkerchief.

 

“If circumstances were different and a famous person I was familiar with came and spoke with me, I might have acted in a different manner…” Ludmila's voice trailed off as she recalled the previous year's visit to the duchy capital. “Commoner girls lead much simpler lives and would certainly have the freedom to act in a more frivolous way. Nobles, regardless of gender, should at least have the basic knowledge required to administer their own realm. After all, no one wants to see a legacy generations in the making squandered by an indulgent wastrel of an heir, and a lady that cannot assist in the management of her husband’s fief is at a disadvantage when measured against one who can.”

 

Ludmila wondered why she was made to answer these strange questions – it was as if the Adventurer had a ridiculously fantastical image of the aristocracy, akin to that of the tales spun by Bards in cheap taverns deriding fantastically foolish nobles. While not all noble families had the more militant mindset of a frontier house like her own, achieving a position of power and maintaining it was a monumental task filled with duties that took up most of the daily lives of a noble and their vassals. Gross mismanagement could result in their liege citing violations of duty as just cause to strip them of their titles and grant them to another...or keep them for himself. No noble house wished for generations of their work to be seized in such a manner. Even if one’s liege was oblivious to what was going on, the ruin wrought by negligence would still find them sooner or later.

 

Momon continued his questions, however, seemingly unconvinced.

 

“Then what of the Royal Court?” He asked.

 

“The Royal Court?”

 

“Yes,” he nodded. “I’ve heard it said that, in the time leading up to the events at Katze, the Great Houses of Re-Estize treated the affair as a trivial event. It’s also claimed that they were more concerned with matters of prestige and used the prolonged debate over the conflict as a means of maneuvering for their own internal power struggles. With the Imperial Army threatening the Kingdom’s borders, it hardly seems like the time and place for such behaviour.”

 

Ludmila bristled at the words trivial event, but she held her tongue against the provocation. Certainly, the whole affair had been catastrophic for House Zahradnik, but beyond that…

 

“It should be as you have heard,” she said.

 

“Do you mean to say that this behaviour should be pardoned?” The Adventurer’s tone held a hint of incredulity.

 

The young noblewoman pursed her lips as she thought of a way to express what she understood.

 

“Any noble that reviews their accounts should have been aware of the continual shortfalls produced by the hampering of the autumn season – even if they were not aware of the specific details, they would definitely feel their purses shrinking. However, there was nothing the King’s vassals could do directly that would change the slowly unveiling outcome of the Empire’s strategy. As wealthy or as powerful as any one of the Great Houses may be, they are individually not powerful enough to confront the Empire on their own. Lashing out impulsively at the Empire alone as a single lord in some delusion of grandeur would only result in their complete annihilation by the Imperial Legions, weakening the combined military strength of Re-Estize.

 

The situation was untenable, but in the end it was only the leadership of the King that could rally the nobles and put an end to the predations of the Empire. A minor house like my own is not privy to whether the full might of the Kingdom was enough to put an end to the Empire’s schemes, but ultimate authority lies with the throne. It is the King’s decision to make, and the Great Houses are his vassals to lead in decisive action. It should be noted that despite all of their jockeying for prestige, the Great Houses mobilized when the decision was made. This is not something that can be done at the drop of a hat – it takes upwards to a year for a large territory to fully prepare and mobilize a levy, meaning that they had already committed to the Kingdom’s defence preemptively and were simply awaiting the resolution for war.

 

If the King will not lead, his nobles will not follow. Without clear leadership, it is only natural that the aristocracy continues to uphold their end of the noble contract and ensure that the interests of their respective fiefs are put forward – whether they be presented directly to the Royal Court or through diplomacy with other nobles and influential parties. The King’s vassals will simply continue to carry out their regular duties until directed otherwise.”

 

Momon moved his gauntleted hand below his helmet again; he couldn’t actually stroke his chin in contemplation through the plate armour, but Ludmila supposed it served the purpose of showing that he was deep in thought.

 

“So even knowing the results in the end,” he said, “you still hold to your reasoning.”

 

Ludmila narrowed her eyes. She had heard this juvenile rationale before from the more unreasonable members of her social circle.

 

“‘Knowing the results’ is a whimsical fancy when judging past decisions,” she replied testily. “There is only what one knows at the time that decisions are made.”

 

She paused for a moment to correct her tone, not wanting to pointlessly antagonize her escort.

 

“If the testimony I received was to be believed, then there was nothing Re-Estize could have done against this catastrophe. The losses go far beyond any sort of reasonable expectations based on past conflicts. In previous years, my lord father would take little more than a few dozen men with him, and return with the same number. It has always been an affair full of symbolic pageantry rather than pitched battle: a show of power and wealth – not only between the Kingdom and the Empire, but between the noble houses as well. If someone had claimed that nearly everyone would be lost, they would most likely be dismissed out of hand as delusional…or considered a coward.”