\chapter{Ludmila Zahradnik}

Lady Shalltear’s attendants helped to carry out Ludmila’s small tower of books and folders – much to Aemilia’s visible relief – as they made their way out of the manor. The Death Knight that had been dispatched was back at its post and, between itself and it’s partner, had turned the exit of the manor lane into a spiky obstacle once again. Lady Shalltear led the procession, not caring to even slow as she approached the guards. The two sentinels parted and stood at attention as they passed through, heads held high behind their massive tower shields.

 

Ludmila felt a tug at the hem of her bolero – Aemilia nervously clutched at her, crowding in closely as they crossed the threshold onto the road. The heavy, metallic tread of sabatons over the street sounded from behind them as the two Death Knights fell into step behind them, and the group made their way briskly towards the offices near the front gate of the district. Several of the guest manors that they passed showed signs of activity within, their chimneys smoking as fires were maintained to keep their occupants warm on the cool spring morning. Though none had Death Knights stationed, none showed any of the usual chores being done by household staff outside.

 

Ludmila had to raise her voice slightly to be heard over the brisk wind that the clouds had followed. She hoped that it wouldn’t be perceived as her shouting at her liege.

 

“Lady Shalltear,” she asked, “would it be possible to have several of the other nobles accompany us?”

 

“Hm? That would be inadvisable,” her liege returned, “they don’t have the same…mental fortitude as you do. Well, you’ll see what I mean shortly.”

 

Ludmila turned her head to see if Aemilia had anything to say, but it seemed she was too busy jealously looking over the other attendants. Their alabaster garments, seemingly designed for a much warmer climate, were composed of sheer, layered silks which were very flattering when it came to emphasizing their voluptuous appearance. They, on the other hand, seemed to pay no mind to the envious looks from the young maid, following after their mistress with silent steps.

 

The civil offices of E-Rantel occupied the blocks just inside the southern gatehouse of the district. They were constructed along the main promenade leading up to the Royal Villa, framing the palatial structure with their dignified masonry, alongside rows of blossoming trees along the street. The trees themselves cared not for who occupied the city, flowering in a grand display of pastel petals. If the day had been a bit brighter, she might have reminisced over the day when she had first been brought to the capital and rode into the avenue from the gate, marveling at its vibrant splendour while sitting in her mother’s lap.

 

The first office on the opposite side of the road was their destination: one that served to receive petitions and reports from nobles and other functionaries. Stately stone steps, in front of a stretch of pavement allocated for carriages to drop their passengers off onto the sidewalk, led up to the main entrance to the three storey building. There were usually a pair of city militia stationed at the bottom of the stairs, but like the guest houses in the district, the Death Knights that she saw posted throughout the city were notably absent. As their group ascended the steps, the two that had escorted them to the office took up these positions at the bottom of the stairs. At her arm, she heard Aemilia breathe a sigh of relief as they left the Undead footmen behind, stepping away to follow at a respectful distance.

 

The large doors at the top of the stairs were framed with oak and set with large panels of crystal glass. The face of the building had been fashioned in a similar manner, with large windows to allow light into the interior as well as to provide a view of the street for those that awaited within. Lady Shalltear’s attendants stepped forward to prop open the entrance, and the odors of parchment, ink and vellichor wafted over them as the doors swung open, revealing the darkened space within.

 

There were no queues of petitioners, nor any individuals awaiting appointments seated in the private alcoves that lined the walls. Lines of velvet rope strung between the metal posts that guided queues hung forlornly in the middle of the chamber, and the sturdy carpets on the floors leading up to the reception remained pristine – unmarred and unsoiled with the marked lack of visitors. A broad counter of polished maple was divided into several sections, each normally having a government official awaiting to service the next client. Aemilia had informed her that the Sorcerous Kingdom had dealt with the absence of administrative staff in the city by using Undead, and Ludmila now confirmed this with her own eyes.

 

At each of the eight sections of the reception counter, an Undead being awaited in still silence. Rather than the heavily armoured Death Knights, they were more akin to the ones that she had encountered posted inside the guardhouses of the city, robed in black with yellowed strips of cloth, inscribed with some unknown language, hanging about their withered forms. As the door shut behind them, they all turned their heads towards the group – sixteen crimson points of light glaring upon them in the baleful manner that Ludmila had over the last day simply come to informally categorize in her mind as ‘Undead gaze’.

 

There was a heavy, thumping noise, accompanied by the flutter of papers and sound of falling books: the sound of her maid and the articles she was carrying hitting the carpet laid over the polished hardwood floor. Unlike the rest of the group, Aemilia had slowed down after the doors had closed as her eyes adjusted to the dim interior. When the maid regained her vision, she had immediately fainted under the combined stares of the Undead clerks. As Ludmila turned to tend to her fallen attendant, Lady Shalltear’s amused voice sounded from behind her.

 

“Ah, that’s it,” she said lightly. “The last noble that attempted to enter ended up the exact same way.”

 

“A more concise warning might have been appreciated, my lady,” Ludmila said as she knelt down beside her servant, checking for injuries.

 

Lady Shalltear sniffed dismissively.

 

“Perhaps,” she said. “Or perhaps I was seeing if your influence was strong enough to affect others to the point that this outcome wouldn’t occur.”

 

Ludmila carefully moved Aemilia to a cushioned chair nearby and, after taking a moment to make sure the maid was alright, she turned back to speak to her liege.

 

“My influence?” She asked, “What do you mean?”

 

Lady Shalltear tilted her head curiously at her.

 

“Your ability to influence those around you, of course,” she said. “This is something that we’ve already observed a handful of nobles demonstrating in our time here so far – whether they know that they’re doing it, I cannot say. Countess Jezne appears particularly proficient out of the ones here, able to stir even other nobles to action. Emperor Jircniv as well, if I recall correctly, was able to steel his escorts to a degree when he was granted an audience with His Majesty. Even walking out of your residence with that maid in tow is quite the achievement, all things considered…how many servants do you see running around in this district?”

 

Ludmila bit her lip as she thought it over, unconvinced.

 

“I do not feel that I have done anything outstanding, my lady,” she said. “People can be prompted to action by the actions and words of others from many backgrounds: it is not something reserved for nobles.”

 

“How curious…”

 

Lady Shalltear stepped forward, until there was barely a metre between them. She turned her gaze upward at Ludmila, as if trying to peer at something within her.

 

“M-my lady, what–”

 

“You Humans have Adventurers, yes?” Lady Shalltear asked, “When you see a party of them, don’t you look and think to yourself ‘this one’s the Fighter’ or ‘this one’s the Wizard’.”

 

“Well yes, but–”

 

“By the same token, your common folk have vocations of their own: Merchants and Cooks; Blacksmiths and Farmers. Do you not consider these vocations along similar lines? Can someone that has been a Noble for all their lives pick up a hammer and declare that they’re a Blacksmith? Can a Fighter one day decide that they want to be a Wizard the next?”

 

“Of course not, my lady,” Ludmila replied. “They would need to learn how – if they are even capable of doing so in the first place.”

 

“Then what is a Noble?” Lady Shalltear asked her, “What sets them apart from other Humans? What do they do that others do not seem to?”

 

“We…lead and administer, I suppose. We oversee our fiefs, upholding the oaths and obligations to our liege and to our vassals. The people look to us for direction and leadership; security and prosperity. It is our charge to realize this for our lands through the means available to us.”

 

“Has it ever occurred to you that those of other vocations cannot do these things as effectively,” Lady Shalltear said, “unless it is also something that they also happen to do?”

 

“Well, no,” Ludmila said. “I think anyone should be able to learn and perform the same administrative tasks that I am capable of, my lady.”

 

“So if you take someone under your wing and train them, what do they become?”

 

Ludmila looked around the reception hall, thinking on how to reply.

 

“It depends…” She said, “If it is to assist with my administrative tasks, perhaps a clerk or an accountant. If it is to help patrol the border or protect the demesne, a Fighter or a Ranger. If we are grooming someone for the role of a village or town leader without granting them land, they would simply be a village chief of a small fee or a provost that oversees and organizes towns, cities and their surroundings.”

 

“And if you teach them everything you know, do they become a Noble?” Lady Shalltear asked.

 

“Perhaps, if they earn extraordinary acclaim,” Ludmila said, “their liege will propose to have them married into their house, or grant them a title if the long term services of their family are deemed valuable enough. However, nobles are usually born as nobles. Even those who are granted titles, like my great-grandfather, retain the skills of their previous vocations and have to learn the responsibilities and skills of the nobility after that…it is said that he did not take very well to them and he preferred to do what he was good at, delegating the majority of his civil duties to administrative assistants.”

 

“Very good,” Lady Shalltear seemed satisfied with her answers and stepped back a short distance.

 

Ludmila’s eyes widened as a remarkable transformation occurred. In place of Lady Shalltear’s black ball gown were glistening segments of crimson plate, armouring her from head to toe. A demi lance appeared in her right hand: a weapon of peculiar design and construction that she had never seen before. Her shining silver hair trailed down from under her helmet between a pair of pure white wings. The equipment had the look of being suited for heavy cavalry, but for her short weapon and open-faced helm. Ludmila’s senses told her that this armor was not designed for mounted use, but for something that required even higher mobility and awareness. The sleek form of deadly beauty that Lady Shalltear presented caused any doubts that Ludmila had concerning her principle role as a combatant to dissipate as if they had been a fanciful delusion. The voice that issued forth had a quality beyond the one that echoed off of the walls of the alley, and Ludmila could only be still as Lady Shalltear spoke.

 

“I am a Vampire. I am a Cleric. I am a Knight and I am a Valkyrie. I guard the realm of the Sorcerer King against all that would defile it with their unwelcome presence. By His command, I will fight until all of His enemies lie slain or I fall carrying out His Supreme Will. There is no distance too far, no duty too great or small. I live and die for my Master, and it is both my pride and my pleasure to serve.”

 

The words of her declaration resounded through the empty reception hall of the office. Lady Shalltear was not very tall, but at that very moment her presence dwarfed all in attendance. Her eyes shone with a clear conviction that would sweep away any challengers to her claim – those eyes now turned to Ludmila, holding her attention hostage.

 

“All that I am capable of – all of my fighting prowess; the divine might I bring to bear; all of the awe and terror that I inspire; everything I love and desire – are because of who I am. I cannot be any less than this, and neither can you. So I will stop beating around the bush and ask, Ludmila Zahradnik: who are you?”

 

Arrested by Lady Shalltear’s noble bearing, Ludmila searched for an answer to her question. After what seemed like an eternity of silence, her liege closed her eyes and sighed. Ludmila blinked, and just as suddenly found Lady Shalltear once again attired in her black ballroom gown.

 

“Perhaps, like me,” she said, “you grasp things better by experiencing them directly. Let’s try this another way.”

 

Lady Shalltear looked past Ludmila to the maid passed out on the chair near the window behind her.

 

“Your servant,” she said. “Tell her to wake up.”

 

Ludmila looked askance at Lady Shalltear, then back to her maid when no explanation appeared to be forthcoming. She slowly walked over and knelt down beside Aemilia.

 

“Wake up, Luzi,” she said softly.

 

The maid’s shallow breathing continued uninterrupted; her eyelids remained still with no movement behind them. Ludmila turned her head back to look at the group watching her.

 

“You must do more than simply speak words,” Lady Shalltear said. “Think on how you were able to encourage your maids to follow your lead.”

 

Ludmila stood up, looking down at the young woman, thinking back on the previous evening when she had simply acted and the two maids cowering in her solar had eventually followed suit. Still a bit uncertain whether the feeling she had settled on was what Lady Shalltear was referring to, she tried again.

 

“Wake up, Aemilia.”

 

Though she had spoken just as softly as before, her words sliced through the air like an icy blade. More than simple words, it was akin to expression – carrying the tone of confidence, expectation and authority. Her will was carried into the air by her quiet words, heard clearly by all those around her.

 

Aemilia stirred, and her eyes fluttered open. She turned her head, still laying on the cushions, to face Ludmila.

 

“Lady Zahradnik, what–”

 

The maid’s eyes widened in terror as she looked around and found the Undead waiting at the counter still staring in her direction. Her eyes rolled up into her head, and she fainted again.

 

Ludmila felt a twinge of guilt as Aemilia collapsed back into her chair with a sigh. She looked to Lady Shalltear, who had stepped in beside her, arms crossed under her ample bosom.

 

“Again,” Lady Shalltear told her.

 

Ludmila licked her lips and cleared her throat. Stepping over to fully block her maid’s line of sight to the counter, she leaned down and spoke again.

 

“Wake up, Aemilia.”

 

Once more, her words cut through the silence, and the maid responded. As she woke fearfully, Ludmila cradled her maid’s cheek with her left hand and tilted her face towards her, keeping Aemilia’s emerald eyes focused on hers.

 

“Calm down, Aemilia,” Ludmila said, “I’m with you. The Undead here are not our enemies: you need not fear them so much.”

 

When her maid calmed down visibly, Ludmila stepped back, helping her to her feet. She continued to hold her hand as she stood aside, facing the interior of the office with her. The maid’s grip tightened as she wavered at the sight of the Undead at the reception counter, but this time she did not faint.

 

“I see that you’re a quick study; you should keep in mind what you’ve learned here,” Lady Shalltear smiled slightly. “You should also keep in mind that there are most likely more things that set you apart from the others – if I can piece this together with what little I know, I’m sure those around you have noted it as well. Not seeking to understand the extent of your own abilities is unforgivably foolish, and misplaced humility can bring as much harm as empty pride.”

 

Lady Shalltear turned, walking towards the front desk with her attendants following behind her. As Ludmila fell in line to her side again, she asked a question.

 

“How did you know about this…ability, my lady? Are you able to do this as well?”

 

“There are some things that you may find similar,” Lady Shalltear answered, “but my abilities in that area are not precisely related to your own. I do, however, have several acquaintances that have powers much like yours.”

 

“Thank you once again for your help,” Ludmila said.

 

“You can show your thanks by using your skills for the benefit of the Sorcerous Kingdom,” Lady Shalltear told her. “You have your own work ahead of you, and I believe you’ll be able to use these abilities to great effect in the future.”

 

They covered the space between the street windows and the front counter, and Lady Shalltear came to a stop. The Undead clerks had not moved the entire time beyond observing their progress through the building. Reaching out to a board where a row of small wooden plaques hung on brass pegs, she took the closest, which had been engraved with the number ‘1’.

 

She held it out to Ludmila.

 

“I believe your number is next, Baroness.”