\chapter{Ludmila Zahradnik}

Lady Shalltear’s Vampire Brides, Aemilia and the Elder Lich joined them shortly after; each of the three attendants carrying a portion of the books and files that remained after Ludmila finished submitting her forms. Arranged before her was the manifestation of those forms, and Ludmila was now mentally going through the checklist of things that she wanted to have taken care of before the day was over.

 

The applications that she had filled were meant to provide only raw labour, so the fact that many of the Undead standing in front of her were armed was unexpected. Unfortunately, being armed did not really help with the task she had requisitioned them for. It was up to the applicant leasing the Undead labour to provide the appropriate equipment, though there were a few recommendations that came with them in the provided almanacs. In hindsight, procuring the Undead labour was probably the easier part of what she had to do: it was the exact opposite of what she had originally expected to go through to find new tenants. Though she would still need to find tenants to direct the Undead Labour, the number required was drastically reduced compared to what would have been required before. Ludmila thought that she could at least get things started while she waited for them, and see how things worked for herself. She turned to address Aemilia.

 

“Luzi, take these things back to the guest house,” she instructed her maid. “Actually, hand me the blue folder first – I’ll be needing that.”

 

“Yes, my lady,” Aemilia said as she handed over what had been requested.

 

“I hope you don’t mind my borrowing your servants, Lady Shalltear,” Ludmila said.

 

“It’s not a problem,” Lady Shalltear replied. “We’re trying to produce results as quickly as possible here.”

 

Ludmila turned to the Death Knights that had accompanied them.

 

“Escort Luzi back to the guest house,” she told the one standing on her left, “return with her when she has completed her task.”

 

Aemilia, who had already started to walk back to the house, overheard that a Death Knight would be coming with her. She darted along the road with the Vampire Brides, walking faster and faster over the cobblestones, but the Death Knight slowly closed in on them despite her efforts.

 

“I hope no one gets the wrong idea seeing that,” Ludmila remarked as she watched the Death Knight chase the women up the street.

 

“I thought the goal was to assuage the fears of the citizens, not feed them.”

 

Ludmila frowned and looked down towards Lady Shalltear, but the Vampire only looked on innocently. Ludmila turned to the Elder Lich.

 

“Well, I suppose we should get on with the next order of business,” she said. “Will these labourers stay here, or is there somewhere that they can assemble and wait for their equipment?”

 

“They were instructed to present themselves for inspection in front of the Civil Office,” the Elder Lich answered, “they are under the leaseholder’s authority upon delivery.”

 

Ludmila looked around absently as she thought of a place to have them wait – leaving them in the main avenue of the central district was probably something that would disrupt traffic if the city was even slightly busy.

 

“Are they permitted transit through the city on their own?” Ludmila asked.

 

“They will not be intercepted if they traverse the city in a non-disruptive manner,” the Elder Lich answered.

 

“Alright then…” She turned to her new labourers, “Head to the Military District, using the main roads. Assemble at the first available mustering field to the west of the south gate and await me there.”

 

The Bone Vultures all took wing at once, while the other groups of Undead marched away in formation. Ludmila watched with some satisfaction as the formation filed off under her orders.

 

“That was interesting,” Lady Shalltear noted from beside her. “You didn’t even raise your voice to issue your instructions, but they all heard you over the wind. Considering that you just realized you had these powers...when did you learn how to do that?”

 

“Just then, my lady.” Ludmila’s voice was a bit bemused as she answered, “I was actually going to raise my voice like those famous captains and generals in the tales that minstrels tell, but when I started speaking, I noticed that even the ones all the way in the back that shouldn’t have heard me had already reacted. So I just spoke normally. In regular circumstances, they should not have heard me, but this ability carried my voice to everyone.”

 

“Did you know if they would arrive at their destination?” Lady Shalltear said.

 

“Er…no?” Ludmila looked towards the receding labourers in alarm, “Wait, they won’t?”

 

“They will, in this case,” Lady Shalltear replied. “As long as they receive their orders, they will perform according to your intent…as long as it is something that they themselves are able to manage without more precise direction. In the worst case, the Death Knights with them will rally any lost Skeletons. You will probably need to show these labourers how to do some uncommon things at some point, since your territory seems to produce goods that are not commonly cultivated in Re-Estize.”

 

Ludmila breathed a sigh of relief. The last thing she needed was to have inadvertently commanded her newly acquired workforce to rampage through the city on the way to their destination.

 

“Well then,” she said. “I need to find where my goods have disappeared to now…”

 

“What happened to them?”

 

“Before I left Warden’s Vale, Momon threw everything into a hole much like the one that you used yesterday evening.”

 

“Ah, yes, that was me. Aura and Mare had quite the time catching all those things that suddenly came flying through,” Lady Shalltear smiled at the recollection. "Your goods are in the government warehouses; let’s be on our way.”

 

Lady Shalltear turned in the direction of the Royal Villa and walked off. Ludmila followed, and the Elder Lich followed after Ludmila. The day had brightened considerably since the morning, with the overcast skies breaking up to reveal the azure heights beyond. A brisk wind was sending the clouds southwards rapidly; she wondered if the rain of the previous night would arrive as snow in Warden’s Vale.

 

They continued around the Royal Villa and past the gazebo that was used as the location to teleport in and out of. The entrance to the city stores was a fortified and guarded gate tucked away on one side of the central district, where a ramp led down to the vast warehouses had been carved deep into the hill below. The city had furnished it with magical devices that enchanted the entire space with a Preservation effect, which would keep the tremendous volume of siege provisions stored within from spoiling. They passed between the two Death Knights standing guard at the top of the large ramp that led down into the cavernous areas below, steps echoing lightly off of the tunnel-like passage.

 

After two turns, most of the light had been swallowed in darkness, and Ludmila found herself looking at row upon row of shelves that reached all the way to the ceiling, which was perhaps five metres above her head. They were supposed to be filled with the supplies that had been meant for the armies of Re-Estize, but after scanning their contents, she saw that the nearest portion of the warehouse was already being emptied and there were many bare spaces. After passing several aisles, Lady Shalltear stopped and turned to face an aisle to her right.

 

“The things on the bottom shelf there should be yours,” she pointed down the way a bit, “make sure nothing has…wandered off.”

 

Ludmila stepped towards where Lady Shalltear was pointing and quickly located the shelf that appeared to have the goods from the warehouse in Warden’s vale. They had taken up a significant portion of the storage space in her home village, but here they only occupied perhaps one third of the bottom shelf of a small fraction of the city warehouse. She felt rather tiny as she checked what she saw against one of the documents in the blue file folder to ensure that everything was in order.

 

“It looks like everything is here, my lady,” Ludmila called out, “are there problems with theft down here? The security in the city seems overwhelming.”

 

“I was just making sure,” Lady Shalltear said. “There are no issues with thieves, but samples are sometimes taken for analysis if we find something that might be interesting or different. What do you plan on doing with all this?”

 

“I need to have it loaded onto a wagon, and then search for someone that is available and willing to purchase these goods.”

 

“Well none of the ones in the warehouse are being used, so it shouldn’t be an issue. You,” Lady Shalltear addressed the Elder Lich, “submit a request for a wagon from here on behalf of Lady Zahradnik. We’ll pick you up at the civil office on the way out.”

 

The Elder Lich bowed silently, and walked away towards the entrance.

 

“I was not aware that they could do that, my lady,” Ludmila said as the tapping of its staff receded into the distance.

 

“Well, it’s supposed to be your administrative attaché, is it not? I’m pretty sure you Humans do the same thing – sending others that function under your authority.”

 

“That is correct, my lady,” Ludmila admitted. “I guess my family has just always done most things directly.”

 

The tread of a Death Knight and the light of a lantern coming from the entrance drew their attention. The four that had left to drop off Ludmila’s files had returned.

 

“Did you run into any trouble?” Ludmila looked between the members of the group as they arrived, “Actually, how did you even find us? I do not recall mentioning where we would be headed.”

 

“No, my lady,” Aemilia said, “Lady Shalltear’s attendants appeared to know where you went after we parted. Mrs. Ro’eh asked if you would be having lunch at the house.”

 

The maid’s question reminded Ludmila of the wholly inadequate breakfast from the morning.

 

“Hmm…what is she preparing?” She asked.

 

“She was not aware of any itinerary, my lady – only that you would be out for most of the day,” Aemilia replied, “so it’s a meal that can be packed if necessary.”

 

“That will be fine,” Ludmila nodded. “Head back to the house and let her know. While you are there, find my scarf and shawl and bring it with lunch – this wind keeps getting stronger. Wait for us in front of the civil office; you should see the Elder Lich waiting for us there as well.”

 

Aemilia’s head nodded at each instruction. When it seemed that there would be nothing more forthcoming, she curtseyed before them and turned to leave.

 

“Continue escorting Luzi.”

 

Ludmila told the Death Knight to maintain its orders, and Aemilia looked at her like she was about to cry.

 

“Do not run away from your escort this time,” Ludmila instructed her maid, “it looked like you were about to be murdered on the street just now.”

 

Aemilia’s mouth worked silently as she looked back and forth between her mistress and the Death Knight, her expression asking how she ended up being in the wrong somehow. When it was clear that she would receive no consolation, she sighed and slowly walked off.

 

“Despite claiming to be used to doing things directly,” Lady Shalltear noted, “you certainly don’t seem to mind running your new staff back and forth.”

 

“Luzi is aspiring to be my lady’s maid,” Ludmila explained, “but my household currently does not have a page, and the footmen would scare everyone else witless. She should understand this as well as I. Besides, her visibility in the streets in the company of the Death Knight contributes to the idea of safety that we are trying to promote amongst the citizens here, yes?”

 

“I see. Well,” Lady Shalltear looked over to direct her Vampire Brides, “let’s get these things off the shelf and ready to load on the wagon.”

 

From the depths of the warehouse, the sound of hooves on stone echoed through the aisles. As her inventory was arranged near the path that ran through the warehouse by Lady Shalltear’s attendants, a wagon drawn by a skeletal horse turned the far corner. Lurid light shone from within its bony frame, which was embraced with sickly yellow-green fog that shimmered and rippled like living flesh as it trotted forward.

 

The wagon appeared to have no driver, yet it rolled smoothly to a stop in front of them. The Vampire Brides immediately began to place the various articles onto the bed of the wagon in an orderly fashion. Taking in the details of the skeletal horse, Ludmila turned her head towards Lady Shalltear.

 

“Is this an Undead Beast as well?” She asked, “It seems quite different from the ones that you showed me earlier.”

 

“This is a Soul Eater,” Lady Shalltear replied. “They are level forty, so substantially more powerful than a simple Undead Beast.”

 

“This…horse is more powerful than a Death Knight?”

 

“They have very different sets of traits and abilities which makes them useful for different things, but yes: in rough terms, they are.”

 

Ludmila envisioned a teamster driving a cart pulled by beings that could destroy a city. What would happen if there was an accident?

 

“What happens if the cart breaks, or if there is some sort of mishap?”

 

“Hmm…that hasn’t happened yet,” Lady Shalltear tilted her head in thought, “but it’s strong enough to forcefully drag a broken cart loaded with goods around. I’m not sure if everything will stay on the wagon in that situation though; the wagon itself might break apart.”

 

Lady Shalltear hopped onto the driver’s bench as the Vampire Brides loaded the last of the goods. The two attendants took their seats at the back of the wagon bed, their pale legs dangling off the edge. Ludmila pulled herself onto the driver’s seat beside Lady Shalltear. The Soul Eater turned its head to look at her with a glowing eye socket.

 

“Let us pick up the others at the civil office first,” Ludmila said.

 

The Soul Eater turned its head back and began plodding forward. Ludmila looked over her goods worriedly as the wagon rolled up the ramp, but the shallow incline leading out of the warehouse was not steep enough to cause anything to slide out of the back of a loaded wagon bed. She watched the skeletal horse as it made its way up – pulling a freight wagon was something that normally required large teams of horses, yet this single Undead being did so effortlessly.

 

They found that the clouds had completely broken since they entered the underground warehouse, and the warmth of the sun was rapidly turning the day pleasant. Free of the need to carefully maneuver through the tight turns leading out of the warehouse, the Soul Eater picked its pace up to a brisk trot, and the noise of its hooves on the cobblestones made it seem like they were being pulled along by a regular horse – at least until one looked at the horse itself.

 

It took all of two minutes to reach their destination as they circled around the district, finally slowing to pull up in front of the civil office. The trio waiting by the stairs turned their heads at the sound of the wagon’s approach. Aemilia visibly jumped at the sight of the Soul Eater, and she seemed on the verge of panic until her eyes found Ludmila sitting in the front seat with Lady Shalltear. She spotted the other attendants sitting in the back of the wagon and circled around, handing her lunch basket to one of the Vampire Brides so she could pull herself up to join them.

 

Ludmila took a deep breath and released it in anticipation of what was to come. So far her day had been relatively straightforward with the help of Lady Shalltear and the smooth workings of the new administration. It had all been completed within a single morning: so quickly that the next group of tasks were already upon her before she could fully think through what needed to be done.

 

“Time for the annoying part,” she muttered to herself.