
\chapter{Ludmila Zahradnik}

Ludmila’s anxiety mounted as she was led out of the clubhouse and over the swept garden lanes towards the Royal Villa. The waning light of the evening cast a fiery orange glow onto their surroundings as the shadows of the district lengthened over the pristine grounds surrounding the palatial building. Her guide continued to maintain her perfect posture even as she moved ahead: back was held straight and hands arranged primly in front of her. The maid’s hips did not sway, nor did her head bob as her measured gait carried her forward. Even her light adornment – a simple azure bow with a matching sash fixed into a cummerbund – did not infringe upon the image that she projected: that of a perfect and proper attendant.

 

Though she lived in the rough and wild borderlands of the frontier and knew little beyond basic aristocratic conduct, the maid’s composure was such that Ludmila felt compelled to emulate the elements of her own form to match. As she did so, it invariably drew other comparisons between the maid and herself, which in turn fed into her growing anxiety. In figure and form; in grace and manner, Ludmila seemed to fall conspicuously short on every front. She knew that the royal family of Re-Estize practiced a custom which employed young, unmarried noblewomen from prominent families as maids in Valentia Palace, but she imagined that the woman gliding across the cobblestones before her would easily overshadow any of them.

 

It was said that the dignity and skill of a retainer reflected upon that of their master, both on the battlefield and in the court. If such an attendant served the Sorcerer King or even one of his vassals – no, especially if they did – then from what impossible heights of majesty did the Sorcerer King reign? She started to become lightheaded as her sense of self continued to shrink, and after they passed into the entrance of the Royal Villa, she finally felt the need to speak out.

 

“Hold–please, wait!”

 

The maid responded immediately, slowing as she made a seamless turn to face her. Even this simple action seemed almost too graceful to be possible.

 

This isn’t fair! Ludmila cried out despairingly in her mind. She felt unbelievably rustic in the face of her conduct.

 

For a moment, the maid examined her with an unreadable expression before smoothly spreading her skirts in a deep curtsey.

 

“This one goes by the name of Yuri Alpha,” her calm, mellow voice floated up in reply, “my most sincere apologies for not introducing myself earlier, Baroness Zahradnik.”

 

Yuri Alpha rose with a warm smile.

 

“How may I be of service?”

 

That the maid had misinterpreted her mixed expression put a slight crack in her perfect image, but Ludmila’s distraught sensibilities lingered.

 

“I cannot present myself to the Sorcerer King,” she said.

 

The taller woman coolly arched an eyebrow.

 

“Do you mean to say that you are refusing the summons of the Royal Court?”

 

Ludmila’s mouth fell open for a moment before she attempted to explain herself.

 

“I mean to say that I am not in a presentable state,” she said. “The clothes I am wearing are meant for travel on the open roads, my boots are soiled – I need some time to fix my improper appearance.”

 

She had covered quite some distance as she travelled with Momon, and she wasn’t about to present herself to her King in a dusty kirtle and muddy boots. Her hair had been under her scarf for hours and she didn’t even want to know what it had turned into along the way. Her mind went back to Countess Jezne and her reprimand – indeed, she had been the only noble in the room dressed in such a way; clearly unready to attend to official business.

 

Her bags had been taken away from the front desk of the clubhouse by a pair of maids that were instructed to deliver them to her accommodations, so she wasn’t sure where they had disappeared to. Once again, she had been swept along by events and left in a confused and miserable state.

 

“His Majesty is currently attending to business elsewhere,” said Yuri Alpha. “It is the King’s Council that will receive you on his behalf.”

 

The information was surprising, but Ludmila still dug in with the little bit of pride she had left.

 

“As they are acting on his behalf, then I must still conduct myself in the appropriate manner. I will not dishonour House Zahradnik by showing such disrespect to my new sovereign.”

 

Yuri Alpha remained silent, as if to weigh her words. A hand came up as she lightly adjusted the rims of her spectacles. As they shifted, Ludmila realized that there was no reflection of the light coming from the entrance to the Villa – the maid’s eyewear had no lenses.

 

“Very well,” Yuri Alpha said, “but as your presence was requested as soon as reasonable, we cannot spare more than a few minutes to ensure there is nothing untoward.”

 

It did not take long to find a well-furnished drawing room where Ludmila located a mirrored cabinet placed along a wall while Yuri Alpha drew open the drapes. She gingerly removed her scarf, but discovered to her relief that her hair had not become an entirely unruly mess after hours of travel. As she started to slowly comb her fingers through it, a small brush appeared over her shoulder – Yuri Alpha had come to stand behind her.

 

Ludmila received the comb with an expression of gratitude and started to brush her hair as Yuri Alpha worked to remove the bits of her journey that had stuck to her outfit. They worked in silence until Yuri Alpha rose, which prompted Ludmila to return the brush. Checking over herself one last time in the mirror, she felt like she was about to go fetch water from the river rather than attending an official audience with the King. The moist green odours from the woodland trails still clung to her – hopefully she wouldn’t be standing too close to anyone…

 

They returned to the hallway and resumed walking to the council chamber deep within the villa, and Ludmila looked to the grand friezes that lined the walls while she pondered how she should present herself. While the Zahradnik Barony was an independent fief under the Duchy of E-Rantel, Lord Rettenmeier had governed as Royal Provost while holding his position as Mayor of the city. He had a personality that belied his corpulent appearance, and the descriptions of his interactions with Baron Zahradnik – who shared the same straightforward and pragmatic personality – had spoken nothing of the pomp and circumstance that befitted a meeting with a sovereign.

 

Ludmila sighed as she faced forward again. They turned the final corner leading to the audience chamber, and Yuri Alpha led her to a row of seats placed along the wall opposite to the massive Ironwood doors that marked the entrance to their destination.

 

“Please have a seat, Baroness Zahradnik,” Yuri Alpha turned briefly to speak to her, “I shall enter and inform the Council of your arrival.”

 

Ludmila nodded in understanding, then settled herself on the nearest chair. The entire row seemed to be made up of the same low-backed hardwood stools with equally hard wooden seats – it was as if someone was saying don’t get too comfortable to those that waited on their appointments. Having been either on her feet or riding for most of the day, however, the opportunity to rest was welcome.

 

Yuri Alpha closed the council chamber door behind her, and Ludmila looked down the hall both ways before stretching, trying to relieve the tension that had wound up both her mind and body. As she did so, an unfamiliar woman’s voice could be heard in muffled tones through the door. It seemed to be the only voice coming through the door, actually. It droned on for several minutes before pausing, picking up again after a short silence, repeating the cycle over and over again. She imagined this is what she herself might sound like when she relayed instructions, outlined numbers and made recommendations in Warden’s Vale – even her own family looked for ways to escape after being subjected to too much of it at once. Unlike her family, however, she did not think any of the King’s Councilors would come bursting out into the hall in a desperate attempt to flee.

 

After what she thought must have been at least forty minutes, the woman’s voice stopped entirely after slowly losing its momentum over time. Ludmila rose from her seat and stepped nearer to the doors, anticipating her summons. She stood by patiently, ears straining for the approach of someone inside to come out and announce her entrance. The first sound she heard, however, was the rustle of cloth and the sound of vague movement, followed by a lilting, feminine voice that chimed from within.

 

“Well, if that’s all there is, I suppose I should find this Baroness Zahradnik.”

 

After a short pause, Ludmila heard the light tapping of heels slowly approaching the doorway at a deliberate and measured pace. The heavy ironwood doors silently swung inwards to allow a figure to drift out of the chamber and into the hall. Ludmila quickly checked her posture and made ready her greeting but was spared barely a glance; bright, crimson eyes briefly flashing over her from behind an exquisitely crafted fan. The figure turned without missing a step, the hem of her black gown swaying lightly over the polished marble floor as she made her way down the hallway.

 

Ludmila stood, mouth agape, her greeting left unspoken as she was passed by in a flash without a single word. She barely turned her head to observe the woman who had passed her when a wave of murderous ire billowed out from the still-open door. Terror froze her in place until her instincts compelled her legs to send her scurrying down the hall. She dared not turn her head to look into the room as she darted by, instead following after the woman who had long since disappeared around the corner that led out to the main hallway of the building.

 

It was only after the exit of the Royal Villa came into view that Ludmila slowed, struggling to control her panicked breathing. Amidst the wild pounding of her heart, she looked toward where the woman had continued forward – she had paid no mind to Ludmila’s flight down the hallway. Through the clear crystal of the inner doors, she spotted her standing in the vestibule of the building. Two other women had appeared from somewhere to stand beside her. Their sensuous curves were silhouetted by the light of the evening beyond the entrance, ivory figures draped in alabaster cloth.

 

One stepped forward to open the door as the fan in the first woman’s hand snapped shut and disappeared into her sleeve. At the end of the motion, the handle of a parasol appeared over her wrist. Ludmila blinked; the accessory had mysteriously appeared out of thin air without so much as a word or gesture, causing her to wonder if she had lapsed from fatigue after her long journey. The remaining attendant paid no mind to this unexplained phenomena, however: bending at the waist with her arms held out before her. Ignoring the offer of assistance, her mistress left the vestibule, opening her parasol with a smooth motion and bringing it to rest over her right shoulder before proceeding down the lane through the villa gardens.

 

The door whispered softly to a close as the two attendants assumed their places, following behind on either side of their mistress. Ludmila stepped forward to place her hands on the handles of the inner doors, then stopped. As her thoughts freed themselves of the haze of terror, she realized that while events had brought her to this point, she had no idea what she was to do now. The session of the Royal Court had apparently ended, but she was never brought in to present herself. No one had come to retrieve her, and the person that seemed to be looking for her had just walked away without a word. Was she to remain in the Royal Villa until whatever business she was brought in for was concluded? Should she continue following after the lady who had just left? Feeling completely lost, she wished Yuri Alpha or Momon would appear to explain what was going on to her.

 

“I suppose if woodlice become overly large, they cannot creep under doors.”

 

Just as she thought to look for Momon, cold and scornful words prodded her from behind.

 

She turned with a start, finding that Nabe had at some point come into the hallway behind her. She stepped towards the vestibule where Ludmila stood with her right hand still grasping the door, coming to a stop behind her. Long accustomed to her inhuman appearance, Ludmila removed her hand from the door and faced the Adamantite Adventurer. Empty eyes looked upon her from a featureless face, but the beautiful visage superimposed over it wore an expression that mirrored the tone of the words that came before. It occurred to her that this was the first time that Nabe had spoken to her directly, but her desire to clear her own confusion spared her no time to ponder how she had been addressed.

 

“Momon, where–”

 

Ludmila started to ask after Nabe’s partner, but was cut off abruptly.

 

“Momon has left to attend to business elsewhere,” Nabe said. “There is no reason for you to linger here.”

 

A finger tapped impatiently on the Adventurer’s hip. Nabe looked at her expectantly, as if she might conveniently vanish at the end of her sentence.

 

“What about the summons?” Ludmila asked, “The court seemed like it was adjourning…am I to follow the lady that just left, then? It sounded like she was looking for me…”

 

She still did not understand what was going on, so her words simply spilled out in the direction of the Adventurer as she asked weakly for guidance. Nabe succinctly provided an answer; the disinclined tone made it seem more like she was simply trying to get her out of the way.

 

“Lady Shalltear has claimed you in accordance to orders she has previously received from the Sorcerer King,” she said. “You are now hers – the Guardian Overseer has left your matters in Lady Shalltear’s hands.”

 

“Lady Shalltear? The King?”

 

Ludmila felt that the answer left even more questions, but as she parroted the Adventurer’s words, the tapping finger stopped and Nabe’s cold gaze turned into a glare.

 

“Woodlice should not be blocking doorways. Move.”

 

Nabe’s tone did not change, but Ludmila had the feeling that she would be swept out of the villa entrance like some unwelcome insect if she stayed to continue her queries. She turned and opened the doorway, stepping out into the evening air. The sun had crossed below the inner walls of E-Rantel, and the tall lamps of the central district now cast their light over the empty streets. As she walked through the gardens and down the path that led out of the front of the Royal Villa, the clink of metal on stone sounded from behind.

 

Ludmila turned her head to glance over her shoulder, and saw that Nabe was following behind. Passing under another lamp, the glint of light over some polished surface drew her attention to the fact that Nabe was not in the travelling garments that she had seen the Adventurer in earlier in the day. Nabe was dressed in a pitch black dress with some white frills lining its hems, but its many plated segments denied the notion that she might be simply going out to enjoy some part of the city. Ludmila had never seen an mage equipped in such armour before, but she had no doubts that the Adventurer was equipped for combat.

 

“Your armour…did something happen?” Ludmila attempted to start a conversation with the Adventurer.

 

To her surprise, Nabe responded.

 

“The Guardian Overseer has requested that I deal with an issue in the southwest.”

 

Ludmila’s pace slowed somewhat as she thought on Nabe’s words. Did she mean out on the frontier? From what she saw, the way back from Warden’s Vale had very little in the way of anything that suggested internal threats like bandits or roaming monsters. She raised her head from her thoughts as the Adventurer walked past her.

 

“If it’s something on the border…” Ludmila said, “is there anything I can do to aid you? I know the lay of the land around my barony fairly well, as well as the surrounding areas. If there’s some information you would like–”

 

“Lady Albedo has provided me with everything I require,” Nabe curtly cut her off.

 

Veering to the right, the Adventurer stepped onto the path leading to the gazebo where they had arrived earlier in the evening.

 

Ludmila stopped to watch as the mage stepped onto the raised floor of the structure. With Warden’s Vale abandoned, any incursion from the frontier would be met with no resistance, and Adamantite Adventurers were beyond the means of her family to hire. She could do little to repay the favour granted by Lady Albedo – the Guardian Overseer? – but, in her current situation, she could at least express her gratitude.

 

“Thank you for your assistance,” Ludmila bowed her head slightly in Nabe’s direction as the mage made preparations to depart.

 

Nabe turned to look back at her with a strange expression on her human visage. Several seconds passed before her face relaxed a bit.

 

“Lady Shalltear is not one to be kept waiting,” the Adventurer told her. “It is inadvisable to court her displeasure.”

 

With the parting word of caution, Nabe whispered a spell and vanished.