\chapter{Ludmila Zahradnik}

While the lumber merchant was away in his house, Ludmila directed one of her footmen to unload the wagon, arranging the Rosewood and Ironwood logs into separate piles. As Gareth’s muffled shouts continued to sound from within his home, she held up the sheet that he had handed back to her. She had struggled to maintain a neutral expression after seeing the merchant’s revised quote. She wasn’t sure if she was successful in the attempt, but now her expression went from anger to whimsy and back again.

 

“That’s an interesting show you’re putting on there,” Lady Shalltear noted. “I honestly can’t tell if you’re pleased or displeased.”

 

“I am satisfied with Mr. Boyce’s offer, my lady,” Ludmila explained, “but the value of the timber has connotations that make me furious.”

 

“If that’s you being furious, I think I was right about you transforming into a Golem.”

 

“I will not act inappropriately in public,” Ludmila sighed, “but I really do want to strangle this merchant my family has been dealing with all these years.”

 

Lady Shalltear turned to look up at her, head tilted curiously.

 

“That sounds more like something that I should be doing,” the chime in her voice was at odds with the violent nature of her quip. “What is it that drives the very picture of Human composure to such anger?”

 

“These numbers here represent last year’s market prices,” she turned her inventory-sheet-turned-invoice towards the inquisitive Vampire. “They are seven times higher than what we were offered by the merchant last year for the same timber.”

 

“It seems that you were cheated,” Lady Shalltear said.

 

“Yes! Well, no. Not exactly.” Ludmila quickly corrected herself, “Mr. Boyce said that this merchant included the costs of an Adventurer escort and labour, presumably to keep up the image that it was his own venture and he was shouldering all of the risk. A party of Adventurers powerful enough to force their way through the southern wilderness and maintain a safe environment for this sort of operation should be at least Mithril rank. The cost of having a party of Mithril rank escorts for weeks at a time was assumed to be a part of the market price listed here.”

 

Lady Shalltear stared blankly at Ludmila’s words. Ludmila attempted to expand on them, and in doing so she became increasingly annoyed.

 

“There was little risk for this merchant,” she said. “Minimal investment with no venture. Like Mr. Boyce said, it was pure profit for him and he had us all dancing to his tune. It is a surprise that no one in the Merchant Guild even checked with the Adventurer Guild to see if there was actually a Mithril-ranked Adventurer team holding such long contracts. He saw an opportunity and gambled on the hope that no one would catch on to his scheme, and he won. I can’t even blame him, even though I feel like it – we all willingly accepted his business without question, so in the end we cheated ourselves. I have been helping out with demesne business for several years now, and this possibility only occurred to me after Mr. Boyce essentially wrote it down and handed it over. I am just as guilty of this same oversight that has been plaguing my House.”

 

“How long have you been dealing with this merchant?” Lady Shalltear asked.

 

“That’s the worst part. My father had been doing business with this man since before I was born,” she felt her voice taking on a tinge of anger, “this has probably been going on for generations.”

 

“Generations? Was this merchant an Elf?”

 

“No, that’s not what I meant,” Ludmila said. “It has to do with these market prices. Look at the numbers.”

 

“I don’t know how you value things around here. Is it that much more than it should be?”

 

“That is a colossal understatement,” Ludmila wanted to laugh ruefully. “Warden’s Vale would be at least a large town supporting dozens of villages throughout the barony if we had these prices for the last century. We would have been able to grow so quickly, developing more land and expanding our holdings. Even if the other Frontier Nobles had lost their fiefs, we could have simply fortified the entire border on our own with the growth that these numbers represent. Well, that is perhaps slightly optimistic, but with that length of time, House Zahradnik might have been as prosperous as the nobility of the interior. Instead, we simply scraped by in our ignorance for generations, content with our simple lives when we could have been performing our duties so much more effectively.”

 

“The way you put it, it really does sound miserable,” Lady Shalltear said. “You’re sure you don’t want revenge on this merchant? I could help you hunt him down, and we can make him suffer slowly for his wrongdoings. It would be quite satisfying, yes?”

 

Aemilia, who had come to see what her mistress’ fuming was about, nodded energetically to her side.

 

“I agree! I can’t believe such good people could have this happen to them.” She balled up her fist and held it up with a fierce expression, “We should find him and get payback.”

 

This time Ludmila did laugh, albeit softly. The image of her unexpectedly vicious lady’s maid who was deathly afraid of the Undead teaming up with a powerful Vampire was too ridiculous.

 

“No,” Ludmila shook her head. “It is not worth pursuing now, and he is only one of many merchants that probably took advantage of our blind trust. Now that I know, I will figure out how to prevent this in the future. I can only move forward now and work on transforming Warden’s Vale into what it was always meant to be.”

 

After the words passed from her lips, Ludmila felt embarrassment creep up her neck at how she must have sounded, considering she had yet to really do anything herself. However, Lady Shalltear gave her a look of appraisal while Aemilia’s eyes sparkled at the statement. The loud sound of the house door being shut dispelled the atmosphere, though, with Gareth hobbling out towards them with a gangly youth.

 

The ‘boy’ who had been described as ‘half a man’ was near full grown, perhaps one or two years from being considered an adult. He had a similar enough appearance to the lumber merchant, though the boy was still all arms and legs. Upon seeing the group of women, he kept looking back and forth while blushing vividly – his father seemed to have the right idea about what would entice him to leave their home.

 

“Sorry for the wait,” Gareth held up a small block of wood that appeared to be a stamp. “I’ll just stamp that there and you can head over to the Guild for your payment.”

 

“Thank you,” Ludmila said as she received the stamped invoice, “do you know which Merchant Guild branches are still doing business?”

 

“That’s a good question,” the lumber merchant scratched his chin. “Your best bet is probably the head office in the main plaza. You should get the rest of your inventory settled first though, so you can get paid out all at once.”

 

“That seems reasonable enough.”

 

“Right. It’ll be a bit to offload your cargo so you might want to check out some of the shops nearby…ah, what am I saying, no one’s open.” Gareth turned and shouted, “Boy! Quit your gawking and roll out the gantry.”

 

Gareth’s boy jumped at his father’s voice, blinking a few times before pointing to the ground at the log piles. After seeing all the cargo neatly laid on the ground, the older merchant swung around, looking back and forth between the women in the yard.

 

“How the–”

 

“My footmen offloaded the cargo while you were in the house.” Ludmila explained as she directed the Soul Eater to take the wagon back out of the yard, “they are back out of the alley now.”

 

“Footmen strong enough to carry logs like that, huh. Retired Adventurers? Well, you ladies would want at least that much to feel safe travelling around the city, I suppose.”

 

While their attendants filed out with the wagon as it left the yard, Ludmila remained to ask a question.

 

“I will probably return with more timber,” she said to the lumber merchant, “will you be available to do business in the near future?”

 

“Hmph,” Gareth grunted. “If what the lady here says is true, it’ll be a seller’s market soon enough. But yes, I’ll be here if you need me.”

 

“I will be sure to drop by again,” Ludmila paused. “By the way – what happened with your leg? Have you had the priests take a look at it?”

 

“Nah, it’s an old injury, back from when I was a lumberjack,” his tone was dismissive as he replied. “Damn tree fell the wrong way for no reason – must have gotten on the bad side of a damn Dryad or something. I was too stubborn to go back to town and have a priest look at it, and my leg ended up healing funny. That’s how I ended up in this business – priests said there’s nothing to be done about it after I finally did get around to visiting a temple.”

 

Ludmila looked to Lady Shalltear.

 

“Is that true, my lady?” She asked.

 

“No,” the Cleric replied.

 

“You saying the priests lied, lady?” Gareth frowned and narrowed his eyes.

 

“Probably not on purpose, no. Let’s just say the solution would be what you consider ‘inhuman’.”

 

Gareth had a sour expression on his face. He shifted his weight around several times before speaking again.

 

“Out with it then, lady. How can the priests fix my leg after it’s already been healed up?”

 

“They can destroy your leg,” Lady Shalltear’s words came out simply, “and regenerate a new one.”

 

Both Gareth and his boy blanched at the casually offered solution.

 

“That’s some evil thing you’re saying, lady,” the lumber merchant said in subdued tones.

 

“From a certain point of view, I suppose.” Lady Shalltear smiled slightly, “If an ally loses a limb in the heat of combat, a Cleric would most certainly act to heal their injuries – if it was within their capacity to do so.”

 

She pointed her finger at Gareth’s leg.

 

“You are injured,” she told him. “If nothing is done, you will carry that injury with you for the rest of your life. Should your priests not endeavour to relieve you of your hardship? Or is your suffering such a good thing that it would be evil to relinquish you of it?”

 

The lumber merchant stared at the point of Lady Shalltear’s finger, wrapped in its white silken glove, for a long while. He swallowed loudly before speaking again.

 

“I’ll see what the priests have to say,” he said.

 

“You do that. I would be most interested in hearing their answer.”

 

Lady Shalltear turned to exit the lumber yard and Ludmila followed after her, leaving Gareth Boyce alone in the yard with his boy.