\chapter{Ludmila Zahradnik}

Thirty minutes later, Ludmila slouched in a daze on the wagon. More so than any work she had done during the day so far, the half hour with Count Völkchenheim had been stressful and draining.

 

“Say, my lady,” she asked tiredly, “was Count Völkchenheim using some sort of ability?”

 

Lady Shalltear, who had assumed her seat beside her, shrugged.

 

“Who knows, I didn’t feel anything.”

 

“You said mind-affecting abilities have no effect on you, did you not?”

 

The Vampire shrugged again, and Ludmila groaned.

 

“Fine, whatever.” She tried to perk herself back up, turning to the Elder Lich, “Who do we have next?”

 

“Baron Victor Beyron Dale Ardoin, guest house twenty-three.”

 

“Lady Shalltear…” Ludmila began tentatively.

 

“Yes?”

 

“Maybe I should just go with Luzi for the next one.”

 

“Did I just hear ‘wait in the wagon’?”

 

“Thirty minutes, my lady!” Ludmila complained, “It took thirty minutes to get what we needed out of that overeager–rrgh! Lady Corelyn only took five!”

 

It had all started innocuously enough.

 

Lord Völkchenheim had been all courtesy and smiles, eager to listen to what their request was. Except he kept trying to invite them in for tea. Or lunch. Or to gaze upon the beauty of the gardens or ‘discuss the future’. The young man was around the age of Ludmila’s brothers, so she had expected maybe something, but her patience quickly wore thin. He wouldn’t take his eyes off of Lady Shalltear, all the while constantly fixing his posture, straightening his clothing or trying to pat down an imagined tuft of unruly hair that wasn’t actually there – which had the effect of further undoing the efforts of his hurried grooming with every attempt.

 

Whenever any of Ludmila’s questions finally got through to him, he wouldn’t turn to respond – he would simply speak as he gazed at Lady Shalltear, spewing forth copious amounts of archaic, flowery language while listing addresses and names in an effort to impress his eloquence upon her. Lady Shalltear simply smiled, leaving Ludmila to do all the talking as she observed the exchange. It had become infuriating to the point that she itched to reach out with both of her arms and twist his head over to actually look at the person with whom he was conversing with.

 

She held back – as a Baron could hardly raise their hand against a Count – but, in that moment, she thought if there was ever a reason to advance in court politics, it would be to gain the authority to act against those that had taken leave of their senses. In the end, she had mentally limped away from Völkchenheim’s residence, with his valet Andrei looking on apologetically.

 

“At this rate,” Ludmila muttered darkly, “we will not be done collecting contacts until tomorrow evening. Your appearance is simply too dazzling, Lady Shalltear.”

 

“I could change forms,” she offered. “I’m nice and calm again, but all I’d need is a little bit of blood to help me set things off.”

 

“They would collapse before answering anything.”

 

“Then how about I just dominate them?”

 

“Using magic to procure statements is treated as collecting information under duress, my lady,” Ludmila said. “It is illegal under the Crown Laws and a violation of common regional conventions.”

 

“I broke a law of the Sorcerous Kingdom back in the civil office?” Lady Shalltear turned her head to look up at Ludmila.

 

“I said what I was going to say anyways, my lady, so I will not press charges.”

 

“Well it’s a silly Human law anyways,” Lady Shalltear sniffed dismissively, “we should have it changed.”

 

Ludmila looked over at Lady Shalltear incredulously. She had drawn her fan from somewhere and now held it open in front of her face with a coquettish look in her eyes.

 

“No,” Ludmila said flatly. “People will think that you are flirting with them if you do that. Well…maybe if you drop the look it might work.”

 

The crimson eyes behind the fan seemed to droop a bit.

 

“We should move on to the next manor,” Ludmila ordered the Soul Eater to their next destination, “Count Völkchenheim has taken up too much of our valuable time.”

 

Fortunately, Baron Ardoin had not turned out to be the next Count Völkchenheim – perhaps he would have, if he hadn’t been twelve years old – and they were able to get some of the information that they needed in a few minutes after he had been coaxed to open his door to speak to them. By the middle of the afternoon, they had visited all of the nobles that were currently residing in the city and Ludmila looked over the long list of names and addresses, trying to determine their best prospects.

 

Countess Jezne was particularly helpful, pointing out a couple of ‘especially hard-headed lumber merchants’. Ludmila thought to start there as they rolled out of the administrative district while she munched on the sandwich Aemilia had handed to her for the short trip. The food had been left for so long that the sauce Terah made soaked into one side of the bread, which just so happened to suit her tastes.

 

As the wagon slowly trundled through the city streets, she spotted a few onlookers peeking out of their windows at the noise before they vanished at the sight of the Undead in their entourage. The roads were still empty of citizens, but it was more life than she had seen on the main streets the evening before. The thoroughfares of the common area, while paved, were rougher than the well-maintained cobblestone pavement of the central district, so the long freight wagon occasionally bounced and stuttered as it ran over the cracks and holes in the street.

 

A few Elder Liches flew by overhead, looking down at the noise of the wagon. They were nearly indistinguishable in appearance from her attaché, so she wondered whether it could fly as well. It wasn’t until she looked down at its feet that she realized it had been quietly floating alongside the entire time as it took notes in its leather tome. The footmen following after the wagon continued their heavy tread, and she could hear Aemilia in the back of the wagon continuing in her efforts to converse with the Vampire Brides.

 

Once Ludmila completed her meal and put away the basket, she turned to Lady Shalltear to speak.

 

“My lady, does the Sorcerous Kingdom have any ships?” She asked.

 

“Hmm…maybe?” Lady Shalltear said, “I’d have to check back home. The Underground Lake should have a few, but I’m not sure if we can lend those to anyone. Why do you ask?”

 

Ludmila had no idea where the ‘Underground Lake’ was, but explained her situation anyways.

 

“Have you tried searching for it?” Lady Shalltear asked after listening to her issue, “If it’s a ship, it should still be somewhere along the river, shouldn’t it?”

 

“The land route from Warden’s Vale to the western highway doesn’t follow the river,” Ludmila said, “so we did not have the opportunity to look for it on the way here.”

 

“I can send a few members of my Household to check the river while you try to find merchants for your goods,” Lady Shalltear offered.

 

“I would greatly appreciate the assistance, my lady.”

 

A small swarm of black bats appeared from the shadows on the road, chittering and fluttering over their heads.

 

“What does this boat look like?” Lady Shalltear asked.

 

“A ship with a single sail,” Ludmila said. “As far as I know it is the only large vessel that operates on the river.”

 

Upon hearing her rough description, the bats veered southwards and disappeared over the shingled rooftops of the city. The Soul Eater continued driving the wagon, down the gentle incline of the main streets as they rode further from the city centre. Eventually, the road opened up into the main plaza, which was the largest of the open spaces that dotted the city and the closest one to the gate of the administrative district.

 

To their right was a cathedral and, to the north of it, the Adventurer Guild. Both buildings appeared to be open, as opposed to the many others bordering the plaza with their shuttered windows and sealed doors. She did not see any Adventurers in front of the Guild, nor did there appear to be anyone around the cathedral. Looking at it, she was reminded of Bohdan who had led the villagers south into the Theocracy; she wondered how they were faring in the foreign land, and how she might be able to have them return now that it seemed that their flight had been a needless one.

 

The wagon continued following the street, crossing between the large fountain in front of the temple and a tall column which dominated the plaza. Streetlamps were set apart evenly around the square, and Ludmila noticed many conspicuously open spaces where market stalls of various sizes should have been. The empty state of the city plaza seemed especially lonely, now that she knew that the buildings all around were most likely fully occupied, their tenants too fearful to leave their homes.

 

The Soul Eater turned after passing the fountain, cutting across to where the street left the plaza from its southwest corner. They traveled several more blocks until the wagon turned into an alley to stop beside one of the branches of the Merchant Guild. The building looked no more promising than those around it. The windows on the main floor were not simply shuttered like the ones on the second and third floors, but boarded in an effort to prevent the looting that often accompanied a hostile occupation. The hollow in which the door stood was shadowed and unwelcoming.

 

“I don’t hear anyone inside.” Lady Shalltear noted.

 

“...you can hear inside this locked-up building?” Ludmila looked at her.

 

“Yes. I don’t have any specific skills in search or detection, but I do have keen senses – especially when it comes to certain scents and hearing in general.”

 

“How are you not driven to distraction listening to thousands of people all around you in any given part of the city?”

 

“The same as anyone else, perhaps,” Lady Shalltear shrugged. “Do you have trouble with your perception when you are in a crowded street? Let’s keep going.”

 

They made several more stops, finding those buildings unresponsive or empty as well, before finally reaching an address that appeared to be occupied. It was the home of one of the merchants that Countess Jezne had noted was ‘especially hard-headed’. When the Soul Eater stopped in the alley beside the wattle and daub house, she saw that there was a gate that looked to be an entrance to a large lumberyard. Ludmila peered between the bars of the gate: beyond, it looked like the yard had been mostly emptied. There was a man walking around the few remaining piles of timber with a board in hand.

 

Ludmila stepped down and went to stand outside the gate, but couldn’t see any chain to pull or bell to ring. She rattled the gate to get his attention, but either he was too far to hear, or too hard of hearing to notice. She finally resorted to using her newly-learned ability.

 

“Gareth Boyce.”

 

She spoke at a normal volume, but the man jumped with a startled shout anyways, looking all about him for the source of the voice. For some reason, the gate where they stood was the last place he turned to. He hobbled forward, scratching his head. He was perhaps in his fifties, with leathery sun-baked skin over his tall and wiry form. His skinny neck, sharp nose and nest of unruly and fading red hair made Ludmila think of a woodpecker. He peered through the gate at the women assembled on the other side.

 

“This is a lumber yard,” he called out far too loudly for the short distance between them, “not a boutique.”

 

“I would not have called you by name if I did not know where I was,” Ludmila replied.

 

“Fair enough, miss,” the man conceded, “what can I do for you? As you may have noticed, there’s not much to buy here. The Royal Army bought up most of it during the winter. Not that it did them any good.”

 

“What do you have left in inventory?”

 

“The expensive stuff, mostly,” he immediately replied. “The army took all the cheap timber for firewood. There were some things that needed fixing in the military district as well when they came in at first.”

 

Ludmila winced. Most of the timber that had been chosen for delivery to the capital from Warden’s Vale were luxury goods that usually fetched a high price. There was no helping it, however.

 

“I’ve brought a wagon with several tons of timber to sell,” she said as he continued to stand across the gate from them. “Countess Jezne recommended you to me as someone that would continue to operate even with the city as it is right now.”

 

“Countess Jezne? Her boy is gone then…that’s a damn shame. That old harpy was right though, up to a point,” the gate rattled as he stepped forward to unlock the heavy padlock holding the gate chained shut. “Can’t do any business with an empty yard.”

 

The last of the links slid off with a clatter, and Gareth pulled the gate open after hanging up the chains. He dusted his hands off as he stepped into the alley.

 

“Alright then,” he said, “let’s see what you have.”

 

Ludmila waved her hand to the Soul Eater at the entrance of the alley, and it brought the wagon forward.

 

“My driver is bringing the wagon in,” she warned Gareth, “you may want to step out of the way.”

 

The Soul Eater deftly brought the long wagon into the dusty lumber yard from the narrow alley, making a small loop to face the gate. Gareth backed away wide eyed as it did so, hurriedly stepping well out of its path. Aemilia and the Vampire Brides hopped off of the back of the wagon after it stopped. The two Death Knights stayed to stand watch at the entrance of the alley to the street, and Ludmila did not see the Elder Lich anywhere until she looked up and saw that it had flown high above them. The ghostly figure of an Imp sat on a portion of the fence a few paces away, intently looking down at her.

 

Ludmila leafed through her folder, locating the page listing the timber inventories that had been transported to the city. She stepped over to the owner of the lumber yard, who was still standing a short distance away in the alley.

 

“This should be everything related to your business,” Ludmila proffered the sheet of paper, “let us know what you can offer for it.”

 

Gareth absently took the sheet and looked down to read it. As his eyes scanned over the inventory, his brows furrowed as he turned his head back up to look at the wagon. The man hobbled back into the lumber yard, circling around the wagon to look inside. His pace slowed somewhat when he encountered Aemilia and the Vampire Brides; after a moment he shook his head, muttering something unintelligible as he pulled himself up into the back of the wagon.

 

They watched him work from the ground behind the wagon – he slowly tracked over the wagon bed, occasionally leaning over to run his hand over the tree trunks or kneel to inspect their cross sections. When he reached the front of the wagon, he stopped to look over two trees that appeared to have been kept whole. He leaned over to rub his hand over one of the smaller branches, bringing his palm up to his face. He shook his head once again while muttering to himself.

 

Ludmila took a step back to give Gareth room to come down from the wagon, looking at him expectantly.

 

“Where do you come from, young miss?” The lumber merchant kept his eyes on the inventory sheet, running them down the list again.

 

“Zahradnik Barony,” she replied simply.

 

“So that’s where that bastard got his stock…” Gareth was half-muttering again, then noticed the questioning looks he was getting. “You came with Jezne’s recommendation, so I figured you for the daughter of some magnate from her territory learning the family trade. We haven’t gotten any new timber all winter, and the merchant inventories are all dried up.”

 

The merchant pulled a stick of charcoal out from behind his ear and started to scribble on the paper.

 

“Anyways,” he didn’t look up as he wrote, “there’s another guy in the guild who always turned up with all the expensive stuff like you have here. Kept it all hush hush – he was pretty proud that he could produce wood that no one else was able to. We all thought he was undergoing some reckless operation; all of the timber you have in your wagon doesn’t grow around E-Rantel.”

 

“It doesn’t?” Ludmila was familiar with her own territory, but wasn’t sure of other places in the duchy.

 

“Nope,” he said, “too wet, or not warm enough. Jezne County exports a lot of timber, but it’s the type used for regular construction, mostly. Everything here should be from the southern slopes of the border ranges or even further. That’s why we thought he was doing something risky – hiring Adventurers and the like to guard his teams while they harvested in Demihuman-infested lands. Turns out that he probably got it from you folks.”

 

“Where is this merchant now?”

 

“Gone. He got pretty rich trading this for years on top of all of his other business – we all thought he was including the overhead for everything needed to safely get this inventory, but seems like it was pure profit for him. He pulled up his roots and moved to some nice city in the north of the Empire to retire with his family before the winter.”

 

“I see…so what is it actually worth?”

 

Ludmila was sure she wouldn’t like where this seemed to be leading. Gareth finished writing on the inventory sheet, and handed it back to her.

 

“Like I was saying before,” he said, “the army cleaned out all the cheap lumber to use, so I need to restock on that for whenever business picks up again – you don’t have any here, though. You have a lot of Rosewood; but that ain’t what we need now. It’s used for good furniture, expensive paneling and fixtures – fancy doors, windows, railings and the like. Carvings, perfumes and instruments as well. I can take it off your hands, but I can’t give you last year’s prices for it; it’ll take a long time to use it all up with the way things are, or maybe I’ll have to find a buyer for it elsewhere…if caravans will even come to the city any more.”

 

Ludmila couldn’t help but frown, the Rosewood logs were two-thirds of her timber.

 

“You’ll have a shortage of it soon, I think.” Lady Shalltear spoke from beside her.

 

“Oh? And who might you be, young miss?” Gareth folded his arms over his chest.

 

Ludmila wasn’t sure what results the man’s casual attitude would produce, so she interjected on her behalf quickly.

 

“Lady Shalltear is a close confidante of the King,” she told him. “I have not heard anything about this though. What did you mean by this, my lady?”

 

“‘Close confidante…’”

 

Lady Shalltear repeated the words, her expression turned strangely loose. After a moment, she realized that there were others watching her and she straightened her face, clearing her throat lightly.

 

“The section of the city containing the slums has been cleared out and cordoned off, by order of the Guardian Overseer. It’s being torn down as we speak.”

 

“Why would she do that?” Ludmila had a worried expression, “thousands of people live in that part of the city – where will they go?”

 

“Because it is a monument to failure,” Lady Shalltear spoke sternly. “Or at least that’s how the Guardian Overseer described it. Its very existence is offensive, a mark of shame against those of the previous administration. The leaders of this city were charged with its management, and the fact that such a construct had manifested is proof of their failure at doing so in a fully productive manner. Pending certain results, the displaced population will be relocated to the rural regions to work the lands to the northeast that have been abandoned in the past year. For the time being, they are being housed in other parts of the city and provided for.”

 

“That’s big talk, lady,” Gareth’s voice was grim as he digested her words. “I’m no great lord, but from where I stand, that’s something not even Lord Rettenmeier could do with the old king’s support. So what does this have to do with the shortage you’re talking about? You all plan on building something?”

 

“That’s right,” if Lady Shalltear took offense to the merchant’s attitude, it did not show. “The entire city quarter is to be repurposed into an area for Demihumans, and it will be fashioned in such a way that those with various needs not provided by Human accommodations can live there comfortably. You will not want for demand in the near future.”

 

Gareth was silent as he considered her words, shifting slightly on his feet. When he looked to have made up his mind, he turned and looked about to spit on the ground, but decided against it in the presence of all the women.

 

“Fine,” he said. “If your tip turns out, it’ll be busier than I’ve ever seen in my life. I’ll have to let the guild know as well, there’s no way I can keep up with just my yard.”

 

“Then the Rosewood…” Ludmila said tentatively.

 

“Last year’s prices,” Gareth told her. “It’s still a lot to use up – we’re going to need a lot more of the timber that’s needed for construction, if you’ll let Countess Jezne know. The Ironwood I’ll gladly take as well; the army took that to use for their weapons. I won’t take the Sandalwood though, that’d be a waste – you’re better off selling it elsewhere.”

 

“Where should I go with it?” Ludmila was barely keeping up with the change in direction, “Do you know anyone that would buy it?”

 

Gareth snorted derisively.

 

“If they’re as old as they look, the Alchemists and the Jewelers will be fighting each other over who gets to buy it. So, do we have a deal?”

 

“This is fine, I think…”

 

Though the prices that he offered were attractive, Ludmila wasn’t really certain whether they were correct or not. However, she didn’t think she had much of a choice with the city as it was.

 

“Good, I hate haggling.” Gareth turned and shouted in the direction of his home, “Boy!”

 

His voice echoed off the alley wall, carrying over the roofs nearby.

 

“BOY! ...Gods damn it. Half a man and he’s still jumping at shadows. I’ll be back with my seal,” Gareth limped off in the direction of his house “Boy! There’s some pretty girls in the yard waiting for you!”

 

With a loud bang, the back door of Gareth’s house slammed shut behind him.