\chapter{Ludmila Zahradnik}

According to the Elder-Lich-turned-clerk, it would take half an hour to process their request. Ludmila was directed to one of the alcoves to wait to be called upon. It had enough room to seat four people on its cushioned benches, with a magical glass lantern that cast its light over the polished wooden table. With a sound resembling a light grunt, Ludmila set all of her things down, pushing it towards the wall. She waited for Lady Shalltear to be seated before taking her place across the table from her.

 

“Do you think things will go well, my lady?” A shadow of doubt still played across Ludmila’s mind after she had submitted her requests, “It seemed a bit too easy.”

 

“The clerk submitted your documents to be processed,” Lady Shalltear shrugged. “There are not many layers of bureaucracy to get through…there should be someone that double checks your documents, then another who organizes the orders. Like I said earlier, these Elder Liches are newly trained, but they are eager to prove themselves useful in their service to His Majesty. It would consider any errors on its first official job absolutely unacceptable.”

 

“So you do know how things work,” Ludmila said.

 

“I know bits and pieces here and there,” Lady Shalltear admitted, “I’ve been…placed on standby for the last little while, so between ensuring my territory is secure and seeing to the realm's logistical needs, I've had a lot of free time on my hands. I wander the city and the realm, watch what goes on and sometimes I do some things for myself, but I would much rather be serving His Majesty directly in some way.”

 

Lady Shalltear seemed a bit sullen as she spoke, and her downcast manner made Ludmila frown. Once again, her liege acted in a way which seemed very out of place with the quality of the woman who had graciously taken Ludmila under her wing.

 

“Well, I for one am appreciative of your time on my behalf, my lady,” Ludmila said in an attempt to pick up her spirits, but she didn't think the gratitude of a relative nobody counted for much.

 

“Hmph, spare me the flattery,” Lady Shalltear rested her cheek in hand. “The Royal Court has been working hard to carry out His Majesty’s Will. In His infinite wisdom, He has given us the time to fulfill His wishes, but that time will be over sooner or later. We must present to Him a thriving realm, and we dare not disappoint Him. You are simply a means to that end.”

 

“Then what is His Majesty’s Will?” Ludmila asked.

 

“You were there yesterday, were you not?” Her liege answered, “What I declared to the people in the city are His wishes for the Sorcerous Kingdom.”

 

“But surely that can’t be all?”

 

There was a long pause between them. Lady Shalltear traced a circle over the surface of the table as she thought on what to say.

 

“Well…His Majesty is truly unfathomable,” she replied, “so it is only what we have discerned from both His stated intentions and His actions. He desires a realm where all peoples can thrive and prosper. A nation that can shine as a testament to His mercy, wisdom and glory to the rest of the world. Lord Ainz has the power to turn these territories into a blasted and barren wasteland, yet He chose to grant a swift and decisive end to those who would oppose Him and presented a hopeful future to His new subjects. As His loyal vassals, we cannot understand – in our eyes, the Humans of this realm are repaying grace with spite.”

 

Ludmila felt a pang as Lady Shalltear lamented the current state of affairs. To have one’s goodwill and effort go unappreciated and perhaps even scorned was not something anyone could feel pleased over.

 

“I assure you that is not the case, my lady,” she said reassuringly. “You might not trust the people of the city when they say so directly, but you should not let this sentiment fester in the Royal Court without confirming whether it is true or not. Admittedly, I have only been here a short while, and I do not know everything that goes on in the city, but not once have I heard anyone – not the nobles, nor the common folk – speak in ways that I would consider spurning His Majesty’s goodwill.”

 

Lady Shalltear watched her carefully as she spoke, yet somewhere along the way, her expression started to sour.

 

“Is something the matter, my lady?” Ludmila spoke carefully as a scowl began to form on the Vampire’s face.

 

“Then why?” The question was delivered in a low voice, a growl from a beast about to pounce on its prey.

 

“I-it’s because–” she stammered as she watched Lady Shalltear’s appearance shift, the ethereal visage of delicate beauty melting away, leaving only the menacing image of her true form.

 

“WHY?!” The Vampire’s voice had turned into a rasping, malevolent hiss, filling the alcove.

 

Ludmila was about to glance beyond the secluded space to see if anyone was watching, but the crimson glare flared and her will was forcefully wrested away from her before she even knew what was happening. Dozens of rows of needle-like teeth came close, and the tinge of blood filled the air.

 

“Tell me!” Lady Shalltear’s voice came out as a sibilant whisper that slithered into Ludmila’s mind, “Tell me the truth. Tell me why these Humans continue to defy the Will of Lord Ainz!”

 

“They are not defying His Majesty’s will,” Ludmila felt her own voice come out in response, flat and emotionless, “they are only scared. It is only fear.”

 

“This is a lie! A lie! Fear? What is there to fear? Are His precious words not enough for you? Do you believe it to be deception? Tell me, is it hate? Do you hate Him? He, who has granted His infinite mercy to you – to us?!”

 

As the questions broke over Ludmila one after another, Lady Shalltear’s voice rose as her words turned into accusations. A tear rolled down the pallid flesh of her cheek at the last as she howled at her.

 

“I would strike you all down for your insolence, if not for His order to stay my hand. Turning this entire world into a sea of boiling blood would not nearly be enough to pay for your scorn!”

 

“It is not a lie," Ludmila said. "It is not distrust; it is not hate. It is fear…and we are only Human.”

 

For long moments, Ludmila was pinned in place by the Vampire’s gaze. She watched as the image of Lady Shalltear’s beautiful form eventually returned, superimposed over her true appearance. As she pulled back from leaning over the table and settled into the cushions of her seat, Ludmila felt herself being released from her liege’s mental hold. Across from her, Lady Shalltear was drying her tears with a handkerchief that she had pulled from a pocket inside her bolero. Several minutes passed in silence, before Lady Shalltear spoke tentatively.

 

“I...I...was just thinking about my Lord’s wishes,” she said, twiddling the silken handkerchief in her fingers. “About how nothing ever seems to go in the right direction…and I lost myself. You will forgive me.”

 

“You are forgiven,” Ludmila replied in a flat, emotionless tone.

 

The fingers stopped and she looked up at Ludmila, squeezing her eyes shut tightly and opening them again as her eyelids fluttered and her slitted pupils dilated. Realization that Ludmila had imitated a charmed voice dawned over her face.

 

“That’s not funny!”

 

Lady Shalltear tried suppressing a laugh, but failed; the effort resulting in something halfway between a laugh and sob. She sniffed, then blew her nose loudly into her handkerchief. Ludmila waited quietly, attempting to reassert her usual mental state before speaking.

 

“When we spoke yesterday,” she said, “you expressed the state of the citizens before I could even share my thoughts on it. You always speak of your service to His Majesty fondly, and I don’t think anyone could question your devotion when they hear you. If I found something that inspired such conviction in me, I think I might become furious as well if something like this happened.”

 

“I swear…if you keep up with that unwavering coolheadedness of yours,” Lady Shalltear said, “you’ll turn into a Golem one day.”

 

“…is that even possible?”

 

“No. Not like that, anyways.”

 

Ludmila wondered if Lady Shalltear was trying to get back at her for her prank. The thought brought her back to what had occurred between them.

 

“That ability that you used just now…” She asked, “Is that what it feels like every time I use my own on Luzi?”

 

“What, are you trying to make me feel guilty?” Lady Shalltear made a face, “No, that was an ability that Vampires possess. Our power to charm others has to do with the supernatural nature of our race. Your abilities have to do with your own race: Humans have a social caste that specializes in administration and leadership; so your Nobles have abilities related to their role in Human society. Demiurge – one of the most intelligent of His Majesty’s servants – speculates that every race with a ruling caste will have their own classes along the same vein as your Human aristocracy. He also speculates that races that have become overly reliant on the abilities of their ruling class can be easily disrupted by eliminating them at opportune moments, or better yet – by taking control of them in some form and having them lead in a manner that suits our objectives.”

 

Ludmila felt that talking about usurping those in leadership while sitting in a government office seemed terribly wrong, so she steered the conversation in a different direction while nervously looking towards the reception counter.

 

“Still, telling people to do something and having them act as a result of an ability,” Ludmila mused. “Even Countess Jezne only seemed to be able to encourage the nobles around her to collect themselves...if that was even her ability at work. I still can’t tell whether one has been persuaded to act through normal means or through the use of an ability.”

 

“Yes, that’s something interesting I noticed as well,” Lady Shalltear said. “What you did was not just subtly influencing others, but reinforcing them and ordering them into action. This is something that those with Commander classes do, but as of yet, we haven’t encountered any other Nobles that have demonstrated active command abilities. We know that Commanders exist amongst Humans at large – Carne Village reportedly has a Farmer girl with the ability to do so, but this arose out of a decidedly strange set of circumstances. Since Humans appear to have many classes that are unfamiliar to us, I think you may have something along those lines.”

 

Ludmila already knew how she was going to reply – it had been under her consideration for a while now.

 

“There is something you said earlier: to think about what people notice that I never considered truly special. More than a few have mentioned nobles from the frontier as being…beyond the rest of their peers – that we were made differently, somehow. My maids said something along these lines shortly after we were first introduced and they entered my household.”

 

“Oh?” Lady Shalltear straightened in her seat, “This is a promising lead. What did they say, exactly?”

 

“Aemilia said that I could brave the city streets when none of the other nobles were capable of doing so,” Ludmila made an account of her memories, “even after said nobles had worked up the courage to try. That I appeared like a gallant warrior, ready to fight at any time. Countess Jezne said she had expectations of me, though she never elaborated on what she meant. Bohdan – the village priest in Warden’s Vale – remarked that I shared a similar trait with my ancestors: the willingness to face danger with a resolute will and he, too, told me that the people of the frontier were different than those of the interior. My parents said many things as well, but all noble parents seem to teach their children that they are superior in some way…I never really considered it seriously until now.”

 

“So is it true?” Lady Shalltear asked, “Everything that they said about you.”

 

Ludmila shifted uncomfortably in her seat: frontiersmen were not ones to brazenly advertise themselves, and she was no exception.

 

“I think so, yes,” she replied. “There’s so much more now that you’ve brought it to my attention. My brothers were much better fighters than the other noble scions when they practiced together, and they almost always stood at the centre of a crowd. I can feel that I am stronger than other people as well: I can run a bit faster, last a bit longer, carry more and fight better. My parents could outfight any of the Rangers and Fighters in the village, and during the Battle of Katze Plains, my lord father was able to keep his men from breaking…right until the end.”

 

Ludmila swallowed after the last of those words left her mouth. She wasn’t sure when she had decided her family was lost, and now she felt absolutely terrible hearing herself say as much.

 

“Hmm…this is a lot to think about.” Lady Shalltear said solemnly, “If all these claims can be proven to be true, then it will be a matter of grave importance.”

 

“Surely you cannot mean that, my lady,” Ludmila said incredulously. “With so many powerful servants at His Majesty’s disposal, it hardly seems to matter.”

 

“You’re correct that at your level it makes a negligible impact in combat as an individual,” Lady Shalltear agreed, “but a Commander placed over a company of powerful soldiers should still make them that much stronger. I would also be negligent in my duties to think that the world would conveniently present weak opponents forever. I need to speak to Demiurge about this – no, Momon would be the closest to an expert that we have. He was even right about you yesterday during the council meeting…just how much of this has he planned out, I wonder?”

 

“You will be taking your leave then, my lady?” Ludmila asked.

 

“No. You Humans have your inconvenient need for sleep, and we’ve still other things to do before your day is over.” Lady Shalltear looked to the reception area, from where a figure approached, “I believe your paperwork has gone through.”

 

An Elder Lich had appeared from the office behind the counter, circled around the reception desk, and was now purposely walking their way. Its tattered robes of black silk shimmered as it walked by the windows and it held a long, gnarled staff in its right hand. The end of the staff touched the ground in time with its steps, but Ludmila could hear neither the tapping noise that should have accompanied the action, nor the sound of the Elder Lich’s footfalls.

 

It came to stand a few metres away, bowing to Lady Shalltear, then looked to Ludmila. It had the same stained strips of cloth lined with strange lettering like the other Elder Liches at the counter. In addition, it held a large, leather-bound tome pressed to its chest.

 

“Is it saying something, my lady?” Ludmila frowned, “I was watching it approach, but I did not hear anything at all.”

 

“Oh, that’s right.”

 

Lady Shalltear motioned for the Elder Lich to step forward. After a single stride, its footsteps could be heard – as could the sound of its staff tapping on the floor.

 

“The Humans that constructed this city are quite adept at building spaces for large numbers of citizens in close proximity,” her liege said. “These alcoves were designed to provide privacy without the need to construct additional rooms. We’ve revisited many of these concepts when we occupied the city and created additional security measures. We decided for a Silence spell to be maintained for these alcoves so that the office’s clients can discuss their personal business privately within.”

 

“The other nobles should be pleased with this consideration once they become accustomed to life in the city, my lady.” She looked up to the Elder Lich that was now standing beside the table, “So…were there any problems with my submitted requests?”

 

“No outstanding issues were identified,” it replied, and Ludmila let out a relieved sigh.

 

The Elder Lich had a markedly different voice than the one they had spoken to at the counter. It still had something of an abrasive and dry rasp, but the tone was distinctly female.

 

“Your request is being seen to,” it informed her, “and will be arriving shortly outside. This one has been ordered by the Guardian Overseer to accompany Baroness Zahradnik to her territory as an attaché.”

 

“An attaché?” Lady Shalltear peered suspiciously at the Elder Lich, “why would Albedo suddenly want to stick her big nose into something she didn’t want anything to do with just yesterday?”

 

“Lady Albedo has deemed it to be the most efficient manner by which to fine tune various mechanisms of administration and labour in their associated fields.” The Elder Lich replied dispassionately, “This has been mandated as standard practice when information is insufficient to publish suitable manuals.”

 

“Ugh, did she train you to speak like that too?” Lady Shalltear complained in a long-suffering tone, “The last thing I want to hear is hundreds of Elder Liches parroting that insufferable bi–ahem–the Guardian Overseer.”

 

The Elder Lich gave no response, which in turn appeared to worsen Lady Shalltear’s disposition.

 

“Where will the units from the request be delivered?” Ludmila hurriedly filled in the silence, “Will I be able to review them before they are deployed?”

 

“They are currently en route to the main avenue,” the Elder Lich answered. “You may review them in front of the civil office.”

 

As if on cue, Aemilia appeared in Ludmila’s line of sight, standing over five metres behind the Elder Lich. Her lips were moving as she made fretful motions with her hands, but the enchantment preventing sound from crossing the threshold of the alcove stopped the maid’s words from reaching her. Ludmila rose from her seat, stepping past the Elder Lich to leave the alcove.

 

“–ounded by Undead, my lady! Thousands of them!”

 

Aemilia’s panicked words met her as she stepped out of the alcove. Her auburn hair was jostled as she bounced anxiously on the balls of her feet.

 

“What do we do?” She said worriedly, “Are we under attack?”

 

Ludmila placed her hand on the maid’s shoulder to still her as she turned her head to look towards the window. The angle was poor, so she ended up walking out of the office entrance to take a look from the top of the stairs. Arrayed below were her requested workforce, but rather than a loose collection of various labourers, they were neatly organized like a company of professional soldiers.

 

On the road nearest to the sidewalk were forty Bone Vultures, arranged in a rectangle ten wide and four deep. Directly adjacent to their formation was another consisting of twenty Undead Beasts in the form of Boars: they were set five wide and four deep. Behind their lines were one hundred Skeletons armed with round shields and short spears that glistened when breaks in the mostly overcast skies allowed the sun to shine through. Like the Undead Beasts, they were arranged in groups of twenty. At the corner of each of the Skeleton formations, a Death Knight stood where a sergeant would normally be. The Death Knights still held their massive tower shields, but their blades were sheathed. Their weapon hands instead gripped tall banners upon which the vermillion standard of the Sorcerous Kingdom flew proudly in the spring breeze.

 

Ludmila supposed that if it were a company, then all they lacked was a captain. She stepped down to take a closer look, and as she arrived at the bottom of the stairs, the avenue was filled with a singular noise as the entire group stood to attention. Lady Shalltear appeared at Ludmila’s arm with her dark parasol open over her shoulder, speaking over the stiff breeze that scattered the spring blossoms into the air around them.

 

“Are they to your liking?” She asked her.

 

“The numbers check out, my lady,” Ludmila replied. “However, any spectators would think that I am about to go forth to conquer my enemies rather than conquering unruly fields.”

 

“You have enemies?” Lady Shalltear raised an eyebrow, “That’s hard to imagine considering how unflappable you seem to be.”

 

“Well, there are types that we are not particularly fond of, but not in the sense that most would consider enemies to be.” Ludmila thought to the wariness that her father held for Count Fassett, “Being Frontier Nobles, House Zahradnik stood apart from the squabbling that occurs in the interior. Our enemies have always ever been those that would infringe upon and act unlawfully within the realm of our liege.”

 

“If it had been any other of your kind standing here saying that,” Lady Shalltear said, “those words would have felt like lip service, I think.”

 

“Did I unconsciously use my ability on you, my lady?” Ludmila made to apologize.

 

“I doubt it,” her liege smiled slightly for some reason. “Undead are immune to mind-affecting spells and abilities.”