\chapter{Ludmila Zahradnik}

“You’ve been progressing steadily thus far,” Lady Shalltear picked up on Ludmila’s soft mutter, “why would the next part present any difficulties?”

 

“The next part involves finding the right people out of all of the citizens that are hiding in their homes,” Ludmila returned to her usual, clear voice, “and I am not quite sure how to accomplish this, my lady. Frontier Nobles are nobles, but we only share some very basic similarities with the nobles of the interior. You mentioned a little while ago about how you believe you are only good for fighting, but I am in something of the same situation as well. I have been trained in all of the things required to carry out House Zahradnik’s duties in defending the border – this would include logistics, organizing and leading armed patrols, as well as managing our small fief, but my skills in administration and commerce are nowhere near as substantial as someone like Baroness Corelyn. Our house does not have much in the way of connections, either.”

 

“Well what did you do last year, then?” Lady Shalltear asked.

 

“Our goods were sold to a wholesaler,” Ludmila answered, “merchants who have both the capital and storage to take in large quantities of goods and bide their time to turn a profit meeting the demands of the markets. That way, we would be able to return to our duties on the border within a couple of weeks, after dealing with some other noble functions. However, if the city is like this, not only will it be difficult to find such a merchant, but the markets will have slowed to nothing as well and the prices for everything may not be as projected.”

 

“So you have to ride around the entire city until you find someone?” Lady Shalltear frowned.

 

“Perhaps…perhaps not.” Ludmila turned to the Elder Lich, “Are there any markets that are still active in the city?”

 

“As of this morning, no open market areas have been reported in the city,” the Elder Lich replied. “Emergency supplies are currently being distributed by Lady Shalltear Bloodfallen and her staff in the interim.”

 

“What about guilds?”

 

“The Adventurer Guild and Mage Guild are maintaining limited operations.”

 

“How about the Merchant Guild?”

 

“There has been no reported activity from the Merchant Guild or any of its associated Trade Guilds in the past week.”

 

Ludmila bit her lip lightly as she thought about what she could do.

 

“How does the city procure goods when there is no commerce?” She asked.

 

The Elder Lich remained silent. Its fingers lightly tapped the leather-bound book that it held to its chest while it pondered her question. Lady Shalltear spoke, filling in for the perplexed attaché.

 

“The short answer is that we’re not, currently,” she said. “The government warehouse is slowly being depleted over time – you estimated that they would last one year, while the Guardian Overseer’s estimates are closer to two if rationing measures are enforced immediately. She expressed great confidence that E-Rantel would not need to resort to such a policy initially, but with the lack of progress in the past week I believe that she is beginning to consider it as an option.”

 

Ludmila grimaced. The siege-like nature of their situation felt ever more real with the idea that the people might begin to see their necessities limited.

 

“Will the city purchase goods while the markets are closed, my lady?”

 

“The Sorcerous Kingdom guarantees a minimum rate for basic materials,” Lady Shalltear said. “But...they would most likely not be favourable compared to regular market prices. The merchant I spoke of yesterday shouted ‘ridiculous!’ and stormed off, leaving Sebas standing alone in the street with only his good intentions to keep him company.”

 

“How was he able to trade in the city then?” Ludmila asked.

 

“I don’t think he did. The following council meeting, it was reported that he spent the day running all around the city’s markets and guilds with no apparent success. He left the city the next morning.”

 

Ludmila exhaled sharply. She had hoped that information from the lively merchant whom Lady Shalltear had mentioned would lead to a solution to her conundrum as well. With one avenue closed, she decided to pursue another, turning to the Elder Lich once more.

 

“Do you know where the nobles currently residing in the city are housed?”

 

The Elder Lich nodded silently.

 

“We will stop by the nobles’ clubhouse first, then,” Ludmila decided. “After that, we can find the remaining nobles that were not present there – the ones in the city should be in their respective manors here since they are supposedly too frightened to move around much more than that.”

 

As the wagon rolled forward, the two Death Knights fell in line to either side of the Wagon. The Elder Lich kept pace on the road at Ludmila’s side of the front seat. Lady Shalltear looked up at her from the side.

 

“You have an idea?”

 

“Perhaps, my lady,” Ludmila said. “My family was not as well-connected as the other nobles but, since everyone else here is staying put and not doing anything, I was thinking that we might be able to make use of their connections in exchange for a finder’s fee or perhaps a future favour. That is our best chance now, I think.”

 

It was not long until the wagon pulled up in front of the clubhouse. The ornate building did not show any signs of being occupied from the outside, though this was also the case for the previous evening.

 

“Luzi, come with me,” she called to her maid sitting behind. “Excuse us while we check if anyone is here first, my lady.”

 

Ludmila stepped down from the wagon as Lady Shalltear lazily waved her away. Aemilia joined her, stepping ahead to open the doors. They were greeted by an empty reception desk, and the lounge area was vacant as well. There were no odours of food or beverage in the air and the furniture lay pristine and undisturbed. Aemilia went around the halls, returning after a few minutes and shaking her head as she looked towards her.

 

“Alright,” Ludmila said, “I guess we will have to visit each of them in turn, then.”

 

After they returned to the wagon, she spoke with her attaché.

 

“I need to know where all the nobles in the city are staying – beginning with Baroness Clara Odilia Dale Corelyn.”

 

“Baroness Corelyn resides at guest house number eighteen,” the attaché replied almost immediately.

 

“Take us there,” she instructed the Soul Eater, “find a corner out of sight of the main entrance to stop, however. If the residents are still fearful, then we should keep their fears out of sight for the time being.”

 

The wagon rolled forward again with its small entourage.

 

Not half a minute had passed when the Soul Eater stopped in the service lane that ran along the wall, behind the outer ring of manors which circled the district. Ludmila stepped off of the wagon again, remaining still while Aemilia checked over her appearance. Lady Shalltear came around with her attendants, watching the maid as she worked to fix any flaws in Ludmila’s outfit.

 

“Have you considered getting enchanted equipment?” Lady Shalltear idly spoke as she observed their activity.

 

Ludmila turned her head at the question, trying to remain stationary for her maid.

 

“You mean arms and armour, my lady?”

 

Magical equipment was far beyond the means of her family, whose meagre fief existed only a little beyond subsistence. The outfit that she currently wore was all that consisted of her formal wardrobe, and even that had been the product of the better part of a year’s worth of hard work; it had required her to sacrifice other things in order to be able to afford it.

 

“Just daily clothing, in this case,” Lady Shalltear said. “Enchanted items will adjust to fit themselves perfectly to their wearer. They’ll also restore themselves to form unless they completely run out of durability, so you don’t even have to worry about the sort of thing you’re doing right now.”

 

Aemilia froze upon hearing this; her hands stopped partway while moving to fix a crease in Ludmila’s skirts.

 

“Is it normal to have magical clothing in your demesne?” Ludmila asked, “Re-Estize has little in the way of magical items. Most of them belong to Adventurers and mages, or are heirlooms of powerful noble houses. What people more commonly see are tools that help with daily life, like magical faucets or the lighting in the city streets.”

 

“It is. Even the lowest maids have enchanted uniforms, so there is no great fuss concerning maintenance. Nearly my entire wardrobe is enchanted to various degrees,” Lady Shalltear’s voice took on a rare proud note. “Perhaps one day, after you’re successful in your task, I’ll display a few pieces for you.”

 

“I have never seen enchanted clothing before, my lady, so that would be wonderful. I believe Luzi would be very much interested as well.”

 

The maid’s hands started working again. A minute passed before she stepped away, indicating that they were ready to move. Ludmila took the blue folder that lay on her wagon seat, and together they made their way around the guest house to the front. The Soul Eater, Elder Lich, and the Death Knights remained in the service lane, under the shadow of the wall.

 

Like all of the other manors in the district aside from her own, there was no one stationed to guard the entrance. The manor itself was styled in a similar appearance to all the other guest houses, though there were a few differences in its structure. Aemilia walked ahead to pull the chain for the doorbell and returned to stand behind Ludmila a few metres away from the entrance.

 

She heard movement coming from inside, but it was a long time before they heard someone walk up to the door. There was the brief sound of a lock tumbling before the entrance opened a sliver, and an almond-shaped eye peeked out. The eye looked from person to person until she recognized Ludmila standing amongst the group.

 

“Ludmila?” She said suspiciously, “This is not some sort of trick, is it?”

 

“We just saw each other yesterday Clara,” Ludmila replied, “why would this be a trick?”

 

There was a short pause as the fearful noblewoman examined her face, followed by a relieved breath as she visibly relaxed and fully opened the door. She was in a simple dress of pastel yellow, and she seemed well enough beyond her nervous countenance.

 

“Ever since Count Fassett,” she explained, “every time one of us goes to have an audience with the Royal Court, the rest wonder if they will ever return.”

 

“Have other nobles disappeared like this?” Ludmila’s eyebrow rose.

 

“At least one other that I know of,” Clara nodded, “then a little while ago, Baron Hamel was looking out of his window and started shouting about how some poor women were being run down in the street by the Undead. I could not even bear the thought, never mind look out to see. When the doorbell sounded, I thought it was the end for us.”

 

Baron Hamel? Ludmila tried attaching a face to the name, but came up short. However, she spotted the face of the boy she had left in the clubhouse the previous evening poking his head around the corner of the corridor further within the manor.

 

“Clara,” now it was Ludmila’s turn to be suspicious, “why is Baron Hamel in your manor?”

 

Clara noticed Ludmila looking past her shoulder and quickly turned her head to look behind her as the mop of sandy blond hair disappeared back around the corner.

 

“That’s…erm, the Baron has taken up residence in the neighboring manor, and we have neighboring fiefs as well. We already knew each other from before, and he wanted to stay over because he was scared to be alone.”

 

“I see,” Ludmila’s voice was flat.

 

“Nothing untoward has happened!” Clara’s amethyst eyes looked at her innocently, “It is just comforting to be with others with everything that has gone on recently. Besides, we followers of The Six have our own ways, yes?”

 

Ludmila supposed that Clara was correct: as followers of The Six, they had their own approach to selecting consorts. Still, harmful rumors might come out of it.

 

“What of your servants?”

 

“We do not have any! All the ones that were offered by the city were not in a state to work at all.” Clara laughed nervously, “Housework has been quite the adventure–wait, how do you have servants out and about?”

 

“They just needed a bit of confidence, I think.” Ludmila replied, “You should try and encourage them some time.”

 

Lady Corelyn gave her a strange look, not understanding the meaning of her words.

 

“Also one of the women with the Death Knight was probably my maid Luzi here,” Ludmila continued, “I sent her on a few errands with an escort.”

 

Clara’s mouth fell open.

 

“Y-you command these Undead now?” She asked.

 

“The Death Knights are on loan from His Majesty as footmen for my household,” Ludmila answered. “They are remarkably competent, actually.”

 

The fearful expression appeared on Clara’s face again and she looked all around, as if expecting Undead to be hiding around every corner. Ludmila stood to the side, allowing her a clear view of the street in front of her home. She calmed down again after seeing that there were no horrors lurking about.

 

Lady Shalltear lightly cleared her throat, and Ludmila proceeded to the matter at hand.

 

“I have come on official business, however,” she said. “Do you have some time to spare?”

 

“Oh, of course,” Clara’s eyes shifted over to Lady Shalltear, then back to Ludmila, “but who is this beautiful girl?”

 

Ludmila straightened, realizing that she had been rude to not introduce her liege first.

 

“Apologies for my rudeness in not introducing her beforehand,” Ludmila turned to present Lady Shalltear, “this is Lady Shalltear Bloodfallen, Minister of Transportation.”

 

Clara’s mouth was agape again.

 

“A-a Royal Councilor? Here?!” She immediately dropped into a deep curtsey, “Welcome to my residence, Lady Minister. Baroness Clara Odilia Dale Corelyn, at your service.”

 

“You have never seen Lady Shalltear before?” Ludmila asked curiously, “I thought all of the other nobles had an audience with the Royal Court upon their arrival in the city.”

 

“She might have been there, I-I am not sure,” beads of sweat formed on Clara’s brow. “There were…others there, and I was scared witless. They sent me away and I can barely remember anything about the audience. A-anyways, I am being rude. Allow me to entertain you in the parlour; we have some refreshments…biscuits that were delivered earlier today. We have water as well, as long as you do not mind the charred flavour.”

 

“We are in a bit of a hurry, actually,” Ludmila said as she glanced sidelong to Lady Shalltear, “I need to borrow your merchant contacts in the city.”

 

“Merchants? I don’t think your demesne uses the same merchants as ours does, does it?”

 

Clara was right; the territories on the gentle slopes of the Riverlands cultivated vast vineyards and orchards which went into the desserts, jams and liquors produced in the territory.

 

“Anything is fine at this point,” Ludmila said. “Even if they cannot help directly, they might know someone who can. How about blacksmiths – toolmakers and the like?”

 

“We have a village blacksmith that does nearly everything,” Clara replied. “Merchants passing on the highway to and from the Theocracy sell us raw materials and everything else, usually.”

 

After they received what information Baroness Corelyn could provide, Ludmila thanked her and they started walking back to the wagon.

 

“Writing with a stick of charcoal seems a bit inconvenient,” Lady Shalltear remarked as Ludmila wiped her hands on a handkerchief.

 

“Carrying an ink bottle around would be a mess waiting to happen, my lady,” Ludmila said as she settled back on the driver’s bench.

 

“I can lend you a pen, if you’d like,” Lady Shalltear held out her hand, and an elegant-looking instrument appeared in her fingers, “you're going to have charcoal stains everywhere by the time we’ve gotten all the information we need.”

 

“This is…a fountain pen?” Ludmila tried writing with it, and her letters came out smoothly. “Thank you Lady Shalltear…or is it Lady Bloodfallen?”

 

“My vassals usually address me as Lady Shalltear, so what you’ve been using is acceptable.”

 

The next house they came to was occupied by Count Völkchenheim and, to Ludmila’s surprise, the door opened shortly after they came calling. A tall, middle-aged man with a rough appearance appeared in the doorway, holding a long bronze candlestick in one hand. Something about the image he projected tugged at the edge of Ludmila’s recognition.

 

“Oya?” After noticing that it was not some monster that had come to the door, he placed the candlestick aside and his face brightened, “To what does House Völkchenheim owe the pleasure of such beautiful young ladies today?”

 

“Count Völkchenheim?” Ludmila asked while still attempting to place his appearance.

 

“Ah, no,” the man hastily denied the appellation, “I am Andrei, a retainer of the Count – currently serving as his valet.”

 

His movements and mannerisms finally came together in Ludmila’s mind.

 

“A Ranger?”

 

“Why yes, young miss,” he replied with some surprise, “how did you know?”

 

Ludmila felt a bit of a twinge. Völkchenheim County was not a frontier territory, but they had been forced to take up arms to defend themselves as the frontier territories that were supposed to be holding the wilderness at bay slowly collapsed. Demihuman raids on their territory were not severe, due to their distance to the border ranges, but it was still something of an unasked-for burden.

 

“I am Baroness Ludmila Zahradnik,” she introduced herself then motioned to her right, “this is Lady Shalltear Bloodfallen, Minister of Transportation. We are here to speak with Count Völkchenheim.”

 

Andrei’s face paled as the titles rolled out of Ludmila’s mouth.

 

“Forgive my rudeness, Lady Bloodfallen, Lady Zahradnik,” he hurriedly bowed, his voice rising in apology as he bent at nearly a perpendicular angle. “I will call for the Count–please, come in and take a seat in the patio garden…”

 

His speech slowed as he looked to be deciding whether he should be seating the Count’s visitors, informing the Count of his guests, or dividing himself in half to accomplish both tasks at once.

 

“We won’t be long – we just require some information from Count Völkchenheim,” Ludmila spoke to eliminate his indecision. “It will be fine for us to wait here.”

 

He gave them one last, conflicted look before leaving the doorway behind and disappearing around a corner. They heard him shouting for the Count, then he seemed to cut himself off realizing that he was shouting for a noble in the presence of other nobles.

 

“Well, he certainly seems quite different,” Lady Shalltear mused.

 

“He carries himself like a frontiersman,” Ludmila said, “To be honest with you, I am more used to that sort of conduct than I am this whole dance of etiquette that the inner nobles conduct.”

 

“Perhaps you should act more like yourself then?” Her liege suggested, “There’s no need to put on airs with me.”

 

“I am acting like myself,” Ludmila replied, “at least how I act in an urban, public setting. The villagers I am used to are the ones that act like him…also my brothers…and my father.”

 

“Are you saying you’re the only person in your entire Barony that acts like this?”

 

“Well, yes,” Ludmila paused for a moment. “Though my mother did so as well; everyone says I take after her. Even though we were a remote border territory, she always behaved in a manner that suggested we were more than that and everyone around her was influenced as a result. Thanks to you, my lady, I understand why she did this now.”

 

“So when you’re out in your own territory, you speak more like this fellow?”

 

“Not exactly, my lady,” Ludmila replied. “Well, perhaps more informally. My conduct, however, would be unacceptable in the city according to Luzi here.”

 

The maid reacted to being named, but stayed silent. There was a thumping of heavy footsteps as someone came down the stairs, followed by a shadow in the light of the courtyard inside. A young man appeared in the hall, looking very much like he had rushed to dress and groom himself. Somewhat winded, he came forward, but stopped partway down the hall to stare at his visitors. Then, he turned right back around and disappeared behind the corner that he had come from.

 

Ludmila thought she could hear some fierce whispering, and after several moments, the young man appeared again. Additional effort had been made to fix his appearance, though his outfit still held creases from where it had probably been haphazardly thrown somewhere and left for hours. He came forward stiffly with his greetings.

 

“Torkel Karan Dale Völkchenheim,” he made an exaggerated bow as he introduced himself, “Count of Völkchenheim.”

 

“Baroness Ludmila Zahradnik,” Ludmila curtseyed, then rose and swept her arm out to present Lady Shalltear, “Lady Shalltear Bloodfallen, Minister of Transportation.”

 

“How may I be of service, my ladies?”

 

Count Völkchenheim’s eyes kept bouncing back and forth between all of the women arrayed before him, before his gaze finally settled on Lady Shalltear.

 

Behind him, Ludmila thought she saw Andrei roll his eyes.