\chapter{Ludmila Zahradnik}

The wagon rumbled down the street while Ludmila looked through her lumber invoice, reevaluating the calculations that she had made for the development of her demesne. The dramatic difference between the figures she thought she would have to work with and the actual market value of her goods forced her to rethink all of her budgeting. She no longer needed to worry about being able to afford all the tools her labour required, nor the various parts and supplies that the village required to stay in one piece.

 

Provided she could secure everything that was needed, her schedule had advanced considerably and, if the projected results of the Undead labour were to be believed, she would need to find a large number of tenants to move into her fief soon. The Imp from the lumber yard had lost its ghostly image and was now perched on a rail of the wagon, looking over her shoulder at the papers in her hands.

 

Lady Shalltear broke the silence that had hung over the entourage since they departed the lumber yard.

 

“Say, was my idea really that bad?” She asked.

 

“No, my lady,” Ludmila replied as she continued thinking about her budget.

 

“Then you’d have taken me up on my offer?”

 

“Yes, if I was certain that you could do what you claimed, then I would without hesitation.”

 

“Why the difference, then?” Lady Shalltear asked.

 

Ludmila lowered the page, looking to her liege sitting next to her. If she were perfectly honest with herself, she didn’t really know how the subjects of the inner territories conducted their lives, or how they reacted to the world around them. She could only relate her thoughts in terms of her own life on the border, and guess how others might be different.

 

“This is probably not unique to me,” she answered. “Anyone that is accustomed to a life where they need to obtain every advantage to survive would probably accept your solution. On the southern frontier, we are constantly under threat by our neighbors in the wilderness – ambushes and raids can happen with little to no warning. If we turned down the offer to heal an injury that made us unable to fight properly, it could not mean just our own deaths, but the failure to perform our duties to their utmost and the loss of those we care about. Losses that we might have prevented had we been whole.”

 

She looked down the street, at the long lane with its shuttered buildings to either side. Even with most of the daylight hours gone, there had not been any sign of life beyond the rows of smoking chimneys and the barely perceptible scents of meals come and gone. A patrol of Death Knights stomped by, heading in the opposite direction but, aside from the Undead, the streets remained empty.

 

“In the stability of the towns and cities of secure and developed lands, if you fail at something – if it doesn’t get you killed – you can try something else. When some doors close, others open. As long as you have something others value, you can find a place for yourself. Perhaps choices presented before you are the right ones, and turning away from them results in a lifetime of regret. Or it could be that said choices are rash, but your failures in them help you find greater success elsewhere. Because there are always options, men like Gareth Boyce can exist. Putting off the treatment of his injury led to him becoming a successful merchant in the first place. Success can lead to further success, but that same success can also turn you from making decisions that might have actually been for the best – even if it is an obvious decision for others.”

 

“Then how do you Humans find the right path?” Lady Shalltear frowned at Ludmila’s words. “I cannot fathom this sort of transient and aimless existence, devoid of inherent purpose.”

 

“We do not know which paths are ultimately right, my lady,” Ludmila replied. “We just end up where we are because that is where the choices of our lives lead us, for good or for ill. Thinking there is some perfect path that you are destined for and waiting for it to appear in front of you is a fantasy for fools.”

 

“You seem to be doing well enough for yourself now.”

 

“I was born a noble, my lady – I had very little in the way of choices in that sense. I just happen to find my place quite enjoyable and fulfilling...but I still have no idea about whether it is the right path or not.” Ludmila smirked, “I have many choices that I must make from now on; you can ask whether they were right or not at the end of my life, which hopefully will not come any time soon.”

 

Lady Shalltear wrinkled her nose, but it was probably not at Ludmila’s reply. Odours were carried on the wind as they turned northwards, filling the air with a multitude of different scents. As the wagon proceeded, the scents became stronger, some eye watering as they wafted by. They occasionally passed buildings of odd construction, fashioned for the manufacture of potions, ointments and oils. Most of the Alchemists of the city were located in this loose area in order to keep the emissions of their craft from permeating throughout all of E-Rantel. The wind would blow the fumes produced by their work over the wall nearby – conveniently into the huge cemetery which occupied the western quarter of the military district.

 

The wagon rolled to a stop at a building with windows that faced westwards towards the afternoon sun. The curtains inside were drawn, but the store itself did not appear to be closed. Ludmila had issued orders to the Soul Eater as an experiment when they were in the alley outside Gareth Boyce’s lumber yard: to head to the Alchemists’ area and find a shop that had someone working inside. That they had stopped in front of a building with a sign with the words ‘LeNez’ written over it in garishly bright lettering seemed to suggest that her instructions had worked unerringly well. She wondered if the Soul Eater already knew where to go in advance, or if it used some strange sense to carry out its instructions.

 

Aemilia went ahead to the workshop door and held the entrance open for the others to pass through. A wave of heat billowed over them, carrying with it the overpowering odour of far too many fragrances overlapping one another. At the long glass counter along the aisle leading into the store, a young woman who appeared to be in her early twenties reclined in a high-backed stool, facing the row of alchemical burners at the back of the workshop. She had a slovenly appearance: her shoulder-length strawberry blonde hair was matted with sweat, which beaded on her skin as well. Her shirt was unbuttoned and clung to her in various places, and she wore shortened trousers that rode far too high up her thighs. The image conveyed an overheated sensation which made the temperature in the sweltering workshop seem even hotter than it already was.

 

“Oy welcome~” she called out at the sound of the chimes hanging over the door, then turned her head upside-down towards them from her reclining position. “Cheh–if at all possible, could you go back outside and come back in as a group of cute men?”

 

At the rear of the group, Aemilia clicked her tongue in disapproval at the expression of disappointment.

 

“Just kidding,” the woman inside raised her hands – also upside-down – disarmingly. “It was a joke, a joke~”

 

She straightened in her seat, spinning it to face the counter whilst buttoning up her shirt. It did not improve her sweat-soaked image much.

 

“Gods, I was such a dumbass building an Alchemist’s Workshop with a west-facing storefront. Heat’s even worse in the summer, ya know,” she tied her hair in a loose ponytail as she rambled on. “Anyways, what can I do for you girls…ladies? I know it’s spring and all, but the men certainly aren’t coming out these days, no matter what scent you wear.”

 

“You are the owner of this workshop – Miss LeNez?” Ludmila asked.

 

“Yep, that’s me,” she nodded, “Germaine Lenez: fashioner of fragrances both sweet and seductive. Well, Maine is fine – I used ‘LeNez’ on the sign since it looks trendier, if ya know what I mean~”

 

“Why not just cool the place down by opening the door and windows?” Ludmila asked.

 

“Ahaha, yeah, right. Everyone downwind would come and burn my place to the ground.”

 

“I see…we are here to sell Sandalwood,” Ludmila said.

 

“Oh, Sandalwood. That’s pretty rare around these parts. What do you have?”

 

“Two, uh...trees? I am not sure how to describe it.”

 

Germaine slid off of her chair, slippers slapping lightly on the floor. She walked over to where a thin coat hung, snatching if off of its peg and throwing it on as she headed back the other way to come out from behind the counter.

 

“That sounds crazy,” she said, “but let’s take a look.”

 

She made her way past them, pushing the door open; then she froze.

 

“HOLY CRAP!”

 

Germaine’s voice reverberated over the rooftops. It was somehow much louder than Gareth Boyce shouting for his son. The Perfumer closed the door and turned around, facing the other women.

 

“Uhm…there’s Undead outside,” she said in a low voice. “Were they there when you got here? Can I tell them to go away? Should I Acid Cone them? I think I got just the right angle to hit them all at once from here…”

 

“That’s not the usual reaction,” Lady Shalltear observed.

 

“They just up and parked in front of my shop!” Germaine complained, “there’s no way any customers will come in like that.”

 

“They’re not going to run away just because you spray them,” Lady Shalltear told her.

 

“Oh~ you sure know your stuff, miss. Sorceress?”

 

“Cleric.”

 

“Hah, coulda fooled me,” the Perfumer opened the door a crack, peeking outside. “Well, it usually works. Whenever I get nasty folks showing up for whatever reason, I just start casting and they make themselves scarce real quick. Except for that one stupid Militia Inspector. City made me pay for his healing on top of the fine.”

 

“Why did an Inspection Officer come to see you?” Ludmila wasn’t sure if she wanted to know the answer.

 

“I was trying to air out the place,” Germaine said, turning back to speak to them, “was the middle of summer and hot as hell – I just couldn’t stand it any more. The neighbors all started complaining about the fumes and this guy just came up all snooty-like and ordered me to close up.”

 

“What happened then?” Lady Shalltear asked.

 

“Well…I was really cranky from everything so I just pointed and sprayed,” Germaine pointed her finger out the crack in the door. “His face melted right off. So did his arms. Maybe one of his legs? Fell into a puddle of his own goop with his goons shouting bloody murder while dumping their healing potions on him.”

 

“How did they not imprison you for that?” Ludmila was shocked.

 

“Oh, they were hopping mad,” Germaine grinned, “but when you can melt a giant hole in the prison wall that’s definitely more trouble than it’s worth. Got slapped with a big fat fine but they never came back after that.”

 

The Perfumer tilted her head at her own words.

 

“I guess it did work, now that I think about it.”

 

Ludmila was beginning to draw some similarities between the people she had met so far that weathered the presence of the Undead, but she felt that coming to any immediate conclusions would have lasting effects on her own ego.

 

“The Undead outside are with us,” she said after clearing her throat. “The wagon in front of the shop is hauling my cargo.”

 

“That so?” Germaine glanced out the door again, “They won’t steal my soul or bite me or say hurtful things, will they?

 

“The order of severity seems backwards but, no, they will not.”

 

“You’ve probably just never fought a Banshee. Well, what’s the hold up then?” Germaine brightened immediately, “I’m dying to get some fresh air.”

 

She turned and walked out of the door without a shred of hesitation or shame.

 

After they filed back out of the shop, Ludmila found the Perfumer standing on the wagon bed, repeatedly tugging on her shirt to cool herself.

 

“Ahhh~ So good,” Germaine sighed in contentment. “One of these days I’ll get a whole stack of those magical cooling boxes that they sell in the Empire to make my shop livable in the summer.”

 

If she showed any sign of self-consciousness as she stood in the breeze, she did not show it. She stretched and fanned her shirt and took her time adjusting her shorts before she held out her hand and cast a spell.

 

“「Appraisal Magic Item」.”

 

“That’s not supposed to work on non-magical items…” Lady Shalltear said suspiciously.

 

“Ahaha, you’re right, Miss Cleric,” the Perfumer knelt to take a closer look at the Sandalwood trees, “sure impresses the heck out of anyone that doesn’t know that, though.”

 

“But it’ll drain your mana, won’t it?”

 

“I’ve got mana if you’ve got coin~” Germaine’s voice floated over the edge of the wagon.

 

Not a minute passed before she stood up again.

 

“Yup, they’re the real deal,” Germaine cradled her chin thoughtfully with one hand, “these don’t grow around here though. How’d you come across two whole Sandalwood trees older than everyone here combined?”

 

“They are from my demesne, I think,” Ludmila replied, “the Rangers floated them down the river to the village from wherever they found them.”

 

“Your demesne? Baron Zahradnik was a man, last I checked.”

 

“You knew my lord father?”

 

“Nope,” the Perfumer replied. “But Warden’s Vale is the only territory even remotely close to where these grow. Those Rangers of yours must have ranged pretty far south to run into these, Baroness.”

 

“I was not on the patrol that found them,” Ludmila said, “so I am unsure where exactly they went.”

 

“A shame,” Germaine let out her breath in a huff, “there’s a lot of good stuff out there, but it’s teeming with nasties.”

 

The Perfumer turned around to look through the rest of the wagon.

 

“What about the rest here?” She asked, “Got anything for me?”

 

“It is all food,” Ludmila answered. “Mannagrass, Watercress, Arrowhead tubers.”

 

“Hum…all nice produce if I was in the market for produce – the stuff they’ve been dishing out of the city warehouse has been getting pretty boring lately. Not that I mind free food. Was hoping you had alchemical herbs or something. Ever since the Bareares moved out to Carne it felt like half of the incoming shipments were going straight to them.”

 

“The city has a potion shortage?”

 

“The city is going to have an everything shortage soon,” Germaine walked to the edge of the wagon bed. “Once whoever is running things in central decides enough is enough and chases everyone out of their houses, they’re gonna find that all of their supply chains are in shambles. I don’t think anything has really come in or gone out since midwinter: no traders, nothing from the duchy, nada.”

 

Ludmila exchanged glances with Lady Shalltear.

 

“How many people do you think realize this?” Ludmila asked.

 

“Everyone that does business seriously in this city probably does,” the Perfumer said, “but there’s not much most can do. E-Rantel is the biggest trading hub in the nearby region, but we’re set up to receive all of the merchant traffic coming through here, not the other way around. There are only a handful of merchant companies based out of the city, and they’re mostly owned by nobles who may or may not still be around. Once people come out of their hidey holes, they’re gonna find that there are no materials or products to handle; no work, no food. Even the Adventurers are going to be in trouble – most of their jobs here came from keeping Katze from being more uppity than the surrounding countries would like, but I’m not sure if our Sorcerer King would even care that there’s a handful more Undead wandering around. They’d probably just walk right in through the front gate and sign up for his army.”

 

Germaine hopped off the back of the wagon, rubbing her hands together with relish.

 

“So, Lady Zahradnik,” she said, “how would you like to settle this? Due to the current shortfalls, I’ve got plenty of capacity to extract the oil out of these trees. I can sell some to a jeweler I know as well – he’d love to turn such high quality Sandalwood into fragrant ornaments and the like…maybe you’ll end up buying a few? Gods know you’ll be living large after this.”

 

“How much are we talking about here…” Ludmila was wary after the revelation from Gareth Boyce.

 

“Well,” Germaine turned back to look at the wagon, “these two trees should yield around two litres of the highest quality oil. That’s enough to make incense of a calibre that even the Theocracy can’t easily get their hands on for every one of their temples. Or half a year’s worth of perfume for every single noble in one of the big marches. I’ll probably be slowly doling it out over time to make sure I get the most out of it. The parts that I don’t use I can easily find a buyer for…I can take that off your hands and sell it for you if you don’t mind a small surcharge for my time and connections.”

 

“I do not mind,” Ludmila said, “as long as it is not unreasonable.”

 

“Right then,” the Perfumer smiled. “All said and done it should come out to ninety-six platinum coins.”

 

“…is that the right amount?” Ludmila’s voice felt very small when it came out.

 

“Hm?” Germaine scratched her head, “Should be. The finished products are worth more of course. After all the overhead is accounted for, it should leave me with a small margin – as long as I can manage the products properly. Maybe I can finally go out and get a few of those cooling boxes I was talking about.”

 

Germaine cackled; she seemed more excited about the future improvement to her comfort than the fact that she was about to part with nearly a hundred platinum coins.

 

“Actually,” she added, “before we sign off on this, is there anything you’d like to purchase from my shop?”

 

“You are a pretty shrewd merchant.”

 

“Surely you jest, Baroness,” Germaine laughed. “Any good merchant would do at least this – you never know what people want until you ask, after all. Might even be rendering a service by showing your customers things that they never knew that they needed.”

 

“Still, having ninety-six platinum coins available to make purchases with is incredible...”

 

“Ahaha...I don’t actually have that much, personally, but the Guild knows how much these are worth and will help finance the trade.”

 

“Luzi,” Ludmila called to her maid, who stepped forward with hands folded in front of her.

 

“Yes, my lady?” Aemilia replied.

 

“Put together a full inventory of her merchandise that we will need for the city manor,” she told her, “as well as for the manor staff. I will be having Terah fill the role of interim Housekeeper to hire suitable personnel to work there.”

 

“Yes, my lady.”

 

“Also a smaller set for various official functions.”

 

“Yes, my lady.”

 

“Bring Lady Shalltear’s attendants with you as well,” Ludmila added. “Maybe they will find something to her liking.”

 

Aemilia curtseyed before she and the Vampire Brides turned and followed Germaine back into her workshop.