\chapter{Ludmila Zahradnik}

After informing Terah that she would be having her breakfast in the drawing room, Ludmila walked down the main corridor to the entrance of the guest house. Judging by the appearance of the patio as she passed by the courtyard, the streets would still be damp and gloomy. She opened the front door and walked up to where the two Death Knights faced the street at the end of the lane by the letterbox.

 

Looking at all the spikes on their armour, it seemed a hazard to even attempt passage between the pair of towering sentinels. Standing behind them on the path leading from the door, she cleared her throat just loudly enough to be heard, and the one to her left turned to look in her direction. It did not move like a Human normally would, instead twisting its body around with the joints of its dark armour somehow allowing the uncomfortable looking action. The web of red veins that ran over the black plates made its armour seem more like a carapace, pulsing with malignant energy. Its baleful crimson gaze turned down to meet her own, much the same way as the one in the streets did the previous evening. Maybe they just looked that way all the time. She shifted to face her Undead footman.

 

“Inform Lady Shalltear that I will be ready to meet with her in an hour,” she said. “There will be a single maid from my household accompanying me.”

 

Without awaiting anything further, the Death Knight marched off. Its partner moved to occupy the position that had been left vacant, purposefully stepping over to the other side of the lane. It seemed that every one of them wielded their weapon on the right – the tower shield it held would have blocked its line of sight to the entrance it was guarding if it had stayed where it was. Not only were these Undead frightening and powerful in appearance, they seemed to display a measure of competence as well.

 

After looking into the letterbox and finding it empty, Ludmila returned into the guest house, closing the door behind her. Breakfast had already been set in the drawing room; it seemed that Yuri Alpha had left the ornate dinner tray with its polished cover behind to be reused. She was greeted by fresh bacon and fluffy white bread with a dish of butter on the side. It was very different from the village stew she was used to; there was a distinct lack of greens…and everything else. She wondered if it had anything to do with the supply situation in the city, or if it was just what her maids considered a regular breakfast. Her father had always insisted they prepare the same stew that he had become accustomed to – going so far as to bring all the ingredients along on the trip – so she had never experienced the local breakfast before.

 

After finishing her meal, Ludmila decided that her father had the right idea. While the light breakfast had a refined feeling which was complemented by the tea served by Terah, it felt insufficient for the active lifestyle that she was used to. She suspected that she might end up having lunch early to make up for it.

 

Terah spoke while coming forward to take the tray away.

 

“If you have a moment to spare, my lady,” she said, “the other two maids would like to make their introductions.”

 

“How are they?” Ludmila asked, “I’ve heard they’re still having difficulties adjusting to life here.”

 

Terah harrumphed dismissively.

 

“No more than Aemilia and I,” she said. “It’s no excuse to hide under your covers until you start growing mold. They sure as hell started working once I threatened to make them stand outside with the guards.”

 

The older maid coughed, smoothing out her rough tone.

 

“That is, they’ll be useful to you in short order my lady,” she said mildly. “Ever since we’ve entered your service, things have started to become, well, more normal. You had the gist of it yesterday, I think…all it’ll take is time. As more people resume their lives, the more others will be compelled to do so.”

 

Ludmila wasn’t sure if Terah meant the act that she had put on for them yesterday, their short discussion, or both. Even so, she took it as a sign that she was on the right track when it came to getting the people back on their feet.

 

“Show them in, then,” Ludmila told her. “I’ll be away for most of the day, so it’s probably best to do this while we have the chance.”

 

She rose from the couch as Terah motioned for her fellow maids to enter. They were of an age and height with Aemilia, perhaps slightly older. The two were remarkably similar to one another: both sported shoulder-length dark teal hair, with pale faces and paler expressions. Dull grey eyes peeked out from under their bangs at her, then shifted away when she looked at them directly. They seemed dangerously thin, even under their voluminous maid uniforms.

 

“You’re being rude to the Baroness, girls.”

 

They jumped at Terah’s words, curtseying before Ludmila. The older maid sighed.

 

“Please forgive them for their behaviour, Lady Zahradnik,” she apologized. “These two are the Linum sisters: the one on your left is Wiluvien, Lluluvien is her younger sister.”

 

“We are at your service, Baroness Zahradnik,” they greeted her in unison, albeit timidly.

 

As they rose, Wiluvien gasped as Ludmila reached out and cupped her cheek, tracing her fingers up her jawline before lifting her hair to reveal her ears.

 

“Elves?” Ludmila murmured absently. She had never seen them before, only recognizing their telltale features.

 

“H-half-Elves, my lady,” Lluluvien spoke as her older sister trembled under Ludmila's touch. “We’re sorry, my lady.”

 

“Why are you apologizing?” Ludmila frowned.

 

“I’m sorry, my lady. It’s…I’m sorry.”

 

Ludmila withdrew her hand from the quivering Wiluvien, casting a questioning look at Terah.

 

“Did something happen?” Ludmila asked.

 

Terah sucked in her lips as she appeared to think on how to answer. There was clearly something going on with the two sisters, but it seemed she was a bit reluctant to share what she knew.

 

“I’m not sure if you’ll want to hear this my lady,” the maid said.

 

“This whole buildup certainly seems to beg the question.”

 

There was a pause as Terah looked to the sisters, then back at her. Her mouth worked behind closed lips, as if she was still trying to work out what she would say.

 

“Speak,” Ludmila said sharply.

 

She was growing impatient. Some time had passed and she expected someone to arrive to retrieve her at any point.

 

“They were in the service of Count Fassett,” Terah said. “The two sought refuge within the city after the battle.”

 

“That doesn’t sound bad at all,” Ludmila said, “why would you deliberate so much over that?”

 

“They weren’t maids, my lady,” Terah replied, “…they were his bed slaves.”

 

“Slavery is illegal, Mrs. Ro’eh,” Ludmila’s voice was stern. “Both in Re-Estize and the Sorcerous Kingdom.”

 

Terah shrugged, as if Ludmila’s statement could simply roll off of her shoulders.

 

“I don’t know much about laws, my lady,” she said, “but that’s what they were. Count Fassett was a powerful man in the duchy – as long as he was discrete, no one could gainsay him.”

 

Ludmila narrowed her eyes at Terah’s words. Her father had been wary of the man and shared his thoughts with his children, but she never imagined that the Count went so far as to flaunt the Crown Laws – something did not seem right. She turned her attention back to the sisters.

 

“Are Mrs. Ro’eh’s words true?” She asked.

 

“...she speaks truly, my lady,” Lluluvien hesitantly answered for the both of them.

 

“How did you come to be where you are now?”

 

“Our mother was a slave as well,” Lluluvien replied. “We were born slaves.”

 

Ludmila blinked several times at the reply, but it wasn’t the answer she was seeking. She rephrased her question.

 

“What I meant was: what happened that led up to your seeking refuge here?”

 

The Half-Elf maid looked up fearfully at her, and Ludmila saw herself reflected in Lluluvien’s eyes. She didn’t think her face was that scary – why were they so frightened?

 

“T-the Count…he sent us out to the military district to entertain his men a few days before the battle,” Lluluvien explained. “We were still there when the survivors came rushing back to the city, fleeing for their lives. Seeing how much confusion and panic there was, we went and vanished into the city, planning to escape when we had the chance.”

 

Lluluvien swallowed, staring at something in her memory.

 

“Except that chance never came. This city is now ruled by the Undead and we thought there was no way for us to survive when we saw that there was no work to be had. We returned to the Count’s manor here in the central district when we found out he had returned to the city, hoping he would take us in again…but he disappeared that very same day, and no one knows what happened to him. His household wouldn’t let us in, either. Miss Alpha found us on the street near to the manor, and she offered us the chance to work as maids in the city.”

 

Though it was an act born of desperation, Ludmila found it remarkable that they had made their way to the middle of the city when the regular citizens would not even leave their homes out of fear of all the Undead stationed in the streets. With how frail and frightened they appeared to be before her, she would not have imagined that they could.

 

“Are we fired?”

 

Ludmila looked back to the source of the voice.

 

“I’m sorry, my lady,” Lluluvien said quietly. “Are we fired, my lady? Women such as us...we aren’t qualified to serve as maids, are we?”

 

Ludmila knew that they were correct. Women of their background would not be considered suitable as maids, even in the loose sense of the profession in the central district. While she did not expect any of the hired maids here could even measure up to true maids of noble households like Yuri Alpha, their disreputable history also disqualified them even as temporary hired help. If the royal maid had not personally taken them in, they wouldn’t have even warranted consideration for training.

 

She glanced to Terah, who stood stone-faced to the side – there would be no feedback from that front. It was a conundrum where the Linum sisters’ unasked-for circumstances ran counter to their will to create a future free of that past. If Ludmila was not in such a sensitive position, she would not have any issues with taking them with her to Warden’s Vale to create new lives there. Such as it was, however, having second-generation bed slaves in her employ was both inconceivable and improper. The scales of her judgement, unfortunately, leaned clearly to one side: against her personal feelings on the matter, and she sought some way to reach an agreeable outcome.

 

She turned to examples, searching for some pretense from the past or present, and eventually thought of the previous evening in the cramped alleys of the city. Lady Shalltear had reached out to tend to the battered and sick harlot, in plain view of a throng of bystanders. It had sent a powerful message to the people, herself included. Even the city temples that she knew of might have shown open disdain for the woman, perhaps only tending to her out of sight in order to avoid unwelcome speculation. Yet her new liege had done so in complete disregard to her station as a direct vassal of the Sorcerer King and to her office as a high-ranking member of the clergy. She was in a position of incredible political power but she cared nothing for appearances – only for the will of her sovereign.

 

If her benefactor was willing to interact with a prostitute, then Ludmila could not rightly turn down slaves trying to escape a similar fate.

 

“I would like to speak with Yuri Alpha about a few things,” she said, “but no, I do not intend on immediately dismissing you. We should also have a priest examine the two of you to ensure you are healthy after your ordeals.”

 

Wiluvien turned her face up to look incredulously at the words. Lluluvien brought her sister close as she turned tearful at Ludmila’s response.

 

“Yes, my lady!” They cried, “Thank you, my lady!”

 

The sisters kept bowing and thanking her – it was already feeling awkward after the first few seconds. Fortunately, the doorbell rang from the maids’ office. Terah turned and headed out to answer, leaving Ludmila with the two Half-Elven sisters who continued with their wholehearted show of gratitude.

 

“What’s the delay?”

 

Lady Shalltear’s voice sounded from the hall, and she entered the drawing room with a pair of her beautiful attendants at her heels. Ludmila turned and stepped forward, presenting herself respectfully.

 

“Good morning, Lady Shalltear,” she said. “Thank you for personally coming to retrieve me.”

 

The maids, realizing that their mistress was addressing her own superior, immediately followed suit. Wiluvien and Lluluvien had already been halfway to their knees thanking Ludmila, and ended up with their faces to the rug. Lady Shalltear leaned to the side to look around Ludmila at the maids prostrating on the floor.

 

“Training your servants is all well and good,” Lady Shalltear said lightly, “but didn’t we have an appointment?”

 

“That’s not what I was doing–actually if you don’t mind, my lady, could you check the health of these maids?” Ludmila asked, “They’ve been through a bit of a…a…thing.”

 

She faltered at the end of her request, unable to provide an appropriate euphemism for their circumstances.

 

“If that’s all that’s holding us up, I suppose. Hmm…”

 

Lady Shalltear circled around to look down at the nearly prone maid sisters.

 

“You may rise,” she said.

 

At her voice, the Linum sisters’ kneeling forms unfolded and they sat up. Looks of awe appeared on both of their faces as they laid eyes on her peerless beauty. Without Ludmila’s Talent inadvertently tempering their reactions with her hidden appearance, she supposed this sort of enthralled state was to be expected.

 

“Well, beyond being nervous and fatigued, she hasn’t sustained any damage to her body.” The Cleric said absently as she shifted her gaze from Wiluvien to Lluluvien, “This one is also uninjured, except…ew?”

 

Lady Shalltear turned back to Ludmila. Even her monstrous appearance lurking under the enchanting visage seemed to portray a bit of disgust, somehow.

 

“Where exactly have these girls been?” She asked.

 

“They were sent to serve as…company for one of the nobles’ men in the military district,” Ludmila answered, “in the days leading up to the battle that took place at Katze Plains.”

 

“Were they intimate with anyone after that?” Lady Shalltear continued her queries, “The last thing we need is a city full of disease on top of everything else.”

 

Ludmila looked to Wiluvien and Lluluvien. They shook their heads vehemently and Lluluvien spoke, flush with embarrassment.

 

“No, my lady–my ladies?” She said, “After all t-that, we wanted to avoid it as much as possible, but…how did you know?”

 

Lady Shalltear had not appeared to cast any spells, yet she was able to discern the state of their health at a glance. Now that Ludmila thought about it, Bohdan and Sophia were able to keep the village’s health in order as well, somehow. Growing up in a village with a priest was a bigger boon than she had realized – she supposed that in a city there would be many that did not benefit from the Temples, especially if they lived a life in the shadows, or simply could not afford it. A settlement without a priest would need to rely on a local druid or an apothecary of some sort.

 

Regardless, Lady Shalltear did not deign to answer, instead reaching out for the maid.

 

“「Remove Disease」.”

 

Just like the previous evening, Ludmila saw the faint glow of magic pass over Lluluvien.

 

“There,” the Cleric withdrew her hand. “Now, shall we get to work? We have a big day ahead of us.”

 

“Of course, my lady,” Ludmila lowered her head in gratitude. “Thank you for your assistance.”