\chapter{Pandora's Actor}

The rains found E-Rantel once again in the night, assailing the city’s roofs and streets; walls and plazas as it often did in the spring. As the torrent washed the dust of the day away, lightning would occasionally make its presence known, followed by a low rumble of thunder that rattled the manor windows in their frames. Within the darkened room of the manor’s solar, a singular figure brooded on a lavish couch; the flashes coming through the windows offering occasional glimpses of his unflinching appearance.

 

Pandora’s Actor once again spent most of the day in the countryside, revisiting the towns and villages that lined the main highway from E-Rantel to the Re-Estize border. He had just recently returned from the furthest town in Fassett County, where the people had brought him to the largest tavern and detained him with an endless stream of toasts and propositions well into the evening. His role as Momon in the past few weeks was simple to perform…yet, as those weeks passed, he had come to understand that it was an arduous task as well.

 

There were dozens of towns and villages that served as the centres of their respective fiefs and hundreds of other settlements scattered throughout the territories. The Guardian Overseer kept dispatching Momon and Nabe out to the more distant fiefs in particular, as well as those communities along the main thoroughfares where information could traverse rapidly. Albedo had not voiced the reason behind these dispatches, but he knew well the root of her concerns.

 

The pall of fear still hung over the duchy, and constant vigilance was required to keep the flames of panic from igniting anew; creating a mass exodus akin to the one that had occurred while E-Rantel was still being formally ceded to the Sorcerous Kingdom. The source of the panic did not even matter: it would enter into the existing tension like a spark into so much kindling, taking on a life of its own. Their shortfalls in this task were made painfully clear by the restrictions that had been placed on them and frustrations continued to mount – it was as if their Master had, in a single elegant stroke of a brush, made plain all of their weaknesses and withdrew into seclusion to allow Nazarick’s denizens time to address them.

 

Even he had not escaped unscathed from that masterful stroke. The citizens had no trust in their new sovereign or his servants – the only individual that had earned universal recognition and respect was the persona established by their Master: the Dark Warrior, Momon. However, as Pandora’s Actor revisited the places where his previous journeys had taken him, he was dismayed to find that his efforts appeared temporary and limited: a short-lived wave of hopeful emotion created through the excitement generated by his presence. According to the escorts and observers assigned to perform reconnaissance around him, the people remained close to their dwellings even as he came calling, and returned to them not long after he left.

 

Whatever courage he inspired; whatever sense of security, seemed only ever enough to sustain their fearful watchfulness from within the perceived safety of their homes. Between all of the efforts of his fellow NPCs, little headway had been made – they provided for the people, made sure they were safe and created the mechanisms in which to secure productive and prosperous lives. Yet, even after occasionally being coaxed out to see what had been established for their benefit, the citizens were still wrapped up in their fear and anxiety.

 

It felt like he was playing to an audience that refused to receive him in earnest and the creeping sense that he was slowly, but inevitably, losing the battle to keep their fears at bay haunted him – that the spell cast upon the people by his Master, the enchantment that was the Legend of Momon, would surely break at some point and its undoing would be his own doing. That Pandora’s Actor might fail in his act created a disquieting sensation that rose from the depths of his being, and it sometimes felt as if he could hear the footsteps of failure stalking in his shadow.

 

And so he brooded. Unlike some pose that he might have struck because it fancied his tastes, he brooded in earnest and the sense of authenticity only whetted his flair for the dramatic even more: Momon of Darkness, brooding darkly in the darkness. The rain continued to lash against the manor and lightning clashed outside; he thought that the only thing that could add to the perfection of this scene was for a horrifying monster to come crawling in through the window.

 

Then, as if the world itself had catered to his whims, the next flash of lighting cast an additional shadow: its distorted silhouette displaying itself starkly on the patterned wall which he faced. He rose abruptly and turned to see the figure of Shalltear Bloodfallen floating outside, blurred by the water that washed down the glass panes. As he went to unlatch the window and opened it out into the night, he noted that she cradled a large bottle in one of her gloved hands while holding her dark parasol in the other. Shaking away the depressing threads of thought from his mind, he made to welcome his late night guest.

 

“One of the beautiful courtiers of the Sorcerous Kingdom has come in the dead night to the bedroom window of the Hero of E-Rantel – bearing a bottle of liquor, no less. This should surely be a source of the most scandalous gossip.”

 

The Vampire expressed no reaction to his greeting as the wind tossed at her hair and gown.

 

“Well, please do come in,” he stepped aside and bowed, sweeping his left arm towards the interior of the room. “You are most welcome in my humble abode, dear Fräulein.”

 

Shalltear made her way into the room, unequipping the black parasol as Pandora’s Actor received the bottle and closed the window behind her. As she seated herself on the couch across from the one where he had been brooding, he produced two fine crystal goblets and placed them lightly on the table between them. With a flourish, he wiped away the droplets of moisture that had collected on the bottle with a fine linen cloth and uncorked it, leaning forward as he filled the vessels before him.

 

He offered one of the glasses to his guest before seating himself opposite to her. Bringing his own goblet forward, he sampled the aroma of the beverage while rolling the dark liquor lightly. Its fragrance marked it as a beverage procured from Nazarick; holding little similarity to the wines produced in E-Rantel which were derived from the fruit of their local vineyards. There was another scent, however – one that had immediately caught his attention as she glided past upon entering the room.

 

“That fragrance you wear,” he noted after taking a sip from his goblet, “is not from Nazarick, is it?”

 

“My Vampire Brides picked it out today,” she replied. “From a Perfumer in the city.”

 

Shalltear produced a tiny crystal vial from her inventory, laying it on the table between them. Pandora’s Actor reached out to retrieve the item, leaning back into his chair as he examined the offered article.

 

“Oh…”

 

“Interesting, isn’t it de-arinsune?” Shalltear remarked, “Even in their weakness, they find ways to create unexpected strength with what little power they have.”

 

The vial was cleverly constructed: its size and structure made it difficult to accidentally break. In addition, it was imbued with a minor enchantment that gave it nearly negligible damage reduction. Combined with its physical qualities, he questioned whether even tossing it from the window out onto the pavement would have broken the item. Any chips or cracks that did occur would simply repair themselves due to its nature as a magic item, as insignificant as the enchantment was. In the everyday life that this perfume vial was meant to see, it was practically indestructible – one would have to go out of their way to purposely destroy it.

 

“It’s an innovative use of low tier enchantment, I agree…yet the content itself is also most curious,” Pandora’s Actor turned the vial in his fingers. “I can hardly imagine that this would be a popular fragrance amongst Humans. This individual has not only created a practical low tier magic item but, in a short period of time, has successfully devised a fragrance that seems to be quite suited to the Undead – to whom I can only presume they plan on marketing this perfume towards.”

 

He returned the vial to the table.

 

“It seems that there are many gems hidden in this land,” he said lightly, “if one only knows where to look.”

 

“How much did you know?”

 

The shift in Shalltear’s previously conversational tone gave him pause. Across from him, she held her goblet between her fingers. Her head was tilted slightly and her chin was raised as her crimson gaze bore down on him through half-lidded eyes. She was much shorter than he was, but her imperious posture very much lent to the feeling that she was looking down at him as she spoke.

 

Pandora’s Actor once again leaned back onto the sofa, unperturbed, stretching his arms wide over its ornate oaken frame as he responded.

 

“Now then…I know a great many things,” he replied in a cavalier tone. “Sometimes I surprise even myself with the depth of knowledge that I’ve been instilled with.”

 

“The noble that you brought to the attention of the others yesterday,” Shalltear’s voice did not change, cutting cleanly through his cryptic preamble, “Baroness Zahradnik. Just how much did you know about her before you brought her existence to our attention?”

 

“I didn’t lie when I delivered my thoughts on her potential usefulness yesterday,” he shrugged lightly, “though your apparent concern shortly after having her come into your care makes it sound like you’ve something to share...did something happen?”

 

“Too much has happened,” she snapped, sitting up to peer at him suspiciously. “Enough to make me believe that I’ve been entwined in someone else’s schemes de-arinsu.”

 

Shalltear’s behaviour suggested that the piece that he had put into play had done something extraordinary in her eyes – to a degree that perhaps exceeded his initial expectations. He had cast the die on the matter of the young Baroness at the previous evening’s council meeting, but he had certainly not expected significant returns on his gambit within a day.

 

“Then let us go over what causes you to believe this to be the case,” Pandora’s Actor leaned forward, folding his hands in front of him. “I would very much like to hear of your experiences with this Human.”

 

Seeing that she would get no direct answer to her suspicions, Shalltear settled into her seat and began to speak at length about the past day. She spoke of her first encounter, their journey through the streets and time in the alley; the discussion of that evening; of her time in the civil office and the day they had spent traversing E-Rantel to make connections, secure capital and begin her efforts to rebuild her demesne. She spoke of the noblewoman’s personality and conduct, the interactions she had with others, and even her cursory thoughts on the future of the Sorcerous Kingdom.

 

Throughout her account, Pandora’s Actor had her stop to clarify various details. He had her expand on her feelings during those experiences, the atmosphere they carried and her observations of the scenes that surrounded them. He beseeched her to share her thoughts on the events that occurred and he would have her hold so he could digest her words and think quietly on their meaning. The night grew long as they sat across from one another and spoke; the bottle of liquor slowly draining away. Even after her words ran dry he remained seated, deep in thought, reviewing what she had said.

 

“The way you describe it,” he murmured thoughtfully, “she appears to possess some mysterious power beyond our comprehension.”

 

“She does have powers – which makes it all the worse because, but for a single case, she hasn’t really used them to directly achieve any of her ends in any meaningful way. I’ve been with her for most of her waking hours, observing and asking questions. The administrative systems that Albedo has prepared are as simple to understand for her as Albedo claimed they would be to any of these Humans. The tasks that Baroness Zahradnik set before herself were done in the mundane order and manner that she described. Interactions – discussions, transactions and even small talk were nothing if not normal.

 

“In the space of a single day de-arinsu, she has accomplished in her own small way what none of us could in a week. She navigates this absurd Human society with no more difficulty than you or I would walk through the floors of Nazarick. As she makes her way, everything seems to naturally shift into place: obstacles are only detours – pieces of the puzzle grow legs and walk over to where they need to be. All that she understands and does works in the same way as we ourselves understand their workings, yet she is able to do what we haven’t been able to despite our own best efforts. It is as if we all have the exact same key to the exact same lock to the exact same door, yet only she knows how to open it de-arinsu.”

 

It was as he had suspected. While not exactly noted for her intellect, Shalltear’s intuition was extraordinarily keen compared to most of the other NPCs. In his own travels with Nabe throughout the lands of the new realm, Pandora’s Actor also felt that there was something missing, even while he played his role as the Dark Warrior. It was akin to lifting a tablecloth the size of a nation at a single point: once he let go and moved on to lift the next point, the part of the fabric that he had raised up simply returned to the surface of the table and ultimately nothing would change. Though she might not be able to articulate her thoughts concisely, Shalltear seemed to have surpassed that understanding in the short time she had taken responsibility for the young noblewoman through experience and intuition alone.

 

Pandora’s Actor rose from his seat to pace back and forth across the red carpet beyond the seats in the room. He cradled an elbow in one hand and his chin in his other and occasionally stopped to motion vaguely into the air as various thoughts came across his mind. Sometimes he slowed as if to speak, then abandoned the idea and continued his pacing. Shalltear absently reached for the bottle to refill her glass, but she found that it had been completely emptied and it made a hollow noise when she placed it back onto the table.

 

“Did you tell her something? Teach her some secret, perhaps?” Her queries prodded him from his thoughts, “Or did Ainz-sama instruct you to do this?”

 

The latter part of her string of questions held a hint of jealousy within them; since the founding of the Sorcerous Kingdom, their Master had kept himself mostly secluded from his servants so his attention was at an even greater premium than it usually was.

 

“No,” he responded as he stopped his pacing to answer her. “Our Master gave me no direct instructions on this matter…though one may consider it a rough extension of the role I play as Momon to help stabilize the realm. My interactions with the young Baroness have been nonexistent since she and I parted ways before the council meeting yesterday – I only admonished her to keep her reactions to what she observed with her Talent in check as to not disrupt the lives of the citizens of the realm, appealing to her orderly disposition.”

 

“Well, she certainly seemed to take your words to heart – she barely reacts to anything.” Shalltear sighed, “Then the truth of her work eludes us; it is as if all the mechanisms of this world only respond to her act de-arinsu.”

 

Pandora’s Actor stepped forward to begin pacing anew, then he stopped and suddenly rounded on the Vampire reclining on the couch.

 

“...what did you just say?” He asked her quietly.