\chapter{Ludmila Zahradnik}

The sun was hanging over the battlements when the Soul Eater parked the wagon in the service lane behind the manor. After sending Aemilia into the house with their things, Ludmila instructed the Death Knights to carry the crates and barrels of food into the cellar.

 

“Is the ship still there, my lady?” Ludmila asked.

 

“This child came back right after they located it.”

 

Lady Shalltear pointed to the air above their heads, where Ludmila noticed a small black bat fluttering about.

 

“The rest stayed to guard the location,” Lady Shalltear told her, “so it should still be there unless it somehow dislodges itself and continues downstream.”

 

The footmen returned from their task and Ludmila directed the Soul Eater to meet her in the port village of Corelyn Barony. She fell in step with Lady Shalltear as they walked along, entering a service lane behind her manor.

 

“Are two Death Knights enough to move something that heavy?” Ludmila asked.

 

They left the service lane, and it turned out that the gardens between the clubhouse and the Royal Villa were not far at all if one cut through the back ways.

 

“Going by what was conveyed to me,” Lady Shalltear answered, “they should be able to work it off whatever it’s caught on. Are we ready to depart?”

 

“Yes, my lady,” Ludmila replied. “Thank you.”

 

“「Gate」.”

 

The familiar black portal opened in the air before them in the centre of the gazebo. At Lady Shalltear’s prompting, Ludmila stepped through. She blinked as her vision shifted from the surface of the gate to the filtered sunlight of the ravine that was their destination. It was close to where she had expected their location to be by the description that was given earlier. The river flowed down from the south, coming out of the steep gorge that started at the southern end of Warden’s Vale. Its flow was broad and deep, curving around the northern edge of the barrier ranges to meander its way eastwards towards the Katze Plains. She could see signs where people had waded to the shore, leaving prints on the riverbank and a trail of disturbed plants up and into the forest above.

 

The Death Knights appeared through the gate behind Ludmila and Lady Shalltear and her attendants appeared shortly after.

 

“Oh, it’s a Knarr,” Lady Shalltear said when she laid her eyes upon the vessel.

 

“Is that what this type of boat is called, my lady?” Ludmila asked, turning her attention back to the river. “We always just called it ‘the boat’ or ‘the ship’.”

 

“Even though you’ve used it for generations?”

 

“It is the only such vessel in use around here,” Ludmila shrugged. “I suppose there was no need to refer to it as anything else. How did you know what it was called?”

 

“One of the territories at home has several vessels of similar appearance,” Lady Shalltear said. “Still, it’s strange that you don’t even know what you’ve been using. How did it come into your House’s employ?”

 

“My ancestors found it mostly intact on this river somewhere. The villagers managed to refurbish it for transporting goods back and forth from E-Rantel…we never learned how to build more of them, but if what is claimed about the Undead labour in the administration’s materials is true, we will need more vessels like this to keep up with my fief’s production.”

 

Lady Shalltear’s gaze crossed over the boat, then looked out over the river.

 

“This type of ship is designed for travel on both rivers and large bodies of water,” she said. “Perhaps, if you travel further down the river, you will find out why it was here – perhaps you will find more ships to use as well.”

 

“It may be as you say, my lady,” Ludmila agreed. “Besides, one day I would like to see where the river leads.”

 

There was a mass of chittering in the air above, and she looked up to see Lady Shalltear’s Household fluttering down to disappear into the shadows surrounding her. The Vampire watched from an outcropping that overlooked the riverbend as Ludmila directed the Death Knights to extract the Knarr from its predicament. After it had been worked off of the hidden stones and placed fully onto the water, Ludmila stepped over the railing and into the boat as the Death Knights held it fast against the current. She walked up and down its length and hopped a few times in different places, but could not hear or feel anything amiss. Ludmila looked up to Lady Shalltear.

 

“I need to take the ship to the village port south of E-Rantel,” she called up to her, “would you like to join us, my lady?”

 

“You go on ahead,” the Vampire made a waving motion. “I need to prepare for the daily meeting of the Royal Council. I’ll find you after we’re done.”

 

“Ah…we may have to meet again tomorrow morning then,” Ludmila apologized, “the current in the spring is swift, but I will still only arrive some time in the middle of the night – or perhaps early in the morning.”

 

“That long? Can you operate this vessel between the three of you?”

 

“I don’t need the sails going downstream,” Ludmila said. “All I need to do is keep the ship away from the shore; the river is quite deep. Come to think of it, the navigators always preferred that I take the night watch...I guess I never realized why until now.”

 

Lady Shalltear looked down at them for a moment before floating down.

 

“Is something the matter, my lady?” Ludmila asked.

 

“Too long,” Lady Shalltear said. “You still need to buy what you need for your work in the barony, and we need to get your Undead labourers on their way.”

 

She looked over the Knarr, then out at the river again, at a point not far downstream.

 

“「Gate」.”

 

A black portal wide enough for the ship to easily pass through appeared in the river. The roar of churning water issued from behind it.

 

“This will take your ship to the section of river before the port,” Lady Shalltear told her. “I’ll meet with you after you return to the city.”

 

“Thank you, my lady.” Ludmila paused for a moment before asking, “What happens if I am unable to get the whole ship into the Gate?”

 

“I don’t think anyone has purposely tried that before,” Lady Shalltear answered. “I’d advise against you experimenting with it.”

 

Ludmila called the Death Knights to board the vessel and slowly steered it out from the shore as the current began to move them. Their course stayed true, until they started getting closer to the Gate. The water near the edges of their route was being drawn around the Gate due to the tumultuous current caused by the gap in the river behind the portal. She struggled with the tiller, trying to keep the vessel straight, but it started to veer and tumble on its axis. Fortunately, there was still enough space to fit through even while the ship was oriented at a strange angle.

 

On the other side, the abrupt change in current jarred the vessel after they left the Gate, throwing all of its occupants off-balance. One Death Knight was driven to its knees, while the other was thrown completely overboard with an unexpectedly quiet plop that was drowned out by the roar of the water leaving the portal behind them. Ludmila was painfully knocked into the tiller, causing the vessel to lurch violently even further and she leaned limply over it, winded by the impact. Through teary eyes, she recovered her footing and straightened the boat’s course once again as the portal silently shut far behind them.

 

Ludmila worriedly scanned the water’s surface, searching for the Death Knight that had fallen overboard, but there was no visible sign of its passing, nor anything at all to indicate where it actually was over the murmur of the river. Hoping it was still somewhere nearby and had not been carried far downstream by the current, she called out over the water, instructing it to follow them along the northern riverbank. A few seconds later, she sighed in relief as its horned helmet broke the surface of the water and it stomped its way onto the shore to follow them, armour glistening wetly in the late afternoon sun.

 

Leaning back tiredly into her seat, Ludmila placed a hand on her sore abdomen. Not far ahead, she saw the familiar sight of Corelyn Village’s earthen jetty. Like the one at Warden’s Vale, it had been built to deflect the river current and provide a calm harbour to moor vessels in. She directed the Death Knight on the shore to run ahead to the harbour and grab a large rope to throw to its fellow on the boat when they maneuvered in closer. Between the two sturdy Undead, the ship smoothly pivoted around the jetty, its momentum carrying it all the way into the calm waters of the port. As the boat lightly bumped up against the pier, she hopped off to secure it to its moorings.

 

While she worked, a scream drew Ludmila’s attention towards the village, where a girl had appeared from a building not too far from the shore. She turned in a panic, stumbling over her feet several times as she fled.

 

“Wait!” Ludmila called out after her.

 

The fleeing villager did not stop, even though Ludmila had unconsciously projected her ability along with the word. The girl did not even slow at her voice as she scurried away down the empty village lane, shedding doubt on her confidence that she could use her abilities properly. The sight of the Death Knights stomping after the girl to make her ‘wait’, however, did not give her much time to ponder. She hurriedly recalled them before inadvertently starting some sort of mass panic in Clara’s home village. The encounter had her decide against waiting on the Soul Eater at the port, and she led her footmen onto the highway to meet the wagon on the way.

 

She spotted the Soul Eater already galloping down the hill from the city. The roads allowed it to speed along without damaging the wagon and, within another fifteen minutes, it came close to where they awaited it on the highway. After it had turned the wagon back around towards E-Rantel, she hopped on and it took off back towards the city. Now that she was a passenger, the ride did not seem as smooth as it had looked when the wagon had come down the hill. As it was formerly a part of Rampossa III’s demesne, the highways had been paved, making them much better for carriages, carts and wagons to travel on. At the wagon’s current speed, however, Ludmila was vibrating so violently in her seat that she held worries as to whether the vehicle would shake itself apart before they returned to the city.

 

The Soul Eater assumed a canter after she became concerned enough to tell it to slow down and, a little over thirty minutes later, they arrived at the massive main gate of the city. The two Death Knights on either side of the entrance looked towards her briefly before returning to their watchful vigil. They did not move to impede her as she entered, and the wagon thankfully rumbled through at a much more reasonable speed than it had taken north along the highway.

 

As they crossed into the military district that lay between the outer and second walls, it occurred to Ludmila that she had forgotten all about her labour force. Standing up as the wagon rolled by where they were ordered to wait, she spotted them neatly arranged exactly where they should have been. She sat back down, feeling a bit guilty about neglecting them for so long, but at the same time wondering if they would wait forever if they were just left there.

 

The wagon made its winding way through the thoroughfares of the city towards the main plaza, and Ludmila looked up towards a familiar, barely audible chittering noise – a small black bat fluttered above them. Further above, she spotted the Elder Lich, who might have been trailing her the entire time. She wondered if the Imp was lurking about somewhere as well. She was about to order the Soul Eater to stop and see if Lady Shalltear would appear when her liege suddenly alighted on the front of the wagon, the lacy frills of her gown fluttering in the wind. Without a word, she once again seated herself beside Ludmila, as if dropping out of the sky in such a manner was perfectly normal.