\chapter{Ludmila Zahradnik}

The cool air of the spring evening greeted them as they left the Merchant Guild and descended the stairs to where the wagon awaited in the plaza below. Ludmila flipped through the materials that she had received from the clerk briefly before returning to study the invoice template. The paper was more sturdy and thicker than a normal sheet would be, feeling slightly heavier in her hand; it was designed to be durable as a long term reference to create duplicates from. She had a thought and turned to the Elder Lich.

 

“Are you able to create copies of this template?” Ludmila asked.

 

She held out the sheet, and the Elder Lich immediately took it into its hand.

 

“Easily.”

 

The Undead attaché’s raspy voice held no apparent emotion as it spoke, but the near instant reply gave the impression that it had scoffed at her question.

 

“I need five copies for this evening,” she instructed her attaché, “and fifty additional forms by the morning.”

 

It faced forward and set about its task as the wagon rolled off towards its destination. The flutter of leathery wings turned Ludmila’s head towards the Elder Lich again as the Imp alighted on its shoulder. She watched as her attaché held out a solid board that it had produced from somewhere to use as a writing surface. The Imp deftly drafted the first copy not long after as the pair floated forward alongside the wagon. They studied the work together and, after finding the results satisfactory, continued their task.

 

“Is it really necessary to have that many copies at once?” Lady Shalltear voiced her question as the shadows of the eastern quarter fell over them.

 

“They are for the residence in the city, my lady,” Ludmila replied, “if my household needs to order anything or do any other business on my behalf, they will be able to use the account at the Merchant Guild if I prepare forms in advance. The manner of conducting transactions that the clerk described seems to have fewer faults than simply handing over a bag of coin to be kept in the manor.”

 

“You don’t trust your servants?”

 

“Well, I have barely known them for a day,” Ludmila said, “though even if they had earned decades of trust, the system in use by the Guild still seems far more elegant overall in function. Out in the barony, there will be a need for funds on hand so it will be the usual methods there.”

 

“The lives of Humans seem filled with uncertainties,” Lady Shalltear shook her head. “You cannot trust your servants and your purpose in life is undefined and seemingly ever changing.”

 

“You are able to always fully trust your servants, my lady?”

 

“Of course. All the way down to the lowest being. They are bound to me – inextricably a part of my realm. Having them turn on me of their own will would be as inconceivable as your legs walking off without the rest of your body of their own volition. Deception in crucial matters is unthinkable, as is failure,” Lady Shalltear’s gaze observed the surroundings that they travelled through. “Yet Humans can ignore their obligations so easily. So few continue to function in this city, while the rest neglect their roles in your society to the eventual ruin of all. I’ve even witnessed those that would turn on their fellows, if only for a moment’s reprieve from their hardships.”

 

Ludmila listened quietly as her liege spoke. That everyone who served her could be treated with such confidence felt fantastically unrealistic. It was no small wonder that the Royal Council would be frustrated with the seemingly unreliable citizens of the duchy if this was truly the case. Perhaps the Sorcerous Kingdom would always look down on their Human citizens, as the current issues were the result of Human nature rather than any willful resistance or insubordination.

 

“It is difficult to refute your words with things as they are, my lady,” Ludmila said, “though I had not realized there was such a difference between the Human realms and your own. His Majesty shows great insight to have retained the laws of the realm, even when considering his existing vassals. Rather than have them directly dealing with the unfamiliar in an effort to manage the population directly, his decision allows those accustomed to the workings of their own to make changes smoothly.”

 

“Then what am I to do with you, I wonder?” Lady Shalltear turned her face towards Ludmila, eyes glowing at her as they went from shadow to shadow, “you are now mine – an odd vassal that does not quite fit in with the rest.”

 

Uncertain of where she now fit into the grand scheme of things, Ludmila could not answer.

 

“In many ways,” Lady Shalltear continued, “you are much like me in your role as a frontier noble. You guard the realms of your liege in a roughly similar function as my own in defending His Majesty’s realm. It can even be said that your burdens are far greater. You have not been gifted with great strength, nor vast intellect or powerful magic. Your demesne does not possess strong fortifications or armies. You are ignorant of the world beyond your borders and you are pitifully weak, but you will toil and struggle and fight and die against any and all intruders that would come, as your House has done for generations. Yet, for all of these efforts, your names become as dust to those that reap the benefits of the peace that you win for their lands.

 

In many other ways, you are different. You have ambitions beyond the immediate service to your liege, and you act as if it’s a natural thing. You actively seek the strength of others with the understanding that you’ll never truly be able to fully trust them. You are ultimately Human, and bound to your Human nature.”

 

Ludmila was at a loss as her liege conveyed the evaluation. She thought Lady Shalltear had followed her mostly to learn about the city and its workings as well as possible solutions to the predicament that it faced. Ludmila had not realized that she herself was being carefully watched the entire time as well. For all of her strength and influence, the Vampire had kept mostly to herself throughout the day as she had quietly observed her. She thought of the tales of another Vampire, Landfall, and wondered if Lady Shalltear’s behaviour was due to being a wise and perceptive Cleric, a predator accustomed to stalking their prey, or perhaps both.

 

Ludmila pondered her liege’s words, trying to find an answer they could both find satisfactory.

 

“My lady, the relationship between a vassal and their liege is maintained by contract.” She began tentatively, “For most nobles, especially those of the interior, it has become a sort of formal negotiation where those long established in their rule find agreeable terms between themselves. This contract – a pact of oath and obligation; duty and fealty – is the foundation of noble society and these realms by extension. It is the core of the relationship between liege and vassal, be they king and noble vassal, or landlord and tenant.”

 

“Go on…” Lady Shalltear had her chin in hand, looking up at Ludmila as she spoke.

 

“Nearly two centuries ago,” Ludmila continued, “when people came to settle the lands that would become Re-Estize and Baharuth today, there were no ties of blood, culture or trade that bound society together. There were only the leaders who established themselves over their people, carving out borders and defending their lands against any and all that would challenge the order that they sought to establish in the wake of the Demon Gods. These were the founders of the aristocracy of the Human nations of the north – nobles not unlike the frontier nobles: great captains of men and militant in both mind and disposition. The most prominent houses became the Marcher Lords: many of which you still see holding these titles today, though they mostly no longer carry the same traditions as their ancestors.

 

One house – the House of Vaiself – eventually unified the lands through diplomacy or war and the nobles who fell in line formed contracts between themselves and the throne. These contracts defined the relationships between House Vaiself and their vassals, continuing down the hierarchy of administration to form the foundation of Re-Estize. This contract, the oath of fealty between liege and vassal, is the core of what it means to be a noble of these lands: without it we are not much more than simple despots.”

 

“So what do these contracts look like?” Lady Shalltear asked.

 

“Well…I had thought to bring ours with us but decided to leave it at home since the duchy was fully ceded to an entirely new sovereign. That contract is effectively void now, but some may attempt to have old contracts ratified under their new liege in order to retain certain privileges from the previous government. I suppose since the transfer was so…clean, it would encourage at least a few to try.”

 

“Ah, so that’s what that was all about,” her liege seemed to remember something.

 

“My lady?”

 

“That noisy Count,” Lady Shalltear had a decidedly unimpressed look as she recalled the memory. “Fassett or something. Once it was clear that E-Rantel would see a bloodless transition, he came into the council chamber – bold as you please – demanding that his rights be recognized. As you might imagine, he got a rather cold reception: Cocytus flung him into the Gate that I opened even as he continued shouting about it. Considering how hard he was thrown, he probably didn’t survive the landing.”

 

“I thought there was only one place where you could use teleportation spells in the central district.”

 

“He came quite quickly. We were still implementing the framework for the government and finalizing security arrangements.”

 

“The Royal Court did not even wait to hear him out, my lady?”

 

“Oh, we did,” Lady Shalltear said. “He was very spirited, so we thought that this noble who had approached us before we even officially started our work must have possessed some merits. It was mostly preposterous, though – I think the disappointment added to his velocity.”

 

“Then what did he say?” Ludmila asked.

 

“Hmm…a few things that should have been a given: faithful service, some amount of taxes, the pledge to provide a levy, tributes for special occasions.”

 

“These are fairly standard in an oath of fealty,” worries began to mount in Ludmila’s mind, “though the details may vary…what did the Royal Council find offensive, exactly?”

 

“Well, he did deliver it in a very loud and presumptuous manner, but there was also his list of demands. In addition to the guarantee of his title, he wanted ownership of the abandoned territories bordering his own. Then there was the obligation to have His Majesty stand in his defence in court, as well as the full protection of all of his armies, the rights to enforce regulations upon the Guilds and control over the western highway that ran through his fief. He went on for quite some time, but I lost interest partway – the man was clearly not going to survive his audience.”

 

It was a mix of demands that were mostly within the realm of reason, though the expansion of territory and control over the Guilds was brazenly overreaching at best.

 

“Lady Corelyn mentioned something about other nobles vanishing as well,” Ludmila said. “Did they end up like Count Fassett?”

 

“Not that I can remember,” Lady Shalltear said. “Some fled their holdings after their audience – we didn’t care to detain them since there was no point in keeping administrators who were willing to abandon their responsibilities. The remaining nobles were advised to avoid committing the same offence as Count Fassett.”

 

“So none have attempted to reinstate old contracts or create new ones?” Ludmila frowned.

 

“Not a one,” Lady Shalltear replied. “Though I don’t even see a point to your asking. Some of what Count Fassett either offered was what should already have been a given and he asked for the same. Everything else was anywhere from incomprehensibly greedy to outright blasphemous.”

 

“It is still an integral part of a noble’s life,” Ludmila said. “Without it, the relationship between vassal and liege remains undefined and we are effectively without purpose. Some nobles need to add uncommon clauses to their contracts as well. Frontier Nobles, for instance, pledge to protect the realm’s borders. Since their territories are usually not that well developed, their liege is expected to put together a stipend from the other nobles in the demesne that benefit from their protection in order to maintain security. Is that so unreasonable?”

 

“No, not at all,” Lady Shalltear replied. “But it is not rooted in selfish greed like the terms Count Fassett dared to push on His Majesty.”

 

“So you would say that arrangements which are reasonable for the fief in question, or benefit the realm as a whole are acceptable?”

 

“Of course, but you had better be prepared to provide an explanation if I ask.”

 

“I think we should sit down together at some point and work this out, my lady,” Ludmila was still uncertain of what was safe to ask. “I do not want to inadvertently add some clause that would result in being thrown to my death if I can avoid it. It can come after I have done all this though – I still do not know what His Majesty wants from the nobility for the long term.”

 

The Soul Eater brought their wagon around a corner, where a large workshop of brick and stone occupied most of the city block. During their conversation, they could hear the sounds of the forge working out of sight as they approached from down the street, so the conversation invariably wound down.

 

“You’re probably thinking too much,” Lady Shalltear said. “You Humans are weak, and military support in the fashion of your former arrangement means little to nothing. There are those that would say that being productive and paying your due is good enough.”

 

Ludmila’s heart sank at the words, and she shifted uneasily in her seat. Her original expectation when Momon had delivered the royal missive in Warden’s Vale was that she would continue to carry on in the duties of House Zahradnik, much like how her family had served House Vaiself. However, nothing she could offer seemed to mean anything – indeed, the Royal Court’s perception of what held value was foreign to her own. A gaping void in her identity had suddenly appeared, and there seemed to be nothing that she could fill it with.

 

Lady Shalltear had described herself serving a similar role in the Sorcerous Kingdom to her own, so Ludmila was hoping that she would be able to empathize with her situation somewhat.

 

“And you, my lady?” She asked, her hopes dimming, “What do you think of this?”

 

“In all honesty, I don’t really see any point to it,” her liege answered, “but it is His Majesty’s Will to give Humans their…space. His ways have ever always eluded us in their entirety, so perhaps there are some things that we may not understand or appreciate yet.”