\chapter{Ludmila Zahradnik}

Ysbrant Mesmit grumbled to himself as he walked up and down rows of pallets piled high with spears, tightening the ropes that secured the oiled tarps laid over them. The hardened earth in the shadows of the makeshift lanes were still damp with the rain from the previous evening, and he could see laden clouds once again rolling down over the distant foothills of the Azerlisia Mountains to the north. He thought he heard the rumble of thunder carried on the evening winds and picked up the pace of his work – the last thing the shop needed was to have one of the protective covers ripped away by the stormwinds and his inventories exposed to the deluge that was sure to come.

 

After he was satisfied that everything was tied down properly for the night, he made his way back to the forge complex, stomping his heavy boots as he crossed the open yard in an attempt to dislodge the mud. He reached the first door and stopped, grunting in annoyance – the habits of his usual routine had brought him to the mill first, but the building had already been locked up for days. Events since the autumn had thrown his entire business into disarray as the patterns of industry were cast to the winds.

 

The space that was filled with spears was supposed to be the ore yard for the mill, but they had long since run out of ore to process. The spears in the yard were originally an order for the Royal Army, but the army had been routed on the first day of the annual skirmish with the Empire and so the majority of the weapons were left unclaimed and unpaid for. The confrontation itself had been pushed back from autumn to late midwinter, upending the usual cycle of production for the city’s forges.

 

They had to switch their efforts from forging spears to rushing tools and parts for all of the duchy’s territories that had suddenly found themselves with unexpected, additional manpower to perform their regular seasonal work. Then the advance orders from the Royal Army came in, forcing them to suspend the work they had switched to in order to fill the mounting demands of the nobles that were coming with their levy of hundreds of thousands of men.

 

His grumbling turned dark as he thought of all the wasted fuel and labour. The spears were now slowly being turned into plowshares, shovels and other tools as he could do nothing but redirect his workers once again to prepare for the planting season. Sheltered in buildings out of sight and away from the streets occupied by the Undead, they worked long hours into the night in the effort to reverse their bad fortune.

 

The faint sound of an approaching wagon turned his attention away from his grousing. He left the door to the mill and jogged across the yard to the main gate, unlatching it and pushing it open slightly before heading to the warehouse nearby. He grabbed a clipboard that was hanging just inside the entrance of the building and turned around just as the sound of the approaching vehicle stopped in the alley on the other side of the wall. A shadow separated from the one cast by the wagon, which was shortly joined by a second. Ysbrant straightened his posture as light steps approached the gate.

 

Rather than a merchant and his assistant or a pair of noble retainers, however, two finely-dressed women slipped in through the opening provided. The first was a moderately tall and slender young woman in her teens. Her forest green dress with few flourishes gave the impression that she was attempting to balance a feminine appearance with an outfit functional for more mundane activities.

 

The second woman projected an image which eclipsed the first’s. Though she only stood below her companion’s shoulder, she had a stunning appearance that would have drawn longing gazes everywhere she went. Her own outfit seemed incalculably valuable: an elaborate ballroom gown seemingly woven from silken shadows that devoured the evening light.

 

Their attire was in stark contrast to the rough and dirty surroundings of the forge. He had not seen the second woman before – with her unforgettable appearance, he would have had to have gone senile to not remember her – but the first seemed familiar somehow. After considering that she was just barely an adult, he was finally able to put a name to her face. She was taller since the last time he had seen her.

 

“Hm...the Zahradnik girl, isn’t it?” His voice came out gruffly, “In that fancy dress that your brothers complained about too. Here to use your allowance to buy a spear this time?”

 

Surprise briefly passed over her face at his recognition before she smiled slightly and spoke.

 

“My brothers must have said something memorable for you to remember that.”

 

Ysbrant grunted and he scratched the stubble on his cheek. The girl had a disposition much like her father’s – casually receiving his jabs and returning with an unruffled reply. Her companion showed no reaction either way, scanning the contents of the yard as if a workshop lot was an uncommon thing.

 

“So, what are you here for?” He asked.

 

“I need to purchase tools and parts,” she replied. “Do you have any in stock?”

 

Upon hearing her request, he sucked in his lips and stood in silence for a while. That she had come personally without any of her family seemed like bad news. Considering the fate of most of the Royal Army that winter…well, it was probably better left unspoken – he was already worried that he had unwittingly slighted her by reopening recent wounds, unaware of her family’s fate.

 

“I see.” He finally replied as he turned around to pull open the warehouse doors, “Well, take your pick.”

 

The space inside was filled with equipment, tools and parts for all sorts of labour. The women looked about silently as he continued speaking.

 

“It’s already spring, but no one’s come to buy anything,” he explained as he led them through the building. “Plenty of nobles should’ve sent in their orders by now and we’d be pushing our goods out nonstop, but production’s about to stall for lack of proper storage since no one actually is.”

 

“It looks like your workshop is still running, though.” Lady Zahradnik said as she handed her order to him and turned to motion for someone in the direction of the gate to bring in her wagon.

 

“A forge is expensive to run,” Ysbrant replied as he looked it over, “can’t just stop half way and pick things up the next day. We were going to keep working ‘till the current batch of fuel was out, but it looks like we’re gonna have a bit more space available after this order here.”

 

He turned to walk away before he even finished his sentence, heading out the opposite end of the warehouse and into the smithy.

 

“Hey Satch,” he spoke to the first body he came across, “get some of the guys and help load this wagon.”

 

“Yes, Forgemaster,” the young journeyman replied.

 

Muffled voices could be heard shortly after, and several other journeymen appeared, along with a handful of apprentices. One pushed a cart into the room and the others set about while listening to his instructions. They worked together to move the first of two wide gang ploughs that were on the young noblewoman’s order. They were wrought from iron, and it took several minutes to move. The group got about as far as the exit of the warehouse to the yard before they found themselves facing two undead – Death Knights, if he had heard correctly from the procession some days ago – as well as some sort of horse creature hitched to the wagon. The two groups stared at each other for a good three seconds before his employees backed away and turned around as one, leaving the cart with the plough behind.

 

The Forgemaster sighed as Lady Zahradnik directed the Death Knights to load the plough onto the wagon.

 

“Sorry for the trouble,” he apologised.

 

“I suppose it was to be expected,” she said. “It is already quite a feat to have working staff at all.”

 

“The ones you see are all live-in apprentices and journeymen. They’ve been able to ignore what’s going on outside, busying themselves with work. They’ll probably end up doing that as long as they have something to distract themselves with.”

 

Ysbrant felt a bit dissatisfied as he spoke about his employees. It seemed rather shameful that these two women were able to function normally – the Undead even seemed to be working for them – while his own men were basically carrying on by denying reality. Sooner or later they would have to face it, and he wasn’t sure how things would pan out. The first of the ploughs had already been securely loaded by the time the next one was rolled out on another cart. The two groups somehow alternated to avoid contact with one another as they continued delivering tools to the wagon.

 

“I am just glad I could find someone to purchase equipment from,” the young noblewoman said as the three of them watched the strange dance going on in front of them. “Once the other nobles get back to managing their fiefs, you might have a monopoly on their business.”

 

The Forgemaster snorted.

 

“If only it was that easy,” he replied. “A big noble like Jezne or Fassett could clean out my entire inventory ten times over in one trip and still come back for more later. I don’t even have the raw materials with all of the trade dried up. Even though the other forges might not all be working, they’re still hoarding what they have left.”

 

He pointed over to a different part of the yard, where the thousands of iron spears were laid out, covering most of the open space along the far wall.

 

“Only thing that’ll probably keep us going are all the unclaimed weapons that the Royal Army didn’t pick up,” he said. “They ordered them to replace lost or broken equipment for the month or so that they expected to be here for, but now we’ll have to melt them back down and recast them for lack of ore.”

 

“Did they pay you for the spears?” The Baroness asked.

 

“Nope. Just have to make do. The city’s feeding the people for free right now, so at least we got one less thing to worry about. Want to buy one?”

 

Lady Zahradnik replied after considering his offer for a moment.

 

“Now that you mention it, yes. A few other things as well, if you have them.”

 

“Hah. Guess I was right when you came in, after all.”

 

Ysbrant led the group away through the complex as the wagon continued to be loaded, taking them between the buildings towards the back door of the closed shop that faced the street. It was propped open by a large stone, but the interior was not lit. He strode in without slowing, hitting the service bell with his palm as he passed the sales counter and walked straight to the storefront to open the wooden shutters.

 

He unleashed a great amount of clattering, curses and stomping about as he moved across the windows to open the locked shutters facing the street. Most of the store was a showroom for equipment: suits of all types of armour as well as a variety of weapons displayed in the rows. He returned to the counter and slapped the bell again, and when there was still no response he started hitting it repeatedly.

 

Muffled yelling could be heard from above, but he kept striking the bell. Finally there was the sound of someone coming down the stairs in a rush and the sound of the bell stopped. A man in his twenties looking half-asleep came down out of the stairwell and immediately started shouting.

 

“The hell is wrong with you, you fat sack of sh–”

 

“Customer.”

 

Ysbrant cut him off, anticipating his outburst. With business as it was, his shop clerk had turned into an inactive lump, sleeping most of his days away.

 

The man on the stairwell abruptly cut off his words mid-sentence, looking to the group, back to the Forgemaster, then back again. He finished his descent while tucking in his shirt and grabbed a worker’s hat to cover his unruly head of hair. Putting his palms together, he seemed uncertain what to say after his coarse display.

 

“Feel free to take a look around,” the Forgemaster filled in for him. “This guy’ll take care of you if you find something.”

 

As the two noblewomen browsed the aisles, the man stepped out from behind the counter to follow. Ysbrant folded his arms and leaned against the doorframe leading to the back as he watched them. Lady Zahradnik stopped to take a spear from a rack that lay against the near wall. The smooth wooden haft of the polearm was as tall as she was, with a steel blade that extended an additional forty centimetres.

 

“You use a spear?”

 

There was a pleasant sounding voice as her companion spoke for the first time, but Ysbrant frowned when a dubious expression appeared on the girl’s face as she examined the weapon. It reminded him very much of a prideful noble that looked down on equipment that did not strike their fancy.

 

“Our entire village was trained to use them, my lady,” Lady Zahradnik replied as she placed the spear back and examined another, “we found ourselves fighting monsters and beasts perhaps more than Demihumans; they are well suited to dealing with those problems.”

 

As Ysbrant pondered who the girl that Lady Zahradnik was deferring to might be, he saw her eyes go to the spear that the taller woman had just rested back on its stand. She examined it with that same, dubious expression for a while before her delicate, gloved hand reached up towards the blade of the spear.

 

The Forgemaster straightened from where he was leaning to warn her of the sharpness of the blade. Before he could, however, he saw her pinch it between two fingers. It bent suddenly at a ninety degree angle, then was just as suddenly straight again. If the girl had not been surreptitiously peeking about after the fact with a guilty look on her face, he would have sincerely doubted what had just happened.

 

The shop clerk was too preoccupied gazing at the women from behind and had not noticed what had happened to the poor spear. When his eyes met with hers, she offered an innocent smile as she put the spear back on its mount and the clerk’s expression slackened in a ridiculous way until Ysbrant walked up to slap him upside the back of his head.

 

He gave the clerk a glare after the man turned on him with a hurtful expression and, by the time they looked back to the aisle, the two nobles had disappeared around the corner. The spear which had been mysteriously bent and unbent was missing from its place on the weapon rack. Over the displays he could see the points of two spears being carried to the clerk’s desk, so Ysbrant turned around to see what had happened after Lady Zahradnik laid them upright against the counter.

 

While this spear in particular was a weapon that one might find commonly wielded by the city militia, it was still forged out of good steel and by no means of poor quality. As he peered at the spearhead, he could see the line where the metal had been stressed and shook his head in puzzlement as he ran his fingers over the surface of the blade. The only reasoning he could come up with was that she was a powerful individual from some far flung place, much like the Adventurer Momon. It would certainly explain how such a delicate-looking girl could brave the streets of the city without the slightest hint of worry.

 

Over the next half hour, an assortment of equipment built up around the sales counter. A large round shield rested against the two spears and a few sidearms lay on the table: one battle-axe, a hatchet and a long dagger. Two bow staves of different draw weights and lengths lay beside them alongside an open-faced sallet with a hinged visor. Several other pieces of armour were set aside as well – gauntlets, bracers, a gorget and greaves along with an undyed gambeson.

 

It was a familiar selection that he had seen regularly: aside from the common armament of her territory, there were also many choices shared by Adventurers and other fighting individuals that expected to spend significant amounts of time in the forested regions beyond the tamed lands of the duchy.

 

“‘A few other things,’ huh?”

 

“They were…necessary purchases,” Lady Zahradnik smiled sheepishly at his remark.

 

“I always thought it’d be nice if my wife shared more of the same interests as me,” the Forgemaster mused, “but, looking at you here, I don’t think I’d have anything left for myself if that were true.”

 

“This store seems to have everything,” Lady Zahradnik remarked as the clerk tallied the bill. “Was it always like this?”

 

“Several workshops decided to display their wares using a few combined storefronts last winter,” the clerk explained. “It seems to net more sales overall and save room between all of the different vendors.”

 

“Is there an armoursmith included in your number?” the Baroness asked, “I would like to order mail and a coat-of-plates as well.”

 

“We do forge armour here,” Ysbrant answered, “but we won’t be free to work on anything until early summer – well, at least if the other nobles start showing up and buying things…”

 

It was not uncommon for nobles to push their demands onto them, though it was usually limited to a handful of individuals in the more powerful houses. The young noblewoman filled in as his words trailed off hesitantly.

 

“I will be back after I get my labourers started,” she said. “There are several other things I need to look into, but we are already a week into the planting season.”

 

“Of course,” the clerk replied with a slight bow. “Then we will be looking forward to your patronage.”

 

When the clerk was finished with the bill for her equipment – and the cost of the damaged spear – Ysbrant held out the order form she had handed to him upon their meeting.

 

“Here’s the tally for the tools out back – they should be done loading by now,” he said. “If you’re headed that way, I’d appreciate it if you dropped it off at the Merchant Guild.”

 

“I don’t mind…though perhaps you could return the favour by doing something for us.”

 

“And what’s that?”

 

“Keep your storefront open,” the Baroness said. “Just like it is right now.”

 

Ysbrant looked at the noblewoman strangely, then looked out towards the open shutters and the empty streets beyond.

 

“You are open for business, yes?” she pressed her request.

 

“We are,” he answered slowly, still trying to make sense of why she had asked, “well, there’s nothing to lose now, I guess – and this lazy lout needs to stop sleeping the days away. I’ll do as you ask, Baroness.”