\chapter{Ludmila Zahradnik}

Left alone with her thoughts in the empty garden, Ludmila scanned the surrounding district. Though not much time had passed, she could not spot the figure of Lady Shalltear or her attendants anywhere. With little to achieve by standing around, she searched through the areas nearest to the main street, her head turning back and forth as she walked. Eventually, she stood in front of an imposing gatehouse that marked where the main promenade led south into the rest of the city and, with a tired sigh, she stepped across its threshold to take a look beyond the wall.

 

The layout of E-Rantel was suited to its nature as a fortress city. Though protected by three massive curtain walls, the arrangement of the streets was such that any invaders that did make it into the walls encountered a somewhat confusing urban labyrinth. There were no strongholds that were designed to resist hostile forces in each section following a breach, but there were also no clear and direct paths to anywhere important. Even the main thoroughfares followed winding routes through the buildings of the city on their way to the next set of gates. The nature of certain industrial areas within the main section of the city could be identified by sight and smell, but there were no clear written markings or directions to assist outsiders with navigation within or between the various parts of the city. To those unfamiliar with its ways, most of the city’s layout would appear a random mix of shophouses, apartments, inns, warehouses and all manner of institutions such as temples, guilds and artistic venues.

 

Outsiders themselves, her family would hire a wagon that would take them to the various warehouses where they would sell their goods to wholesalers, who would in turn make their living by reselling their inventory as the markets demanded. She recalled her younger self staring out from their hard seats as they wound their way through the veritable maze of streets, buildings and plazas. Even now, as her gaze followed the main road down the slope from the gate, she was under no illusion that she wouldn’t quickly become lost the further she went from the Central District’s entrance.

 

Lady Shalltear and her attendants should have stood distinct from any of the city folk, so she had thought to inquire after their passing with any citizens she could find nearby. However, it turned out that the streets beyond the inner walls were just as empty as those within them. Streetlamps, less ornate than those in the Central District, shone with the same intensity nonetheless: brightening the empty thoroughfares of the city which lay in still and eerie silence. E-Rantel was a major trading hub as well as a staging ground for mercenaries and Adventurers that worked jobs maintaining the nearby Katze Plains, providing escort to merchants and keeping the highways and roads of the surrounding countryside clear of threats. Even with the sudden and unexpected annexation, this work did not conveniently wait for anyone and the city should have at least had a certain amount of life in the streets. It was an odd sight that she would have normally given more thought towards, had her own business not been so pressing.

 

“Where could Lady Shalltear have gone?”

 

Frustration caused her to finally voice her thoughts aloud into the evening air. Without any leads to go by, she decided to turn back and see if there was any way that the administrative offices in the central district could help her locate the mysterious woman.

 

The groan of metal coming from the direction of the gate caused her to slow mid-turn. Where the gate behind her should have come into her field of view, instead was a murky reflection of herself looking back at her. She faced a wall of dark, polished metal twice her size, gleaming in the twilight.

 

The sound continued as the wall of metal shifted slightly. A movement out of the corner of her eye caught her attention – an arm covered in vambraces of similar material, draped in a tattered sleeve, was stretched out from behind what she now realized was a massive tower shield. The arm ended in a wicked gauntlet curled into a fist, and a single clawed finger protruded from it. As her gaze followed down the arm and eventually in the direction indicated by the finger, she realized that it was probably the answer to the question she had voiced to no one in particular.

 

From her vantage below, she could only see the crest of a shining helm behind the top of the tower shield. The tall guard made no further moves and the cloak of its purple robe fluttered in the evening breeze, making a sound similar to that of a large banner. After standing awkwardly for a moment, Ludmila silently nodded her head in towards the shield in thanks before heading in the direction indicated.

 

Assuming a brisk pace, it wasn’t long before she spotted Lady Shalltear’s dark parasol. The pale figures of her attendants could be seen still flanking her as she strolled off casually barely two blocks ahead. It turned out that she had actually not gone far at all, but the erratic layout of E-Rantel was simply obscuring her line of sight. Breathing a sigh of relief, she slowed her pace and mulled over how to present herself and the issues that faced her family’s demesne.

 

As she calmed down and ordered her thoughts, the monumental task that lay before Ludmila formed a growing list of problems in her head. She maintained a vague sense of Lady Shalltear a few dozen paces out in front of her, but for the most part she had focused herself inwards in order to sort everything out.

 

The most pressing issue was that Warden’s Vale currently had a population of one: herself. Without labour, there would be no production, no revenues; stagnancy and decay would soon follow. The normal means by which rural territories secured immigrants – through petitioning the city administration or checking with the temples for hopeful settlers, refugees and the homeless – would not work for frontier fiefs. One could not simply be a Farmer or any other singular civilian profession: if the population was not accustomed to life bordering the wilderness and incapable of holding their own against the threats that lay around them, they would not survive for very long. The weak would simply become food for predators, and becoming known as a place to find easy meals only invited more unwanted guests.

 

Though the Sorcerous Kingdom – according to Countess Jezne – had a standing army, Ludmila was not certain if they possessed the ability to uphold the borders and maintain constant readiness against potential attacks from the wilderness. All it would take was an hour or two and the entire village could be ransacked by a tribe of Demihumans if it lacked ready defenders. Warden’s Vale had established itself as an entrenched Human territory in the eyes of their savage neighbors, but there only needed to be a curious scout or a desperate hunter to find that the village was now open to invasion. The thought did not sit well with her at all, especially considering that Nabe had already departed to deal with some sort of issue in the area, and it was something she wanted to remedy as quickly as possible.

 

The other problems revolved around logistics, such as building a new vessel to transport the village’s goods and refurbishing old infrastructure, as well as making sure all of her legal affairs were in order. She also needed to ensure that her understanding of the law was still in line with that of the new administration’s. In addition, she needed to figure out where her village’s goods disappeared to and hire a wagon to transport and sell them…but all these things would not avail her any if she did not resolve the first problem.

 

The only recourse that came immediately to Ludmila’s mind was the courtier that she had ultimately followed after. Her proud bearing and lavish attire gave off the air of one accustomed to high society and, according to Nabe, she had a connection to the Sorcerer King. Ludmila was not sure if she was actually a noble, but at the least she had risen to a position where her value warranted her attendance in the Royal Court. If she was a powerful noble, the resources she might be willing to bring to bear would make all of Ludmila’s worries seem needless in the end.

 

Resolving herself, Ludmila picked up her pace to catch up with the small procession ahead. Her lonely shadows projecting onto the buildings lining the street made her keenly aware of how much the city had changed from her past memories. The wooden-framed structures with their walls of wattle and daub were sometimes five or six stories tall and even a small city block could house several times the population of her entire fief. This normally meant that street life should be boisterous as labourers parted with their wages in the evening, so the contrast with the reality she was currently experiencing created a dissonant sensation.

 

Every door was shut; every window shuttered. The occasional wisps of smoke she could see rising from chimneys indicated that they were indeed occupied, and that the residents were burning fuel to keep warm in the chill of early spring. She could not make much sense of it. Ludmila understood that the events of Katze were certainly terrifying, but E-Rantel itself did not look like it had been damaged. The streets were unnaturally clean and there was no sign of any looting or arson that one might think would come hand in hand with a violent siege and occupation. For all of its changes, the city still needed to run. Food, fuel and rent would need to be paid for somehow, and the various organizations and businesses in the city still needed to operate to keep trade and production flowing.

 

As she advanced, she saw that Lady Shalltear and her attendants had crossed into a large plaza, passing one of the many militia posts placed around the city. There was a sentry posted that was vaguely similar in appearance to the one that had given her directions earlier: it had the same dark armour, but with veins of bright crimson running through it and it didn’t appear to have the same cloak or robe. Rather than a bright, shining helm, this sentry wore one that was as dark as the rest of its armour. The armour itself had dozens of wicked spikes protruding from it which made her curious about the rest of its appearance but, much like the previous guard, she could not see over the massive wall of dark metal that was its tower shield to take a look at the person behind.

 

The sentinel stood motionless as she crossed in front of it, and the flutter of leathery wings from above drew her attention. Perched on the lamppost that came out over the street from the militia post, an Imp peered down at her with shining eyes. The bright light from the enchanted lamp that hung from the post was reflected off of its copper skin and cast a large shadow of the winged creature on the tall building looming over the guardhouse. She continued to look up at it as she passed under the lamp, and it grinned down in return like some sort of sinister gargoyle come to life. Ludmila had only seen and heard of them from books and the tales of performers, yet their descriptions had matched so closely that she was instantly able to identify it. The creature itself was rather small, so she felt more wary than threatened at its appearance.

 

Ludmila pondered her relatively calm reaction at the reportedly evil being, and her head turned back down to look into the window where the post’s officer usually presided from. With how quiet the city was, she thought it may have not warranted being manned, but a ragged figure stirring inside proved otherwise. A desiccated hand appeared at the counter, and the figure leaned forward into clear view. She followed the flowing black fabric of its robes until her eyes came to a stop at its face. Two points of angry crimson light flared back at her – it was a dead man’s face, weathered by the passing of untold ages. Its flesh had dried and pulled back his thin lips in a ghastly sneer as he stared down at her from the guardhouse window.

 

She let out a startled cry as she immediately fell away, tumbling onto the flagstones of the pavement. She scrambled back to her feet and fled into the plaza. Rows of stands and benches filled the space – it was a place which would usually have hundreds of merchants displaying their wares and many times the number of citizens, travellers and other folk perusing the vast selection of goods. But like the street that she had dashed out of, it was silent and empty, the evening wind blowing across what should have been a vibrant centre of city life with a lonely moan. Neither sound nor movement could be heard following, but she dared not turn to look over her shoulder as she bolted forward.

 

With the shift in how she profiled her surroundings, she began to notice other things as well. The Undead she had encountered at the militia post was not the only one. Several similar figures in black robes flew over the plaza, vanishing over the rooftops and out of sight while others appeared shortly after, heading in different directions. In each corner of the plaza, there was a similar guardhouse and the one that she was quickly closing in on seemed to have the same arrangement: a tall, dark sentinel with a tower shield and an Imp perched on its lamppost. Nothing had reacted to her panic, but she made a wide circle around the guardhouse as she followed after Lady Shalltear and her attendants, who seemed to be entirely unruffled as they had passed. Slightly incensed at the sight and the fact that she seemed to be the only person reacting to everything, Ludmila brushed off her skirts and took a closer look at the street that they followed. As she continued to examine her surroundings, she thought back to her encounter at the first militia post, recalling every detail.

 

Several minutes passed before their winding route led to another small plaza. She walked directly up to the militia post ahead and steeled herself. If a citizen had seen her, she thought that they might have shouted out in warning or terror. Perhaps they would have marveled at her foolishness and awaited the inevitable, gruesome result. But when she stepped directly in front of the sentinel and its grimly gleaming tower shield, Ludmila did not sense that she had any spectators.

 

As she reviewed her journey through the streets of the city, she reoriented her perception. Even with the Undead present, E-Rantel was undamaged and of the slaughter of its citizens, there was no sign. The sentinels had not reacted to her presence and nothing had chased her when she fled in panic. The only time she had gotten any sort of response was when she received directions from the guard at the gatehouse. She looked up past her reflection in the shield to the crest of the helmet peeking above it. The Imp sitting on the lamppost was looking down at her, but she decidedly ignored its grinning leer. Poking her head around the shield, she took a close look at the sentinel from the side.

 

Eyes that glowed with angry crimson light glared back down at her, but the sentinel did not stir beyond its notice. As Ludmila registered the features behind the open face of its helm, she had no doubt that this sentinel was Undead. She suspected that every one of the dark, armoured warriors she had walked by were also Undead, but their behaviour was unlike any Undead she had seen before.

 

Occasionally, the wilderness tribes in the upper reaches would have conflicts between themselves, and the dead bodies resulting from their battles would be washed downstream. These corpses would occasionally result in Undead like Skeletons and Zombies that pulled themselves out of the water, drawn to the abundant life in Warden’s Vale. They would immediately chase after the hundreds of geese wandering around the marshy floodplain, which created an endless, annoying racket until a handful of villagers showed up to put an end to it.

 

Since she couldn’t even sense how strong they actually were, these Undead were far more powerful than the Skeletons and Zombies that occasionally popped up in the barony…but they seemed to care nothing for the living beyond observing them. While they did not exactly seem to be inclined to interact with her like Human militia might, they were sentries all the same. Ludmila turned and stepped away from the sentinel, walking past the guardhouse. Looking into the window, she saw there was the same type of Undead that had startled her witless before staring back at her. She held its gaze as she passed the guardhouse, satisfied with the result.

 

While it appeared that death stood in the streets and flew in the skies overhead, the truth was that the city of E-Rantel had been laid siege to by the spectre of their own fear.

 

Ludmila continued on her way down the street where Lady Shalltear had gone, no longer paying any mind to the Undead standing watch over the city.

 

Duty cared not for fear, and time awaited no one.