\chapter{Pandora's Actor}

The room grew still after he asked his question. Shalltear looked up to him questioningly as she slowly repeated herself.

 

“The truth of her work eludes us,” she said. “It is as if all the mechanisms of this world only respond to her act…de-arinsu?”

 

Pandora’s Actor straightened himself. He held his gauntleted hands up before him, absently staring down at the black metal encasing his fingers.

 

“What a fool I have been,” his soft words were filled with ruefulness and disdain.

 

He slowly turned his hands over, then turned his palms upwards again. He flexed his fingers repeatedly until his hands finally balled up tightly into fists.

 

“A fool!” His wailing shout filled the room, “To think that I, of all people, should have allowed this to escape my notice.”

 

Pandora’s Actor’s voice smouldered as he continued to berate himself.

 

“How great my hubris must have been, to have blinded me from this simple truth!”

 

Shalltear looked at him worriedly over his sudden change in disposition.

 

“Are you…is everything alright de-arinsuka?” She asked.

 

“No! Everything was wrong!” He cried in despair, “I was wrong about everything. To think that I, the greatest of actors in Nazarick, had disregarded this piece of wisdom left by the Supreme Beings…until now. Thanks to your reminder, meine Dame, everything is right again. It is not too late to act.”

 

He looked back down to his hands – still curled into fists – at the end of his words and opened them. Then a chuckle escaped his lips. The chuckle turned into a laugh, and the deep sound rose until it filled the room as he threw his head back uproariously, throwing his arms wide as his body shook. Bits of Momon’s armour were unequipped in sequence, until only the militant mustard uniform of Pandora’s Actor remained. Its polished medals, buttons and chains glistened as he expressed his joy and the worries that stained his thoughts were washed away.

 

“What did I remind you of?” Shalltear’s face was a mass of confusion, “I don’t understand.”

 

Pandora’s Actor stilled his laughter, but his mirth remained. He looked back down to the Vampire watching him from the couch. In a sudden move, he leaned over to lightly grasp Shalltear’s fingers, pulling her gently from her seat as she let out a surprised noise. He swept her across the floor in an impromptu waltz, leading her through several joyful turns around the room. As the pair returned to where they had started, he paused dramatically to speak.

 

“Die ganze Welt ist Bühne…”

 

He led her into a final turn, raising his arm to twirl her out to arms’ length. With his free hand, he removed his cap, holding it over his heart as he genuflected before his speechless partner.

 

“...und alle Frauen und Männer bloße Spieler!”

 

He rose again, the atmosphere surrounding him undiminished. He continued to hold onto her fingers as he spoke.

 

“I was a fool,” he said quietly. “I perhaps thought myself above the others, who saw all who fell under the dominion of Nazarick as new acquisitions – as pawns to be used to achieve the ends desired by our Master. Yet I did just the same: I saw them as an audience, who only needed to respond to my act to produce the results that I desired. I see now that I was wrong; I see now what must be done.

 

“The people of this world are not like us: created to serve, existing assured in our purpose and common cause. Instead, they come together to develop civilizations with the cultures and societies that they have found to best suit their species in the circumstances that they each find themselves in. It is as much a part of them as our existence is to us: we cannot expect them to become something else simply because we fashion new paths that we arbitrarily decide are fit for them, even though they may rightly be so.

 

“The Humans of this realm do not act out their lives on this stage alone; their roles are intertwined with the roles of many others, and those other roles with their own intertwined. And so we must create a place where they can all act, and it must be a place where all newcomers can join the act as well, regardless of their origin. What we have built here so far – what we have planned to build in the future – is but a body without a soul; a sad puppet held aloft by the strings of our shallow machinations, bereft of the spark of life. A place for everything, and everything in its place...but not a place to be. For the Sorcerous Kingdom to become what our Master desires, all of its citizens must join on its stage: to act and sing and dance according to the roles that their lives lead them to fill.

 

“We knew this – we knew! Yet even as our eyes perceived it, we blindly refused the existence of beings so different from us. Before His seclusion, our Master even helped establish the initial laws and policies of the realm, yet we were all blind to this truth that He so plainly pointed us to. We took the words that carried His Will – words that we should have embraced wholly – and…twisted them into conditions: challenges to be faced and defeated through artifice, contrivance or technicality.”

 

Shalltear listened attentively as he shared his explanation. She opened her mouth several times while he spoke, then closed it again without interrupting his words. When at last he finished, she asked a question.

 

“Then we should tell the others about this, no? The truth of the Sorcerous Kingdom that Ainz-sama wishes to create.”

 

“You reported none of what you told me tonight at this evening’s council meeting,” he replied. “Why is that?”

 

“Because…I didn’t think something like this would matter to the others de-arinsu.”

 

“Indeed,” he said gravely, “it would be to no avail. This truth is something they must arrive at on their own to understand in its full depth. You were the first, I think, though you understand it intuitively rather than in any manner that can be wholly articulated. Some of the others may have grasped hints of it as well, but they do not appear to be fully aware of it yet. If they are simply told, it will just be treated as a new set of conditions to be approached in the same manner as before.”

 

Pandora’s Actor looked down at the cool, deceptively delicate fingers that he still grasped within his own. He hesitated a moment before speaking again.

 

“I must ask you, Shalltear Bloodfallen…just as we have danced here in this room, would you join me in this dance that all must eventually join in order for the Sorcerous Kingdom to become what it needs to be? Not simply as a pawn, or as a convenience, but as a fellow servant of Nazarick who would see the true wishes of our Master fulfilled – to become a leading actor in His Great Work that would turn this dream within a dream into an impossible and glorious reality!”

 

Shalltear gave him a long look, and withdrew her fingers from his grasp. Pandora’s actor felt his heart sink. He did not look back up, instead watching as the Vampire crossed her arms over her abdomen.

 

“Yesterday, at the council meeting,” her voice emerged, measured and calm. “Was it your ploy to have Baroness Zahradnik come under my authority, arinsu?”

 

“...yes.”

 

“Yet you came to this revelation only just now,” she noted. “Sebas would be a much more suitable candidate if you wanted to find a benevolent individual for her to serve under…so why?”

 

“Because he is not qualified.” He answered simply, “He is too kind; too benevolent – to the point where it can blind him to the consequences of his well-meaning actions. If the Baroness had been placed under him, she would not have pursued the course that she had, in order to work out her problems in the ways that she knew how. She would have been provided with everything she needed, and we would have gained nothing for it.”

 

“Furthermore,” he added, “Sebas is not a Floor Guardian. If ever a time came when the Baroness required more substantial support, he would not have the authority nor the resources to provide it.”

 

“The others might argue that the opposite is true for myself arinsu,” Shalltear pointed out. “I’m fairly certain Yuri Alpha thought I was going to devour Baroness Zahradnik the moment I had her alone.”

 

“I did not believe that would happen,” Pandora’s Actor replied. “You are not like that.”

 

“Hm?”

 

“The others may believe you to only be an engine of chaos and destruction but I believe that you have other, more important traits that make you the ideal candidate for taking the Baroness under your wing. You see, I made a great study of everyone and everything I could when I entered into this world from my seclusion in the Treasury – you were no exception.

 

“You are the strongest amongst the Floor Guardians and you oversee the greatest number of floors, yet your domain is filled with the weakest of Nazarick’s denizens and you are well accustomed to managing them. Though you may not understand what it means to be weak, you are still able to intuit the capabilities of those under you for any given circumstance. You are attentive to your Area Guardians, even as you diligently perform your duties patrolling your Floors, and you will only severely punish those that fail in tasks that they should have been capable of accomplishing in the first place. I believed that, once the Baroness had become your vassal, her treatment would not differ all that much from this, even as an outsider.”

 

“I see,” he could still not detect any change in Shalltear’s tone. “Is there anything else?”

 

“There is one more thing,” he added. “The most important thing…though I feel that I may anger you if I speak of it.”

 

“I think I’m becoming angry just by hearing you say that.”

 

Pandora’s Actor was not sure if she had said the last in jest or not. That it came out in the same measured tone that was entirely uncharacteristic of the usually expressive Vampire made the prospect all the more terrifying. He could usually turn to his Doppelganger abilities to skim the thoughts of those around him but, as one of the Undead, Shalltear was immune to this. He decided that he should check her disposition before going further but, to his surprise, her face seemed as calm as her voice when he finally looked up.

 

He held her gaze for several moments before speaking again.

 

“It is because you are the greatest of the Floor Guardians; yet even as you are, you have also experienced the greatest failure. Your pride: the supremely self-assured pride that we have in our being creations of the Supreme Beings has been shattered. Everyone – including you yourself – stands ever ready to examine your faults…no matter how insignificant they may seem. You are broken, Shalltear Bloodfallen: and because you are broken you are the most eminently qualified.”

 

Pandora’s Actor resisted the urge to pace about as he hurled himself into his words. This was too important, and he poured all of his energy into conveying his thoughts to Shalltear, who continued to maintain the calm expression that gave none of her own away.

 

“Our Master has done much in these past few months since our arrival in this strange new world,” he continued. “So many things He has done that seem so incomprehensible, yet there is one thing that we have all been made to feel keenly. Throughout this time, He has…tested us: cast us into situations that lead to failure and defeat. He makes decisions that make us question our own abilities – to reexamine ourselves and the way that we perceive His Will. All of us come out changed in ways we would not have conceived of as our former selves.

 

“This is the crucible that Ainz-sama has cast us into. A creator’s crucible. The crucible of the greatest of the Supreme Beings. We are left to be exposed to the flames of our trials and those very flames burn away our impurities and prepare us to be forged anew. It is for you, Shalltear Bloodfallen, that these flames have burned the brightest; the hottest – all has been taken away, leaving only the very essence of yourself. I believe that you have been ready to be reforged for our Master’s purposes for some time now; with the revelation of this evening, I am even more convinced of this.

 

“The scales of pride and presumption have fallen from your eyes and, in this new realm of our Master, all the experiences of your travels; all of the duties you are assigned, will be the hammer blows that will forge you into the instrument of His Supreme Will. Be it as His Lance or His Lady, you shall be the one that binds the people of this world together on the grand stage of His Great Work.”

 

Shalltear’s expression did not change, even as he concluded his appeal. The silence which followed his heartfelt outpouring stretched for a minute, then two, and Pandora’s Actor dared not to break it lest he mar her decision in some way. The quiet rustle of silken skirts was the first sound to fill the room as Shalltear turned to walk away. With unhurried steps, she went past the couch and around the table; the handle of her black parasol appeared over her wrist.

 

With his cap still held over his chest, Pandora’s Actor turned to watch her as she made her way back to the window by which she had entered. The window was opened, and the sound of the rain outdoors dampened his spirits even as his mind raced to salvage the situation.

 

I thought I finally understood – everything was in place! Where did I go wrong? Was it something I said? How did I fail?

 

As he berated himself, finding more flaws; more possibilities and potential problems in his performance, the rain continued in its cold accompaniment. He looked up from his thoughts and moved to close the window, then stopped when he saw that Shalltear had not yet left. She was gazing up at the night sky, the lazy curls of her silver hair framing the pale beauty of her face. She did not turn to face him as she spoke, continuing to watch the downpour.

 

His breath caught when he finally heard her decision over the sound of the rain.

 

“I will play my part,” she said softly. “For Ainz-sama’s sake.”