\chapter{Ludmila Zahradnik}

Ludmila stared over at Lady Shalltear, whose crimson eyes had taken on a dim glow in the fading light. None of the Undead around her reacted or even seemed to care that someone had fallen out of the sky, and Ludmila started feeling a bit out of place being the odd one out.

 

“My lady,” Ludmila asked, “will it become a normal thing in the city to have people landing in the street like that?”

 

“There are many Heteromorphs and Demihumans who have the ability to fly,” Lady Shalltear said. “Magic users and wielders of magic items enchanted with flight spells also do so…so it should be a more common sight in the future as more peoples fall under the dominion of His Majesty.”

 

“There are no laws regulating flight in Re-Estize,” Ludmila said. “Perhaps you should propose a few as the Minister of Transportation to prevent incidents in the future. I cannot imagine airborne accidents ending very well for anyone involved – or the people below.”

 

“The sky is quite vast,” Lady Shalltear replied, “and the chance of randomly bumping into others is much lower than walking on a street…but I suppose something should be in place to prevent potential damage to His Majesty’s realm.”

 

“You have never collided with someone in flight before?”

 

“Only when I’m aiming for them,” Lady Shalltear smiled.

 

Ludmila shook her head, uncomprehending. Meanwhile, the Soul Eater turned as it entered the still-empty main plaza, driving the wagon towards the front of the main office of the Merchant Guild. It was a grand structure of three stories, occupying the entire side of the plaza where it had been constructed. Windows of clear crystal lined the second and third levels of the building, which would offer a glimpse of the archives and offices within. The main entrance had two pairs of glass doors at the top of the broad granite stairs leading up from street level.

 

The imposing building stood directly across the plaza from the city’s main cathedral, which had been sponsored by the Theocracy at the site of the original chapel that had been built when the city was founded and Re-Estize was still young. The guild office was not only placed across from the cathedral, it was also built at the same height as well – as if daring to challenge the might and authority of the Temples. The fountain and column that they had passed between on the way to the outer reaches of the district were a reminder that this rivalry was very much real. When the main office of the Merchant Guild was constructed, it was said that the Temples commissioned the beautiful fountain on their side of the plaza to remind the citizens of the life and provision that the gods provided. But then the Merchant Guild had raised the column: an elegant work of art which dominated the square.

 

Years ago, she had overheard a conversation amongst the ladies of the nobility concerning the rivalry between the Merchant Guild and the Temples. That E-Rantel was a city of trade and in the secular government of Re-Estize, the power of the Temples was dwarfed by the influence of the Guild. Because of this, the Temples were said to be perpetually jealous, but could only make ineffectual motions outside of their direct spheres of authority. Worship of the Six Great Gods had long since waned in the north with the rise of the faith of The Four, but the situation remained the same: commerce was the lifeblood of the city, and the Guild was its beating heart.

 

That heart seemed still now. The gleaming head of the column caught the light of the evening sun over the rooftops, scattering its shimmering radiance in bright fragments over the plaza, but the Guild Office itself appeared as silent and inactive as when they had crossed the main plaza earlier that day. The windows that peeked into the archives and offices had their curtains drawn shut with no light visible behind them. There were no clients entering or leaving the building, nor anyone resting on the stairs or benches outside.

 

As Ludmila stepped off of the wagon and approached the main entrance, she saw that there was a single light visible from the entrance, where a balding man stood at one of the reception counters. The large door was light and soundless as she pulled it open for Lady Shalltear, and the measure of their footfalls whispered on the long carpet as they approached the front desk. The old man made no move to recognize them – his head was bent over the unadorned counter as he leafed through the thick binder that lay in front of him. It was only when they had come directly in front of his stall that he raised his head. Sharp brown eyes that belied their owner’s apparent age looked over to Ludmila; then to Lady Shalltear. His gaze then went down to their hands before finally settling on the blue folder in Ludmila’s possession.

 

The old man looked Ludmila in the eye and spoke in a clipped, yet decisive tone.

 

“What business do you have with the Guild?”

 

Unsure on how to respond, Ludmila opened her folder, retrieved the two invoices within and placed them on the counter. The man immediately took the sheets of paper, holding them up in his lean hands towards the light. It took him a minute to scan over the first invoice, after which he switched to the other. He then walked over to a long table behind the counter, flipping through another binder which lay there. After a few more minutes, the man returned to the reception counter. He rolled a large stamp over an inkpad, and pressed it onto both of the invoices. Ludmila thought she saw the ink glow briefly before he placed his palm over the invoices and spoke.

 

“Do you have an account with the Guild, Baroness Zahradnik?” He asked.

 

“I am not a merchant,” she replied.

 

“You don’t have to be,” he patted the invoices. “Anyone that does business like this should register with the Guild.”

 

“Why is that?” Ludmila asked.

 

“Have you ever seen someone pull a hundred platinum coins out of their pocket?” He tapped his finger on the Perfumer’s invoice.

 

“Well...no,” she admitted.

 

“Me neither,” he said. “That’s what the guild does. You don’t carry coin around doing business like this: you just use invoices like the ones on the counter here. The Guild ensures that each transaction is authentic and then the money is transferred between accounts. The only time people move real coin around is with an armed escort to places where there’s a need for it.”

 

“What about all of the people in the city that trade in coin?”

 

“We usually don’t deal with them,” he said, “but we do deal with the merchants that take their coin and deposit it here. The Guild mostly deals with real money, sums of Platinum like these invoices or even greater.”

 

“It goes higher than Platinum?”

 

“Sure does. Mithril and Adamantite coins. Gem coins and official plaques of credit. You don’t see that around here though. Too poor.”

 

Just this morning, Ludmila was agonizing over how to budget out a few hundred gold coins to supply her demesne. Now, after she had come into wealth she had never seen before, much less expected to possess so soon, this man was telling her that platinum was the smallest denomination of currency that they normally dealt with, and that the largest trade hub in the nearby region was considered too poor to deal in anything greater.

 

“Alright then,” she said, “how do I register an account?”

 

“You’ll need to provide proof of your identity and a seal so we can add it to our archives for authentication purposes,” he replied.

 

“But you just addressed me as Baroness Zahradnik?”

 

“A courtesy.”

 

“Then what do you deem suitable as proof of identity?” Ludmila asked.

 

“Official documents from the administrative office that you report to,” he said. “Or you can have an official vouch for your identity.”

 

“Oh! I can do that,” Lady Shalltear said from beside her.

 

The old clerk turned his attention to Lady Shalltear, whose shoulders barely appeared above the counter.

 

“...and you are?”

 

“This is Lady Shalltear Bloodfallen–”

 

“Never heard of her.”

 

“Lady Shalltear is the Minister of Transportation.”

 

“Lady Shalltear will need to provide proof of her identity and provide a seal so we can add it to our archives for authentication.”

 

“Lady Shalltear is about to turn this entire building into a heap of cinders with a Fire Storm spell.”

 

Seeing her liege’s mood take a turn for the worse, Ludmila hurriedly attempted to deescalate the situation.

 

“A moment please, my lady,” she implored Lady Shalltear in placating tones.

 

She turned towards the entrance and paced hurriedly towards the door. When she stood at the top of the stairs outside, she looked around for the Elder Lich. Spotting it floating above the plaza, she waved for it to come down.

 

“Do you have proof of identification and a seal of office as a member of the administration?” She asked.

 

“Yes,” it said.

 

“I require your assistance, then. Come with me.”

 

Ludmila turned back to enter the office, hoping that she was fast enough to prevent whatever a Fire Storm spell was from befalling the building. Fortunately, Lady Shalltear did not appear to be casting anything when she returned to the counter – but, upon seeing the Elder Lich with what was needed in hand, her expression darkened even further.

 

“The official here can vouch for our identity,” she motioned for the Elder Lich to come forward, “are these credentials acceptable?”

 

The attaché placed what appeared to be a small plaque and an ebony seal on the counter. The old man raised the items to the light no differently than he had the invoices, and there was no sign he even cared that an Elder Lich had walked up to him. Shortly after, he placed them back on the counter and produced two identical forms from somewhere out of sight below the desk. Ludmila filled her form and stamped it with the seal that she had brought with her from Warden’s Vale. The seals of the Merchant Guild and the Civil Office of the Sorcerous Kingdom followed soon after.

 

They moved to work on Lady Shalltear’s documentation, but when the Elder Lich raised its hand to stamp the form, the Vampire shouted.

 

“Wait!”

 

Three heads turned to Lady Shalltear at the interruption.

 

“Not you.” she said to the Elder Lich, “You.”

 

Ludmila found Lady Shalltear’s finger pointed towards her.

 

“My lady?”

 

“You can vouch for me and use your seal on the form,” Lady Shalltear said. “You had your identity verified by this attaché, yes?”

 

It seemed needlessly convoluted, but Ludmila acquiesced. The guild clerk disappeared into the office, shaking his head, after which Lady Shalltear spoke.

 

“That gorilla did it on purpose,” she said testily.

 

“What is a ‘gorilla’, my lady?” Ludmila asked.

 

“It’s – never mind. The Guardian Overseer is making things hard for me on purpose. There’s no way she didn’t know that I would need these things eventually, and then she sent this Elder Lich with everything that you need as your ‘attaché’ to serve as a constant reminder of her influence even as you are subordinate to me.”

 

“Lady Shalltear,” Ludmila licked her lips as she tried phrasing her question tactfully, “are there…issues in the Royal Court?”

 

“Issues?”

 

“You seem to have a rather disagreeable relationship with the Guardian Overseer.”

 

“Ah, that’s what you mean,” Lady Shalltear said. “We are rivals, not enemies. There is solidarity when it comes to the Will of His Majesty and the defence of His realm.”

 

“Then...if I may ask, my lady,” Ludmila was still unsure if it was a delicate subject or not, “what is the nature of this rivalry?”

 

“The only thing that matters, of course!” Lady Shalltear said matter-of-factly, “To earn our place at the side of His Majesty, in all things. Do ambitious Human nobles not seek great achievements within their courts? To win the appreciation and trust of their liege?”

 

“In many things, yes, that is the case, my lady,” Ludmila replied.

 

“This rivalry can become a bit…intense sometimes,” Lady Shalltear said, “but it has never grown to the point where His Majesty’s realm has suffered for it.”

 

“Thank you for the explanation, my lady. I will keep this in mind.”

 

As they waited in silence, Ludmila looked at the Elder Lich that had stood on the other side of her for the entire conversation. It displayed no reaction to the accusation that it had been dispatched as a form of harassment. She heard shuffling steps as the old man reappeared. Ludmila turned to face him as he placed several documents between on the polished counter, pushing them forward.

 

“These are the relevant templates that you should use when drawing up bills and invoices related to Guild business. Make sure that the staff that you assign to work with us are familiar with the format.” He straightened after his explanation, “Your registrations with the Guild are now complete and your account balances have been updated. These are your balance books. Is there anything else you need, Minister Bloodfallen? Baroness Zahradnik?”

 

Ludmila reached out to take the small booklet bound in black vellum. She opened the unmarked cover: the front page was similarly blank, but the next page had rows and columns lined upon it. Written on the first row was the balance of her account with the Merchant Guild. Between the invoices from Gareth Boyce’s lumber yard and the LeNez workshop, House Zahradnik had received 108 Platinum coins. It was an amount she had never thought she would ever have available to use at once. The digits were written in simple cursive, but they represented a responsibility that she would now need to wield for the prosperity of her demesne.

 

“I need to purchase tools for farming and forestry,” Ludmila asked the clerk waiting patiently across the counter. “Is there an open business where I can find those?”

 

“Just head to where all the forges are,” he told her. “If there are any working, you’ll definitely notice.”

 

The answer seemed obvious, after the fact.

 

“When is it appropriate to deposit and withdraw at the Guild?”

 

“There are no set rules on that,” he replied, “but as a general guideline, any amount that you feel unsafe carrying around.”

 

“Can the guild be used to hold coin for anything?” Ludmila asked.

 

“Yes,” the clerk nodded. “We prefer it that way, in fact. It’s easier to deal on paper, but a lot of people can’t trust that. Unless you’re a high noble, you probably can’t afford the type of security that the guild has. The new King has also contributed some of his soldiers to ensure that the wealth of the city remains secure.”

 

“Then you don’t mind if wages and such are withdrawn by my staff?”

 

“Mmh,” the clerk grunted. “Petty amounts should be withdrawn as part of a lump sum. We’ve a few members that send escorts with their agents to collect wages for the whole of their staff to be distributed at their business or homes. You should do the same.”

 

“Is there anything I should avoid doing?”

 

“Nothing illegal: you’ll be reported to the relevant authorities if you do,” the clerk said. “If there are any other transactions that run afoul of guild regulations or seem suspicious, you’ll be informed as well.”

 

It nearly felt to her a barb, though the man probably did not know. If House Zahradnik had used the services of the Guild instead of relying on themselves, generations of financial hardship might have been circumvented altogether. It brought to mind something that she had thought about shortly after learning the depressing reality.

 

“Does the Guild recommend merchants?” She asked, “I would like to hire staff that can manage the commercial transactions for my demesne.”

 

“Hmm…we set up apprentices with masters, but it’s rare that a noble comes looking. They usually employ the ones from their own fiefs,” the man scratched his chin as he thought. “The city’s had a pretty good shakeup, so there might be some loose ones available.”

 

He fished up a blank sheet of paper, placing it on the counter between them.

 

“Put down what you’re looking for here. The types of goods and services you’ll be dealing in, compensation, licenses you’re offering, security arrangements and such.”

 

Ludmila’s borrowed pen scratched over the paper for several minutes as she tried to think of everything she might need. When the old man read over her requirements, his eyebrows rose.

 

“I’ve…never seen a request like this before,” he told her. “Nobles usually hire their own merchants to assist with managing things, but you’re looking to put one on retainer to help handle the business of your fief. Most nobles are passable at dealing with their own territories, so they tend to have a hand directing their own production and trade. If it comes down to it, they’ll have one of their children trained as a professional merchant to run the family business.”

 

“House Zahradnik has never been known for being merchants,” despite herself, Ludmila still nursed some of the bitterness from the afternoon in her heart. “I will have my hands full directing the development of my fief, so I would feel much more comfortable if there was someone to take care of this end of things…several such retainers, if necessary.”

 

“Well, any merchant will hire apprentices and assistants when business is good, so it should be the same for whoever you take in, except that apprentice will become a member of your retinue as well. Most merchants can’t do better than what a noble’s retainer gains through their service, but the sudden exposure to authority and wealth is sure to get into most people’s heads. I’ll see what I can do, but I wouldn’t hope for anything spectacular – especially with things as they are right now.”

 

Ludmila nodded at the response. The old clerk’s reply brought her to her last question.

 

“I understand,” she said. “Send word to my residence in the central district if you find anyone appropriate. There is just one last thing both the Minister and I would like to know.”



“And what is that?”
 

“The city has become…paralyzed after the duchy changed hands,” Ludmila said. “The markets and shops are closed and, barring the few places I’ve found, the various industries have become silent as well. How is it that the Merchant Guild remains open? Or more to the point – how can you still stand and serve clients here, when nearly all of your associates still hide in their homes?”

 

“That’s simple,” the clerk didn’t even bother to stop and think before answering, “the city is open, so the Guild is open. In our line of work, we deal with the fear that comes with opportunity and risk every single day – those that lose themselves to their fear have no right being here.”