\chapter{Ludmila Zahradnik}

By the time Ludmila caught up with Lady Shalltear again, they were crossing another, smaller plaza on the western side of the city. The evening light cast itself between the spaces in the streets and buildings, painting their path with its fading glow. The dark folds of Lady Shalltear’s gown swirled in contrast to the pale white figures of her attendants; its luxuriously rich fabric seemed to eagerly devour what remained of the day. Her parasol still lay over her shoulder, twirling idly on occasion and obscuring Ludmila’s view.

 

Though she roughly knew what she needed, Ludmila still struggled to find the appropriate words to convey her plight to Lady Shalltear. After settling herself with the presence of the Undead, other worries arose: worries that if she slighted her in some small way, even unknowingly, she would doom her demesne to ruin. Thus, she continued to follow silently after her as she worked up what little she knew of dealing with high nobility and deciding what forms of etiquette would be appropriate to observe.

 

She followed them out of the plaza, along the large road as it meandered through the buildings. It continued to feel unnaturally empty; no one looked out of the shuttered buildings on either side on the road to watch their procession. At each intersection, the dark sentinels stood tall beneath the streetlamps, in silent challenge to any opposition.

 

As far as they had travelled, Ludmila wondered if their journey would simply continue in its winding circuit around the rest of the city and have them arrive at the northern entrance to the central district. She found herself drawing closer to the trio ahead of her as she thought of their journey continuing past that, entering the less reputable and poverty stricken areas of the city, before noticing that the group ahead of her had slowed their pace. Looking to the gatehouse at the wall that set the poorest sections of E-Rantel apart from the rest, she saw two more of the same dark sentinels standing on either side of a closed gate. A heavy wooden bar lay across it; she realized that the pauper’s quarter had been closed off. No signs of activity could be heard over the wall and Ludmila wondered why it was so, and if the residents still remained within.

 

Her question would remain unanswered as the entourage turned a few blocks before the gate, into an alley between a pair of prominent buildings: a large inn that appeared to be meant for all manner of guests with a tavern on its ground floor, and a warehouse belonging to the Merchant Guild on the other. Unlike the main streets, the smaller lanes and alleys of the city were not paved and had damp sections left over from the wet winter season of the lowlands. The stretch nearest to the street was a loading area for the warehouse and many wooden planks of varying lengths were laid over places where wagon wheels had worn muddy ruts into the alley. Looking into several of the open loading bays as they passed, she saw that the building appeared to have been vacated: nothing but scraps of paper and a few discarded crates strewn about the warehouse floor. The inn opposite to it was shuttered and locked away like many of the other buildings in the city that she had seen along the way.

 

As they moved beyond the warehouse, the height of the surrounding buildings grew shorter, but the alley tapered to a width that could only accommodate pedestrians. In front, Lady Shalltear and her attendants walked single file: the alabaster-clad women coming before and after their mistress. Ludmila slipped in behind them, not wanting to stray too far in the lonely passage. The lane was no longer as straight as it had been nearer to the main street and angled one way or another as they advanced. Their path now seemed more like a narrow canyon than a city alley; the soil under their feet remaining damp and muddy with the pittance of sunlight it probably saw in a day.

 

She focused on her footing as they made their way down the alley, stepping around puddles and potholes that intermittently appeared along the way. A short while later, Ludmila felt wisps of the cold spring breeze filtering down between the crowded buildings. Faint hints of woodsmoke were carried along with it, and she raised her gaze to look far ahead at the first signs of life she had seen in the capital since her brief visit to the Royal Villa.

 

Shadows cast by the flickering orange flames of an unseen fire danced on the alley wall. Any details were still too distant to make out, but the smoke-tinged air carried with it the distinct smells of Human habitation: the aroma of food being cooked and the odours of sweat and worn fabrics. As she approached, the surroundings grew brighter and the faint murmur of voices carried through the haze of cook fires: over which hung large, cast-iron cauldrons. Overhead, she noted open windows where people of various ages could occasionally be seen inside. Many curiously looked down at the small group that had come in from the main streets.

 

It was a short distance before the alley opened up into a small courtyard nestled deep within the packed buildings. Tall braziers had been placed at the corners of a crudely cobbled square and several men and women stood about them, speaking amongst themselves in low tones. Despite signs of having been cleaned up recently, there was no hiding the age of the buildings that surrounded the open space. Yellow and brown watermarks stained the walls. Patches of whitewash and old clay plaster could be seen all along them. This tiny pocket deep in the bowels of the city seemed to have been forgotten by time: a throwback to an age when the city was still young; the streets and buildings less grandiose. Even the materials used to construct the buildings and the layout of the yard seemed fashioned in an entirely different style to the main thoroughfares of the cosmopolitan city that they had left behind along with its paved roads. Perhaps only those that lived nearby even realized that the hidden plaza existed.

 

A middle-aged man bearing an unmarked load over his shoulder crossed in front of them, bending slightly in respect to the group as he passed by. His gaze lingered on the women but his pace did not slow as he vanished into the narrow alley to wherever his destination lay. Going by the reaction of the people who noticed them, it was not the first time they had seen Lady Shalltear and her attendants in this secluded little pocket of the city which was well out of sight and away from the Undead sentinels.

 

The way the people carried themselves and interacted amongst one another marked them plainly as common folk, but they did not have the fresh appearance of villagers in more rural areas like Warden’s Vale. Though they appeared to have done what they could to maintain their appearance, many had worn clothing marked with the grime, soot and sweat of city life. These were the citizens that worked in the alleys and buildings behind the pristine storefronts, guild offices and warehouses of E-Rantel – the hands and feet and backs supporting the city’s twin pillars of commerce and industry.

 

As Lady Shalltear made her way towards the centre of the plaza, Ludmila looked for a place where she could quietly observe its people without getting in the way. Two women standing under one brazier took note of their passage and after a quick exchange, one of them hurried off into the short doorway of a nearby building. The remaining woman turned to approach one of Lady Shalltear’s attendants. Standing in an unoccupied space behind the group, Ludmila could not make out what the woman was saying as she bowed her head, but the low, plaintive tone made it seem like a petition of some sort. The attendant remained silent and made no motions as she heard the woman out.

 

With the sound of the woman’s voice in the background, Lady Shalltear and her remaining attendant made their way to a small pile of crates where another attendant with a slightly different hairstyle stood with a clipboard in hand. Their mistress stopped and turned to survey the surroundings, looking back towards the way they had come and the small groups of people going about their evening. The other attendant had moved forward to meet the woman standing at the crates, who began to speak at length with the clipboard held in front of her, gesturing at intervals with some sort of pen in her other hand. The mannerisms of a warehouse clerk were at odds with her fine appearance, and Ludmila observed bemusedly from the side as the two conferred quietly between themselves.

 

The return of the first attendant caused Ludmila to turn her attention back to where Lady Shalltear stood near the middle of the yard. She continued to stand with her back turned to her as she listened to what the attendant had to say. Four long shadows extended from her figure, cast by the braziers in each corner, dancing across the ground as the fires flickered and crackled around her. The parasol had disappeared somewhere and the long fan had returned to her left hand. After receiving a slight nod from her mistress, the attendant in turn looked to where the petitioner stood and motioned for her to approach.

 

The woman walked to the building where her companion now stood supporting a third girl in the doorway, and together they helped her come forward to the lady clad in shadowed silks awaiting in the middle of the courtyard. As the trio came fully into view, recognition caused a memory from a year past to jump out at her: a startled and pained yelp from one of her brothers as their father pulled his ear sharply to turn his gaze away from some gaudily dressed and painted women standing at a street corner. It was evening as they were returning to the central district, on an empty wagon through the streets of the city, and her father – who was preoccupied with scolding his sons – did not notice that his daughter was examining their appearance as well. The two women supporting the third, though not nearly as brightly dressed as those from her memory, were most likely prostitutes.

 

Slowly shuffling forward as they supported the girl between them, the three women came before Lady Shalltear, gazes cast downwards. After they helped the girl kneel before her, the first two respectfully backed away, bowing multiple times before stopping to stand quietly at the edge of the plaza. Wrapped in a short, worn blanket, the woman kneeling on the ground shivered in the chill of the early spring evening. She had a thin, ragged appearance and her skin was marred by cuts and bruises. There was a dark splotch where she had received an injury to her head over her left temple, and a deep cut caked her blonde hair with dried blood and glistened slightly as it continued to ooze. Her light blue eyes seemed to focus and unfocus unsteadily as she looked down at the hem of Lady Shalltear’s gown. The girl did not seem quite there. Ludmila looked at the gash over the side of the woman’s head again and decided she must have suffered some other, unseen injury from being struck.

 

The arrival of the injured woman had drawn the notice of several passers-by, who had been alarmed at her bloodied appearance as she was carefully led to the tiny plaza. As they stood to watch, others slowed down and stopped to see what was going on. Silence grew over the courtyard, and eventually only the occasional crackling of the braziers punctuated the still night air. Out of the corners of her vision, Ludmila could see the people scattered around the rough, cobblestoned yard watching the two figures in the centre of the plaza. The sudden quiet led to residents appearing in the windows overhead, looking down for the source of the uncharacteristic stillness in the air. Lady Shalltear stood silently at the centre of attention, as if waiting for the expectant energy in the air to rise further. Then, without word or flamboyant action, she stretched her hand out to the woman kneeling before her.

 

As she reached forward, Ludmila’s eyes grew wide as she noticed for the first time what had been obscured from her vision as she followed Lady Shalltear through the city. Where a slim, delicate arm with beautiful porcelain skin glowed in the firelight also appeared pallid flesh stretched over a sinewy appendage. It extended far longer than that of a normal person’s, ending in a hand with elongated fingers tipped in what were far too long and sharp to be Human nails. As she cupped her chin, the woman showed no reaction to this monstrous sight and Ludmila understood that it was something that she alone was perceiving through her Talent.

 

Ludmila’s mind whirled, trying to understand what she was seeing. Lady Shalltear tipped the woman’s chin upwards to face her fully and, after a moment, her clear, feminine voice could be heard across the plaza.

 

“「Regenerate」.”

 

A bright, magical glow briefly pulsed over the woman and the bruises visible on her face and body faded away without a trace. The gash over her temple closed as the spell mended the cuts on her skin. The girl blinked as the pain that must have accompanied her injuries slowly subsided. Her jaw worked as if to speak, but the fingers grasping her chin maintained their firm hold.

 

Lady Shalltear’s voice sounded again.

 

“「Remove Disease」.”

 

A second, dimmer, glow issued over the woman – this time she froze in place, eyes looking up at Lady Shalltear. In the silence that followed, a tear rolled down one of the woman’s cheeks, then the other. All at once, she collapsed to the ground, sobbing quietly. By the third shuddering breath, her quiet, wracking sobs had grown to a wail that filled the night air. The woman tightly grasped the hem of Lady Shalltear's dress, pouring into it a life of desperation and anxiety; of fear and shame. At the edge of the plaza, the two women that had brought their companion forward were wiping tears away as well.

 

Though the weeping woman clinging to her dress was at least half again Lady Shalltear’s height, her small figure did not budge. Indeed, it seemed that she paid the weeping woman at her feet no mind at all, instead intent on once again observing her surroundings.