\chapter{Ludmila Zahradnik}

The events unfolding in the small back alley square had, by then, drawn a crowd of people. Some had come from the surrounding alleys, while many others occupied the windows looking down into the dimly lit area. They looked on in silence as the heartfelt sobs of the woman continued, seemingly unwilling to disturb the scene playing out before them.

 

From her place behind the impromptu stage, Ludmila silently digested the events leading up to the scene before her. Until that moment, she was unable to make very little sense of their course so far. The reason why this highborn lady, who had a direct connection to the King, would walk halfway around the city to some forgotten back alley on the border of the slums had been a complete mystery.

 

The revelation that Lady Shalltear was a divine caster shed some light on the questions that had continued to rise in Ludmila’s mind. It would not be uncharacteristic for a priest to come and minister to the people. Were her attendants clad in their fine, alabaster garments Acolytes? Their uniform appearance lent credence to this thought. The light, almost sheer cloth of her attendants’ garb could perhaps be found in much warmer regions of the world. The black gown and bolero of Lady Shalltear with its silver and carmine highlights, however, did not match the vestments of any faith she had ever encountered or read of.

 

What manner of priest is she? She wondered to herself.

 

“Cleric.”

 

Lady Shalltear’s voice snapped Ludmila out of her thoughts and she focused her attention on her.

 

“Cleric,” the correction came again, “not Priest.”

 

It was then that she realized that, at some point, she had voiced her thoughts aloud. Though the words had caused her to go silent once again, she couldn't hide the dubious expression that painted her face. Clerics were a part of the priesthood of every religion she knew of. Though they were often trained and specialized for the battlefield, they usually did not mind being called priests. Looking at the back of the slight figure before her, she could not imagine a woman so much smaller than herself standing at the forefront of pitched combat: bolstering her allies and delivering divine wrath upon her enemies.

 

“But surely you are here to minister to the people?” Ludmila asked.

 

This was the first time since they had encountered one another that Ludmila had Lady Shalltear’s attention, so she quickly brushed aside her doubts at the previous statement to press her with questions. As Bohdan had tended to the needs of her village, so too did the priesthoods of larger towns and cities serve their own populations. They gave spiritual guidance, performed charity and though they legally held no political power in Re-Estize, the Temples had a degree of cultural influence and certain rights concerning the use of divine magic.

 

She voiced her query, and Lady Shalltear's posture stiffened momentarily. A short silence ensued. The fan, which she had been waving lazily in front of her face, snapped shut. She turned smoothly with her head tilted slightly, the silken folds of her dress swirling around her.

 

Though Ludmila had mentally braced herself after seeing the Cleric laying hands on the battered and sick prostitute, she felt herself take in a sharp breath as what she now saw rooted her feet to the ground.

 

As with Nabe of Darkness, Lady Shalltear had two appearances.

 

The first was that of a peerless beauty – far beyond that of Nabe – something that Ludmila would not have believed possible were she not witnessing it herself. The Cleric’s luxurious silver hair had been tied up in an off-centre ponytail that spilled down the length of her back. Long, lazy ringlets fell about a delicate face of perfect frame; clear and bright crimson eyes turned up towards her beneath long, silver lashes. In vibrant contrast to pale skin reminiscent of a porcelain doll, her cheeks were flush with life while small, soft lips parted with the hint of an alluring smile.

 

It was a bewitching appearance that anyone would fall to; any feelings of jealousy or envy swept aside by adulation and longing. Wealth and power beyond all reason would be squandered to obtain even a moment of her favour. She was possessed of a legendary beauty that could topple nations and spark wars that set the world aflame, and the world would gladly become ashes for her sake. But even as Ludmila stood entranced by this vision, her Talent made her aware of a second, horrifying appearance that lurked beneath the first.

 

Like the arm she had seen previously, pallid flesh was stretched over a face that invoked a dark and primal fear from deep within her. Her mouth, parted in a ghastly smile, was impossibly wide with pale lips stretched thinly around it. All around the inside of her mouth lay row upon row of wickedly curved, needle-sharp teeth, much like the lampreys that would occasionally be found latched to sides of fish caught from the river. A long red tongue writhed sinuously within, running over the carpet of teeth like a fleshy rasp. Glowing crimson eyes shone from within their dark hollows, and Ludmila felt like nothing more than helpless prey. Even the lustrous silver strands that framed her face seemed about to move on their own.

 

As Ludmila stood transfixed by what she saw, Lady Shalltear seemed to be gauging her reaction. The corner of Lady Shalltear's mouth twitched, and when it seemed that nothing more would be forthcoming from the girl standing rigid before her, she straightened from her coy posture to speak.

 

“It is the Will of Ainz Ooal Gown, the Sorcerer King, that His domain stands as a beacon of prosperity and harmony for all the world to see.”

 

Lady Shalltear's answer was clearly not only for Ludmila and her soft, lilting voice chimed lightly across the square.

 

“By the grace of His Majesty, you are afforded protection as His citizens.”

 

The arm holding the closed fan swept out over the onlookers surrounding the square as she turned away from Ludmila with a grand gesture. Her feminine figure swayed seductively in the light of the braziers as she made her way back to the centre of the plaza. By this point Ludmila could see a throng of people gathered in their surroundings – even the rooftops had people looking down from them.

 

Lady Shalltear’s pace slowed as she came back to stand near the stacked crates again. The healed prostitute had collected herself and knelt with her companions. The Cleric’s gaze surveyed the surroundings before finally coming to rest on the wooden containers before her. Following that gaze, Ludmila saw that a meagre-looking plant had been laid on the corner of one of the boxes. With small flowers of white and yellow, she recognized it as one which commonly grew out of the cracks in the pavement and masonry of the city.

 

Producing a silken handkerchief, Lady Shalltear gently picked up the flower, placing it on the cloth to be folded within. Then, while holding the humble tribute in her left hand, she raised her right.

 

“「Gate」.”

 

A hole opened in the air behind where the boxes lay – it was similar to the one that had appeared in the warehouse in Warden’s Vale. Wide enough for several grown men to fit shoulder to shoulder and just as high, it hovered silently in inky darkness. The Acolyte with the pen and clipboard came to stand before Lady Shalltear.

 

“Pandora’s Actor will know what to do with this,” the Cleric said as she handed the wrapped flower over to her attendant, who had her palms held out to receive it.

 

Lady Shalltear’s hand motioned lazily at the crates in a dismissive gesture.

 

“Return these.”

 

As she turned away, another attendant came to pick up one of the crates. The hollow sound it made as it bumped against the others upon leaving the ground suggested that it was empty. Falling in line with the other Acolyte with the clipboard, they stepped forward into the hole in the air and disappeared.

 

After a moment, the Acolytes reappeared with identical crates, but they made a more solid noise as they were set down in place of the ones that had been carried away. Back and forth the attendants went, not seeming to tire or mind their burden. As the crowd looked on, the attendants eventually refilled the space formerly occupied by the empty crates, neatly arranging them behind Lady Shalltear.

 

“It is the Will of His Majesty that His people shall not want for shelter or provision,” the end of Lady Shalltear's sentence was punctuated with a thump as the last of the crates settled on the ground behind her. “It is His Will that His people are provided with the security and stability to thrive – regardless of their ability, occupation or station.”

 

As Lady Shalltear once again wove around the plaza, her swaying movements and graceful steps seemed almost a dance – more suited to the polished floors of a palace court than the dirt and puddles of the alley. The rich silks of her black ballroom gown swept over the ground and the sweet sound of her voice filled the square; those watching stood transfixed by the vision made manifest before them. It was as if they had found themselves transported into a song of legend and they were witnessing a noble of the highest calibre. Their cramped and dirty alley had been transformed into the grand courts of some far-flung empire, where the lady before them was delivering not a message to the riffraff of a city conquered, but a proclamation to the heads of great houses and rulers sitting on their thrones. In one hand she held healing and salvation; in the other she offered peace, prosperity and the hope for a greater future.

 

As she spoke, the attendants had all returned and opened the newly-arrived crates. They revealed food – staples, vegetables and cuts of meat. Others contained bolts of flax and linen, balls of wool yarn and spools of plain thread. Coal and charcoal could be seen filling others still; as well as logs of wood and kindling. A great plentitude of life's necessities were arrayed behind Lady Shalltear as she continued to speak, adding a simple to understand weight to her words.

 

“Those who strive to serve under His rule shall be rewarded in equal measure,” Lady Shalltear rested her hand on the shoulder of the woman she had tended to. “Those that would dare to bring harm to what is His shall be granted no quarter.”

 

She beckoned for an Acolyte to come forward with her free hand. Immediately, one of the gorgeous women clad in alabaster silks stepped before her and deeply bowed.

 

“The one that did this,” Lady Shalltear's voice could be heard clearly across the square as she issued instructions. “Find him, and bring him here.”

 

The woman raised her head, and Ludmila thought she saw a predatory gleam in her dark eyes before she turned away, walking straight towards the edge of the crowd on the opposite side of the square. It took a moment for the bystanders to realize that the last words they heard had been an order, but upon this realization a disturbance arose from the direction the woman was walking towards. The crowd turned their heads. A small opening formed in the wall of people: revealing a tall, lanky man with the appearance of a common labourer. He had already taken several steps, trying to shove through the crowd, but it was too late.

 

“「Hold Species」.”

 

The man froze completely mid-step, magically paralyzed by Lady Shalltear’s spell, his arms held out in front of him as he was trying to push his way through the wall of people in the way. Those around him did not even have enough time to register what had happened as the Acolyte scooped him up entirely, carrying the man like a hollow wooden mannequin back to her mistress with no more visible effort than she had shown when she delivered the filled crates.

 

Lady Shalltear nodded as she opened a new Gate. The man was still frozen as he was carried off to some unknown fate.

 

The spellbound feeling over the crowd had partially broken due the commotion, but the Cleric’s declaration still echoed in their minds. Lady Shalltear had rejected the notion that she was a priest, but what had transpired delivered a message more powerful than any sermon Ludmila had ever attended. As she looked around the plaza at the faces in the crowd, all those present had clearly been moved by her words.

 

No...rather than moved, something had taken root. Though Lady Shalltear’s unveiled appearance had tempered Ludmila’s reception somewhat in her own eyes, she still felt the lingering appeal of her words. A colder, more calculating part of her mind reared up in alarm – an ember had been instilled in the hearts of the people here, and from deep in the lowly alleys of E-Rantel, it would spread and perhaps set all its citizens aflame with the evening’s message. It was something many a noble both sought and feared at the same time, something that could become extraordinarily dangerous if it flew out of control.

 

As she watched the people slowly disperse, the attendants had taken up positions in the middle of the plaza, distributing the supplies to the queues that had formed after their mistress had retired from the stage. Charity was also a component of various faiths, but the sheer abundance before her would have beggared even the largest of city temples before long. As Ludmila watched them work, she felt a presence brush up near her.

 

“Baroness Zahradnik.”

 

Ludmila looked down at the familiar voice and her body jumped – most of what appeared below her was a yawning pit of needle-sharp teeth. She was only thankful that she didn’t cry out as well. Lady Shalltear’s slight stature certainly allowed her to move about without being noticed, if she wasn’t purposely drawing attention to herself. Ludmila had a great many things to ask of her, but everything she had thought of seemed to want to come out at the same time, resulting in her mouth opening wordlessly and not much else.

 

The Cleric in the black gown seemed amused by her reaction, and wrapped a hand lightly around Ludmila’s elbow.

 

“Let us speak privately elsewhere.”