\chapter{Ludmila Zahradnik}

The pair appeared at the same gazebo that Ludmila had arrived in alongside Momon and Nabe earlier that day. Night had fully fallen over E-Rantel, and the cool air was refreshing after being in the crowded atmosphere of the smoky alley plaza. The wide open space under the clear night sky had a relaxing effect on Ludmila as she stepped off the platform behind Lady Shalltear, who had let go of her arm after they had arrived.

 

“This gazebo appears to be quite popular,” Ludmila said casually while stretching.

 

As the words left her mouth, she realized the sort of sloppy appearance she was putting on – not to mention speaking out of turn with a member of the Royal Court. Her heart sunk as she brought a hand to her mouth at her own rude behaviour. All of her efforts to organize proper protocol her mind seemed to have been for naught.

 

“Hm? Ah, that place is the only spot where teleportation isn’t prevented here,” Lady Shalltear peered around the grounds as she responded to Ludmila’s words, not even bothering to turn around before speaking.

 

Ludmila blinked several times upon hearing this. While she had not even known of the existence of teleportation magic before today – never mind that it could be restricted – it didn’t seem like such a good idea to reveal security measures openly in public. Perhaps it wasn’t as important as she felt it was; Lady Shalltear’s voice had lost its formal tone, leaving only her light, lilting voice that seemed not too much different from a young woman around her own age. Ludmila wondered if it meant that she herself could relax and put formalities aside…or perhaps Lady Shalltear was graciously covering for Ludmila’s breach in protocol.

 

Deciding that it would be for the best to not to press her luck, Ludmila remained silent as she followed behind her, resolving her self once again to demonstrate the proper decorum. Lady Shalltear’s attendants had been left behind to distribute supplies to the crowd of people in the plaza, so they walked alone together through the empty streets of the central district. Several of the guest houses they passed had dim lighting that filtered through their windows, so it seemed that the nobles’ meeting had adjourned – she would have to find some way to catch up on everything.

 

They crossed several intersections, circling around partway behind the Royal Villa, before Lady Shalltear turned and headed into the yard of what looked to be an unoccupied guest house. Ludmila stopped at the gate to look up at the building: it was fashioned in line with the same themes as the rest of the homes in the central district. Unlike the wattle and daub construction of the buildings in the common area, these were sculpted primarily from limestone to match the aesthetic of the Royal Villa and the nearby administrative offices. Rather than a simple guest house, it was in reality a large manor – roughly ten times larger than the baronial manor in Warden’s Vale, its wooden hall included.

 

There was a letterbox with the number ‘04’ on it just inside the entrance of the yard, and the Lady Shalltear was tiptoeing to reach inside. Her tongue was pressed against her lip as she fished around blindly, finally pulling away with a large black iron key. Turning back to the street, she held it out to Ludmila.

 

“My lady, what–”

 

“These will be your accommodations in the city,” Lady Shalltear told her, “for as long as you require them. Well, they’re actually the quarters that were allocated to me since I’m often called to perform duties here, but I haven’t used this place at all. I can return to my own home rather quickly, as you might have surmised.”

 

Ludmila received the key, feeling its weight in her palm. The guest houses in the central district were quite expensive to rent out – it was actually much cheaper to frequent the merchant inns out in the common sections of the city, and nobles with little in the way of discretionary wealth often resorted to using them.

 

“Once I settle the Barony’s goods, my lady,” she lowered her head, “I will pay you back for the rent.”

 

“There’s no need for that,” Lady Shalltear waved her hand lazily. “It's free for me to use anyways.”

 

“Thank you for your generosity, Lady Shalltear.”

 

When she rose again, she found herself face to face with Lady Shalltear and it took all of her will to not jump back in alarm. If Lady Shalltear sensed what had almost happened, she gave no indication of being offended by it.

 

“Surely you didn't follow me halfway around E-Rantel just to gape at my face,” Lady Shalltear said, “If we would speak at length, it hardly seems appropriate for young ladies to be standing outside in the dead of night.”

 

She was right, and Ludmila had found herself once again committing a faux pas in the presence of a royal courtier. Fumbling with the key in embarrassment, she walked quickly through the front yard of the guest manor to its ornately carved door, turning the lock. With a soft click, it swung inwards, opening into a small foyer where she saw her bags had been deposited in plain view near the entrance. Breathing a sigh of relief at one less thing to worry about, she stepped inside and looked around for a lamp.

 

“What are you doing?” Lady Shalltear’s query floated in from outside the door.

 

Ludmila poked her head out of a closet further down the corridor.

 

“I am looking for a lamp, my lady,” she replied. “Or a lantern, or something similar to help light the house.”

 

“But you don’t actually need it, do you?”

 

Ludmila’s hands ceased their searching, and she stepped out of the closet again to look at Lady Shalltear with an uncomprehending expression on her face.

 

“Beings with Truesight do not need light to see,” Lady Shalltear answered the question on her face with the matter-of-fact statement.

 

Ludmila closed the box she had been rifling through, placing it back into the closet.

 

“You are aware of my Talent?” She said carefully.

 

“Of course,” Lady Shalltear replied. “Momon did mention it clearly in his report to the Guardian Overseer...well, since it is a Talent, he wasn’t sure whether it was exactly the same or not. Actually…”

 

Lady Shalltear stretched out her arm towards her, and an exquisite rod of clear crystal materialized in her grasp.

 

“「True Seeing」. Well…what do you see?”

 

Ludmila opened her eyes, having flinched when she felt the spell being abruptly cast on her. She turned her head to look around for a minute, finally bringing her gaze back to Lady Shalltear.

 

“Nothing," Ludmila said. "I mean, nothing has changed, my lady. Everything looks like it usually does.”

 

“And so you have it.” Lady Shalltear nodded as the rod vanished again, “Though there are some distinct differences between a spell that emulates Truesight and the sense of those that have it naturally, it should basically function in much the same manner.”

 

While they spoke, the scent of rain drifted in from outdoors. Looking beyond the yard outside, Ludmila saw tiny droplets starting to fall.

 

“Please come inside, my lady,” she motioned to her liege, who was still standing at the door. “It will not do for someone of your standing to become soaked outside.”

 

Lady Shalltear tentatively stepped into the manor and, when she found herself fully inside, smiled to herself for some reason.

 

Ludmila picked up her bags and carried them further into the manor, committing the layout to memory as she walked through its halls. She pondered over how her Talent worked. Ludmila had always thought the others in the village could see as well as she did, or perhaps she just had slightly better vision than the rest. Activity around the rural village revolved around the availability of daylight; even border patrols established camp in the evenings. Her assumption had been that it was simply how Humans behaved – working during the day and sleeping at night – and so she did the same. She had never realized that she had a Talent while she grew up in Warden’s Vale, but now that it had come to light, she had become more and more curious about its potential.

 

The manor was much larger than she had initially thought, with a large patio in the centre of the building around which the corridors leading to the manor's various chambers ran. A flight of stone steps ran up one side of the courtyard, presumably to the residents’ private rooms upstairs. Ludmila slowly walked around the open space of the ground floor, looking into each door as the pitter-patter of raindrops on the patio accompanied her steps. After going past several doors, she found what she had been looking for – the main hall of the manor – though it had been converted into something more along the lines of a large drawing room to entertain guests. She stepped inside and looked about the richly furnished space. Its drapes had been drawn closed and, though it had all the furnishings of a wealthy noble’s manor, the polished surfaces of its tables and shelves lay bare.

 

There was a pomf sound behind her; Ludmila turned to see that Lady Shalltear had followed her to the room and was now settling onto a long sofa positioned near the fireplace with its empty hearth. Seeing this, Ludmila moved to see if she could get a flame started.

 

“Now what are you doing?”

 

Lady Shalltear spoke from where she was reclining, stopping Ludmila over ten paces from the fireplace.

 

“I was going to start a fire to warm up the room, my lady,” Ludmila answered.

 

“Come here and sit down,” her liege’s tone brooked no argument.

 

Ludmila turned around and headed back to where Lady Shalltear was reclining. Selecting a large chair which was set to face the others, Ludmila placed her bags on the floor beside it. As she seated herself, she registered figures moving around them.

 

Four Skeletons, complete with arms and armour, materialized from the ground. Ludmila immediately rose in alarm but Lady Shalltear, lying across from her, made no move, nor did she seem to even care. Two of the Skeletons walked over to where the fireplace was. One walked back and forth from the rack of firewood nearby, piling logs in the fireplace while the other stood guard with the fire iron in hand for some reason. After a half dozen logs had been neatly arranged on the hearth, the Skeleton stopped and Lady Shalltear – still reclining on the couch – raised her arm, holding her palm out towards the ceiling.

 

“「Flame Strike」!”

 

With a tumultuous roar, a column of flame streaked down through the chimney and into the logs arranged the fireplace. The two Skeletons standing by the fireplace were simultaneously blown apart and incinerated as the flames struck the hearth and exploded; the fire iron was sent whistling end over end until it buried itself in the couch just above where Lady Shalltear was reclining.

 

Ludmila, already on edge when the Undead had mysteriously appeared, leapt over the arm of her couch at the sound and remained behind her cover against the flaming debris landing all over the room. After the chunks of wood and stone stopped raining down around them, she thought she heard an “oops” drift quietly over the sofa. Peeking over the armrest, Ludmila was fairly certain that the word did not come close to describing what had happened.

 

The large fireplace had crumbled apart below its mantelpiece and the polished stone floor in a three metre radius around the hearth was scorched and shattered. The remaining two Skeletons were running around frantically scooping up flaming bits of wood and tossing them into the pile of rubble that was once an extravagant showpiece of the hall. One stopped to try to beat out a fire that had caught on the drapes nearest to the disaster. As the flames licked their way up the fabric, the Skeleton gave up on its attempts and tore the entire thing down, tossing it over the flaming pile of what remained of the hearth. Ludmila wondered how many gold coins had just gone up in smoke.

 

She waved her hand in front of her face as she coughed, trying to clear away the traces of smoke lingering in the air before her. As she went to air out the room by opening the now-drapeless window, she heard Lady Shalltear speaking on the sofa.

 

“Yes! No! Yes, that was me. Wha–our fireplaces don’t do that…no, you don’t have to send anyone over, it’s fine...I said this is fine!”

 

Unable to stifle her curiosity, Ludmila turned around to look behind her but couldn’t see who Lady Shalltear was speaking to.

 

“That girl? You mean Baroness Zahradnik? She’s okay, she’s–”

 

Lady Shalltear stretched her neck to peek around the fire iron which remained impaled in the couch above her supine form.

 

“Alive. Of course she’s alive! ...you don’t have to sound so disappointed when I say that!”

 

Ludmila turned back around and checked herself over after she opened the windows. Aside from some splinters and soot stuck to her skirt, nothing appeared to be amiss. Outside, she could see several of the tall sentinels that she had encountered around the city gathered on the street in front of the manor, the crimson points of light in their eyes looking towards her. She tried waving them away like someone might have waved off a militia member looking into a disturbance, but they ignored her and continued to stand on the pavement being pelted by the rain.

 

She turned back just in time to see Lady Shalltear roll off the couch, brushing her dress off after getting up. Lady Shalltear eyed the fireplace poker embedded halfway into the couch with a frown, grasped the handle, and gave it a firm yank. The instrument came out in a single motion, but the prong had hooked onto the contents of the cushioned backrest, pulling out a long trail of stuffing behind it. With an expression that looked somewhere between displeasure and embarrassment, she flicked the wrought iron instrument in the direction of the destroyed fireplace, where it buried itself in the pile of flaming rubble all the way to its hilt.

 

The Cleric waved her right hand in a dismissive gesture, and the two remaining Skeletons dematerialized where they stood. She turned to face Ludmila, not quite looking her in the eye.

 

“Do you think there’s any tea in the kitchen?”