\chapter{Ludmila Zahradnik}

As it turned out, there was no tea in the kitchen.

 

Ludmila looked through the empty pantry for a few minutes before deciding that since there was no expectation of anyone living in the manor, it had just not been prepared for residents. In the end, she couldn’t even find any teacups, dishes or utensils anywhere either, so Ludmila ended up fishing out two wooden cups from her baggage. Now they were sitting across from one another over a kitchen counter, nursing their cups of river water which had been drawn before her departure from Warden’s Vale. Long minutes passed with the sound of rain filtering into the kitchen, and Ludmila quietly worried over whether her actions constituted as being a gracious host, or an insulting one.

 

Lady Shalltear broke the lull between them first, rubbing her nose and checking her fingers for soot.

 

“So…do you have any questions?" She asked, "Is there anything else that you require beyond accommodations in the city?”

 

Ludmila looked up from her cup of water. On the other side of the counter, both appearances seemed to be waiting expectantly.

 

“Then...do you know what my Talent actually does, my lady?” She asked, “The Adventurer Momon – of Darkness – seemed to recognize what it was, but we parted before I was able to ask.”

 

She decided to start with something that Lady Shalltear seemed to be familiar with rather than dumping a whole pile of her demesne-related problems onto her lap all at once. Due to the calamity in the hall, the air of tense formality between them had dissipated by a large degree. Ludmila thought it might be a good opportunity to develop an understanding of the powerful woman on a more personal level.

 

“Truesight is one of the most potent sensory abilities known,” Lady Shalltear said. “Since you were born with it, I suppose its use should come to you as naturally as any of your other senses. As you already know, it allows you to see through darkness, but not only the absence of light – it also sees through visual obscurement maintained through magical means.”

 

She extended her arm towards the doorway leading to the courtyard and cast a spell.

 

“「Darkness」.”

 

Inky blackness smothered the opening but, while Ludmila saw it appear, she simultaneously saw through it as clearly as if it was not there.

 

“Normally,” Lady Shalltear told her, “Humans will only see a wall of darkness in the doorway, but you should be able to see plainly through it.”

 

Ludmila nodded, and the Cleric continued her explanation.

 

“Truesight will foil all magical or supernatural forms of visual deception in your eyes, even if they aren’t explicitly targeted at you. Invisibility, optical illusions, shapeshifting – even the most subtle alterations of form by magic – will all be laid bare to your sight. They should appear to you just as I do right now.”

 

Lady Shalltear smiled, which was simultaneously dazzling and terrifying. Ludmila offered no overt reaction, and Lady Shalltear pouted a bit before speaking again.

 

“You are prudent to limit the awareness of others to your ability,” she said. “Vampires like myself don’t particularly care whether we are seen or not, unless it compromises some other purpose, but races whose natural advantages are linked to their ability to alter or conceal their forms would probably react to you as a threat.”

 

Recalling Nabe earlier in the evening, Ludmila was forced to agree. While Ludmila’s Talent seemed more wondrous as she learned about it, in the end she was only Human, and perception in the face of overwhelming violence would do little in light of her relative weakness.

 

“Since you’ve been born with Truesight as one of your natural senses, the usual magical means of defeating it will not work. Counter-divination spells, items that protect against scrying and anti-illusion magic, even the most powerful forms of visual deception reliant on magical or supernatural powers – those that your people would consider the realm of the gods – are powerless against your ability.”

 

Ludmila swallowed: her own Talent was beginning to scare her. She raised her cup to moisten her throat before asking a question.

 

“Then how do you fight Truesight, my lady?” She asked, “Is there anything I need to be careful of?”

 

“Why, of course.”

 

Lady Shalltear pointed a finger at her.

 

“「Blindness」.”

 

The noblewoman cried out in surprise as the world turned dark. The wooden cup fell out of Ludmila’s hands, but she didn’t hear it clatter to the table or the floor.

 

“If someone can rob you of your vision in ways that Truesight does not defeat,” Lady Shalltear told her, “then you become as blind as anyone else that has lost their sight. If a thought is planted in your mind that you cannot confirm with your own eyes – say a smell, or a sound – then, obviously, your ability will not save you: it is something that is bound to your vision, after all…it’s a bit unsatisfying how quickly you become calm, you know?

 

「Remove Blindness」.”

 

Ludmila apologized, wondering whether it was something to actually apologize over.

 

“I am sorry, my lady,” she said. “I was trying to pay attention to what you were saying.”

 

Blinking several times after her vision was restored, she realized that Lady Shalltear might have a bit of a sadistic streak...or at the least she seemed to enjoy teasing her. Ludmila located her cup, which had been placed to the side, and reached out to nurse it in her hands again as she continued listening.

 

“There should be some other things you should have put together by now,” Lady Shalltear continued. “Truesight doesn’t let you see through walls or clothing, so any sort of conjuration that produces something real will obscure your vision, even though they were originally created through magic. But while you may not be able to see the face behind someone’s mask or cloak or armour, mundane tricks that rely on light to deceive observers will probably not work on you, since you do not require light to see.”

 

Lady Shalltear produced a long, white silk glove from somewhere. As she pulled it over her hand, Ludmila furrowed her brow as Lady Shalltear's elongated fingers seemed to shorten and conform to the shape of the glove. The rest of her hand followed as she finished putting on the glove, with no sign of what Ludmila had witnessed before. Such an obvious thing did not actually occur to her: clothing and physical barriers were a normal part of her life and she did not really treat it as a special sort of exception in the short time that she had become aware of her Talent.

 

“Finally, just because you see the true form of others does not mean you can also always deny other guises they may assume.”

 

Lady Shalltear’s ungloved hand reached out to grasp her wrist. The grotesque appendage with its elongated fingers and wicked talons did not touch her – instead it was the delicate, carefully manicured hand that lightly rested its cool fingers on her skin.

 

“A polymorphed creature will interact with you according to its current physical form,” Lady Shalltear told her. “Just because you see that your enemy is a mouse turned into a bear doesn't mean it will not maul you. A Human Druid transformed into a Manticore will still injure you when it hurls its spikes – and the venom will affect you all the same. Similarly, the reverse is true. The hand around your wrist may appear to be a false form, but it is real all the same and the nails of my true form will not dig into your flesh as I do so.”

 

Ludmila made a mental note, and asked her next question after seeing that Lady Shalltear had completed her explanation.

 

“How can I combat the methods of defeating Truesight that you’ve described?” Ludmila asked.

 

Lady Shalltear released Ludmila’s wrist, brushing her cheek lightly with her fingers as she pondered.

 

“Hmm...well, there are various potions and items that will defend against or remedy these problems, though you will have to discover if they are sold locally here. As for those mundane things, I suppose it will be a test of your skills of perception.”

 

As she spoke the last, a gleam formed in her crimson eyes and her lips curved upwards in a slight smile.

 

“What?”

 

“I think I’m beginning to agree with what Momon said at the meeting today,” Lady Shalltear said.

 

Ludmila straightened herself, waiting to hear what had been said about her before the Royal Court.

 

“While you are Human and certainly react in Human ways,” Lady Shalltear said, “you are very different from most of your kind that I have witnessed. When presented with the things that they fear, most will avoid it: they will cower and hide, or they will run. A few – perhaps brave, foolish or mad – would thoughtlessly stand up to their fears...perhaps on behalf of another or for some intangible ideal. Not many would act as you do: in the face of things that you should fear, you do not seek a way to escape such an encounter. Instead you ask questions. Analyze. Plan. Even your polite manner of speech has faded away as your true nature unveils itself. In the end, you look to attack and defeat the very things that would defeat you. As weak as you are, you are like us, in various ways.

 

If Cocytus were here, I suppose he would go on about it being the way of a warrior or some such nonsense, but amongst all of the Humans I have come across, the only one that behaved as you do was not one of your pitiful warriors, or even those so-called Adventurers.”

 

“I do not know who Cocytus is, my lady,” Ludmila replied, “but I think that sounds about right…the way you describe it, it seems to very much be something like a warrior’s mindset. When you are what stands between your opponent and their objective, then you must do your utmost to prevail.”

 

“Well, it wasn’t,” Lady Shalltear said. “He was a merchant, if you can imagine that. To be sure he was startled when he arrived and found the city to be occupied by the Undead, but he recovered quickly and was quite infuriated that his business had been disrupted. He turned the city upside down looking for ways to keep his trade going, until Sebas finally came out to deal with him and sent him on his way. That merchant was quite the wonder – it made us curious why the rest of you Humans couldn’t just all do the same.”

 

Lady Shalltear pulled on a second silken glove and folded her hands on the counter before her. Her light, conversational voice took on a more serious tone.

 

“Momon has suggested that you might be able to solve some of the problems currently plaguing E-Rantel,” she said. “As you have seen tonight, the citizens cower in their homes – they will only come out when they need to, and when they see that Momon is in the city. That gor–ahem, the Guardian Overseer does not understand Humans, and only deigns to deal with them up to the point where she believes that useful ones can be...encouraged. She has a mind of order and duty, an endless stream of numbers and rules; a plethora of plots and schemes and mechanisms that drive the gears of what she envisions our Master’s realm to be. She believes that the citizens should feel safe when they are told that they are. That they should work when told to work; eat when they are told to eat, and die when they are told to die.”

 

“You...do not think the same, my lady?” Ludmila asked tentatively.

 

“If His Majesty declared this to be the case,” Lady Shalltear said simply, “then it must surely be so. But he has not. In fact, it's precisely the opposite. E-Rantel has been allowed to keep its laws and his vassals have been given free reign to administer as they see fit. This would mean that he trusts us to govern in accordance with his decisions with as much flexibility as is necessary, yes?”

 

Ludmila thought on her words. Countess Jezne had also said something along the lines of E-Rantel retaining it’s crown and ducal laws, but she had not heard anything about the King’s cabinet having a free hand over the nation. It was an unheard-of amount of freedom that she did not think any reigning sovereign would willingly tolerate. Lady Shalltear continued as Ludmila pondered the Sorcerer King’s decision.

 

“At any rate,” Lady Shalltear continued, “if there’s anything you can do to help get things moving again, or if there’s anything you need from me in order to do so, just let me know. If it gets us even one millimetre closer to fulfilling His Majesty’s desires, I'll be more than happy to do what I can to help. My specialty lies in battle, so the most I can probably do is to help ensure no one gets in the way of your work. Beyond that, I know little about taxes or industry or the citizens or whatever else that goes into all this.”

 

“Surely you can’t mean that, my lady,” Ludmila responded incredulously, “all those people in that alley…they were clearly moved by your words.”

 

Lady Shalltear tilted her head curiously.

 

“I-is that so? We deliver supplies to many parts of the city like that every day, though? I only decided to speak after you said you thought I was ministering to the people…and even then, I only repeated the Sorcerer King’s desires for his new realm.”

 

“If that’s all you truly think that you did,” Ludmila said, “then you must be gifted beyond belief. Hundreds of people were enthralled by your words and actions by the time you finished.”

 

The Vampire across the counter fidgeted with her wooden cup.

 

“Suppose what you say is true…” She drew out her words, “I didn’t exactly tell them to do anything. What do you think might have even come out of it?”

 

“I do not know,” Ludmila replied. “Maybe all the people needed was more reassurance. What follows might just come on its own.”

 

The ringing of a bell somewhere near the room interrupted their conversation. Ludmila turned her head at the sound, looking out the kitchen doorway. Large manors had offices that were normally staffed by hired or personal maids. Several bells would be in that office, which were activated from various parts of the house and used to signal the staff on duty. However, as the house was previously unoccupied, no such staff were in attendance.

 

The bell sounded again, coming through the corridors from the room across the courtyard. As Ludmila rose to answer, she felt a cool, silk-clad hand reach out and grasp her wrist.

 

“Wait.”

 

Ludmila looked back at Lady Shalltear, who had switched to low tones for some reason. Before she could ask for an explanation, she heard the sound of someone landing on the patio with a light splash. Soon after, footsteps came from somewhere out of sight, accompanied by the sound of the rain. The trepidation shown by Lady Shalltear created an ominous feeling as the sound approached.

 

“Baroness Zahradnik?”

 

Yuri Alpha’s voice echoed through the empty courtyard and through the halls.

 

“Baroness Zahradnik,” Yuri Alpha called again, “are you here? Are you alright?”

 

The maid’s tall figure came in front of the kitchen door and stopped.

 

“What in the world is...Baroness Zahradnik, are you inside?”

 

It occurred to Ludmila that Yuri Alpha could not see through the Darkness spell that covered the door.

 

“Yes?” She replied uneasily, “Yes, I’m here.”

 

“Oh, thank goodness,” the Royal Maid said. “Would you have happened to see Lady Shalltear?”

 

Ludmila turned to look back at her liege, who shook her head vehemently in reply.

 

“Lady Shalltear? She’s, uh…”

 

As Ludmila hesitated, Lady Shalltear slid off of her stool and onto her feet.

 

“「Greater Teleportation」! …dammit!”

 

During the commotion, Yuri Alpha dove into the darkened doorway, rolled over the tiles and rose to her feet with her fists held out before her in a fighting stance. Her eyes went from Ludmila, to Lady Shalltear, and then to the Vampire’s hand gripping Ludmila’s wrist. Following her gaze, Lady Shalltear quickly released her hold and hid her hand behind the counter. The maid narrowed her eyes suspiciously.

 

“Lady Shalltear, did you just try to teleport away with Lady Zahradnik?”

 

“Erk–”

 

“Why is the doorway shrouded in Darkness?” Yuri asked, “Just what were you trying to do to the girl in here?”

 

“T-there’s a good reason for all this, we–”

 

The Vampire tried to explain herself, but the maid had relaxed her posture and turned to speak gently to Ludmila.

 

“You’ll be alright, Lady Zahradnik,” Yuri Alpha said in soothing tones. “His Majesty desires that all of his subjects should live safely under his protection. It’s just that Lady Shalltear gets a little bit…excited sometimes.”

 

As Lady Shalltear sputtered, Yuri Alpha continued on in her comforting voice.

 

“Sitting in a pitch-dark kitchen drinking tepid water is not something a lady of your station should be doing, Baroness," she said. "I've brought a few maids along with me, as well as a pair of sentries for your lodgings. I'll have them bring your things to the solar and have a hot bath prepared. We'll have you changed into a fresh dress and there will be a warm meal delivered.”

 

Ludmila perked up at the offer. Thoroughly exhausted after being thrown from one unfamiliar situation to another throughout the day, it did sound very enticing. Lady Shalltear did not miss her reaction.

 

“What–are you turning on me for a hot bath?” Lady Shalltear exclaimed, “Traitor!”

 

Her brows furrowed for a moment, then her expression brightened again.

 

“Wait! I can give you all that as well…I think?”

 

“You will not be giving Baroness Zahradnik a bath,” Yuri Alpha said flatly.

 

“But–argh! Why am I the bad one here?”

 

“You’re not?” Yuri Alpha arched an eyebrow, “I received a curious report from one of the Death Knights returning from their patrol. Apparently a column of fire came down in the middle of a rainstorm, right into this very manor. I do sincerely hope nothing of His Majesty’s city was damaged.”

 

Lady Shalltear shrank behind the counter.

 

“How mysterious...I wonder how that happened…”

 

Yuri Alpha sniffed, adjusting her spectacle frames.

 

“Indeed. I’ll let in the maids now and have the Death Knights help clean up before they take on their sentry duties. We might need someone for the roof as well, seeing how easily I was able to enter.”

 

The maid made a precise turn and left the kitchen, heading towards the manor entrance. Ludmila looked back at the defeated Lady Shalltear, who had laid her cheek on the cold stone counter. Seeing her glance back in her direction, Lady Shalltear spoke in a deflated tone.

 

“Well, what are you waiting for?” She didn’t raise her head, “Go refresh yourself, I’ll…I’ll be waiting down here.”