\chapter{Ludmila Zahradnik}

The night’s rain had ceased, and the courtyard patio glistened as Ludmila made her way back down the stairs to the main floor of the manor. The corridors were lit – as were the various rooms in use by the new members of the manor staff. She headed back towards the kitchen to see if Lady Shalltear was still there.

 

“Over here, Baroness,” she heard her liege call to her from off to the side.

 

Turning towards the sound of her voice, Ludmila spotted the edge of the black gown with its silver and carmine frills in a drawing room across the courtyard. She made her way around and into the room, coming upon Lady Shalltear who was nibbling on a scone. Seeing the food pass through the image of one mouth and into the other was odd, to say the least. Yuri Alpha was nowhere to be seen. Ludmila took a seat on a short sofa across the rosewood centre table from the Lady Shalltear, whose dangling feet were swinging idly under her skirts as she worked on her pastry.

 

A shallow splash in the courtyard turned their heads towards the entrance of the drawing room. Yuri Alpha had returned, with a covered dinner tray in hand. Shalltear’s sarcastic query met the maid as she entered the room.

 

“You’re not making a dynamic entrance like that every time you want to enter someone’s house, are you?”

 

“Of course not, Lady Shalltear,” Yuri replied. “I was simply repositioning one of the Hanzos from an empty manor nearby; the roof of this building should be better secured now.”

 

Yuri Alpha came over to lightly place the silver tray on the centre table.

 

“Please pardon my presumption, but I took the liberty of ordering your meal, Lady Zahradnik,” she said. “This should be popular amongst young people…at the least, Lady Aura seems to relish it.”

 

Yuri Alpha lifted the cover, and Ludmila leaned forward. An appetizing aroma was released into the room, but the food that lay arranged within was unfamiliar. There was something resembling a sandwich, while the rest of the plate was filled with golden strips. Bubbles rose out of the dark drink in the clear glass beside the plate. That it all seemed to maintain its neat placement was a mystery – especially considering the maid had jumped down from over two storeys into the courtyard.

 

“The sandwich is called a ‘hamburger’,” Yuri Alpha gestured with her hand as she described the meal, “I believe that potatoes are used in Imperial cuisine – those golden strips are called ‘fries’. The beverage is a sweet, fizzy drink called ‘cola’.”

 

Ludmila searched the tray for utensils, but there appeared to be none available to sample the exotic foods enticing her.

 

“This meal is usually eaten with one’s bare hands.” Yuri Alpha informed her.

 

Ludmila cast a look that begged askance at the maid, then she looked back to the meal, hesitantly fishing out one of the strips from the platter. While she had heard of potatoes before, she had never had the opportunity to try them.

 

The starchy food seemed to have been cut and fried in oil, then lightly salted. They had the same rough texture as arrowroot tubers from Warden’s Vale, but were decidedly less sweet and crispy. The method of preparation made them quite tasty, however – she wondered if she could do the same thing with the produce from her barony…though oil for frying was not a commonly available commodity in the highlands.

 

She reached out to bring the glass to her lips, then pulled her head back as the fumes from the drink burned the inside of her nose. After seeing no reaction from the two others, she gingerly took a sip. The sweet drink scoured her throat as she swallowed; she thought it was something that was definitely an acquired taste. The sandwich was a bit more regular – someone had taken minced meat of some sort and grilled it; there was a mixture of savoury sauces in the sandwich that complemented the smokey flavour of the meat. There were also both fresh and pickled vegetables inside, similar to ones she had tasted before. Having not eaten for most of the day, her ravenous appetite had her take all of five minutes to complete the meal while Lady Shalltear and Yuri Alpha looked on.

 

“I trust that you enjoyed the meal, Baroness?” Yuri Alpha asked as she retrieved the tray.

 

“It was very satisfying, thank you,” Ludmila replied. “Especially these fried potatoes…I think something similar could be done with produce from my demesne.”

 

She struggled not to burp as Yuri Alpha looked at her expectantly.

 

“You didn’t…feel anything?” Yuri Alpha said, “The sensation of becoming stronger, or perhaps more robust?”

 

“What do you mean?” Ludmila asked.

 

“The meal should have several beneficial effects upon consumption,” she explained, “though admittedly, Lady Aura does not particularly care about the effects, only the flavour.”

 

Ludmila shook her head, then eyed the half-emptied glass on the table. Did she have to finish the whole meal, including the drink? She had never eaten a meal that provided benefits immediately after consumption. The Sorcerous Kingdom surely had a variety of wondrous things she had never heard of before.

 

“That is quite curious,” the maid said. “I believe the other chefs will find this information of great interest.”

 

Yuri Alpha turned her attention to Lady Shalltear.

 

“If I may ask, Lady Shalltear,” she asked, “how were your scones?”

 

“One was the same, as usual,” Lady Shalltear replied. “The other tasted a bit strange…you should know as well as I that I won’t gain anything from eating them, though.”

 

“We can never be too certain here,” Yuri Alpha said, “and the chefs are being quite thorough in their investigations. There are still many recipes and local ingredients left to cover – any one of them could turn up with something unexpected.”

 

With a slight bow, Yuri Alpha left with the dinner tray, disappearing into the corridor.

 

Her hunger sated, Ludmila leaned back slightly into the sofa, looking across the table at Lady Shalltear, who had long since finished her scones.

 

“So…are you refreshed and ready to work now?” Lady Shalltear said, “There is much to be done ahead of us.”

 

She seemed eager to begin yet, when Ludmila looked around them, there were only crumbs from Lady Shalltear’s snack on her side of the table.

 

“I am still unsure what exactly you have in mind when you say that, my lady,” Ludmila said. “I have some experience in helping to manage my father’s demesne, but I do not know what His Majesty expects of me in my position as a minor noble.”

 

“Well, the discussion didn’t say anything in particular of what they wanted from you, just that you could provide assistance in getting things going again. Did your former liege always tell you what needed to be done?”

 

Now that she mentioned it, Ludmila realized that she may have overestimated the scope of what had been said earlier. The nobles of Re-Estize were by and large autonomous rulers within their own fiefs – only occasionally collaborating with others to tackle their common interests. Similarly, it was rare that they would be called to assist in their liege’s matters; only those exceptional enough to qualify as ministers and proxies were appointed to such important positions. Ludmila had only started to help manage her own family’s territory when she was twelve – mostly in limited capacity until recently – so what was required of her probably had to do with something within her limited experience.

 

“If it is something that has to do with my own demesne,” Ludmila thought it a good time to disclose her own situation, “then I will need to attend to several pressing issues that can only be addressed in E-Rantel. My territory is vacated, so I need to find new migrants that can survive life on the border. Then, based on the numbers that can be convinced to immigrate, I will need to purchase tools, parts and various necessities for living on the frontier. Momon sent my village’s goods…somewhere; I must track him down somehow and find out where they went. Depending on the prices I receive for those goods and how many I need to provide for, I might need a subsidy if there is a shortfall…”

 

Across from her, the Vampire’s bright, crimson eyes seemed to have gone dull. It reminded her of the times when she would speak to her family on these matters – as comprehension decreased, so did their attention span. It usually took her until she got to the strings of figures in her reports to achieve the same effect with her father and brothers, though.

 

Yuri Alpha cleared her throat to the side. While Ludmila spoke, she had been cleaning the table, taking away the remains of the meal and replacing the tablecloth. A tea set was laid out before them on the table, and the maid spoke as she poured out cups of fragrant red tea for them.

 

“I believe you will find the methods to apply for everything you need in the forms and reference materials that have been prepared for the local administration by Lady Albedo,” the maid said.

 

After placing an expensive-looking teacup with floral designs traced over it before Ludmila, Yuri Alpha produced a stack of books and folders from somewhere. As with Lady Shalltear’s parasol, they were seemingly taken out of thin air – Ludmila wondered if it was a magic item or spell common to the Sorcerous Kingdom. The maid gently placed the collection of items on the table but, even so, Ludmila could hear a light thump as the mass was released.

 

Lady Shalltear eyed the pile with the same look that a person might have given to something distasteful.

 

“I thought Albedo didn’t want anything to do with us,” she said.

 

“You should know as well as I that Lady Albedo has prepared extensively for this, Lady Shalltear,” Yuri Alpha replied. “These materials are made readily available to any who would take up related matters in the civil office anyways, so I thought it prudent to save time by picking them up in advance.”

 

As Yuri Alpha finished arranging the items on the table, Lady Shalltear shifted over on her seat. The maid rose to stand beside the sofa, and the Vampire patted the cushions in the space she had made for her, smiling up hopefully. Yuri Alpha pointedly turned her head away in refusal, choosing to remain standing to the side.

 

The brief exchange left Ludmila wondering what the relationship between them was. Even a maid in the service of royalty would be hard-pressed to evade the suggestions of a high noble – much less outright refuse them – as their reception could be perceived as a reflection of their master’s disposition towards said noble. The resulting interpretation of this behaviour could cause no end to the troubles between a host and their guest, and so those in noble employ would constantly need to be aware of the will of their master and perform in a manner appropriate to the expression of their many associations.

 

Though Lady Shalltear had a look of disappointment on her face, it seemed that she had treated the refusal as nothing more than a part of their regular interactions. The way in which Yuri Alpha pressed Lady Shalltear when she discovered the two in the kitchen was also at odds with how a maid would normally act towards a member of the Royal Court. Some might have construed His Majesty's disapproval or even ill-will in Yuri Alpha’s actions towards her.

 

Perhaps the elegant maid held some other position even as she served as part of the royal household. It was not uncommon for unmarried noble scions to enter in such service that suited their station and, going by the dignified atmosphere that always seemed to follow her, Ludmila would not be surprised if the maid was in reality a princess from some other part of the Sorcerous Kingdom. As she studied her face, Yuri Alpha betrayed no indication that could be seen as evidence of her speculations being correct – she simply looked back at Ludmila expectantly, patiently waiting for her to examine the various items that had been placed on the table.

 

Ludmila reached out to take the first folder from the stack in front of her. Within, she discovered what appeared to be forms, drafted in impeccable, uniform script. As she leafed through dozens of them, they all appeared to adhere to the same stringent standard. The clean lines and consistent handwriting over so many documents made the whole feel like an artform in itself – she had never seen the like in her life.

 

They were written to be clearly understandable, though she occasionally came across terms that were entirely foreign to her. Each form was made to assist in requesting articles that were needed in the various industries of the duchy, from the smiths, tailors and processing facilities in the city, to rural activities like farming, mining and logging. There were even those for warehouses, restaurants and various commercial services that were usually left on their own to sort themselves out.

 

“Amazing,” Ludmila remarked as she continued to flip through the documents. “Were these all drafted by a single person?”

 

“The Guardian Overseer created the templates for these, yes,” Yuri Alpha said. “Since then, the work to create copies of them has been handed to administrative assistants.”

 

Yuri Alpha leaned over from where she was standing, selecting a booklet among the items on the table and offering it to her.

 

“If there’s anything you don’t understand,” she said, “this is a glossary for terms that may not be familiar to the people of this region.”

 

Ludmila placed the booklet on her lap and reached for the next folder. The files within appeared to be for calculating and reporting taxes. The last folder contained requests for military assistance. Her eyes widened as she skimmed over the list and encountered Death Knight, Elder Lich and Soul Eater. Recalling that Bohdan had speculated that the legendary magic caster Fluder Paradyne may have become an Elder Lich, she wondered if all of the assets on the various forms were similar. Would all of the Sorcerous Kingdom’s nobles be allowed to field armies filled with creatures of legend? One could easily carve out their own nation with such overwhelming military might. Raising the folder with her left hand, she posed a question.

 

“These seem to state that we can request extended deployment of the Sorcerous Kingdom’s military forces…but there must be limitations?” Ludmila asked.

 

Yuri Alpha adjusted her spectacle frames, putting on a stern look.

 

“Requests for these deployments must be justifiable,” she said, “and for security measures only. Use of His Majesty’s forces in a belligerent manner on an international scale is prohibited by his servants. They are also issued with contingency orders for various events and outcomes, so understand that any attempt to wage war against friendly territories with them will not work and may result in fines or other disciplinary measures if warranted.”

 

“…of course,” Ludmila said. “I was just making sure that there were measures in place against abuse…I was not planning on conquering the Slane Theocracy any time soon.”

 

Lady Shalltear looked up with interest while Yuri Alpha furrowed her brow.

 

“It was a joke,” Ludmila replied hurriedly – perhaps being too serious led to her own brand of humor being taken seriously as well.

 

She shifted uncomfortably in the silence that followed, looking to what was left of the pile on the table. There were four large books – it would not be incorrect to call them tomes – and lifting one felt akin to picking up a block of heavy wood. Placing them side by side, she read the titles on their respective covers: Agriculture, Forestry \& Extraction, Refining \& Manufacture, Commerce \& Hospitality. Reaching out with both hands, she pulled the book labeled Agriculture onto her lap.

 

Within, the pages had been divided into clear halves. One side had been partially filled, listing various agricultural products – both plant and animal as well as intermediate goods related to the industry. Each had its own section in the column, listing supplementary products, such as fertilizer, feed and tools. It came with recommendations for many, but as she leafed through the pages, Ludmila discovered that there were far more blank spaces in each section.

 

The other half of each page was a template meant to be filled in with results: crop and herd yields, as well as space for feedback on the information provided and special concerns. Ludmila already had a fairly clear idea as to what was being asked, but she reached over to lay open the three books on the table to confirm her thoughts. Like the one on her lap, they all displayed a similar format.

 

Each was a sort of makeshift almanac, but there was a lack of information to provide proper forecasts and recommendations. The Sorcerous Kingdom had retained the laws that governed the nation, but the civilian administration had undergone changes to the point where the whole would not be recognizable to what had come before. The new administration needed a bare minimum of functional industries in order to test its new methods and enact policy, but the apparatus had essentially been jammed with the sudden annexation of the duchy and the new realities that came with it.

 

“Do you understand what needs to be done?” Lady Shalltear asked after Ludmila looked back up at her.

 

“I do, my lady.” Ludmila said. “Well, believe I understand what is being asked by these, and I know what needs to be done to achieve what is being asked.”

 

Lady Shalltear and Yuri Alpha had been waiting patiently while Ludmila perused the contents of what had been set before her, and they brightened visibly upon hearing her words. Ludmila had no illusions that remedying the entire situation would be as simple, though.

 

“In order to return the duchy to normal,” she continued, “the people need to understand what the new normal is. With stability and certainty comes confidence; only then will the population come fully back to life. It is something that will take time, but someone has to start somewhere…”

 

As Ludmila leafed through the incomplete almanac on her lap, a sudden thought gripped her.

 

“Say, how is the city doing for food and supplies?” She asked.

 

“When this city was annexed,” Lady Shalltear responded, “the provisions that the Royal Army of Re-Estize had stored in the warehouse were abandoned, so they were seized by His Majesty’s forces.”

 

“How large was the levy this year?”

 

“One quarter million, roughly.”

 

Ludmila did a quick calculation in her head. While rural territories might be able to forage or glean food from their surrounding fields and forests, the ability for the uncultivated lands to support the inland population would quickly diminish and they would still need to be supplemented with food until seasonal activities returned to normal. The city had no such option, relying on imports entirely. The needs of an army and the needs of the citizenry were vastly different, but food and fuel were still the same.

 

“One year,” Ludmila frowned.

 

Lady Shalltear and Yuri Alpha looked at her curiously.

 

“One year?” Lady Shalltear frowned back.

 

“The annual skirmish with the Empire usually lasts four or five weeks, not including the time to organize and station the levy,” Ludmila explained. “The Kingdom brings enough provisions to E-Rantel for roughly six months. This is enough to feed the city and army long enough for emergency relief to be mustered and arrive from the Kingdom in the event of a siege. With the city in the state that it is in, various tools and parts associated with city life will mostly not wear down since they aren’t in use, but the people still need to eat and stay warm. The excess food from the harvest in the inner territories would have probably gone towards this stockpile, so the duchy has a little over one year of food available. Even in the best case scenario, a late planting season will mean that the territories won’t have the same crops that they usually do. We will need to restore operations quickly to avoid this, or at least produce enough so that trade can make up for our shortfalls. If we do not, the duchy will starve next spring.”