\chapter{Ludmila Zahradnik}

Ludmila stirred to the sound of work being done downstairs. The drapes of her solar had been drawn tightly shut and the door to the hallway was closed, but the bustle of the maids on the ground floor preparing for the day still carried through from the open courtyard of the manor. She stretched herself under her covers and tried to rub the sleep out of her eyes.

 

It had been well past midnight when Lady Shalltear and Yuri Alpha left together. Upon hearing that Ludmila had an idea of what the various documents were asking for and what needed to be done, her new liege had wanted to start immediately. Yuri Alpha, however, reminded her that Humans tired out and it would be best to resume after a period of rest, so Lady Shalltear had hesitantly agreed to pick Ludmila up from the guest house in the morning.

 

She slipped out of bed and padded over to the window, parting the drapes slightly to look outside. Though the rains had stopped before she had retired for the night, the skies remained overcast and a grey pall was cast over the district. She was accustomed to rising after daybreak, but it was still dark enough that the streetlamps had been left on. Looking down to the front of the building, she saw the two Death Knights standing guard at the street entrance.

 

There was a light tapping at the door.

 

“Yes?”

 

“Baroness Zahradnik,” Aemilia’s voice sounded through the door, “you requested a morning call an hour after dawn.”

 

“I’m up," Ludmila replied. "Thank you, Luzi.”

 

Ludmila stepped back from the window, letting the curtains fall back down again as the maid opened the door. The courtyard was still being artificially lit in the morning gloom; the air carried with it the smells of woodsmoke and of breakfast being prepared. Aemilia closed the door behind her, then turned to curtsey.

 

“Good morning, Lady Zahradni–oh my, it’s pitch black in here!”

 

Ludmila watched as the maid groped about blindly – it seemed that yet another of the qualities of her Talent that Lady Shalltear had described the previous night was true. Humans could not normally see in the dark; she wondered how she could have thought otherwise for so long without realizing it. Before Aemilia could topple any of the furniture in the solar, Ludmila drew open the curtain again to dimly light the interior. The maid immediately straightened, walking about cautiously in the weak illumination.

 

“Oh, you should let me draw open the rest of the windows, my lady,” she said. “If I recall correctly, there was an appointment you needed to get ready for soon?”

 

“Yes,” Ludmila replied, “they said that one of the fellows posted outside the door would deliver word to them once I knew when I'd be ready. Is everyone else up? I should have one of the other maids let them know.”

 

“Terah chased the other two out of bed a couple of hours ago...um, I don’t think any of us will be able to approach the guards outside, my lady. I’m sorry.”

 

“That’s fine for now. I’ll inform them before breakfast.”

 

Ludmila sat down in front of the dresser mirror and looked around for her comb. The maids had unpacked her things the previous evening, but her personal belongings seemed rather meagre in comparison to the luxurious counter they were laid upon. Before she could reach out to pick it up, Aemilia swooped in and snatched it from the counter.

 

“Please let us take care of you, my lady,” her voice quavered a bit as she started to work on Ludmila’s appearance.

 

Aemilia appeared somewhat slow when it came to herself, but her maid was astonishingly quick when it came to her mistress. Resigning herself to Aemilia’s attentions, she reached out to take one of the files left behind by Yuri Alpha. Before going to bed, Ludmila had sorted out the forms that she thought would be relevant to Warden’s Vale. Though she had referred many times to the reference booklet and the incomplete almanacs that had been included, there were several things that still eluded her comprehension.

 

The process by which everything was filled out was relatively straightforward. One needed to identify their fief’s products, cross reference them with the provided almanacs and fill out the relevant forms. Based on the area of the land being utilized and the projected yield, an applicant would then simply tabulate their needs and write them down. At least it would have been simple, if the references were fully completed. Of all the produce listed in the agricultural almanac, only a handful of the more common crops had been filled out completely – namely several types of grain and potatoes.

 

Warden’s Vale had several old terraces cut into the lower slopes of the valley near to the village – remnants of a time when the barony was still in a position to develop its lands. The hamlet constructed to house field workers had long since fallen into disrepair, and only the nearest portion was left in use. After re-clearing all of the old and fallow fields, they would have roughly four thousand acres to work with. She had referenced the material for Oats, which did well in the cool, moist weather of the highland valley. It was a straightforward calculation but, at this point, several questions arose.

 

The numbers did not make much sense to her. The final tabulation had resulted in eighty light units of labour and four heavy units of labour. But no matter how she could frame these numbers, there was no way eighty tenant Farmers and four teams of draft horses or oxen could work such a large amount of land. A team of draft horses with a wide plough could perhaps cover seven acres in a work day, and four teams would take around five months to till four thousand acres after weather conditions were accounted for. There was also the matter of keeping the land clear and harrowing the tillage…Farmers in the lowlands might have been able to accomplish this with their mild winter climate, but the highland soil would become cold and unworkable in those months.

 

Similarly, she could not picture eighty tenant Farmers being sufficient to maintain and harvest the entire area. At the end of each growing season, the harvest would not be fast enough with what she saw allotted. Perhaps the Sorcerous Kingdom employed magical tools to expedite farm work, but in none of the nations surrounding Re-Estize was this practiced. She would have to take up her concerns with the civil office – hopefully, they would be able to provide clarification.

 

Her difficulties grasping what methods were being employed made the other parts even harder. The majority of the products of Warden’s Vale were harvested from the marshy flats that covered the floodplain of the valley. Rather than being farmed, it would be more accurate to say that they were foraged as there was no work put into planting. The villagers only needed the knowledge and expertise, which was a part of a Ranger's training, to harvest the various plants that grew in the valley throughout the seasons. Until she knew what the realm was providing with these application forms, she could not rightly estimate what she needed to perform these tasks.

 

There were several other documents involving forestry, which met with the same problems. While the application for logging was fairly straightforward, foraging edible products, herbs for medicines and several luxuries such as spices, pigments and plants used for cosmetics had no such detail in the Almanac. At the end of it all, she was dismayed to find that only one third of the documents had been filled out sufficiently, while the rest simply had little to no material to cross reference. The entire system had the sense of being developed for some other place, and they were now attempting to implement it throughout the duchy. Even the terminology required a glossary for an applicant from Re-Estize to interpret.

 

“Your dress is ready, my lady,” Aemilia said quietly behind her.

 

Ludmila turned her head towards the sound of Aemilia’s voice. Her outfit from the previous evening had been cleaned up, ironed out and placed on a mannequin stand. The amount of care that the dress had been given by the maid made Ludmila feel slightly guilty for keeping it packed up at the bottom of her trunk for months at a time.

 

“Shouldn’t I have breakfast before putting it on?” Ludmila asked, “I don’t want it collecting crumbs and smelling like bacon after all the work you did.”

 

Aemilia made a face, then walked over to check through the tall chest of drawers where her clothing had been sorted into. It didn’t take long before she turned back – everything she had brought for herself shouldn’t have even filled one of the drawers, after all.

 

“Aside from this dress,” she said, “I found your outfit for travelling in the country, plus some smallclothes…don’t tell me you plan on walking around in your chemise?”

 

“Yes?”

 

“No. Nonononono,” the maid’s voice went up in scale by two notches, “one does not simply walk around a manor like that. It is absolutely improper for a noblewoman. Allow me to bring breakfast up to you here, my lady.”

 

“I don’t want this room smelling like food,” Ludmila told her. “No one seemed to mind my walking around the manor in the barony, anyways.”

 

Aemilia frowned at her claim, turning to face her with a tentative expression.

 

“And just who did you share your manor with, precisely?” She asked.

 

“With...my family?” She replied, “My father and brothers, and any villagers that came in to take care of things – usually patrolmen in training with duties assigned to them. The priest’s acolyte, as well.”

 

Aemilia’s eyebrows shot up to match the tone of her voice.

 

“There are limits to being brave, my lady,” she said. “Perhaps it’s something that you’ve become accustomed to from your childhood, but an eligible young lady such as yourself should not be displaying herself to men in such a brazen manner…don’t tell me you were planning on speaking with the Death Knights like that?”

 

Ludmila suspected that answering her maid’s question would not end well, so she shrugged slightly. Her attempt at evasion didn’t work.

 

“Absolutely not!” Aemilia was aghast, “Standing out in the street like that…not to mention speaking to those fearful Undead guards in nothing but a scant piece of cloth!”

 

“I don’t think the Undead really care for that sort of thing…”

 

Undead aside, Ludmila thought the sensibilities between Aemilia and herself were a bit too far removed from one another. Rural villages were composed of homes which were essentially large, shared spaces, so privacy was not really anywhere on the list of luxuries with that sort of lifestyle. Her ‘manor’ in Warden’s Vale was no different in this regard.

 

“Who’s to say? I’m no expert on the Undead, my lady, but who’s to say that there aren’t some lascivious ones out there?” The maid shuddered after the words left her mouth, “Well thanks for that thought, my lady.”

 

Ludmila wanted to point out that it had been entirely Aemilia’s own doing, but seeing that her maid had stopped accosting her over her appearance and lapsed into the gossipy tone that she carried after they first met, she counted it as a win of sorts. Setting her papers aside, she stood back up and the maid helped her into her dress.

 

“I'll need an attendant for the outing,” Ludmila said as Aemilia was making some final touches on her appearance. “Will you accompany me?”

 

“Of course, my lady!” Aemilia immediately brightened at the prospect, but her expression grew shadowed just as quickly. “Where are we going? The rest of us were busy making the place livable; all I could tell from your meeting yesterday evening was it had something to do with this monstrous pile of paperwork you have here.”

 

She motioned to the stack of books and file folders filled with documents. Ludmila pressed her lips into a thin line: she didn’t like the idea that others would listen in on official business like that, but she wasn’t sure what measures she could take against it in the future.

 

“Yes,” she said. “I need to turn in these forms to the civil office and meet with an official to clarify some things. In addition, I’ll need to deliver my fief’s goods to the merchant warehouses to sell. Then, there are some purchases to make based on what I can secure from the administration with these requests.”

 

The young maid, having already agreed to accompany her, now looked a bit cornered. She obviously knew something that Ludmila did not.

 

“What’s wrong?” Ludmila asked, “You seemed excited to accompany me at first.”

 

“That’s…well,” Aemilia licked her lips apprehensively, “the Sorcerous Kingdom has replaced the missing administrative staff with Undead, my lady. I’m not confident that I can stride boldly into a building full of them like you can.”

 

“Well, you can wait outside if you don’t feel up to it,” Ludmila said. “I wanted you to help out with some personal articles, mainly. I need to replace old clothing that I’ve grown out of as well as find new pieces for daily use.”

 

Aemilia perked up a bit at her words. Ludmila had laid out the prospect considering her maid’s attitude earlier about the lack of a wardrobe, and it seemed to have some effect.

 

“Alright, I’ll take another look at your things and figure out what you need while you have breakfast,” the maid made some last-minute checks on the dress, then stepped away. “We’re done here, my lady. Please enjoy your meal.”