\chapter{Ludmila Zahradnik}

The Soul Eater brought them back to the manor, parking its wagon in the service road behind the building. On the way, Ludmila was relieved to see that all of the Undead had made it back to the avenue in front of the Civil Office. As the wagon rolled by, she issued orders for the new labourers to stand by near the villa gardens.

 

She still needed to drop by the Merchant Guild to drop off the forge’s invoice and look into the notices that were delivered while she was away. There was also the strange man that had come to visit the manor claiming to be a Farmer. She wanted to visit Baroness Corelyn as well to let her know that her village was waiting for her return, and Countess Jezne needed to know that the city needed her demesne’s exports of fuel. It was a moderately long list of things to do, but there would be a few hours left before the time she had agreed to meet with Lady Shalltear; just before the daily meeting of the Royal Court. Ludmila thought about paying Germaine Lenez a visit, but she still hadn’t come up with anything substantial to entice her with.

 

Following a quick lunch at the manor, Ludmila decided to stop by and visit Baroness Corelyn first. Clara came to answer much more quickly this time, opening the door with only a hint of hesitation.

 

“Ludmila?” Clara Corelyn said with a puzzled look on her face, “Didn’t you just leave for Warden’s Vale a few days ago?”

 

“I did,” she replied. “I came back for a day to see to some things, but I’ll be headed out again this evening. Lady Shalltear has graciously helped us get to and fro.”

 

“I see…” Clara’s tone suggested that she did not get what Ludmila meant at all, “well, we’ve just finished lunch – would you like to come in?”

 

“Thank you, Clara,” Ludmila replied, “but I still have to drop by Countess Jezne’s manor before heading out into the city. How is Baron Hamel doing?”

 

“He goes back and forth now,” Lady Corelyn said. “We still take meals together. He can’t cook at all, but at least I can cobble together something passable for us.”

 

“Did you see about getting new manor staff? You’re going to be too busy to do that sort of thing sooner or later.”

 

“I’ve tried,” a hint of exasperation entered Clara’s voice, “That Head Maid is nowhere to be found. We’ve been instructed to see her for our staffing needs, but she's never available – it’s almost as if she’s actively avoiding us.”

 

This was the second time today Ludmila had heard of the difficulties revolving around the ‘Head Maid in E-Rantel’. Why did this mysterious person even exist if she couldn’t even perform her duties?

 

“Have you checked with Miss Alpha?” Ludmila suggested, “When I first arrived, she was the one who introduced me to my current Household staff.”

 

“The Royal Maid?” Clara frowned, “That hardly seems appropriate. The Royal Household should be attending to His Majesty – they shouldn’t need to chase around the central district’s support staff.”

 

Clara was correct: there was absolutely no need for the Royal Household to be doing what Ludmila had suggested.

 

“Luzi,” Ludmila addressed her lady’s maid, “do you know anything about this ‘Head Maid’?”

 

“Yes, my lady,” Aemilia nodded. “Tsuareninya – The Head Maid in E-Rantel – was responsible for training the four of us, and she was training more staff besides. I admit it is an unheard of position: E-Rantel has had no such office before now. Development of household staff is usually part of a housekeeper or butler’s duties.”

 

What her maid said was in line with the common knowledge of the region. While temporary hired help might receive training from outsiders, professional households were usually trained internally as a matter of necessity. Ludmila had no complaints about the four maids who had joined her household, but it was still an unconventional arrangement.

 

“What is she like?” Ludmila asked.

 

“She is a bit older than I am, I think.” Aemilia answered after thinking for a moment, “But she is extremely strict. It was almost like she had it out for us even after we passed our evaluations. Miss Alpha seemed to be concerned about it as she monitored our progress. Tsuareninya seemed to be much softer on the Linum sisters, though…I cannot figure out why that is.”

 

From what Ludmila had experienced so far, the Sorcerous Kingdom was run by mostly austere individuals. She couldn’t imagine them allowing anyone to play favourites like that, but perhaps she only thought this because her exposure to their side was limited to Lady Shalltear, Yuri Alpha and the Undead servitors. She thought about sending the Linum sisters to go see the Head Maid, but it probably wouldn’t immediately help Baroness Corelyn.

 

“What about bringing some of the household staff from your territory?” Ludmila offered an alternative, “When I left the other day, it looked like things were returning back to normal in your village.”

 

“Is that so? That would be the best option, I suppose…” Clara’s voice trailed off for a moment, “I’ll have to see about hiring a carriage. I was already in the city when everything happened, and usual ones don’t appear to be available right now.”

 

“I hired a wagon from the city warehouse to get to the harbour,” Ludmila told her. “They’re free to use for the time being.”

 

“That would work. How did you call for one?”

 

“They can be requested from the civil office,” Ludmila replied. “I believe that any regular business you have directly with the Sorcerous Kingdom is being funneled through there.”

 

“So business as usual, then,” Clara nodded slowly. “Did you encounter any difficulties when you went there? Lord Rettenmeier and all of the people under him ran off, so there must be quite a few things to get used to for the new administrative staff.”

 

“There are many new systems in place – they’ve done away with most of the old procedures entirely. Fortunately, there are manuals provided with the new materials and the paperwork is easy to get used to. The clerks will do their best to answer any questions you have as well; the office never closes, so you can visit at your leisure.”

 

“It never closes?” Clara tilted her head, “How does that work? When do they sleep?”

 

“They don’t. The entire office is staffed by His Majesty’s servants.”

 

Lady Corelyn paled, her eyes widening.

 

“You just calmly walked in and filled out paperwork in front of a horde of Undead?”

 

“Well, I filled them out the night before after studying the new systems, but I did spend some time in the office in order to have things clarified. It was a bit before I came to visit the other day.”

 

“Ludmila!” Clara cried in a distraught voice, “You know I can’t handle that! I’m not some Frontier Noble that bathes in the blood of Demihumans every day.”

 

“I what?”

 

Clara half-closed her door to peek out from behind it.

 

“You know what I mean! I can barely leave this manor for fear of the Undead.”

 

Ludmila pushed open the door again.

 

“The Undead won’t be going away at any point in the foreseeable future,” she told her, “so you should get used to them already. Your tenants are already getting back to work – the rate you’re going at here, they’ll be drinking away all of your taxes.”

 

Lady Corelyn pouted, making a dissatisfied sound. Her Barony was one of the wealthiest territories in the duchy due to its place straddling a length of the fertile Katze River Valley. Ludmila’s sales from a few days ago were a pittance in comparison. Clara’s face brightened again as she thought of an idea.

 

“How about we go together then?” She asked, “Just this once. I’ll waive your harbour fees the next time you drop by.”

 

“If it’s fear of the Undead that’s keeping you from visiting the civil office,” Ludmila answered, “I’m afraid that it would only be a short term solution. The wagon you’ll be leasing is drawn by an Undead horse, and all of the assistance that they offer for security and labour is also Undead.”

 

The hopeful expression was dashed off of Clara’s face with Ludmila’s straightforward statement. Maybe she was being too blunt again.

 

“I’ve been employing the Undead for a few days now,” Ludmila made an attempt at reassuring her crestfallen friend, “both within the city and out in Warden’s Vale. There have been no outstanding issues so far and, the way I see it, their use will be commonplace eventually. I’m trying to help you get ahead since we’ve been good friends for as long as I can remember, and our families have always been allies. Your demesne is waiting for you, and Baron Vintner’s lands across the highway look to have been abandoned. If you move to demonstrate your capabilities, His Majesty may grant you Vintner’s title as well.”

 

The idea that she could effectively double the size of her holdings seemed to have some effect. Ludmila knew that Clara was not a greedy woman, but any capable noble would leap at the opportunity to further put their skills to use and expand their demesne. A minute passed before the calculating look passed from her face.

 

“Do you think that’s actually possible?” She asked.

 

“As I understand it,” Ludmila said, “the administration’s priority is getting things back to normal again. They would be ecstatic if a noble of your calibre returned to her duties and, considering how absurdly powerful the Sorcerous Kingdom is, they have no reason to fear you becoming any kind of threat. Just don’t become a repeat of Count Fassett.”

 

Ludmila’s expression of confidence was in no way an exaggeration: Clara Corelyn was nothing short of a genius and, when it came to noble matters, she was someone who knew no peer. Most of Ludmila’s extended knowledge concerning administration, diplomacy and economics stemmed from her long relationship with her childhood friend. Under the auspices of the Sorcerous Kingdom, Ludmila thought Clara’s future seemed limitless…that is, if she could only be prodded out of her fearfulness.

 

“You found out what happened to him?” Clara frowned at the mention of Count Fassett, “We were informed that he had been disposed of for overstepping his bounds, but they left it on that very vague and ominous note.”

 

Ludmila shared what she had learned about the late Count from Lady Shalltear.

 

“That greasy old fox finally went too far,” Clara’s satisfied sounding voice did not even show a hint of remorse for the man. “You know, after we heard that the Royal Army had been decisively defeated at Katze, we started making bets behind his back about whether the Bloody Emperor would purge him. It’s a good thing that the Sorcerous Kingdom could see him for what he was as well.”

 

Her friend’s posture had relaxed quite a bit and her tone had reverted to one that was more suited to casual discussion between themselves. The signs of nervousness and fear started to fade from her countenance.

 

“The man had a shameless ambition well beyond his worth as a noble – the only thing he seemed to be good at was keeping his deeds beyond Lord Rettenmeier’s notice. Did you know he kept approaching us to break off my engagement to your brother so he could marry me to his second son? What happened to House Völkchenheim was House Fassett’s doing as well: that entire family is rotten to the core. I can just picture him walking proudly into the Royal Court to make his ridiculous demands – what I would have paid to be there to watch him get tossed out.”

 

Clara’s gleeful tone was greatly at odds with her usual gentle demeanor. She must have despised the late Count quite a bit.

 

“Knowing this is one looming uncertainty dispelled from all of us,” she said. “If the King’s Justice is not just some thin veneer of order, and he truly intends rule of law for the realm, then we as his nobles will be able to carry out our obligations with confidence. Speaking of which, are our old contracts still valid? What happened between you and the Sorcerer King?”

 

“About that…” Ludmila said, “my title was transferred from His Majesty to Lady Shalltear. I’m no longer a direct vassal of the Sorcerer King.”

 

“So that’s why she was with you the other day,” Clara said thoughtfully. “It seems awfully kind of her to accompany a new vassal personally like that; I suppose she’s the one that helped you learn so quickly. Still, it’s very strange for this to occur – would you happen to know the reason why?”

 

“I didn’t even make it to the audience chamber,” Ludmila replied. “I discovered that she had become my liege after the fact, and I ended up chasing her out the door of the Royal Villa. Lady Shalltear didn’t seem to think the reason was something worth sharing with me either. Even in our short time together, I can say that the vassals that accompanied the Sorcerer King to E-Rantel have a very different way of seeing the world. Perhaps, as we adopt their ways, the reason will come to light on its own.”

 

“Perhaps,” Clara said, “but what about your contract?”

 

Ludmila frowned. The absence of the very thing that defined the relationship between liege and vassal was something that bothered her to no end. She had been rationalizing her lack of having one being due to the unknowns that accompanied the state of the new realm, but no matter how reasonable the justifications were, it still felt like there was a piece of herself missing.

 

“I don’t have one yet,” Ludmila replied. “Warden’s Vale is undergoing major changes and the old contract as a Frontier Noble of Re-Estize is most likely obsolete given the strength of His Majesty’s armies. It’s something I’ll have to draft from scratch, and it will probably require several passes before it is acceptable. You will probably have a much easier time writing up your own since your territory is already well established and the expectations should not change much. The one thing I can be almost certain of is that there will be no need for a levy.”

 

“No Levy?” Clara brightened, “I think it’s been mentioned before, but the last week or so has been one giant blur for me. It’s a relief to hear it from someone that’s been in close contact with a member of the Royal Court. Having the tenants pulled away to fulfil our obligations every year was quite annoying. I’ll ask again to be sure, once I find whoever I need to work with on this.”

 

“You’ll be taking a look at what the new administration has to offer, then?”

 

Clara nodded, though her expression still carried a trace of trepidation.

 

“I’ll head over to the Civil Office later and see what I can learn there,” she said. "I’ll take Baron Hamel with me as well – he stopped staying over, insisting that he needed to prove his bravery.”

 

“That’s cute.”

 

“Stubborn is more like it,” Clara huffed, “he’s probably just as scared as I am. I’ll drag him out there and make him eat his words.”