\chapter{Ludmila Zahradnik}

The following morning, Ludmila left early with her lady’s maid and brought one of her footmen to accompany them. Now familiar with procedures, she was able to make her requests at the civil office and be on her way within a half hour. There were a few differences from her original request, based on the news that she would actually be welcoming new tenants and from what she had learned on the field the previous day.

 

The three new farming teams were each composed of 80 Skeletons, 20 Bone Vultures and two pairs of Death Knights to operate the heavier equipment. Ludmila had originally intended to use the Bone Vultures and Undead Beasts for other work, but the flying Undead had proven surprisingly useful for efficiently transporting small loads to and from the fields, saving precious time as she worked to not fall even further behind in the planting season.

 

She would take the Undead Beasts and half of the Bone Vultures already working in the barony to test out what they had been originally intended for. Additionally, she had requested 40 more Skeletons and three Death Knights, unsure exactly how many each of her new woodcutters could manage. As an afterthought, she filled out a request for four Skeletons to be evaluated in the city manor while she was away – there was no official form for it, but between the Elder Liches at the counter and herself, they managed to draw up a miscellaneous request.

 

When the Undead arrived in front of the office for inspection, they filled the entire avenue with their neatly formed ranks. Rather than having them wait in the military district once again, Ludmila had them follow her wagon out into the city. She had given the Soul Eater operating the wagon instructions to drive to Mesmit’s Forge, and it had trotted off immediately – she wasn’t sure if it was the same Soul Eater as before or it simply knew what she was referring to somehow.

 

Needless to say, the passage of the wagon followed by a column of hundreds of Undead made quite the racket. Looking up, Ludmila saw people peeking out of the windows of their homes, staring wide-eyed as they passed below in the streets.

 

“Doesn’t it seem like we’re leading an army through the street, my lady?”

 

Ludmila did not think that there was much of a difference, especially considering that most came with their weapons.

 

“It basically is?” She replied, “This should become a common sight soon, I think – as long as the nobles have to move large numbers of Undead labourers from the city to their territories…hmm, this might actually become a problem. Nobles with large territories will disrupt city life with thousands of Undead labourers running around like this. I don’t know where they are keeping them all, but they’ll need to stop having the labourers present themselves in the central district every time someone’s request is approved.”

 

As they made their way through to the eastern quarter of the city, the scene continued repeating itself. She imagined all the people that would normally be using the streets: heading to and from their places of work, transporting goods and driving carts and wagons. It would definitely be a bad idea to march this many Undead around when the city returned to normal, blocking traffic and interfering with business.

 

She squeezed the Undead column into the alley leading to the back gate of Mesmit’s Forge to get them off of the main street. The Soul Eater parked the wagon near the storefront and the sound of chimes accompanied their entrance to the shop. The shopkeeper raised his head at the sound and stepped out from behind the counter, bobbing his head in greeting.

 

“Welcome, Baroness,” his eyes briefly went from Ludmila to her maid, then scanned for any additional visitors before returning to her. “How may we assist you today?”

 

“I have a need for more equipment,” she held out her order as she replied. “Do you still have inventory left for purchase?”

 

“Indeed we do, my lady,” The shopkeeper said as he received the sheet of paper, “We haven’t had anyone else come by since your visit a few days ago.”

 

He looked down at the order form, which used the template provided by the Merchant Guild. His eyebrows raised momentarily, then drew down as he tilted his head silently.

 

“Is there a problem with the order?” Ludmila said after the silence stretched on for several moments.

 

“No, my lady,” he looked back up to her and replied. “We are more than happy to fill your order – the problem lies…elsewhere.”

 

The shopkeeper opened the back door and gestured for them to follow as he voiced his thoughts.

 

“Your purchase will clear space in the warehouse so we can continue dealing with all these abandoned orders of spears – ah Forgemaster,” he interrupted his explanation when the muscular frame of Ysbrant Mesmit appeared to fill the corridor before them. “Baroness Zahradnik has come to make another purchase.”

 

The Forgemaster took the order form and made a gruff hpmh noise after glancing over it.

 

“Looks like you’re getting pretty ambitious here, Baroness,” he said as they continued on their way. “Too bad we can’t take advantage of most of the space you’ll be freeing up.”

 

“I was just explaining that, Forgemaster,” the shopkeeper said. “While we have thousands of weapons left to cast into tools, we’re going to run out of fuel soon.”

 

“Sounds about right,” Ysbrant affirmed. “Since charcoal is produced in the duchy, we usually don’t need to stock a whole lot. But shipments have stopped – just like this whole damn city has stopped – since the territory was annexed.”

 

“What about the city warehouses?” Ludmila suggested, “The central administration has been keeping the citizens supplied – I do not think they would mind selling you some of their stores, considering your purpose.”

 

“I asked when the lady that you were with the other day came around to distribute food and sundries to the neighborhood yesterday,” the Forgemaster replied. “Most of what the city has is firewood, which doesn’t burn hot enough for our work – we can’t exactly turn it to charcoal in the middle of the city either. The bit of coal and charcoal that they do have isn’t anywhere near enough to keep us running. If the territories producing charcoal don’t start shipping soon, the city forges’ll go cold within a week of restarting operations.”

 

“I see,” Ludmila recognized it as an appeal from the taciturn man. “I will visit Countess Jezne later today and ask if there is anything she can do.”

 

“That would definitely fix our problem, Baroness,” his voice tightened as he pulled the main warehouse door open, “at least this particular one. I didn’t know why you had me keep the storefront open back when you asked, but I feel pretty stupid for letting everything that's happened blind me to running my own damn business. It’s easy to take for granted when things are normal, but when even one piece is missing everything else grinds to a halt.”

 

“You are not alone in this, Forgemaster,” Ludmila said. “We are fortunate that His Majesty is possessed of both the grace and wisdom to provide for us in this time of transition.”

 

“I guess that’s true,” the Forgemaster admitted. “If this sort of thing happened in Re-Estize, who knows what would’ve happened. Maybe they’d have sent armed men into the streets to try and force us back to work.”

 

Ysbrant moved to open the gate to the yard, but stopped when he saw the hundreds of Undead standing in the alley.

 

“The hell?”

 

Ludmila hid her smile at the gruff man’s reaction.

 

“Worry not, Forgemaster,” she said from behind him, “they are not here to force you to do anything. I brought my labourers along this time to pick up their equipment. In hindsight, however, it is probably not such a good idea to block the road with them.”

 

“You’re using Undead to farm?” Ysbrant said dubiously, “Is that even safe?”

 

“I have just started testing them out in the fields, but their performance so far has been promising – enough that I am quadrupling the amount of labour to speed things along. They will come in to pick up what they have been ordered to retrieve, so your employees can continue working without interruption.”

 

Heeding Nonna’s ‘advice’ on her abilities, Ludmila was experimenting with how well these Undead could carry out her orders. Before they had arrived, she stood on the wagon bed and issued a chain of orders to the column of labourers following her. Both Lady Shalltear and Nonna had stated they could only follow simple instructions normally, so she wanted to test her ability to command relative to that basic outline. All there was to be seen now was how well the orders held.

 

The Forgemaster opened the gate, standing back as the Undead walked in single file to pick up their tools from the warehouse. The first step was working so far. The Skeletons came in, picked up their tools and walked back out of the gate. When the tools within easy reach ran out, they used each other as makeshift ladders to take equipment from higher shelves. This was not something she had specifically instructed them to do – the descriptions that she had heard about their capacity to follow instructions was very general, so she did not use any contingency orders to see how they would go about completing their tasks.

 

Watching the outbound line file out of the yard, Ludmila hoped that they would make it all the way to their next destination, which was back in the Central District. She spaced the Death Knights – who were intelligent enough to be able to follow all of her instructions – at even intervals between the Skeleton labourers. If the limit of her ability happened somewhere along the way, they were to round up the lost Undead and take command of their respective formations, marching them the rest of the way themselves.

 

“That easy, huh.”

 

The Forgemaster had his arms crossed over his chest, warily watching the orderly procession. His shopkeeper nervously stood beside him as the Undead passed by, shrinking behind his boss every time a Death Knight came close.

 

“I’ve had a bit of practice,” she replied.

 

Ludmila did not want to boast about her own ability, but what came out instead made it sound like anyone could learn how to command vast numbers of Undead servants with this degree of complexity – which was probably not the case. She tried to expand on what she had carelessly said.

 

“I think anyone that has experience directing large groups of people should be able to do this.”

 

“You’re saying I could do the same?” Ysbrant laughed, “I got eight journeymen working under me; does that mean I can boss eight of these Undead around?”

 

“My maid has been ordering around four of them all of yesterday,” she looked to Aemilia, “so I would say at least that many should be a reasonable expectation. You could use the Undead to assist you, and each of your journeymen should be able to do so as well.”

 

Ludmila looked across the yard to where Ysbrant’s employees were working to see if she could figure out an example for their use.

 

“The Skeletons can only perform straightforward tasks,” she said, “so pumping bellows, cleaning the workshop and helping to move things around would be among the things they should be able to do without much difficulty. What they can do beyond that would be subject to your own imagination and skills, as I have little knowledge about your trade. You would need to figure out how many you actually need to keep up with each person’s work. Maybe just one or two is enough, but it still means that you would go from having two or three of your employees working on a single project to each one of them working on their own.”

 

The Forgemaster scratched his chin with a thoughtful expression on his face. When Ludmila had initially gone through her own calculations, her imagination had run off with her entirely and nothing had worked out exactly as planned thus far. Ysbrant seemed like a much more level-headed person than she was, though.

 

“B-but that’s crazy!” The shopkeeper exclaimed. He appeared to have digested her words as well.

 

“Any fool can see that,” snapped Ysbrant. “You said they can do this for any simple labour?”

 

“As far as I have seen, yes,” Ludmila said. “There are stronger, more intelligent Undead like the Death Knights available, but I am not sure if it is worth having them just to handle heavy loads. Most of your labour seems to be tied up doing lighter work.”

 

“So what’s the downside?”

 

“As long as the demand for your work outpaces your capacity to provide it,” Ludmila said, “there should be no direct downside. Even the skeletal labourers on the lower end of the leasing schedule do not get tired, do not need food or sleep and follow instructions precisely as long as they are capable of carrying them out. They do not become excited or depressed, nor do they complain – well, I had one that complained, but it was because he thought he lacked work to do.”

 

“And the cost?”

 

“The ones I have for agriculture are rented out for a tenth of the harvest – if I have it right, it comes out to being less than what it costs to support a single tenant farmer for an equivalent amount of time. If they maintain that rate for other forms of labour, it would be far cheaper than having a skilled worker doing menial tasks.”

 

“I get that,” Ysbrant said as he watched the Undead who had emptied out most of the warehouse. “Everything will change if what you say pans out, am I right?”

 

“For better or worse,” Ludmila said in a subdued voice. “Each noble and business will have to decide how to incorporate this new source of cheap labour. Hopefully, they are not tempted to just put their Human labourers out into the street in favour of the Undead. If that happens, there will be a lot of people looking for work all at once. But, sooner or later E-Rantel will become many times more prosperous than it has ever been – especially if you only consider things purely in terms of productivity.”

 

The last pair of Death Knights walked out with their plough and the Forgemaster locked the warehouse and the gate up behind them. He led them back out to the storefront.

 

“Well, once I get my fuel issues fixed,” he said, “I guess I’ll see what this is all about.”

 

While they were waiting for the shopkeeper to settle the bill, the sound of the door chimes turned their heads. A large man stormed in – he was similar in disposition and frame as Ysbrant, so Ludmila assumed it was one of the other smiths in the quarter – and immediately started shouting when his eyes found him.

 

“Mesmit! You’re alive! I saw all those Undead come in and run off with your inventory: were you just robbed? I knew that those things would be up to no good eventually.”

 

“You coward!” Ysbrant shouted back angrily, “Did you really just wait ‘till they all left? Were you coming to see if I was alive, or did you come to dance on my corpse?”

 

As they shouted back and forth across the length of the store, Ludmila wanted to cover her ears – especially with the Forgemaster standing right beside her. Did they always yell at each other like this?

 

“Anyways you’re dead wrong, heh,” Ysbrant chuckled at his own words. “The Lady here just cleaned out my warehouse.”

 

“WHAT!”

 

The response rolled over them like a shockwave; Ludmila wondered if this man or Germaine Lenez was louder.

 

“Oh.”

 

Seeing Ludmila and her maid, the man at the door removed the cap from his head and did something that she thought might have been a bow. He turned back to his exchange with Ysbrant Mesmit.

 

“Why didn’t you say anything, you greedy ass!”

 

“Bullshit!” Ysbrant returned, “It’s your own damn fault for closing shop. Sell me your charcoal too since you’re not using it anyways.”

 

“Like hell I will!” The other smith turned to Ludmila, “Since this guy’s burned himself out, you should drop b–”

 

“Here’s the bill, Baroness,” Ysbrant pushed the stamped sheet into Ludmila’s hands and guided his clients out past the other smith. “You should get out of here before he tries to sell you some crap you don’t even need. Make sure you let Countess Jezne know we need her charcoal.”

 

The two women quickly found themselves out on the street, and the sounds of shouting continued to come through the door of the shop even as the Soul Eater rolled the wagon away.