\chapter{Ludmila Zahradnik}

After exchanging farewells and leaving Baroness Corelyn’s manor, Ludmila and her lady’s maid walked over to visit Countess Jezne, whose residence was a short distance away. Her butler promptly answered the door: a silver-haired man with a distinguished air who had served House Jezne for as long as she could remember. He led them into the building, guiding them to the courtyard where Vilette Jezne was seated in the shade of a Magnolia tree. Ludmila waited at the edge of the open space.

 

“Lady Zahradnik,” the butler announced in a clear and dignified voice, “Baroness of Warden’s Vale.”

 

“You just told me that a minute ago,” Countess Jezne snapped. “What is it?”

 

Ludmila nearly faltered as the words jabbed at her while she stepped into the courtyard, curtseying before the aged matron of House Jezne. She didn’t think she could ever harden her mental defences against the ornery old woman.

 

“Good afternoon, Lady Jezne,” she said. “I hope I find you well.”

 

“I’d be well if not for all these blasted books,” she tapped a gnarled finger on a familiar looking tome on the table set out before her seat. “Whoever wrote these damn things doesn’t care a lick for the elderly. I’ll have gone blind before I finish getting through all of them.”

 

Ludmila tilted her head to read the spine of one of the books: it was one of the almanacs provided by the administration.

 

“You have been to the civil office, my lady?” She asked.

 

“Oh yes. A line of those dried up Undead ogled me all the way to the front desk. I went to ask for a few things and ended up with a pile of this garbage instead,” Countess Jezne huffed. “‘Familiarize myself with the proper procedures’, they said. What tripe.”

 

Despite her verbal hostility towards the new system, it seemed that she was doing just that. Ludmila spotted a pile of forms neatly filled out on the stone bench beside the Countess.

 

“Did something happen, my lady?” Ludmila was curious what had driven her to action, “Why the sudden rush?”

 

“Momon happened,” the aged matron replied. “According to the couriers that started appearing yesterday, that troublemaker popped up in my territory and started wandering around; riling everyone up. Now a man appears every few hours from one or another of my vassals, begging for directions. Everything's a mess. E-Rantel is still asleep and my entire demesne is screaming for goods so they can keep working.”

 

It seemed that the Adamantite Adventurer was now starting to work the strange magic that she had seen take effect in Corelyn Village in other territories as well. Having her territory come back to life all at once had the Countess working at a frenzied pace, trying to deal with the supply bottleneck it had caused.

 

“Is this happening everywhere?” Ludmila asked.

 

“Is Momon more than one person?” Vilette Jezne returned in a snide tone.

 

Ask a silly question, get a silly answer.

 

Ludmila decided to deliver her message from Forgemaster Mesmit so the Countess could continue with her work uninterrupted.

 

“I stopped by to deliver a request from the eastern quarter, my lady,” Ludmila said politely. “Their stores of charcoal are running low.”

 

“Tell me something that I don’t know,” Countess Jezne rolled her eyes. “It’s obvious that if I don’t send fuel for over a month, they’ll run out, yes?”

 

“Well, I’m sure they will be relieved that you’re on top of things.”

 

“On top of things? Hah!”

 

Ludmila paid her respects once more before leaving the Countess to her duties.

 

They departed again, returning to the manor to ride the wagon out of the central district. They arrived at the Merchant Guild a couple of hours past noon.

 

This time, there was a young woman in the uniform of the Merchant Guild working at the reception counter. Her hand slammed down onto a stack of papers that had begun to flutter from the breath of wind that accompanied their opening the doors. She startled herself with the noise she had made and looked up. Rather than beautiful, her face would be more accurately described as handsome: framed in well-defined features that belied her timid reaction. She attempted to blow a loose curl of blonde hair falling over her face out of the way several times before finally giving up and brushing it away with her hand.

 

“Welcome to the Guild, Baroness Zahradnik.”

 

The woman bowed, and the curl fell over her face again.

 

“You know who I am?”

 

“Of course!” She said brightly, “I recognized you the moment you stepped into the building. Or maybe I felt it? Anyways, you’re exactly as the guildmaster described: even your clothing is the same. Oops.”

 

The clerk’s hand came up to cover her mouth. Ludmila placed the bill from Mesmit’s Forge on the counter along with her account book. As the woman looked down to scan the invoice, Ludmila looked around the office.

 

“The man I dealt with a few days ago was the guildmaster?”

 

“Oh yes, that was him,” the clerk replied as she turned to make her way into the office. “Never missed a day of work as far as I can remember. He’s up in the archives right now doing something. I’ll be right back.”

 

The way she spoke was reminiscent of the old man’s clipped tone. Ludmila fished up her stamp before the woman returned. The clerk placed her account book on the counter over several additional documents she had come back with.

 

“Your account balance has been updated, Baroness Zahradnik. These are the applicants that came forward and expressed an interest in your offer of tenancy: their addresses are also included. Is there anything else the Guild can assist you with, my lady?”

 

“I didn’t get your name…”

 

“Oh! Apologies, my lady,” the clerk dipped her head. “Edwina Hoffmann. Darian Hoffmann is my grandfather. The guildmaster, I mean.”

 

“I see. Well, give the guildmaster my regards, Edwina.”

 

“Yes of course, my lady,” the receptionist bowed at her desk again as Ludmila turned to leave. “Thank you for your patronage.”

 

Stepping down the stairs of the Merchant Guild, Ludmila looked over the still-empty main plaza of the city. Her eyes were eventually drawn to the cathedral on the opposite end. She had not visited the last time she was in the city, so she thought she should before she returned to Warden’s Vale. She wasn’t sure how the Undead Soul Eater would react to the cathedral – or the cathedral staff to the Undead – so she had it parked a distance away and walked the remainder of the way with Aemilia.

 

The building was old – it had stood for well over a century – but careful maintenance by the temple staff left it in good condition. Though it was massive, there were no ornate frescoes or fixtures adorning the exterior. Stained-glass windows alternated in the colours representing the Six Great Gods. The entrance to the cathedral was framed with two pillars supporting an overhang that shaded the open doors. A light scent of incense filled the air as they entered the vestibule, and a figure standing in the aisles further inside looked to the shadows silhouetted by the light from the entrance.

 

Ludmila immediately recognized the man walking up to them and curtsied as he approached.

 

“I hope the day finds you well, Bishop Austine,” she lowered her head respectfully, and Aemilia followed suit.

 

Ludmila felt a light touch on her head, and a familiar wave of warmth washed over her.

 

“Blessings of The Six be upon you, childe.”

 

The man’s gentle voice was just as warm as the magic that he had bestowed on her. He smiled just as warmly as she raised her head

 

“Ludmila Zahradnik,” he said. “You are much taller than you were last year.”

 

“Any taller and I will be scaring away prospective consorts, Your Excellency,” She replied sardonically.

 

“Consorts?” The Bishop’s face fell, “So your entire family…”

 

His voice trailed off and he performed a ritual gesture and prayer for the fallen.

 

“May the merciful Surshana grant them peace. I am so sorry for your loss, Ludmila.”

 

He leaned forward to embrace her. After a long moment, he pulled away, but his hands remained to grasp her shoulders lightly. He examined her teary eyes before speaking again.

 

“The times are troubling, but in such times we must hold to faith and do what we can for one another. Is there anything I can do to help you, Baroness?”

 

“I would ask the same,” Ludmila replied as she wiped her eyes with a handkerchief, “but there are several things that I must report to you first.”

 

Bishop Austine released his hold on her shoulders and motioned from them to follow him. He led them to his office, which was through a door in the hall running along the side of the building. When they were seated at his carefully organized desk, he leaned forward to hear what she had to say.

 

“When we received news of what had happened,” Ludmila said, “Priest Bohdan recommended that we evacuate to the Theocracy. It seemed prudent with what we could make out from the details.”

 

“A reasonable course of action,” he agreed with a slow nod, “especially considering what information must have made it out there. It is a short distance from your demesne to the border of the Theocracy. What was your decision?”

 

“I agreed with him,” she replied. “I waited as long as I thought was safe, just in case, but in the end I placed the villagers under Bohdan’s care…”

 

“...and you stayed behind.” Austine finished for her with a tight smile, “I may not have lived as long as the venerable Bohdan, but I know your family well. House Zahradnik has a valiant reputation – which has gotten quite a few members of your family into all sorts of trouble in generations past – I suppose it is inevitable that you would choose to face your challenges as well.”

 

“Do you think I made the right choice, Your Excellency?”

 

Bishop Austine leaned back from the desk and rose to his feet. He walked over to another part of the office, lined with large wooden bookshelves that Ludmila understood were filled with the registries of the families that were supplicants of the Temple. He returned with one such registry, which bore the crest of House Zahradnik, opening it in one hand and slowly flipping through the pages. The look on his face suggested that it was not his first time going over the contents: his expression was that of reminiscence, not study.

 

“You are the scion of a bloodline blessed with both strength and resilience, Ludmila,” the Bishop said. “While this strength may wax and wane over the generations, I should let you know that several men and women from your line have risen to greatness in the past.”

 

Ludmila tried to hide her confusion. As far as she knew, the only member of House Zahradnik who fit that description was its founder: Andrei Zahradnik, who was an Adamantite-ranked Adventurer. Bishop Austine did not miss her struggling with her expression.

 

“Most came from the time before Andrei Zahradnik settled in Re-Estize,” he explained. “A few came after: descendants of the family that married off or went to seek their own fortunes and started their own families elsewhere, just as he had. What is even more important, I believe, is how true the members of your family stay to your heritage. No matter how strong or weak, they all display the same stubborn and noble fortitude that has become a hallmark of your House.”

 

The Bishop closed the book and placed it on the desk. After hearing his words, Ludmila had become extremely curious about the contents of her family register, as what Austine shared with her suggested that the Theocracy knew more about her lineage than her own family had. He still had more to say, however.

 

“My superiors would probably say that your bloodline is too precious to lose in this realm that has fallen under the rule of an inhuman Sovereign. They may demand that I somehow safely get you to the Theocracy so that they can help it grow further and flourish under their auspices. But, personally, I believe that you are precisely where you need to be – for what is the purpose of cultivating the strength of humanity, if not to be employed in its hour of need?

 

It is exactly because E-Rantel is in this situation that those of your calibre have the opportunity to shine as an inspiration to the people. Momon might have stayed behind to do just this, but he is ultimately only an Adventurer. You, however, are a noble with all of the influence and authority that comes with your place in society, and it is the nobles that are in the position to do the most for the Humans of this realm. There will be no victory borne from strength here – nothing that raw might can achieve.

 

Humanity needs its Heroes: but the Heroes that we need here now are the ones that will ensure that our place in this land remains secure. So yes, I think your decision to stay was the right choice.”

 

The Bishop’s words were reassuring, yet they placed a burden on Ludmila’s shoulders that she did not feel qualified or capable of carrying. She was barely getting started with her own demesne, never mind turning into whatever he envisioned for her future.

 

“What about the Temple, then?” She asked, “The doors were open – does that mean that you plan on staying, even with the city being ruled by the Undead?”

 

“The presence or absence of the Undead is not what determines whether there is a need for the Temple. We serve humanity. As long as there are Humans here, so shall we be here for them. Our doors will always be open, even when our children go astray. Besides,” the corner of his mouth turned up in a half-smile, “Re-Estize has always been a secular nation; the Temples here have long learned to work without the privileges enjoyed by those in the Theocracy. While they have not directly approached us for any reason, it is said that the Sorcerous Kingdom has adopted the laws of Re-Estize, so the role that the Temples fill should mostly be unchanged. The ones that have forsaken Alah Alaf and Surshana may have a harder time coming to terms with the state of the realm but we, at least, do not ignorantly turn our faces from the aspects of the world that all Humans must face.”

 

Ludmila considered the Bishop’s words. His patient and nurturing disposition was what she was accustomed to, as the priests which served the realm were charged with the well-being and growth of the people. It was what she had based her initial optimism on how the faith of The Six might stand to gain from the transition of power to the Sorcerous Kingdom, and it seemed that the Bishop held something of the same outlook as well.

 

It stood in stark contrast to the vehement accusation spit out at her by the subdued Scripture member. She supposed the difference might lie in the roles that they played – a priest serving a city or village would, by necessity, approach things differently than a warrior whose purpose was far on the other end of the spectrum. As House Zahradnik was sworn not to reveal the existence of the Scriptures or their work, she could not even confer with the Bishop even if she suspected he may know of their movements as well.

 

“I apologize for my thoughtless words, Your Excellency,” Ludmila said. “I should have known better.”

 

“It is an understandable worry,” Austine leaned back into his seat. “I imagine many of the citizens would have the same fears.”

 

“About that…has there been any word about my people in the Theocracy?” Ludmila asked, “Since I know that their homes are safe now, I would like for them to return. I can fund the supplies that they need for the journey back, if that is an issue.”

 

“I have not heard anything from my superiors since their statement of neutrality months ago,” Bishop Austine answered. “I believe communication will return again when the fears have blown over and trade between nations resumes. I will include your query in my updates on the state of E-Rantel when they can be sent on their way.”

 

“I see,” Ludmila said. “In that case, I will have a lot of homes available in my demesne for the foreseeable future. If anyone expresses an interest in settling the frontier, please let me know and I will arrange for their immigration.”

 

“Of course, Baroness – how shall I send word?”

 

“The Crown has made the guest manors freely available to the Nobles in an effort to help us better acclimate to the changes following the annexation: you may leave a message with my staff there.”

 

“Very well,” Austine nodded. “Your kind offer of tenancy to the people is a reassuring thing. Thank you, Baroness.”