\chapter{Ludmila Zahradnik}

By late afternoon, the Undead labourers began to filter in to form up before her. As they neatly ordered themselves Ludmila rose from her grassy seat, brushing off her dress and scanning the field. It did not look very different from how it was before, save for a few large holes where boulders had been pulled out and the space filled in. She wondered how much debris she would end up with by the time all of the terraces were cleared.

 

“The plough teams can get started now,” she looked towards the two pairs of Death Knights. “Don’t go so fast that you’re throwing dirt everywhere – the equipment we have is nowhere near as sturdy as you are.”

 

She pointed to the incomplete formation of Skeletal labourers.

 

“Your group can follow after the plough teams: clear any additional debris that turns up.” She pointed to a set of Bone Vultures, “You, you, you and you, help deliver what they gather to the road with the rest of it. Everyone else, head across this windbreak and start clearing the next field.”

 

Though the old terraces were nowhere near as bad as the partially reforested territories that Ludmila had traveled through with Darkness, there was still much work to be done. The wild grasses that covered the fallow fields stood above her waist, while the bushes and groves of young trees dotting the landscape would prove to be time-consuming obstacles to clear away. At least what they did clear would yield fuel and materials that would come in handy for whenever she could find people to use them. The 80 skeletons that had followed her to the next field was the original number ordered for her 4000 acres of farmland, but the Bone Vultures and Undead Boars – which she had intended for a different set of tasks entirely – also proved to be helpful for clearing the land.

 

The Bone Vultures, especially, had shown extraordinary utility. Her original purpose was to use their ability to fly as an advantage when foraging in the marshes, but she did not consider applying them to places where it was easy to navigate over land until she set them to assist with clearing the fields. After their priorities with the fields were dealt with, she would put several other new ideas to the test.

 

“Bone Vultures, retrieve tools from Jeeves in the hamlet,” Ludmila projected her instructions over the Undead in the field with her ability. “We’ll need 30 sickles, 10 shovels, 10 axes and 10 picks. Skeletons can take one tool as they are delivered and work on your respective tasks.”

 

Much like the other field, all of the debris was to be set aside along the road; including the trees and shrubs that were chopped down and uprooted. The remaining Death Knight would help haul away what the Bone Vultures could not. She assumed that, like the previous field, this one was full of rocks as well so she tasked them with sweeping the field of stones after clearing away all of the growth.

 

“Issuing wide area commands does not tire you?” Nonna asked from beside her.

 

“If you mean the instructions that I just issued over the field,” Ludmila replied, “it doesn't feel any more strenuous than speaking loudly enough to be heard. I want to keep an eye on them for a bit to see if everything works out, though…there were multiple activities I had to convey to them that were associated with each tool and task. What are you trying to figure out?”

 

“Known active command skills consume mana, or require time to reuse,” the Elder Lich opened its tome and flipped through the pages. “Since we have the time, I would like to measure this ability.”

 

“Alright…what would you like me to do?”

 

Nonna pointed to the road beside them.

 

“Head away along the road,” she said, “and periodically use this ability to speak to me. Note any mana usage or similar resource consumption at each point.”

 

“…what does ‘mana usage’ feel like?”

 

“To Humans,” Nonna said, “it is reported to be a distinctly recognizable feeling. If they run low on mana, they will experience symptoms which mirror physical exhaustion. Overexertion may result in incapacitation along the same lines.”

 

“You want me to exhaust myself?”

 

“Simply being able to discern consumption of resources is sufficient. Its relation to your other command abilities is unknown; completely draining yourself may lead to inefficiencies amongst the labourers in the fields.”

 

Ludmila walked back out to the road and strode 300 paces east. She turned to face Nonna.

 

“Raise your hand if you can hear me.”

 

She spoke at a regular volume that she figured would not be heard by a regular person at their distance over the wind. Nonna raised her hand. Ludmila did not feel much different than before she had used her ability. She turned to walk 200 paces further and turned around again.

 

“Raise your hand if you can hear me,” she projected her words out to the Elder Lich.

 

Nonna raised her hand. Ludmila called out again, recalling something about abilities requiring time to reuse, but Nonna once again raised her hand in response before looking down to take down notes. She made her way halfway to the next windbreak, putting herself a kilometre away from where she had started.

 

“Do a backflip,” she said.

 

Nonna raised her hand.

 

Ludmila stalked off all the way to the windbreak at the other end of the field. At this distance, she was barely able to make out Nonna on the opposite end. It seemed silly to actually say anything with no hope of being heard, so she simply mouthed the words.

 

『 Wave at me if you can hear this.』

 

There was something this time. As she watched Nonna wave on the far side of the field, Ludmila felt an inkling of fatigue in her mind. Was it because she did not voice her words? She should have tried it normally first.

 

“Wave at me again.”

 

Nonna waved, and Ludmila felt an identical drain on her state of mind. Her breathing hadn’t changed, nor did her body feel fatigued...perhaps she had not used it enough to manifest the effects that the Elder Lich described. She walked back to rejoin Nonna at the windbreak.

 

“I felt a bit of a mental drain at the furthest point,” Ludmila reported, and Nonna’s pen scratched away as she took notes. “It was gone before I even made it a quarter of the way back, though.”

 

The pen stopped, and Nonna looked back up at her. Twin points of crimson light seemed to peer at her suspiciously.

 

“That should not be the case,” the Elder Lich said. “Are you certain of this?”

 

“Yes, it was like taking a stretch after working at my desk for hours. I was completely fine after that.”

 

The pen resumed its scrawling.

 

“Then there is something else at work,” Nonna said. “Mana does not recover as quickly as you described. The performance of the labourers showed no apparent change at the point you noted the difference in your mental state, either...do you have any other abilities?”

 

“There’s the one that I demonstrated before we met,” Ludmila replied. “I used it to rouse Luzi after she fainted in the civil office.”

 

“Did it produce similar effects on your mental state?”

 

“I don’t think so...but I was also too engrossed in learning how at the time, so I might not have noticed.”

 

Nonna continued writing until she snapped her tome shut after several minutes.

 

“This requires more data and further study,” she turned to stare at Ludmila.

 

“When I have the time,” Ludmila told Nonna, "I’ll try to accommodate whatever you come up with. Let’s head back to the hamlet for now.”

 

After watching the progress in the field, Ludmila decided that there were no problems with the instructions that she had issued to the labourers. Their orders would last well into the night by her estimation, so she returned to the barn with Nonna to retrieve her pack.

 

“Fly back ahead to the village with Jeeves,” she instructed her attaché. “Prepare a copy of the fief’s inventories so I can review them and see if there are any other things that I need to pick up from the city – make sure you inform Luzi about the change in schedule as well.”

 

Jeeves hopped back into his box, closing the lid, and Nonna picked it up and flew off towards the village. Ludmila made one last inspection of the empty settlement before calling down four Bone Vultures circling over the field; tasking them to guard the barn against opportunistic animals before she started the trek back to the village.

 

The evening shadows stretched across the valley by the time she made her way back across the old wooden bridge. Ludmila’s steps slowed as she reached the intersection coming off of the bridge – something was not quite right. Amongst the tall reeds and grasses that lined the flowing waters coursing around the base of the hill, she spotted a meandering trail of disturbed rushes: as if something had made their way through them.

 

Ludmila’s hand went to the dagger at her waist as she cautiously circled around to inspect the shore from the road above. The trail of slightly bent and displaced vegetation disappeared into the tall growths of marsh plants that ran under the bridge. Deciding it was too dangerous to investigate any further alone, she backed away from the edge of the road, turning back around to cut across the hillside to the village entrance.

 

The only sense that anyone was following her came a split second before a wiry arm wrapped around her abdomen and a calloused hand covered her mouth. Even as Ludmila reached up to pull the hand away, she was roughly yanked backwards down the slope. Despite her continuous struggling, whoever was pulling her away steadily continued to do so as she fruitlessly twisted about. She decided that escaping the hold was futile, and her hand went down to the dagger at her waist…but it wasn’t there. She started to kick back at her assailant’s legs in an effort to trip them up and loosen the hold. After several attempts, her feet finally caught something, yet he did not stumble. She tried one more time before her attacker finally spoke.

 

“Gods damn it girl,” a man’s voice came out in a harsh whisper. “I am not your enemy!”

 

Ludmila struggled for a few moments more until his words finally sunk in. His hand still sealed her mouth and the viselike hold was still restraining her movement, so all she could do was calm down to try to understand what was going on.

 

“Are you one of the villagers, girl?” He asked.

 

Ludmila tried to answer, but could only nod with his hand in the way. He felt her movement and continued speaking without releasing his hold.

 

“Then you are lucky I caught you before you got home. The Undead, they have taken this village.”

 

Ludmila froze, standing in shocked incredulity at his words.

 

“It is alright,” he breathed the words out near her ear, “I do not think they noticed you coming down from the fields. I was watching from up on the far slope, above the southern trail, when I saw you coming down to cross the bridge. I came down to stop you from walking into that deathtrap. The village is unnaturally quiet and there is a woman in black and white robes going from home to home with Undead servants. She is probably a Necromancer – there is a boat in the harbor with Undead in it as well, so she must be a minion of this Sorcerer King from the north. The village probably got knocked out with sleep spells and now she is going from door to door to – sorry, I will spare you the details.”

 

Ludmila had little room to imagine any details; Aemilia had gathered the skeletons that morning to help her clean the homes in the village. This would-be hero had probably arrived some time after she had departed with the labourers, given his grim tale.

 

“So…do you understand that, by making too much noise, you will bring the Undead up in the village down on our heads?”

 

Ludmila nodded again, and he slowly let her go.

 

She turned and backed away. The man had an unwashed smell, like he had traveled for days without a way to clean himself. The odor mingled with the green and earthy scents of the forest trails and clung to his plain dark traveller’s garb. Seeing that she wasn’t about to draw attention to them, he gave her a quick once-over and nodded.

 

“Sorry about the rough treatment, girl. We need to get you out of here – is there anyone else out in the fields still coming this way?”

 

“No,” Ludmila shook her head. “There are only Undead in the fields.”

 

“You are the only one left? Damn,” the man shook his head. “You must escape south down the river trail; there is only death in the north. I cannot come with you, but if you are lucky, you will reach the border of the Theocracy safely. They will take care of you there.”

 

He presented her steel dagger, holding it out by its long blade so she could grasp it by the hilt.

 

“Who are you?” Ludmila asked as she received her weapon, placing it back in its leather sheath at her waist.

 

“Me?” The man said as he motioned with his hand, “No one important. I just came in from the south.”

 

As the man’s hand continued to move, Ludmila caught sight of a ghostly green tattoo on his skin that was nearly hidden under a metal bracer. It was a unique symbol of the Six Great Gods she had been instructed to burn into her memory years ago. She then understood that the man was making a sign with his hand, and the tattoo was probably magically concealed: proof of his identity to the right people should he need it.

 

“A Scripture,” she said absently.

 

“What?” At Ludmila’s words, the man peered at her suspiciously, “How do you know this, girl? Only the family of the lord and the priest here should know that. Wait – I heard the old priest picked up an Acolyte, are you her?”

 

Warden’s Vale had a generally amicable relationship with the Theocracy, as a fief whose only practiced faith was that of the Six Great Gods. House Zahradnik similarly had a long relationship with the elite forces of their neighbor to the south, who occasionally assisted in controlling major Demihuman threats that drew too close to the Human realms. It had been a more frequent occurrence in generations long past – they rarely showed themselves in recent times. There were rumors of a war in the south that was occupying the Theocracy, which might have been why they had withdrawn their assistance along the southern border of Re-Estize. Regardless of the reason, it was one of the nails in the proverbial coffin that had collapsed the realms of the other Frontier Nobles.

 

As a child, Ludmila was instructed to cooperate with the Scriptures, as they looked out for Human interests and defended against the most dire of threats that faced them. The last time she saw them was when a party of men and women from the Theocracy was quietly allowed passage through the barony late last spring with this understanding, and a more whimsical part of herself fancied that they were heroes on some great quest on behalf of humanity.

 

The sound of light footsteps brushing through the grass on the hillside interrupted their conversation.

 

“Ah, there you are,” Jeeves walked towards them with a few sheets of paper in his hand. “I–”

 

The man looked away from her towards the sound of the approaching Skeleton. He reacted instantly, pulling a set of bolas from his belt and launched them in a quick and powerful motion towards his Undead target coming down the hill. The weapon caught itself on the Jeeves’ neck, winding around it until the weights on the end converged and shattered his skull. Jeeves tumbled into a heap of his remaining form, disintegrating into motes of light that scattered into the wind. The sheets of paper fluttered down onto the grass.

 

Ludmila quickly went over to where Jeeves had fallen – the only evidence that he once stood there was the imprint of his feet in the soil. She knelt to pick the papers up off of the grass: it was the inventory that she had instructed him to scribe for her back at the hamlet. Slowly rising, she looked to the sky, standing in place.

 

“What are you waiting for, girl?” The man called to her in a low voice, “They know we’re here, we need to leave now!”

 

She continued looking up into the sky, until she spotted what she was waiting for.

 

“Nonna.” She commanded; projecting her thoughts to the Elder Lich.

 

“「Hold Species」.”

 

Nonna’s invisibility fell as her spell was unleashed on the man waiting for Ludmila below. Without a chance to react he simply stood paralyzed, still beckoning for her. Ludmila turned around to glare at him angrily.

 

“How long does that last?” Ludmila asked the Elder Lich as she settled to the ground beside her.

 

“It is temporary,” Nonna answered. “Shall I incapacitate him?”

 

“Do it,” Ludmila said. “I still want some answers out of him, though, so leave him in a condition where he can still speak.”

 

Nonna examined the still-paralyzed man for a few seconds before casting her next spell.

 

“「Maximize Magic – Ray of Enfeeblement」.”

 

A coruscating ray shot out from the Elder Lich’s hand and struck the frozen figure. Ludmila could see no visible difference in his appearance.

 

“「Bestow Curse」.”

 

“「Exhaustion」.”

 

Nonna continued layering spells on her target. As alarming as they sounded, the man did not seem to suffer any visible injuries. Ludmila stepped forward to strip him of his armament. She found a mace and dagger on his belt along with several pouches lined with unmarked vials, in addition to a few other items whose use was unknown to her. She unstrapped a crossbow from under his cloak and took the quiver of bolts from his hip. There was a knife sticking out of his boot and she found several darts strapped to the undersides of his bracers.

 

The man’s paralysis wore off part way through being disarmed and Ludmila stepped away, sensing him stir. His knees wobbled before he flopped to the ground weakly.

 

“I suggest you restrict the man with conventional means,” Nonna offered. “He may still have a way to escape – an item; a potion or scroll concealed on his person.”

 

Ludmila did not have any rope or twine on hand, but she spotted the bolas on the ground nearby. She freed the sturdy cord from its weights with her dagger and came forward to bind the man’s hands. He saw her approach and rose to his hands and knees in an attempt to crawl away.

 

“Nonna.”

 

“「Dessicate」.”

 

There was a wheezing grunt and the man staggered and arched his back as the effects of the spell came over him. Ludmila watched as, this time, the man visibly changed – his skin dried and chapped; lips cracked and bled. His flesh seemed to shrink and shrivel like the moisture from his body was being wrung out of him. After the spell finished its work, she could hear his hoarse breathing, but he doggedly rose to his feet and limped off of the road towards the riverbank.

 

Ludmila sighed.

 

“「Wrack」.”

 

The man stopped to curl up into a ball, unable to restrain a high-pitched keen. His will broke not long after, however, and a horrific wail rose to fill the air, echoing off the cliffs on the far bank of the river. He rolled back and forth, alternating between sobbing, shouting and crying out in agony. Blisters rose from his hands and face, leaking pus and sticky ichor. Tears of blood leaked from his eyes, which were similarly painted a dark crimson.

 

“Wait, no!” Ludmila shouted in alarm over the sound of the man’s hoarse screams, “Don’t kill him!”

 

“The last spell does not actually do any physical damage,” Nonna replied casually. “It only inflicts suffering. Seeing it’s efficacy here, I shall recommend it for enforcement actions in the future amongst my peers.”

 

No physical damage? Ludmila eyed the man dubiously: his appearance certainly seemed to suggest that he had been horribly afflicted. If this was considered a harmless spell, she wasn’t sure that she wanted to know what a harmful one looked like.

 

“That’s definitely not a good idea, unless you get someone as stubborn as this guy,” Ludmila tried to dissuade the Elder Lich from promoting the use of the spell. “Actually no – even then, probably not. Something like this would definitely terrorize most of the citizens that witness it…how long is he going to be writhing around for?”

 

“A few minutes,” Nonna replied. “If he resumes his attempts to flee, I will recast the spell.”

 

Ludmila could not imagine that the man would have any fight left in him in the wake of his excruciating-looking experience. A motion out of the corner of her eye drew her attention: Aemilia was looking down from one of the village terraces, drawn by the heartrending cries of suffering coming from below. Before Ludmila walked back up the hill towards the village, she left instructions for her attaché.

 

“Let E-Rantel know we’ll be ready for transport in thirty minutes. Inform them of our additional passenger as well.”