\chapter{Ludmila Zahradnik}

Ludmila’s borrowed manor in the city was still the only one with Death Knights standing guard, though she supposed that the short time she had been away was too soon to expect any visible change. As they approached the gate to the manor, Aemilia spoke.

 

“A moment please, my lady,” she said, coming to a stop in front of one of the Death Knights. “I should go ahead and let the others know of your arrival.”

 

The maid looked up at the Death Knight expectantly, but when it made no movement, she let out her breath in a huff. She chose two of the spikes protruding from its armour to hang their baggage from and walked between them to the manor entrance, muttering to herself. After the door closed behind her, the Death Knight looked down at the bags hanging off of its armour.

 

“Footmen are supposed to help with baggage and other heavy articles,” Ludmila offered helpfully, “as well as open doors and valet guests. They are also expected to keep the property outside of the manor swept and clean, so you two may want to see to that before the maids come out to harass you about it.”

 

The Death Knight wordlessly took the bags into its hand. Several minutes passed before the door of the manor once again opened, and the three maids that had remained in E-Rantel lined up along the lane to the entrance while Aemilia once again took her place behind her. Ludmila stepped onto the lane and the row of maids curtsied.

 

“Welcome back, my lady,” they said in unison.

 

Terah rose to address her as she walked past them into the manor.

 

“We did not expect your return so soon, my lady,” her Housekeeper apologized. “I thought you should have just arrived in your demesne today.”

 

“You are not mistaken, Mrs. Ro’eh,” Ludmila replied. “Originally, I stated that it would take about this long. Our journey upriver was a full day faster than expected, and we were transported back to the city this evening through magical means. We shouldn’t be staying for more than a day – there are just some additional things that need to be done before we return to the barony.”

 

The manor was significantly cleaner than when she had left it, but the damage to the hall had still not been repaired. Everywhere else, the dust had been swept away and the floors and fixtures polished to a dull gleam. A trace of the scent purchased from LeNez lingered in the air.

 

“Will you be taking your evening meal here, my lady?” Terah asked before Ludmila ascended to her solar.

 

“Yes,” she replied, then paused her steps. “Has there been any response to the staff requests I left with you?”

 

“Surprisingly, there have. But no Cook yet. You’ll have to suffer my food for a bit longer, my lady.”

 

“I did not mean it in that way, Mrs. Ro’eh,” Ludmila smiled slightly. “I rather enjoy your meals.”

 

After the Death Knight dropped off the baggage in her solar, she bathed and changed into a fresh white chemise, covering herself with a dark green robe that Aemilia had picked out in Corelyn Village. The woolen fabric was sturdy and comfortable, and she had to agree that it was more practical to wear about the manor than just a smock or being fully dressed as she had thought of doing before. Her maid had even found a pair of matching slippers to use indoors.

 

Leaving her solar to pass the time before dinner on the main floor, Ludmila found the Linum sisters waiting for her at the bottom of the stairs.

 

“The Dining Room is ready to be used, my lady,” between the two, Lluluvien was the one to speak as usual. “Dinner is nearly ready.”

 

Ludmila had spent so little time actually living in the manor that she had forgotten there was a Dining Room. On the night that she had first looked around, the dusty room’s furniture had been draped with cloth and put away in a corner, so she had decided against using it. The sisters led her around the courtyard and she found that the room was now cleaned and well-lit. There was a long mahogany dining table lined with chairs carved with the flowing designs seen elsewhere in the manor. At the head of the table, a seat had been prepared; dishes and utensils laid out for her use.

 

She seated herself and continued looking over the lavish setting, feeling entirely out of place. The guest manors were meant to impress the hospitality of the city on visiting nobles and dignitaries, so she supposed that it shouldn’t have been a surprise to see such finery on display. The plates and bowls were fashioned out of jade porcelain and there were a half dozen silver utensils laid out on a pure white cloth. Two silver candle stands placed equidistant from one another on the dining table each held three lit beeswax candles. The candles themselves lent very little in terms of additional lighting, so it seemed wastefully extravagant to Ludmila, whose manor in Warden’s Vale used two old oil lamps and a small cookfire.

 

Aemilia appeared a short while later, replacing Wiluvien who had stayed in the dining room to attend to her. Wiluvien left the room and returned shortly after with her sister and Terah. The sisters each held a tray, one with her meal and the other with a tea set, and Terah led the small procession with a set of linen towel napkins draped over her arm. Ludmila watched as they laid out dinner on the table – it almost seemed a ceremony with how focused each of her maids looked as they worked. Her meal was a combination of the food that she had dropped off earlier in the week and the bread and meats that were used to prepare her meals while she traveled. The tubers were roasted, and a thin, spicy soup had been made from the watercress.

 

“You have my apologies if there is a lack of flavour,” Terah lowered her head as Ludmila sampled the meal. “There have been no merchants selling spices or condiments – well, no merchants at all, actually. Meals will be rather plain until they return.”

 

The meal seemed fine to her. Each ingredient had its own distinct taste and texture, so it wasn’t as if the food was bland. With the ingredients that had been included, it seemed a rather fancy variation on her regular meals rather than the substandard fare Terah suggested it might be. She worked through a quarter of it before slowing down to speak to her Housekeeper.

 

“You said there have been responses to the requests you put out?” Ludmila asked Terah after she washed down the portion of her meal with some sort of red tea.

 

“Yes, my lady,” the Housekeeper replied, “I have not been able to see the Head Maid in the city – she is strangely hard to meet with – for household staff, but we’ve received a small handful of replies for tenants.”

 

Ludmila thought that the Head Maid would be the easiest to get a hold of, as she was said to be training new maids in the central district. Perhaps it would have been easier to go through Yuri Alpha, who was the one to deliver her staff on the first evening that she had arrived in the city.

 

“The first was a…strange man that came personally to the manor to inquire about tenancy as a farmer,” Terah continued. “His odd appearance aside, I am not sure how a common farmer could bravely make their way through the gauntlet of Undead in the streets to the central district just to ask.”

 

“A strange man…with an odd appearance?”

 

“Yes, my lady,” Terah nodded. “He seemed less frightened than one would expect and more, hmm…excited? Maybe a bit too excited. I am not sure how to describe it, exactly. You may want to see him for yourself – maybe with one of the footmen, to be safe – he left his address with us.”

 

“I will pay him a visit when I am out in the city tomorrow,” Ludmila said. “Who else was there?”

 

“The Merchant Guild sent us a notice. Several woodcutters and most notably a smith – I believe you’ve placed a priority on finding one.”

 

“Really?” Ludmila’s ears perked up at her words, “That’s a pleasant surprise. Was there any mention as to what sort of smith, or why they came forward?”

 

“There were no details, my lady,” Terah shrugged. “It was a simple note delivered by a very frightened-looking courier from the Guild.”

 

“I see…was there anything else?”

 

“No, my lady. It has been otherwise uneventful here. We’re running out of things to do in the manor, though the hall still needs repairs whenever we can find the people for it.”

 

“How is the city, then?”

 

With the official business out of the way, Terah assumed a more relaxed posture and Ludmila resumed her meal.

 

“I’ve seen very little change from when you left, my lady,” she said. “For the past day or so we’ve been fairly busy cleaning up the manor and making it livable, but I haven’t noticed anyone in the streets from the windows and I have not been out of the manor. Well, there must be some people moving about, considering what we’ve received from the Merchant Guild. The Linum sisters have gotten brave enough to check the letterbox behind the Death Knights in the front, and I still don’t dare give those two footmen any sort of instructions.”

 

“Speaking of which,” Ludmila said as her Housekeeper’s words brought the topic to mind, “we’ve been experimenting with using Undead as labour out in the demesne. Even Luzi was able to employ a group of them to help with village upkeep.”

 

“Surely you jest, my lady.”

 

Terah started with a laugh but, after noticing Aemilia’s somewhat proud expression to the side, the smile fell off of her face.

 

“Wait, you’re serious?”

 

“I am,” Ludmila nodded. “Luzi has been quite successful at it, so we thought that we could reduce the amount of junior staff required for menial labour and simply have a handful of household staff directing the Undead. It would result in better accommodations for the staff that we do take on and cut down on manor upkeep.”

 

The Housekeeper’s gaze turned inwards with a grim expression. Whether she was considering the utility of the Undead or just the idea of sharing the same space as them, Ludmila was not sure.

 

“So all that would remain are the senior staff, chambermaids and the kitchen staff?” Terah asked.

 

“You are the Housekeeper, Mrs. Ro’eh,” Ludmila told her, “so I will leave how things are arranged in your hands. You will probably have to investigate their usefulness at various tasks before settling on what is appropriate. I am entirely uncertain how well Undead labour will handle kitchen duties; the Cook will need to determine this whenever we finally have one. Also, I suspect that attending to guests will mostly still rely on Human staff, so household duties may be a bit unconventional compared to how things would usually be.”

 

“If we’re able to reduce our staffing needs by three quarters,” Terah said carefully, “it certainly seems like it would make hiring a much more simple matter. If Luzi has already approved of their use, they should at least meet the standards required of junior staff for regular household labour. We would have to find those willing to work with the Undead on a permanent basis, though.”

 

“As you have mentioned, Mrs. Ro’eh, we will not need many more – I am also of the mind that we should only be hiring those who can work with the Undead, given the new realities of the realm.” Ludmila glanced at the Linum sisters, “If Wiluvien and Lluluvien fill positions as chambermaids, I’m not even sure if we need any more maids for the city. Between them, they can direct eight Undead labourers to handle menial chores all around the manor.”

 

“D-direct, my lady?” Lluluvien abruptly spoke after hearing Ludmila’s words, “You mean they won’t just work on their own?”

 

Terah shot a reprimanding glance at the Half-Elf maid for speaking out of turn, but Ludmila waved away her concerns.

 

“Skeletons, at least, need some sort of direction,” Ludmila answered. “Their actions are also dependent on the instructions of their handler so, ultimately, the results of their work will rely on your ability to convey your own expertise through them. Luzi has spent most of the day with her own group cleaning up the village, so she can explain much better than I could on how they can be applied to your duties.”

 

Following her words, the room was quiet until Ludmila finished her meal. Placing her utensils and napkin aside, she rose from the table.

 

“I will be working in my solar,” she said. “It will be another long day tomorrow, so I will not need anything further for tonight.”