\chapter{Ludmila Zahradnik}

Most of the morning had passed by the time the Soul Eater drove its wagon, bearing the noble and her lady’s maid, within viewing distance of Corelyn Village. Ludmila had planned on leaving the city much earlier, but she underestimated how much time it would take to sort out the household business that she decided to leave in Terah’s hands. New staff for the manor would need to be hired to see to daily domestic matters as times became busier and retainers that could see about the business of running the fief needed to be identified and recruited.

 

She had left the footmen at the guest manor with Terah and the Linum sisters to help with security, as unlikely as any incidents seemed within the city. The labour force that had been equipped and marched off overland to the Barony was likely more than adequate enough to serve as an impromptu village militia in the event that they did encounter trouble out on the frontier. While the maids were plainly not enthused about the prospect of the Undead hanging about on a prolonged basis, they did not appear as fearful as when she had first met them. She left her instructions, and she told them that if they needed any work done that would normally be handled by footmen, they should just ask the Death Knights who were available in front of the manor. The newly appointed Housekeeper already seemed overwhelmed by her new responsibilities, but Ludmila hoped that slipping in the suggestion would produce the desired results eventually.

 

After all her instructions for the staff of the city manor were settled, Ludmila made a short stop at Clara’s residence, paid the harbour fees that she owed to her, and then set off on the first leg of the trip home. Her work now would draw the scrutiny of the central administration, as they examined all aspects related to the industries and logistics of the realm. For this same reason, there was no Gate or Teleportation-assisted travel provided as there was before.

 

As the harbour village grew closer, she peered down the slope of the valley at the rows of buildings to see if she could spot any activity from its tenants. Much to her surprise, she immediately noticed figures moving around the houses; several more were on the dusty road that ran between the village and the highway, following the course of the river valley. As several turned their notice to the wagon which was steadily approaching from the city, Ludmila instructed the Soul Eater to stop where the rural road intersected with the southern highway, recalling the terrified girl that had run screaming from the Death Knights at the harbour.

 

“Why have we stopped, my lady?” Aemilia asked in confusion as the wagon slowed to a halt.

 

“We’ll be walking to the harbour from here,” Ludmila replied, pulling the bags out from behind the seat of the wagon, “I’m not sure how well those villagers would respond to having a Soul Eater trot into their midst.”

 

They had four bags between the two of them, with most of Ludmila’s personal purchases from Mesmit’s Forge bundled up together separately in a tarp. Aemilia had snatched up three of the bags before she could say anything, insisting that it was her job to carry their things, so Ludmila ended up shouldering only one bag over her round shield while holding the bundle of equipment in one arm.

 

As the sound of the wagon receded into the distance, Ludmila eyed her retainer as she shuffled under the weight of the luggage.

 

“Are you sure you’ll be alright?” She asked.

 

“I’ll be fine, my lady,” her maid quickly replied. “It is my duty as your Lady’s Maid, after all.”

 

As they made their way forward, the scraping of Aemilia’s steps drew Ludmila’s gaze to her maid’s feet. She was wearing shoes suited for the city, which peeked out from under the long skirts of her uniform: the attire as a whole was clearly not meant for rough country roads or muddy village lanes – she looked about to tumble in a tangle of bags and skirts at any point. Ludmila tried thinking of ways to diplomatically get her stubborn attendant to hand over at least one of the bags but, after over a minute of travel with the sound of her feet scraping heavily over the dry dirt road, she stopped to turn back to face her maid.

 

“Hand me one of those bags,” she told Aemilia as she laid her spear against a shoulder and held out her hand. “You’re going to ruin your uniform at this rate.”

 

Aemilia pouted stubbornly but, seeing her mistress’ firm expression, she finally relented. Her shoes continued to shuffle over the road lightly on occasion as they continued walking, but at least she did not look like she was about to fall over.

 

“We need to see about getting you some boots,” Ludmila said after a while as they approached the border of the village. “Those shoes won’t last long out on the border.”

 

“Will that be necessary, my lady?” Aemilia’s voice came from beside her as she picked up her pace, “I thought I’d be mostly working out of your manor.”

 

“You’ll still need to move around the village,” Ludmila replied. “The only properly paved roads in the duchy are the main highways, as well as the major thoroughfares in E-Rantel. Most of the land has roads like the one you’re walking on right now. Warden’s Vale sees a lot more rain than the lowlands, so the paths are often slick and muddy – wearing shoes meant for cobbled city streets will have you constantly falling and you’ll eventually injure yourself.”

 

They passed several labourers on their way out to the vineyards, who nodded to them as they crossed each other on the village road. Though there were fewer people than there should have been outdoors at this time of day, it was a stark difference from the empty surroundings that Ludmila had arrived at the day before. The smells of lunch being prepared wafted over the air as men and women worked near their homes: doing laundry, preparing tools and going back and forth from the shops at the centre of the settlement as they readied themselves for the season’s activities.

 

As they approached the village square two armed men, in the cobalt-and-silver livery of House Corelyn, standing watch at one of the corners of the square stepped away from their post to walk up to them. In addition to their gambesons laid over with shining steel mail, they wore kettle helmets and dull, polished gorgets. Both held steel bucklers and spears roughly the same length as Ludmila’s own, and at their belts each had a war hammer on one hip and a long dagger on the other. Their appearance was a testament to the wealth of House Corelyn: each member of Clara’s baronial militia were better armed and armoured than Ludmila herself.

 

One of the pair stopped roughly four metres away while the other came forward to address them.

 

With salt-and-pepper hair and a balanced posture that lent him the air of experience, he appeared a militia veteran they might have come across keeping an eye on any bustling village or town. His clear gaze went from the taller woman dressed in a villager’s kirtle but carrying a variety of weapons, to the shorter maid standing slightly behind her to the side. He relaxed his cautious posture somewhat and spoke deferentially to Ludmila, probably assuming Aemilia was an attendant of some sort.

 

“Welcome to Corelyn Village, miss,” his gravelly voice came out evenly, not quite matching the warmth of his words. “What is your business here today?”

 

“We’re headed to Warden’s Vale,” Ludmila replied as she rested her spear against her shoulder again and fished around in her bags. “Here is the receipt for the harbour fees.”

 

The man took the folded piece of paper that was offered to him, opening it up to scan over its content. His eyes rose to glance at her for a moment before turning to walk back to his partner, discussing something quietly between themselves.

 

“Is something the matter?” Ludmila asked.

 

The two men exchanged looks before facing her again.

 

“There’s nothing wrong with your receipt, miss,” the older man spoke again, “but the boat is…”

 

His voice trailed off with some uncertainty as he tried to find words to explain. After leaving her hanging for a moment, he gave up and resumed speaking.

 

“Well, you can see for yourself.”

 

They followed after the two militia sentries, who led them down the southern village road that ended at the harbour but, well before they arrived, the pair stopped. Ludmila came out from behind them to see what the delay was. In the distance she could see the figure of the Elder Lich standing on the shore near the pier. She had wondered whether her ‘attaché’ would be accompanying them on their journey; now she supposed she had her answer. In addition to the Undead clerk, however, she spotted several other figures on the vessel itself.

 

Ludmila frowned, stepping forward with Aemilia in tow. When she was close enough to make out the figures sitting in the vessel, she realized that they were a group of Undead. A Skeleton sat at each of the eight oars; another manned the rudder while two others appeared unoccupied. The Undead standing at the rudder was not one she had seen before.

 

It had a similar appearance to the Death Knights that stood as sentries around E-Rantel, but lacked the huge tower shield and carapace-like plate armour. In their stead was some sort of armour fashioned from hides, appearing worn and ancient. A great many strips of cloth, resembling the ones that hung off of the Elder Liches, were wrapped about its head and body, their ends fluttering in the breeze. Between the gaps of its adornment, she could see the desiccated flesh belonging to a being of times long past. She thought that it might have once been a Human, but time had taken its toll and worn away many of its features, leaving a ruin that only suggested what may have been.

 

The blade of a greatsword rested on its shoulder, and it’s right hand cradled the pommel before its waist. At its belt, there hung a great quantity of sidearms – she even spotted several weapons meant to be thrown, in addition to a crossbow. Holding her own newly purchased equipment, Ludmila felt a bit inadequate compared to the warrior standing in the boat. Unlike her gleaming weapons freshly forged, the weapons had the sense of being well worn and trusted companions to the ancient warrior through all of the ages it had seen. She perceived the Death Knights as stalwart and unyielding defenders, but this Undead being looked like the very personification of unholy violence – its armament ready to be unleashed at any moment.

 

“What’s going on here?” Ludmila asked her attaché as she approached the pier.

 

“The Royal Treasurer has assigned a crew for this vessel.”

 

Aemilia jumped in surprise as the Elder Lich replied – apparently it had used some sort of magic to conceal itself and the maid had not noticed its presence near to them. Ludmila was somewhat confused by the archaic term that had been used: the position of Royal Treasurer had long been replaced by the Minister of Finance in Re-Estize. She wondered if the office was similar, and why it still existed in the Sorcerous Kingdom. Aside from that, she had never met the Royal Treasurer, nor any other member of the King’s Cabinet aside from Lady Shalltear.

 

“Are there any terms or arrangements involving the use of this crew?”

 

“The administration did not account for the use of ships in this region,” the Elder Lich replied, “so the employ of an Undead crew is currently being evaluated. Fees associated with their usage will be determined after the value of the service has been assessed.”

 

“So these crew members don’t know how to operate a ship?” Ludmila said dubiously after the explanation, but the Elder Lich gave no further reply.

 

She glared at her attaché for a while, then sighed – there was ultimately nothing she could do about it. It still felt strange that a member of the Royal Court she had never met or heard of before would intervene in her matters directly. She pondered the matter for a while until she decided that, unlike the Duchy of E-Rantel, whose primary trade routes lay on land, the Sorcerous Kingdom viewed ships as a tool for trade so the Treasurer had become involved.

 

Stepping onto the pier near the ship, she held out one of her bags experimentally. The unassigned Skeleton nearest to her took the luggage and stowed it away into the hold while the second came up, reaching out with its arms for the other bag she was holding. After they had stashed her things away, Ludmila turned to look at her maid. With some hesitation, Aemilia stepped forward and held out the first bag she was carrying. Her arms were stretched to their full extent, and her face was turned away with her eyes squeezed shut even as she gingerly leaned forward. The awaiting Undead crewman, for its part, seemed entirely uncaring of her presentation and simply took the bag out of her hands, stowing it away with the rest of the articles already on board. Since nothing terrible had happened to her, Aemilia handed over the other bag in a slightly more normal fashion.

 

Relieved of their burdens, Ludmila turned and walked back towards the village, placing her hand on the small of Aemilia’s back to guide her forward, lest she bump her into the water. She paused in her steps as they passed in front of the invisible Elder Lich.

 

“I’ll be in the village a while. There are a few things we need to purchase before departure.”