\chapter{Ludmila Zahradnik}

As Ludmila and Aemilia headed back to the village square they came across the two sentries again, who had not moved from where they had left them. The men looked over the pair incredulously as they approached, and the elder of the two was the one to speak again as they started to walk by.

 

“How did you…no, wait,” the man peered at her. “You’re the Zahradnik girl, aren’t you? I saw you last winter – you’ve gotten taller now.”

 

Out of the corner of her eye, she saw Aemilia somehow straighten her normally upright posture even more as she nodded.

 

“That’s right,” Ludmila replied.

 

“So that’s why – I mean, apologies Mistress Ludmila,” the militia sentry said. “I was wondering why there were only two of you…”

 

“Lady Zahradnik.” Aemilia’s voice cut in sternly.

 

Ludmila resisted the urge to glance to her side. Her attendant had somehow transformed from the timid girl gingerly handing luggage over to the Skeleton crew to a prideful retainer that one might have expected to represent a powerful noble house. The man’s mouth fell open, looking back and forth between the two.

 

“Lady…? But that would mean…what about your brothers? And Lady Corelyn…”

 

The man’s thoughts fell out of his mouth in a jumble; then he seemed to realize what he was saying and quickly bowed in apology.

 

“I’m sorry, my lady,” he said. “This...this is horrible news – you have our condolences for your loss.”

 

The other sentry quickly followed suit, bending nearly perpendicular beside his senior. They appeared genuine in their feelings, but Ludmila did not wish to touch on her loss with all the work that was looming ahead of her.

 

“Thank you,” she replied graciously. “Many have lost loved ones recently. Lady Corelyn is also aware of what has passed.”

 

The two men raised their heads at her words.

 

“You’ve seen Lady Corelyn? Is she okay?”

 

It was the younger one that spoke this time, his tense look and the amount of worry in his voice suggested that he might be an acquaintance.

 

“In the city, yes,” Ludmila replied. “She is well and residing in one of the guest manors for the time being. The majority of the duchy’s remaining nobles are currently being hosted in the central district. With the transfer of E-Rantel to our new sovereign, many changes have come that will take time to become accustomed to. We nobles have much to learn of the workings of this new realm – as will all of the people in the seasons to come.”

 

“None of the rumors are true, then?” The young man asked.

 

“Rumors?”

 

“That E-Rantel has become a charnel house,” the young man’s expression paled as he spoke. “That the people have been sacrificed to the dark servants of the Sorcerer King, and Undead now stalk the streets.”

 

“Where did you hear this from?” Ludmila frowned, “Do the people actually believe this?”

 

“I-it’s what everyone’s saying,” his voice faltered upon hearing the sharp tone of Ludmila’s words. “We can see the city on its hill from the village here, and there’ve been no traders; no travellers. There’s no sign that E-Rantel is alive at all – we only see the smoke that ever rises over its walls. It’s eerie and unnatural.”

 

After being in the city for a few days herself Ludmila thought the rumor absurd, but she supposed that she could see how the villagers could come to this conclusion.

 

“The Undead do walk the streets,” she stated plainly. “They fly in the skies overhead as well…but those Undead are serving as protectors of the city: much like you two here or any member of the militia. The citizens that have remained in E-Rantel have not been harmed in general, but they are understandably uncertain and frightened with all that has happened, much like your people here. His Majesty has shown great patience and is providing for their needs as they become accustomed to the new way of things.”

 

“See?” The older man said as he leaned over to nudge the other sentry with his elbow, “What Momon said was true.”

 

“Momon?” Ludmila scanned the village for the Adventurer’s distinct black plate armour, “Momon is in the village?”

 

“Ah no, my lady,” he straightened again and turned back to her. “He was here earlier this morning with his partner, Nabe – you missed them by a few hours.”

 

“Did something happen to bring Adamantite Adventurers here?” Ludmila asked.

 

“Not sure – was nothing we asked for, at least. At the crack of dawn, I came out to do my rounds real quick and I found them standing at the harbour looking at the Undead on that ship of yours.” The man looked over her shoulder towards the river, “We’ve all heard of Darkness before, but it’s the first time I’ve met them in the flesh.”

 

“Did he have anything to say?”

 

“Nothing out of sorts, really. Said he was out west all week and came to check up on our village to see how we were doing.” He leaned on his spear and his brow furrowed a bit, “It was a bit strange, now that I think about it.”

 

“Strange?” Ludmila said, “It seems like a very normal thing to ask.”

 

“That’s the thing, though,” the man replied. “Once in a while, we get Adventurers stopping by on their way back and forth doing work out in Katze. But there’s this…you know, a sense of bravado surrounding them. They like to ham it up; to brag and boast about their feats, or talk about their work nearby and how we don’t need to worry when they’re on the job. They acted like, well, Adventurers. Darkness, though – they weren’t like that at all.”

 

Ludmila thought Momon most definitely matched that description. Aside from his response to her mortifying episode when they had met, her few hours with him had the Dark Warrior either declaring things with the air of great certainty or shrewdly drawing information out of her. The idea of Momon acting ‘normally’ seemed greatly at odds with her own experience with him.

 

“Then what were they like?” She asked curiously, “Did they do anything here?”

 

“Well, we walked up together,” he said, “back to the square, where we just talked about regular things. More people saw us standing there in the middle of the village and they came out to see what was going on; even with a crowd around him he never sounded like he had a big head and kept on with the others just like he did with me.

 

He didn’t even seem to mind that the Sorcerer King took over and we were being ruled by the Undead. He just asked us how our spring work was going, how our families were doing and if we had any problems around the village we needed help with. He bought some things; played around with the kids a bit; helped out here and there with odds and ends. After he left, I just stood there in the square wondering what I had been doing with myself all week. Seemed everyone was thinking the same – was plain as day on their faces.”

 

The man looked around himself at his village and the people around their homes, shaking his head. Straightening himself, he seemed to renew his vigilance.

 

“It was like he was reminding us of the lives we had, of what we still needed to do and all the folks that depended on us – things that would keep on going no matter what distant throne claimed lordship over the land. I always thought a Hero would just be another Adventurer out killing even bigger monsters; impressive, to be sure, but far beyond simple people like us. But Momon…he reached down from that high place and pulled us up to stand with him, out of a haze just as deadly as the one out there on the plains.

 

Without those two greatswords even leaving his back, he showed us what a true Hero is – and that we didn’t need to be powerful Adventurers to be there for those around us.”

 

The sentry had a wistful expression on his face and a gleam in his eye as he finished, then he flushed slightly and coughed in embarrassment. The militia parted ways with them, returning to their posts.

 

As they headed towards the small selection of shops on the street that serviced the village, Ludmila wondered what sort of magic Momon had used to breathe life back into Corelyn Village. Beyond her own retinue, she did not feel that any of her actions in the previous day had changed much in the city as she went from place to place with Lady Shalltear.

 

Reminding herself that the journey ahead of them would be long and there would be plenty of time to ponder along the way, she turned her focus to what she needed to purchase for her maid. Nearly an hour later, they returned to the ship with far more than Ludmila had expected to come away with.

 

It was an oversight of her own making; she had assumed Aemilia would prepare on her own for life in the Barony. In addition to proper footwear, her maid had not packed warm, durable clothing in general. Somehow, several other purchases of her own were added along the way as they browsed through the shop’s inventory, and they filled yet another sack which she was now handing over to one of the Skeleton crewmen. As she hopped down onto the deck and helped Aemilia aboard, a little voice in the back of her head was reprimanding her for having the coin on hand to tempt her into overspending.

 

After seating themselves ahead of the mast in front of the oarsmen, she looked around at the silent Skeleton crew. Her gaze went from the Skeletons to the Elder Lich, then to whatever the one with all the weapons was. She had no idea where to start and waved over her attaché.

 

“How much do they know about operating a ship?” She asked after it came close.

 

“They will understand your instructions according to your intent,” it replied. “So long as they are straightforward.”

 

It was becoming decidedly annoying how the Elder Lich avoided directly answering her if it did not have a definitive answer for her questions. Lady Shalltear mentioned the relationship between her own subordinates, and it seemed that Ludmila was not included among them in its eyes. Or perhaps it was some vestige of the rivalry between Lady Shalltear and Lady Albedo, as the attaché had been dispatched by the Guardian Overseer. She looked to the free Skeleton nearest to the pier, pointing to the ropes which held the vessel.

 

“Climb onto the pier and release the ropes holding the ship,” she said. “Throw the ropes onboard after you do so and return to the deck after you’ve completed your task.”

 

Thankfully, the Skeleton clambered up from the ship immediately after she finished issuing her instructions. Rather than untying the ropes that were wrapped around the short pilings, however, it lifted them off while they were still knotted and threw them onboard. The Skeleton jumped back onto the deck with a light clunk.

 

“Make sure you undo those knots when casting off next time,” Ludmila said as she walked over and kneeled down to untie the ropes.

 

As her hands worked, all of the Undead on the ship leaned in to watch and she couldn’t help but slow down at the odd sensation. When she finished one rope, she handed the other to the Skeleton that had gone up to release the ship. It held the knotted rope in its hand, staring down at it, but ultimately it could not accomplish what it had seen.

 

Ludmila frowned. It seemed that knots were too complicated for Skeletons. She looked up to the not-a-Death-Knight.

 

“Are you able to do this?” She asked.

 

It put its greatsword away and held out a hand. Ludmila placed the rope into its palm. Within seconds, the knot was undone.

 

Ludmila was about to take back the rope to put it away, but it seemed the Undead being was not done yet. It retied the knot and handed it to a Skeleton. The Skeleton untied the knot without much difficulty.

 

“Huh?” Ludmila let out a confused noise.

 

“Low-tier Skeletal Undead cannot be taught,” the Elder Lich said from its place to the side. “They cannot learn. They will only carry out the orders that you specify.”

 

“I see...then,” Ludmila looked to the not-a-Death-Knight, “since you seem to be in charge of this crew, you will be the captain of this vessel. Is this something you can do?”

 

The Undead being nodded in response, and Ludmila set about instructing her new ship captain on the operations of the vessel.

 

It took several more minutes to instruct the Undead on how to disembark from harbour and, in that time, several villagers had gathered along the shore to watch the strange scene of the Undead crew and the young woman animatedly walking up and down the ship trying to direct them. When the vessel was finally far away enough from the shore and held steady against the current, Ludmila instructed the two free skeletons to raise the sail. Their Skeletal forms were too light to manipulate the ropes, however, and it wasn’t until she called in the Undead warrior that they were able to manage.

 

With a few adjustments, they were able to trim the sails to the northern winds and soon the vessel was steadily making its way west upriver. Ludmila instructed the captain to keep the sails perpendicular to the wind and to keep the ship away from the shallows, after which she returned to her seat beside Aemilia. Her maid had busied herself by sorting through their luggage and finding things to make their journey more comfortable and, as Ludmila prepared to leave the operation of the ship in the hands of the captain, the lunch that had been packed away was brought out.

 

Ludmila lifted the cover off of the small wicker basket: the meal consisted of the same type of sandwich they had had the previous day, along with some of the dried fruit she had brought in from Warden’s Vale. Distracted as she was in watching the crew and the course of the ship, she slowly worked her way through the meal as they sailed along.

 

“I don’t remember us taking that box with us, my lady,” Aemilia noted after Ludmila was finished. “Was it here before?”

 

It didn’t take long for Ludmila to spot what her maid was referring to. Stashed under a portion of the hold sheltered by the deck, there was a conspicuous black box. Pulling it out from the hold, she brought it back to her seat, placing it in front of them. It was a fairly large object that stood knee-high, but it felt as if it was empty or at least only partially filled. There was a light rattle as something inside shifted around when she had carried it over. Studying the glossy surface of the object, she could not even tell if it was made out of wood or metal.

 

“Do you know what this is?” Ludmila asked, looking up to her attaché standing near the bow of the ship.

 

The Elder Lich turned away from whatever it was looking out at on the river, not even sparing a glance for the object in question.

 

“The Royal Treasurer has provided this article to aid you in your tasks,” it replied in its vaguely old-lady voice. “You may peruse the contents at your leisure.”

 

It turned away again, and two women looked at the box dubiously. Seeing something that resembled hinges on the side of the container facing them, Ludmila rotated it until the front was visible. Rather than a lock or a latch that secured the cover, there was a strip of paper scrawled with unfamiliar writing which sealed the box. The unfamiliar sight caused her to look towards Aemilia, who shrugged in return with an equally unknowing look on her face. With no real clue as to what would follow, Ludmila took a corner of the paper that was hanging loosely from its surface and pulled open the seal.