\chapter{Ludmila Zahradnik}

Ludmila had always appreciated the natural beauty of her own home, but the sight did not affect her the same way as it did Aemilia. Born and raised in the barony, she was used to the vistas that it offered. The reason why Andrei Zahradnik had staked his claim here was said to be the natural wonder that it had evoked in him, so she supposed that any outsider might share those same feelings. Ludmila’s gaze scanned the familiar surroundings: rather than marveling over the scenery, she was searching for signs of damage or intrusion. The Adventurer, Nabe, had mentioned a few days ago that she had been sent to deal with some trouble in the region, so there had been a lingering worry in her mind all throughout her time in E-Rantel about the state of her demesne.

 

In the remaining hours that it took for them to come within sight of the village harbour, she had not seen any evidence pointing to the passage of anyone, never mind intruders. The geese still occupied the flooded marshes; there were no tracks on the narrow sandbar and the village – at least from a distance – seemed unchanged. She turned her attention to the ship’s progress as it approached within a few hundred metres of the pier, watching the Undead crew and occasionally issuing additional instructions when the captain seemed uncertain about what to do next. After they safely guided the vessel into the harbour and secured it to the pier, Ludmila lifted herself out of the ship and examined the hill.

 

It felt strange how unchanged her home appeared. Though her time away had been less than a week, it certainly seemed like it had been much longer so she was expecting at least something to have changed, if only a little bit of growth on the grass and various plants that covered the rocky knoll in small patches. Behind her, she saw that Aemilia had slipped into her pair of new boots, hitching up the long skirts of her uniform to avoid getting them stained by the muddy path leading up through the village. Behind the maid, several of the skeletons were lined up, carrying their luggage. Ludmila did not recall instructing them to do so.

 

“Did you instruct the skeletons to carry our luggage?” She asked Aemilia.

 

“Um…I suppose I did?” Her maid seemed surprised at herself as well, “Before I climbed out of the ship, I just asked them to without thinking about who I was asking. I don’t think I could have if I did.”

 

“The Undead are a part of our lives now,” Ludmila tried to encourage her Lady’s Maid, “so learning how to get along with them is a good thing. You’re a senior member of my household staff, so it will serve as an example to everyone else.”

 

Aemilia’s expression wavered between being pleased at her mistress’ affirmation of her position and being uncertain about her new relationship with the Undead. Ludmila led her odd entourage up the path towards the village entrance, through the winding route between the homes, and stopped in front of the entrance of the baronial manor. It felt absolutely tiny in comparison to the guest manor in E-Rantel – this was a feeling that she always seemed to have after returning from the city. As much as she loved her home, it always felt like the simple and rugged village was far inferior to the city, with its well-developed infrastructure and buildings that weren’t essentially small holes dug into the hillside. She did not want to know what sort of expression her maid had on her face as she opened the manor door.

 

The familiar smells of home wafted out to greet her even as she stepped across the threshold. The familiar smells of home wafting out to greet her also reminded her that she had left half a pot of stew in the fireplace at the beginning of the week. Quickly pulling off her boots, she rushed over to look into the cookpot: to her relief, the recent weather had left its contents nearly frozen. Glancing to the hall, she saw Aemilia off to the side, organizing the contents of their luggage with the skeleton crewmen. Ludmila snatched a brush off of the fireplace mantle, grabbed the iron pot and made a break for the door.

 

“Where are you going, my lady?”

 

Aemilia’s voice stopped her before she could even walk over to where she had left her boots. Ludmila still could not comprehend how her maid was so perceptive when it came to things like this.

 

“Just taking care of this so I can get dinner started,” she replied, not quite looking at her attendant.

 

“Oh, you should really leave these things for your servants to take care of,” Aemilia said with a smile. “There are many other responsibilities that you must attend to, my lady.”

 

Ludmila surrendered the pot and the brush, trying her best not to look like a child that had been caught in some sort of mischief. She spotted Jeeves’ box along the wall, so she picked it up and carried it outside with her. As she made her way back down to the warehouse, Nonna’s flying form crossed her line of sight. The Elder Lich had flown off before they arrived without any sort of explanation and now settled to the ground nearby as she reached the warehouse door.

 

“Where did you fly off to, Nonna?”

 

Ludmila spoke in a conversational tone while opening the lock holding the crossbar in place. She lifted the wooden beam and placed it to the side, opening the door which creaked slightly on its hinges.

 

“Orientation.”

 

Its voice was as expressionless as ever, but Ludmila thought that this particular Undead expressed an inquisitive nature with all of its independent movement and observation. Or it could have received instructions along those lines as a part of its assignment. With it coming and going as it pleased, she was never quite sure which it was. The more fanciful part of herself thought that if it was simply following its assignment as an attaché; it would have just followed her around everywhere without any deviation, so she liked to think that her initial reasoning had some basis to it.

 

“Did you see anything out of sorts?” She asked.

 

As the words left her mouth, Ludmila realized the Elder Lich wouldn’t know what ‘out of sorts’ was, being here for the first time.

 

“Did you see anyone other than our group while you were looking around?” She elaborated on her first question.

 

“No.”

 

Nonna stared back at her after the short reply. With little else to say, Ludmila turned back to the task at hand. Placing the glossy black box beside the small arrangement of leftover supplies in the corner near the entrance, she opened the lid and Jeeves rose out of it in much the same way he did when she had opened the seal to his container.

 

“Good day, madam!” He said in a cheery voice, “How may I be – oh, Lady Zahradnik?”

 

Jeeves stepped out of his box and turned to look around.

 

“Is this the work you spoke of?” He asked as his gaze continued to wander about the mostly empty warehouse, “Is this my inventory?”

 

“It’s the village warehouse, and you’ll be acting as its manager.” Ludmila said, “There’s also the warehouse in the hamlet out in the fields that will be a part of your responsibilities. Our inventories will fill and empty as seasons pass and shipments are sent in and out but, in the meanwhile, you’ll need to familiarize yourself with everything, as well as learn how to read and write.”

 

Ludmila turned to her attaché, who was silently observing them.

 

“While Jeeves is free from his duties,” Ludmila asked, “can you teach him, Nonna? He needs to be able to keep records for accounting and trade, as well as understand any materials provided by the civil office by the time we start sending goods to the capital.”

 

“It will be done.”

 

Once again, the Elder Lich gave an immediate affirmative to a task it was able to accomplish. Ludmila had grown up knowing the Undead as unfeeling, single-minded beings, but Nonna’s distinctly different responses which depended on whether it was capable of performing a task or not spoke to her of a stubborn sense of pride.

 

“The labourers should still take about half a day to arrive,” she had distributed the equipment purchased from Mesmit’s Forge that same evening and sent them out immediately, “so it’s going to be a busy day tomorrow. I’ll be retiring to the manor to rest and prepare, come and inform me should any problems arise.”

 

With that, Ludmila left the two Undead in the warehouse, walking through the village to inspect all the homes which had been shut away. With none of them occupied, the routine half felt like a needless exercise, but she did it anyways to organize her thoughts as she went around. The first thing she would need to get started on the next day was preparing the fields for planting. Though she was developing an appreciation for the tireless constitution of the Undead, her experience so far also left her dubious about whether they would know how to do the jobs that were tasked to them and whether she herself knew enough about each task if they did not.

 

The sight of Aemilia with the skeletal crewmen coming up the hill pulled her from her thoughts. She was carrying the cooking pot and brush, while the Skeletons following her were each carrying two full buckets of water. The maid had quickly become used to them; it seemed that she had enlisted the crewmembers to help out with her chores. Ludmila entered the manor ahead of them and headed to the living space at the end of the hall.

 

The fireplace was already lit, as were the two lamps which hung from the ceiling. Their luggage was sorted with clothing and equipment neatly arranged, and the day’s worth of leftover food that had been packed away for the journey upriver was being prepared on the counter nearby. Ludmila changed into the nightwear laid out on the largest bed for her as the sound of the Skeletons filling the barrels of water in the hall filled the house. Looking around for the administrative materials that she brought along from E-Rantel, she saw that they had been placed on the desk at the front of the hall. Her lady’s maid seemed a bit too attentive, leaving nothing for Ludmila to distract herself with – at least nothing that Aemilia considered beneath her mistress’ noble standing.

 

She seated herself at the desk and started leafing through the pile of materials, but she had gone over them so many times on the trip back that she had nearly memorized their contents. She propped her chin in her hand as she looked out the window, and the fingers of her free hand idly drummed on the wooden surface of the desk. As busy as it had been for the past week, she was now becoming restless with little to do. She turned her head away from the window to look towards the interior of the house where Aemilia had almost finished preparing the evening meal.

 

Seeing this, Ludmila rose from her desk and brought the stack of books and folios to the cabinet where the rest of the barony’s documents were stored. After locking everything away, she stepped over to seat herself at the dining table. The Skeletons appeared at the door again, entering to fill the last of the four barrels that stored water in the manor. With their task complete, they stood by in the hall, awaiting new instructions.

 

“You seem to have been able to put these fellows to work effectively,” Ludmila said idly in an attempt to stave off her boredom. “I didn’t see anything related from the civil office, but I can check to see if they can be hired out for something like this if you’d like them on a more permanent basis.”

 

“I don’t know how it came to this – I really don’t,” Aemilia placed the last dish on the dining table and stood by as she looked at her impromptu helpers. “Maybe a bit of you has rubbed off on me, my lady. You seem to direct everything so effortlessly. I wasn’t even thinking when I directed the Skeletons from the ship.”

 

“Well, not everything I say goes accordingly,” Ludmila responded dryly. “Besides, back at Corelyn Village, Nonna said that they would understand what we intend, as long as the instructions are straightforward. As I recall, Lady Shalltear said much the same yesterday.”

 

“Nonna, my lady?”

 

“I gave the Elder Lich a name yesterday evening; it didn’t seem to mind. Having all these nameless Undead running around everywhere is going to become confusing, so at least the ones we work closely with could do with a name.”

 

“...I see.” Aemilia mouthed the name a few times, “Anyways, I can see how the Skeletons will be a great help – especially when it’s just myself here – but they must come with a price of some sort. How much does it cost to…rent…the Undead?”

 

“Well, the cost for the Undead this season has been waived since we’re basically field testing them and acting as a sort of pilot for their adoption into the duchy’s industries. Normally, it’s a tenth of the production that they partake in. The regular rates have been structured in such a way that it’s actually more cost effective than the traditional shares that Human tenants keep from their work. At least in a direct comparison.”

 

“Isn’t that bad?” Aemilia frowned, “If the nobles replace all of their tenants with the Undead, how will the people survive without their livelihoods?”

 

“That’s a question I’m still trying to answer,” Ludmila looked at her meal and then looked back up to Aemilia. “You should sit down and have dinner as well, there is no servants’ hall in this manor; and it’s just us here anyways.”

 

“Thank you, my lady,” Aemilia sat down across from her after retrieving her meal.

 

“As I was saying,” Ludmila spoke while pushing her food around with her spoon, “you’re right about what you said, I think. While it’s true that the price of food and necessities will go down as a result of Undead labour, it also means that the labourers in basic industries that have been replaced are not earning any incomes whatsoever. The costs of all the unproductive tenants will need to be shouldered by the nobility...and I’m not sure how many nobles would be willing to sustain that arrangement for long. It’s not as simple as having your tenants work other jobs – almost everything that I could think of that the Undead are not suited to requires skilled labour, and apprenticeships take many years before one can qualify to become a journeyman.”

 

She looked over to where the four Skeleton crewmen were standing in the hall. The Undead showed no signs of impatience or restlessness as time had passed: they simply waited without noise or movement.

 

“Take your direction of these skeletons, for instance,” she continued, speaking her thoughts aloud as they came to her. “If a single maid can direct four Undead to function as junior staff performing basic duties – such as cleaning or hauling water and the like – then even a manor as large as the guest houses in E-Rantel might only need three or four household members to fulfil all those duties. Many vocations will be similarly impacted: Skeletons still need Farmers to direct them, so the question then becomes how many can each Farmer supervise properly? I’m not sure as to what the extent of their capabilities lie, however – I think that is something you should explore while you have the crew available at your disposal, and I will need to investigate the impact on every industry to come up with a real plan for developing the demesne.”

 

“If that is your wish, my lady,” Aemilia nodded. “Actually, I’m starting to become curious myself with how easy they’ve been to direct. In my time training as a maid, I know that different members of the staff do not always get along, and junior staff are not always cooperative or do not work out as you expect them to. The conditions of a junior maid are also not very good – the work is hard and the accommodations are often very poor, so having the Undead fill those types of jobs is not something that I actually mind. At the same time, however, it’s as you say: the more we employ the Undead, the more people will lack for work. It seems like a difficult problem…I do not envy you for having to solve it, my lady.”

 

Ludmila considered her maid’s words. In truth, it would not be as much a problem for her as it would be for the nobles with well-developed territories and large populations that needed to be reorganized with the changes. Local economies would be turned on their heads and they would be facing chaos as their tenants were simply outmatched by the Undead for the majority of their basic industries.

 

If, for example, a single farmer was capable of directing four Skeletons, and each skeleton matched the labour provided by a Human household, then three households would be put out of work. The higher the level of development in a demesne, the more pronounced this problem would become, as one could not simply cultivate more land when there was no more land to be had. The process of establishing new industries for all of the freed-up labour would be slow and cumbersome, though having the people become used to the Undead would probably be a slow process that would mitigate the problem somewhat.

 

For her undeveloped barony which had always struggled with manpower, however, the Undead were an unprecedented boon. Rather than creating an overwhelming surplus of Human labour as it would in the inner territories, the Undead created a shortage of Human labour in Warden’s Vale which should be easily filled due to the problems rising elsewhere. It was an edge she would need to exploit, reinvesting the surplus generated by the fief’s exports into developing industries that would retain their value against the turmoil in the markets that was sure to come.

 

Finishing the last of her meal, she rose from her seat and walked over to the hall.

 

“You two, head down and help guard the warehouse,” she pointed to the Skeletons closest to the door, then turned to the others. “You two stand guard outside the door to the manor. Luzi will come and pick you up for work tomorrow morning.”

 

The Skeletons quietly filed out of the manor, shutting the door behind them.

 

“Will there be anything else for tonight, my lady?” Aemilia asked from the counter where she was putting the used dishes aside to be washed.

 

“No, I’d like to get started early tomorrow,” Ludmila replied while letting her hair down. “Don’t let me sleep in – there will be a lot of work ahead.”

 

“Yes, my lady. Good night.”