

\chapter{Ilyish’nish}

A warm updraft carried tiny crystals of ice into the skies, joining the currents flowing to the distant south. The sun blazed overhead and the air was clear, revealing a rare full view of the Azerlisia Mountains far below. Beyond its forested foothills, a vast panorama of plains and wooded lowlands stretched to the far horizons before her.

 

Ilyshn’ish was in a good mood, humming to herself happily as she soared on the icy winds. Her figure would be but a tiny white speck to anyone watching from below: indiscernible from the cerulean skies and scattered wisps of cloud to all but the most skilled observers who just happened to look above them. She had a filling meal yesterday, no one had appeared to challenge her and nothing horrifying had popped up to attack her in the past few days. When nothing happened, she generally counted it as a good thing, for Frost Dragons lived simple lives and most of her kind preferred a quiet and uneventful existence.

 

Most of her kind, at any rate.

 

Her outer eyelids narrowed and a tendril of cold anger rose as she recalled one such individual who did not aspire to such a life: the Frost Dragon Lord, Olasird’arc=Haylilyal. Over a century ago, her father had brought together his consorts scattered throughout the glacial ranges, settling to create a colony deep in the midst of the Azerlisia Mountains. To the Frost Dragons, who lived naturally solitary lives – they usually only came together to mate and go their separate ways again, the Dragon Lord’s actions were considered eccentric to the point of deviancy. Even those of his broods: Ilyshn’ish’s siblings and half-siblings who were hatched and raised in the ruined dwarven capital, Feoh Berkana, had the inkling that their situation was unnatural.

 

Olasird’arc was the reason Ilyshn’ish was soaring far above the mountain peaks, returning from her ranging far to the north over the icy sea. Several months previous, she had come across a fat elk cow and returned with it to the city to dine in safety. Except it wasn’t safe – not from her own family, at least. After slipping through an opening and into the vast cavern containing the open areas of the city, she was immediately ambushed by her father.

 

She tumbled end over end in the air after the Ancient Dragon – well over twice her length and ten times her mass – knocked her aside, sending her meal to the streets below. By the time she had recovered and glided down to the city, her father had already set upon her kill. To her angry protests, he had replied simply:

 

If you wish to retain what is yours, become stronger.

 

It was the unbreakable rule of the world that applied to everyone – Dragons were no exception.

 

Ilyshn’ish snapped her jaws shut after that, taking off in a huff. Certainly, she would supplant him one day. If she was feeling generous and he submitted to her, she might not even kill him. She shook the foolish thought from her head; there was no way he could be allowed to live. If any of her lazy brothers tried to challenge her, she would thrash them thoroughly as well. The enclave would be hers, and the others would bring her food instead.

 

Though that day was but a distant dream, she did not mind waiting. Frost Dragons could be said to have a sort of perfect memory for events, and had a patience that came hand in hand with their long lives. Be it centuries or millennia, she would nurse her ambitions until they could be attained, and that far off day of reckoning would be all the sweeter as the ages passed.

 

Ilyshn’ish studied the terrain below before angling into a slow descent to the mountain face where the dwarven capital opened to the surface. Gliding in slow, lazy circles over the mountain peaks, her sense of caution grew as the icy crags loomed large below. Flying too low exposed Dragons to a number of their natural enemies. While older Dragons such as her parents would only be wary of strong Frost Giants and a handful of powerful monsters that made the glacial peaks and valleys their home, younger wyrms such as Ilyshn’ish had a far wider range of dangerous things to look out for.

 

Looking this way and that, she peered at shadowed cliffs and crevasses, half expecting a spear or a net or a rock to come flying up at her. In the shadows of her mind, Frost Giants lurked: waiting to catch her and turn her into a slave. Or maybe it was a gigantic Polar Worm biding its time under a thin crust of ice that would leap out and snatch her out of the air like a convenient snack. She even imagined the horrible Adventurers she had read about coming to turn her into any number of trendy articles.

 

As the spectre of her fears grew, so did her altitude. By the time she came back to reality, she had ascended several thousand metres again. Her caution still accompanied her thirty minutes later, even as she descended along the final stretch to the gaping holes in the mountain that led down to her home. Not wanting to stay vulnerable at the lip of the entrance, she slipped in quickly and resumed flying through the vast cavern within.

 

Her first sense that anything was wrong was the scent that wafted up from below. It was the smell of corpses – Quagoa corpses. She ate a few on occasion, but the taste and texture were far down the list of her preferences. The odor grew overpowering as she skimmed over the buildings of the city. She thought that perhaps someone had gone on a rampage – perhaps the silly Demihumans had tried to rebel and were slaughtered as a result. It would certainly explain why none could be seen scurrying about in the wake of her passing.

 

She glided silently through the air, trying to puzzle out what had happened. There was no sign of either Quagoa or Dragons – only the overpowering odour in the eerie stillness of the city. After circling over the various districts several times, she alighted on the parapets of the Royal Palace. It was there, overlooking the central promenade leading out from the fortified gate, that she finally located the source of the smell.

 

The entire promenade was buried in what was left of countless Quagoa. It could not even be described as any number of corpses, just a thick carpet of Quagoa parts and accessories. Blood painted the stone faces of the buildings lining the promenade: over the statues and fixtures; a dark crimson flow which oozed into the surrounding streets and alleys. The gory scene had frozen solid as time passed – Ilyshn’ish hoped she wasn’t the one who would be told to clean it up.

 

She let out a puff of frozen breath, which scattered loosely into the air. This explained the smell, at least, but it didn’t explain the absence of her kin. She crept down off the walls and into the huge courtyard of the palace where her parents usually lounged about. Here, too, there was no sign of anyone, nor was there even a single coin left of the Dragon Lord’s hoard. She swallowed nervously at the unsettling sight of her empty home.

 

Entering the arching halls of the palace, Ilyshn’ish could feel her pulse hammering up her sinuous neck as caution rose once again. There were no Dragons anywhere; no sign of a long and brutal battle. She searched through the floors and finally ended up at the door to her eldest brother’s room: it had been smashed and twisted off of its hinges. Poking her head inside, she found it empty – even her poor, shut-in of a brother seemed to have been violently whisked away.

 

Ilyshn’ish continued anxiously down the hall, further into the depths of the palace until she found something which shocked her far more than anything else.

 

The door to the dwarven treasury, sealed shut for longer than she had lived, lay open.

 

All other thoughts flew from her mind at the sight. She trotted towards the treasury with the dusting of frost in the hall swirling with her passage, towards the tantalizing sensation of valuables which lay just beyond the yawning portal. A note of caution managed to somehow squeeze its way into her consciousness, and she slowed to stop just before the opening. She tentatively stuck her head into the vault, followed by her sinuous neck.

 

Laid in neatly organized piles along the length of the chamber was more treasure than Ilyshn’ish had ever seen in her – admittedly short – life of 107 years. Gold coins and jeweled adornment of all manner were piled on the floors, in crates and chests. Suits of armour and enchanted weapons gleamed brightly, untouched by the passage of time.

 

She took a deep breath, sighing in satisfaction. Though there was a small voice which continued to question why the vault had been apparently left open with its vast wealth still stored within, the allure was too great and Ilyshn’ish could only think of how she might explore its recesses. Carelessly coming in with her 10-metre length would undoubtedly make things even worse, possibly breaking the countless valuable items strewn about and potentially triggering whatever security measures lay within.

 

After some consternation, she spun a thread of magic into song, her voice quietly weaving its enchantment about her form. Within moments, only the stocky form of a female Dwarf, clothed in a set of white and blue garments, stood before the arching entrance of the vault. Disliking the idea that her tiny self was standing vulnerable in the open entrance, Ilyshn’ish quickly made her way deeper in, marveling at the contents as she passed.

 

Whereas the front of the treasury contained vast amounts of what one would consider material wealth, the articles stored deeper within were more notable for their age. If she still had talons, they would be flexing in excitement as she passed from the glittering halls to the dusty shelves and cabinets beyond the piles of valuables she walked around.

 

It was something of a quirk of her own family – both her mother, Kilistran=Denshusha, and her eldest brother placed a special value on knowledge and lore which exceeded that of simple, raw wealth. She perhaps felt this more keenly than any of her kin. The weakest amongst their kind, Frost Dragons and their normally solitary lifestyle could fall prey to any number of powerful enemies.

 

Her mother had learned Divine Magic, which had helped her triumph over many Frost Giants and assert her dominance over rival Frost Dragons. It had even attracted her mate, whom she adamantly asserted to her children that she finally let him win her over when she decided to raise a brood; he just happened to be the best option available. With her success in life, she had passed on her values to her children: knowledge gave one the edge to survive – helping to win wealth, power and suitors.

 

With the ability to retain the memories of their experiences in perpetuity, Frost Dragons would eventually be able to collect enough knowledge and develop enough magic to reign supreme over the Azerlisia Mountains and perhaps beyond. It was a cherished ambition of Kilistran’s, and the reason why she had eventually gone along with Olasird’arc’s overtures. She and her children would, with this doctrine, eventually rule over the colony with unassailable strength drawn from the wealth of knowledge and magical might that they had collected between them. The other Frost Dragon broods would be but servants and soldiers to their own.

 

Kilistran’s children embraced her teachings to various degrees. Hejinmal, Ilyshn’ish’s eldest brother, embraced the idea perhaps a bit too tightly and locked himself away in his room with his books entirely. Her other two brothers leaned more towards their father’s side, primarily valuing raw, physical strength and only learning a few spells to shore up natural weaknesses.

 

Ilyshn’ish thought herself somewhere in between: she neglected neither her pursuit of knowledge nor the honing of her natural strengths: in her own estimation, she was one of the strongest Frost Dragons in her generation. If she continued on this path, she thought, dominion over the Azerlisia Mountains was but an inevitability. For now, however, she simply enjoyed learning about new things, so the archives now laid out before her was a tantalizing vision indeed.

 

There was something wrong though. When she finally reached the shelves where rows of tomes and manuscripts should have rested, she found many spaces conspicuously absent of the dust of ages. She mulled over what it meant as she reached out to the nearest remaining tome with a greedy hand, wondering what secrets it contained, but managed to stop herself before her stubby fingers brushed the shelf. Pulling her hand back, she stroked her frosty beard, looking around cautiously. A moment later, her voice rose in song again. It was much smaller than it would have been were she a Dragon, but the spellsong worked anyways.

 

The magically infused waves of sound rippled out over the surroundings, leaving faint auras over everything they washed over. The shelves in front of her indicated that the tomes were exactly that – bound parchment not even enchanted with preservation magic – but it was a shimmering gleam of white and blue in the corner of her vision that pulled her attention from the morsels of knowledge.

 

Not far from where she stood was an item, rather than another tome. Propped up on a shelf was an ancient drum, marked brightly by her melody of magical detection. As her gaze had been pulled over, she felt herself walking towards where it lay. Forgetting she was a Dwarf for the moment, Ilyshn’ish crawled forward on all fours, sniffing experimentally at the instrument.

 

She wove another enchantment, this time checking for traps…but received no reaction to her magic. Apparently the Dwarves had relied entirely on the up-to-this-point impenetrable vault to secure their legacy – or whoever had opened the vault had disarmed everything before her arrival. The latter struck her again as exceedingly strange: why would anyone go through all the trouble of unsealing and disarming everything, only to leave it mostly untouched?

 

Recalling the partially disturbed contents of the vault, unsettling thoughts arose. Perhaps she had arrived while the one who gained access to the treasury – surely one more powerful than the Dragons who had tried without success to open it for decades – had stepped away momentarily, and was already on their way back. She would be trapped in the vault with no way out. Perhaps the room itself had some undetectable trap that had dealt with the first intruder without leaving a trace of their demise...

 

Ilyshn’ish tried to step back – to escape before it was too late – but her desire for the musical artifact rooted her feet to the ground. Unable to escape her own greed, she finally reached out for the drum. Her shaking fingers lightly tapped its taut skin and the instrument let out a low boom that rumbled through the aisles, sending streams of coins skittering down gilded slopes. She cringed at the sound, frantically looking all around her even as her fingers closed on the item.

 

As with most magic equipment, it adjusted itself to accommodate the user, shrinking into a modestly-sized hand drum meant to be held in one arm and played with the other. With her new treasure in hand, she rushed for the exit: the spectre of her imagination once again feeding her mounting panic. Past the dusty archives and piles of glittering treasure she ran on stubby Dwarf legs. She reached the narrow entrance of the vault and prepared to shift back into her regular self but it was too late. Someone was already in the hallway on the other side, a looming monstrosity many times her own size.

 

“Ah, sister, you’ve returned!” A familiar voice called out, echoing through the halls.

 

Eh?

 

Ilyshn’ish blinked as she looked up, pushing away the worries from her overactive imagination. In the hallway stood her brother, Hejinmal. She reflexively hid the drum behind her back.

 

“Hejinmal!” She greeted him cheerfully, “Yes, I have returned…from…uh… Hello!”

 

She didn't have a bad relationship with her brother, as far as relations between Frost Dragons went, but he was currently very large and she was currently very small. There was a good reason why Dragons did not often learn ways to take other appearances: a Dragon was the strongest being in existence already – even if they retained their strength and various traits while doing so, there was very little reason to invite unwanted aggression. Barring that, not many deigned to even imagine themselves in an appearance considered infinitely inferior to their own.

 

Ilyshn’ish backed away cautiously, well back between the aisles filled with treasure, as his snout came closer. Surely he must have noticed the artifact in her possession. She considered what would happen if they fought: she was not well-practiced as a Dwarf, so combat would be quite awkward to say the least. Counting his teeth as he loomed over her, she wondered what she should do.

 

“Hm? Why do you keep backing away, dear sister?”

 

“Why do you keep coming closer, dear brother?”

 

“...”

 

“...”

 

She considered turning back into a Dragon, even if it meant making a mess out of the vault. As she was about to do so, Hejinmal withdrew his head from the doorway, fatty dewlap wobbling at the movement.

 

“Well, whatever,” he said as he looked down at her with an animated expression. “You’ve missed out on quite the event!”

 

“Yes, about that…why is the entire Quagoa civilization scattered across the main promenade? Where are mother and father?”

 

“The Quagoa made an…unfortunate choice,” Hejinmal answered. “Father is dead. Toranjelit as well.”

 

“What!”

 

Her voice boomed down the hall as she returned to her Dragon self beside her brother – this time it was he who flinched and backed away.

 

“Was it an uprising?” She asked, “Was father slain in the conflict?”

 

Her feelings were plainly mixed. On one hand, the death of the Frost Dragon Lord was welcome news: a future obstacle to the seat of power eliminated. On the other hand, he was also their strongest deterrent against their rivals: the Frost Giant clans whose tribes occupied the moors and valleys throughout the range. Toranjelit, the foremost of Munuinia’s brood, was older and physically stronger, but Ilyshn’ish was reasonably certain she could defeat him on her own. Like her mother Kilistran, Ilyshn’ish sought paths to power beyond the natural strength of Dragonkind to complement her aptitudes and gain an edge over competitors.

 

“Oh no, nothing like that,” Hejinmal said. “Father was slain in single combat against a powerful magic caster. It was very one-sided, actually. He didn't even get a chance to attack even once. After that, mother and the rest of father’s consorts were rounded up and taken away with their broods. Except for you, of course.”

 

The statement broke her away from her rebalancing of the scales of power. Ilyshn’ish mouth fell open, then she closed it again with a snap. Did she just miss the opportunity of a century? If it was a magic caster powerful enough to one-sidedly slaughter an Ancient Dragon in such a manner…the only possible beings that came to her mind were the legendary Dragon Lords of old. Had one of the heroes of yore come to claim their enclave? To rule and lead them to a new age of prominence? She glanced around as they reentered the courtyard, seeking a glimpse of the majestic existence that had come to lift them up and out of their situation, but the space remained as empty as it had been before.

 

Ilyshn’ish shook her head. No, of course he wouldn’t linger in the ruins of this ancient dwarven hovel, littered with the leavings of the rodent-like Quagoa. Surely, her mother and the others had been whisked away to this Dragon Lord’s fabulous harem in some far off palace…and poor Ilyshn’ish had been left behind. Her brother too. It seemed that he was deemed too fat and useless to take along.

 

How did he even get so fat, anyways? Could he even fly? Her scales crawled just from watching the rolls of flesh wobble and jiggle as he chonked down the hall. She didn’t think she had ever seen him out of his room – at least not for the past four or five decades. The only times she really interacted with him was when she exchanged a kill or three of hers for another book when she was done reading the last one she had traded him food for.

 

The breath of her sigh frosted the air of the courtyard.

 

“What now then, brother?” She asked, “The two of us cannot hold this city alone if any real threats come our way.”

 

“Ah…we can’t stay here, actually,” her brother replied. “The Dwarves are returning to reclaim their city.”

 

“The Dwarves…” She repeated the words idly, “Eh? You mean all of them?”

 

“That’s right,” he said. “Well, enough to repopulate their capital at any rate, so most of them.”

 

She looked over at him in dismay. The two relatively young Frost Dragons could not hope to fight so many Dwarves.

 

“What do we do, brother? …I guess I should pack my things if we’re leaving for good.”

 

“Yes, I believe that’s a prudent idea,” he nodded. “I myself came back to pick up a few things that I missed from my room.”

 

Hejinmal turned back and disappeared into the palace.

 

Ilyshn’ish went off in the direction of her own place, trying to decide what to bring. It was mostly old books, taken from various places in the city, containing whatever tidbits she found interesting. The majority ended up being tales of Dwarf history: their various achievements, culture and society, technical knowledge and such…plus a few more exotic ones she had found detailing trade and travel beyond their kingdom. Between them, Ilyshn’ish figured that she and her brother had scoured the city clean in their formative years, and all that was left was to read the same old texts over and over again.

 

Still, she was loath to leave anything behind: it was what amounted to her hoard, after all. In front of the door to her room, she spread out a huge canvas banner that she had snatched off of its mounting in the hallway. Upon entering her room, she was greeted with a most dreadful scene. Across the decades, she had collected what could be called a small library of lore. Taking bookshelves that she had found around the city, they had been neatly arranged to line the walls of the room and filled with her precious trove.

 

Ilyshn’ish always looked forward to when she could retire to her lair and sleep in the midst of her treasures...but now all of its shelves lay bare. Dashing into the room, she frantically paced in a wide circle, looking desperately for anything that had been left behind until she finally collapsed onto the floor despondently. This was too much. She wanted to cry. Her eyes looked up to a bare patch of the wall where a composite map of the world that she had painstakingly pieced together once hung, marked with all the places she wanted to visit in the future when she thought herself strong enough to travel. Then she really did cry.

 

Who would do such a horrible thing, and why? She wallowed in depression and misery for a long while before her mind began to work towards finding a culprit. The Dwarves would certainly have taken them, but she had not sensed any in the city and, by Hejinmal’s account, they were still on their way. The Quagoa were generally too timid to intrude upon the palace; they did not read or eat books anyways. Her collection would surely be a pittance to whoever had taken the enclave. Amongst the enclave, there was her mother and Hejinmal…

 

Sorrow turned to fury as Ilyshn’ish exploded out of her room. An unlearned individual would normally associate beings of larger sizes with ponderous movements, but generally the opposite was true – especially amongst predatory species. The charge of a furious Dragon was not something a mere mortal would normally be able to avoid, and the momentum which accompanied Ilyshn’ish’s magically enhanced speed as she streaked down the palace corridors towards the courtyard was such that whenever she made a turn, she ran along the walls and ceilings before returning around again to the floor.

 

Hejinmal had half a heartbeat to register death in the form of his little sister pouncing out from the palace entrance. His obese form was blown all the way back to the main gate by the impact, where he was pinned by her as she snarled.

 

“Where are they!”

 

“Hiiiieee!”

 

“Hiiiieee?”

 

Hejinmal eyed the deep gashes left in the magically reinforced steel gate by her talons before returning his fearful gaze towards her.

 

“W-where are what?”

 

“Don’t play dumb with me, brother! My things! Where did you take my treasures?”

 

The fat Dragon’s eyes swam in their sockets as he tried to comprehend what she was saying. He started to panic and hyperventilate, squirming pitifully against the gate. Ilyshn’ish opened her jaws over his neck.

 

“Ahh! Don’t kill me! I didn’t take them!”

 

“I don’t believe you! Prove it!”

 

“Prove it??? How do I even – AAAAH! It was the one that came and killed father!”

 

His words gave her pause, and she backed away slightly.

 

“Why would that person steal my books?”

 

“I-it wasn’t just your books. Minions were instructed to go all over the place collecting all of the books and manuscripts and such from the entire palace. I was instructed to collect them as well.”

 

Ilyshn’ish peered at her brother. He did not appear to be lying – she did not think his will was strong enough for him to lie to her face. She withdrew; the gate groaned loudly as she removed her talons. Hejinmal collapsed onto his side, heaving for breath.

 

“So why was this person collecting books?” She looked down at him and asked.

 

“…seeking knowledge,” Hejinmal said between breaths. “Wisdom…and information…valuable.”

 

Her evaluation of the unknown subjugator rose by another two notches. She pondered her own situation once again: with the Dwarves coming, she was basically homeless. She could either make a new lair elsewhere…or perhaps she could chase after this mysterious conqueror. Several minutes passed before Hejinmal caught his breath and rolled back to his feet.

 

“I’m surprised you didn’t soil yourself there, dear brother.”

 

“That’s…well, I experienced something far more terrifying recently – maybe I’ve gotten a bit stronger as a result?”

 

Ilyshn’ish eyed Hejinmal. He didn’t seem any stronger from the last time she saw him. As she tried to judge his supposition, her treasure sense brought a small pouch slung around his neck to her attention.

 

“Brother, is that…”

 

“Oh this?” He did not miss her gaze. “It’s something that we’ve all received. Something like a Bag of Holding that allows us to easily fly things around.”

 

Ilyshn’ish twisted her neck curiously, leaning forward to look more closely at the container. They had been subjugated and received gifts? That didn’t make any sense at all.

 

“So you weren’t cast aside, then?”

 

Hejinmal stared at her, blinking stupidly. His mouth opened and closed several times before he answered.

 

“O-o-o-of course not,” he laughed nervously, not sounding entirely convincing. “Like I said, I just came back to pick up some things before going back. Since you’re part of the enclave, you’ll need to come as well – you’ve barely been around recently, and not at all in the past few months…I thought you finally got fed up with father and left, or maybe you were caught by the giants.”

 

“I see,” Ilyshn’ish replied absently.

 

The ember of ambition had rekindled within her once again, and the tip of her tail twitched lightly as strategies started to form in her scaly head. She was nowhere near as powerful as her mother or the rest of Olasird’arc’s consorts, and her accomplishments did not yet vastly overshadow their own. This new individual appreciated knowledge, however, so maybe she could make some sort of connection on that front. She also had the advantage of youth, which had an undeniable charm on its own…

 

She looked at the icy wall, examining her reflection. Panning her head back and forth, she thought her lithe figure was not bad. She was a good hunter, and she had felled many dozens of Frost Giants. A sudden thought interrupted her preening.

 

“The one who defeated father: were they male or female?” She asked Hejinmal, who was looking at her with some bemusement.

 

“Uh, Ainz Ooal Gown is…male? Why do you ask?”

 

Ainz Ooal Gown. The name was not Draconic. An alias likely used by a shrewd individual: names held power, after all. The mysterious Dragon Lord went up another few notches in her estimation.

 

“It’s no business of yours, brother. And stop looking at me like that, it’s disgusting.”

 

“Uh…ok?”

 

Hejinmal turned his attention to his bag, opening the flap and peering into it with one eye.

 

“By the way, brother,” Ilyshn’ish asked, “you said that everyone received one of those bags?”

 

"Yes, indeed,” he said. “It depends what the circumstances are, but we usually have four: each holding five hundred kilograms – two tonnes of cargo capacity per Dragon. I only brought one of them along since it was a private errand.”

 

Private errand? His words made little sense. It was as if he considered the valuable item on his person someone else’s property. No sane individual would expect a Dragon to return their valuables for nothing once they had them in their possession. Well, it didn’t matter, she supposed. The more immediate concern was becoming known to this powerful male and enticing him to father her first clutch when the time came. She could worry about other things later. A last, lingering feeling prompted her to ask one, final question.

 

“Those bags, brother: will I receive them as well?”

 

Hejinmal chuckled, perhaps taking comfort in the customary draconic avarice in her tone.

 

“I said everyone, didn’t I? Without exception. You will get yours too…”