\chapter{Ludmila Zahradnik}

What in the world just happened?

 

Ludmila stared down blankly at the lowered head before her, unable to comprehend why both the literal and figurative change in direction had occurred. In doing something entirely unfamiliar to her, something unintended had happened as a result – something she had no idea about.

 

“Uh…this is quite the change in attitude,” she wasn’t sure if she wanted to know what it wanted.

 

“You told me who you were,” he replied, “so now I know.”

 

“How do you know I am what I said?” Ludmila said, “Going by your reaction, I appear to have done something completely unintended.”

 

“Unintended?” The creature tilted its head to look up at her, “This is not an expression of intent, it is an expression of being. The soul cannot lie, and you cannot be any less than what you are. Claiming to be more is equally impossible. Even in the long passage of time, it is not easily changed – and if it is, then it is.”

 

The explanation did not make much sense – or did it? By doing something she didn’t fully understand the consequences of, he had come to some sort of perfect understanding…and now he was acting accordingly with the assurance that what he knew could not be untrue. If Ludmila wasn’t aware that she indeed did something along those lines, she might have wondered if she was actually dealing with some sort of lunatic.

 

Or maybe she was the one that was going crazy.

 

Rather than dwelling on it and inviting insanity for certain, she decided to address his request.

 

“You said that–”

 

The creature’s head turned sharply away from her, towards the village. Ludmila cut her words short, looking to see what had drawn his attention. Nonna was descending in their direction from the farming village.

 

“She is one of mine,” Ludmila said. “I called for her when you started attacking my sentries.”

 

Despite her explanation, the creature continued eyeing the approaching Elder Lich. She didn’t believe that hostilities would break out again, given the creature’s stark reversal in disposition but, if they did, she suspected that Nonna would lose just as one-sidedly as the Death Knight did. Scanning her surroundings for potential problems, she saw that two teams of the nearby woodcutters were still fleeing towards the road. Jelena’s head poked up from the field where the Death Knight had been standing sentry.

 

『The fight is over: you can go back to work.』

 

The men in the distance stopped and looked towards her. After a few seconds, they started walking back towards their worksites. She didn’t call Jelena to her, in the event that hostilities somehow recommenced. Looking around for a few more minutes and finding nothing else amiss, she turned her attention back to Nonna who had finally arrived.

 

“Did you leave right when I called for you?” Ludmila asked as the Elder Lich settled to the ground.

 

“Yes, roughly twelve minutes ago,” Nonna replied.

 

“That’s…unexpectedly slow,” Ludmila frowned. “I can run faster than that.”

 

“The Fly spell has limitations in speed,” Nonna said. “It is not the same as the natural ability to fly. For travelling longer distances, teleportation magic is instantaneous and more mana efficient.”

 

“You don’t have that, so you used Fly.”

 

“That is correct. Teleportation is not in my repertoire.”

 

Ludmila spent what time she could spare remedying shortfalls in her knowledge, and magic was one thing she focused on in particular. Beyond the spells used by Bohdan in the past, she knew very little and it was something she decided would be a crucial aspect of working knowledge as a noble of the Sorcerous Kingdom.

 

With Nonna on hand in the demesne, Ludmila was able to speak at length about the subject. She also had her demonstrate each spell she possessed so she could think on their potential applications. The majority of Elder Liches used as administrative servitors in the Sorcerous Kingdom all appeared to have the same set of spells, though it appeared that certain ones could do more. Nonna was capable of casting a few tier five spells, but they were few and limited to direct combat.

 

“Well it is good that you made it out here regardless,” Ludmila told her. “One of our Death Knights is on the ground over there…you can use Ray of Negative Energy to patch it up, right?”

 

Nonna looked over to the Death Knight torso lying on the ground nearby. Though the heat from the flames had dissipated, the odours of charred flesh and burnt debris still lingered.

 

“...how did this happen?”

 

“There was a…misunderstanding just now between this fellow here and the sentries,” Ludmila told Nonna. “He stopped before it was a total loss, so recovery is just a matter of time, yes? I will call one of the sentries at the village to take this post while you take care of things.”

 

“This will take a substantial amount of mana,” Nonna said. “I will heal it until movement is restored, then take it back to the village. Moren Boer should be available to assist.”

 

“Moren Boer can cast Ray of Negative Energy?”

 

“Yes,” Nonna replied. “He has been assisting with patching up servitors that take minor damage from workplace incidents. It is not much, by my measure, but it is something.”

 

“Do you have a record of all of this?”

 

“Only to the extent of gauging its performance.”

 

“Then start keeping track of the maintenance work,” Ludmila said. “If we are going to be employing magic casters in this way, I will have to figure out what sort of remuneration is suitable for their labour, er…mana? For the time being, make sure he only does so under your supervision until we figure it out.”

 

As she said so, Ludmila realized that Nonna wasn’t receiving any compensation for her magic, either.

 

“Speaking of which,” she asked, “do you receive a wage of some sort from the administration? It might be useful for comparison.”

 

“I do not.”

 

“…was that something I was supposed to be taking care of?” She furrowed her brow, “I thought the lease covered that, but you did not come with one.”

 

“All that is required of you is that you pay the lease under normal circumstances,” Nonna told her. “His Majesty’s summons exist to serve: we do not require wages. If there is something that we deem necessary, it is provided freely.”

 

“I see…that’s between you and the administration, I suppose. I need to find out what this fellow is doing here, so I will leave the Death Knight to you.”

 

They turned left Nonna behind them, and Ludmila called for a Death Knight from the village as they headed back towards the road. Jelena stood up from where she had been hiding: looking to her, then the strange creature walking beside her. The girl stuck out her hand towards him, and he sniffed at it for a few seconds.

 

“This female does not smell like your offspring,” he said.

 

“Good,” she felt the corner of her mouth twitch, “because I think I would remember that. This one is called Jelena: she is the daughter of one of the men working nearby. Speaking of names…is there one you go by normally?”

 

“I told you who I am,” it’s upper eye blinked up at her as they continued on their way.

 

“There is no…short form? Our people generally use names in the manner I first introduced myself, and I am not sure I can get your whole identity quite right anyways; is it offensive to be called in such a way?”

 

“There is no precedent for offence or otherwise,” he replied. “Our people live isolated from the world: it is a rare thing to encounter outsiders where we live. We only speak to others of our people, so there is no need for such things.”

 

Considering he had simply turned around and started to leave when she was unable to introduce herself properly, Ludmila imagined that they would not require anything like the names that others used. Having to call out his full identity in the manner that she just had her own, however…

 

“Then what about a title?” She asked, “Is there some position you occupy amongst your people? You are powerful enough to burn a Death Knight to the ground with seemingly little effort…”

 

“Destroying most Undead is a simple matter,” he answered, “their weaknesses are easily recognizable. If you insist on using one of these shallow appellations, then Volkhv. I am a Volkhv of the Krkonoše.”

 

The Volkhv’s words gave her pause. The terms were old: she only knew them as something her parents taught her when she was very young – before she joined her brothers under Bohdan’s tutelage. Volkhv had become synonymous with priest, yet it did not carry the exact same connotations as members of the priesthoods in the local Human lands – it defined a slightly different role than the ubiquitous term used by most implied.

 

“Krkonoše…is this the name of your people? Your nation?”

 

“It is the name of our people, who are named after the mountains to the west which we called home.”

 

Krkonoše was what Ludmila’s people called the range of mountains to the west, which extended all the way to the ocean. The windward side of the range, of which Warden’s Vale lay within, was cool, wet and windblown: thick with the vegetation which was its namesake. The range did have an official name, yet again their village’s name that described it had come out instead. These people had named themselves after the place that they lived, and their concept of their home matched her people’s own: creating an image of a region known to both.

 

If not for her upbringing, the more commonly known names for these terms would have probably been heard, and the full meaning lost upon the listener. She was beginning to understand why he thought that her use of language was shallow.

 

“Why did you leave?” Ludmila asked, “For what reason have you come here?”

 

“Because we decided that we could not stay,” the Volkhv’s coat rippled. “Three seasons ago, an evil star fell into the wilderness far to the west.”

 

“And just seeing this ‘evil star’ was enough to cause you to flee?”

 

“Not at first,” He said. “At first, we watched from our craggy peaks. We cast spells to scry the vast lands to the south – to divine what had befallen the low places. The source was veiled from us, but we watched as waves of ruin rippled out from where the star fell, over the peoples that dwelled there. Those that fought to defend their ancestral lands were captured or slain, heedless of tribe or creed. Many who fled were also captured or slain, but there were also those who escaped. We did not stay to determine the fate of the ones who cast themselves at the mercy of this great evil.”

 

They reached the old road, and Ludmila led them in the direction of the farming village. The Death Knight she had called stomped by to assume its post: it was several times faster than Nonna using flight magic.

 

“How many of your people died?”

 

“None. We were too far away: safe in our high mountain peaks, and we left long before the darkness could reach us. Our people went away before the first of the distant Zern enclaves fell into shadow.”

 

“Who are Zern?”

 

“An…insectoid people. Of a sort,” the Volkhv said. “As different from you and I as we are to each other, if not more so. They have dwelled in their holes in the foothills below our mountains for nearly as long as we ourselves have dwelled on our peaks. We were vaguely aware of one another, but nothing more.”

 

It was another race she had never heard of. The story of the Krkonoše was recognizable enough, however: they were refugees fleeing what they considered a great threat. Given the power of the individual trotting alongside her, Ludmila was compelled to learn more, but information usually came at a price.

 

“So you arrived here, fleeing this great evil that has befallen the land; now you wish to enter mine.”

 

“That was our original purpose: to cross this great river and continue over the mountains again, until we could continue no longer. It was...until I came to know who you are.”

 

“Why would knowing who I am change your decision to continue fleeing?” Ludmila asked.

 

The Volkhv’s central eye blinked up at her, then it tilted its head to look at her with one of its goat-like eyes.

 

“Knowing who you are is all that there is,” he answered. “Upon hearing it, I knew your place in this world…and there is no better place in this world for my people than under your protection, Warden.”

 

“I will be perfectly frank and tell you that I have absolutely no idea how you arrived at this conclusion. You should know how much more powerful you are compared to me, yes?”

 

“In these measures you convey, yes. But that does not matter. What matters is what matters – what the world has decided you are to be.”

 

“Are you talking about something like fate?” Ludmila asked, “Did you use some magic to divine my future?”

 

“It is not magic,” the Volkhv answered, “it is soul. The whole has determined your parts; your paths; your place. You gave to me your name; I returned it to you. Even so, you did not understand?”

 

“I understood what I conveyed to you, and I understood what you called me – but I cannot understand why we understand it so differently.”

 

“I understand what is,” he said. “You will come to understand as well. You cannot be any less than what you are, even if you do not understand what you are. Understanding is not required for this to come to pass.”

 

Currently, what she understood was if she was subjected to any more understanding, she might permanently start talking like the Volkhv. Or her head might ignite like her Death Knight. In asking too much, she had learned too much to digest.

 

“Then let us discuss the matter at hand,” Ludmila cleared her throat. “Your request is to move into my territory, but do you unde–realize what that entails?”

 

“We will come under your management as a part of the land,” the Volkhv replied immediately. “You will do what is necessary, and we will do as you say.”

 

Very broadly speaking, that was what would happen. It was not language a noble or some learned Human citizen would use, however. The way he appeared to exercise thought and employ vocabulary was more in line with a Druid or a Ranger, whose scales of judgement assessed things holistically rather than singularly.

 

“As I said,” he spoke in her silence, “I know who you are. What is, is. My people will be in your care, and we would not protest even if you saw fit to kill us all.”

 

“Even if I had a very good reason,” Ludmila told him, “it is not a decision that I would make lightly.”

 

“I know.”

 

The rational part of her mind still screamed at the reasoning that would not make any sense whatsoever if viewed from the perspective of a Human Noble. The other parts of her, however, accepted it for what it was. The fact that any Human Noble would immediately accept such a one-sided agreement in their favour while she fought the reasoning due to the part of her that had already accepted it was an irony that irritated her to no end.

 

Ludmila sighed. She would just have to navigate this confusing situation in what way she could.

 

“Then…how many of your people have come with you,” she asked the Volkhv, “and what do you need to live?”

