\chapter{Ludmila Zahradnik}

The evening grew long, and it looked like they were approaching the end of what needed to be transcribed. A tall stack of pages had manifested as a result of their work, and it was something that would probably take two or three weeks for Ludmila to study properly.

 

The routes between the Dwarven cities were due to be employed in a week’s time, and Lady Shalltear seemed to have put the most thought into them. There was little Ludmila could contribute there, especially considering she had no knowledge of the Dwarven Kingdom and their lands.

 

The last point to visit was the prospective route to the imperial capital of Arwintar.

 

“There’s so much traffic to Arwintar that even Frost Dragon flights are a drop in the ocean by comparison,” Ludmila noted.

 

“Yes, despite that, I decided it would be a good idea to connect the Imperial capital,” Lady Shalltear replied. “We should be able to get an idea of how things are out there as well. Considering what we’ve discussed today, I feel that the only role that the route to Arwintar would serve at this point is for express freight and high security shipments. Even a formation of their air cavalry cannot contend with an Adult Frost Dragon if we get some equipment on them.”

 

“Isn’t that a problematic stance to take with a client state? If something is smuggled into their cargo…”

 

“We will be using the military aviary there, so if anyone manages to get it past all that it’s the Empire’s fault. Once it’s airborne, it’s our problem and they would dare not provoke us after the fact.”

 

“I assume we would still cooperate if there is sufficient justification provided for an inspection,” Ludmila said. “Having something undesirable come across the border might result in problems that could have been averted.”

 

“We will investigate it on our end if we receive such a request,” Lady Shalltear said. “If it’s something potentially hazardous, we will investigate it en route ourselves as well. The Ministry of Transportation is a national department of the Sorcerous Kingdom: lines must be drawn to define the relationship between us and our client states. I do not intend for our officials to be belligerent or abrasive when it comes to these matters, but there should never be a case where anyone from the Empire perceives that they have authority over our agents.”

 

“I understand,” Ludmila made an additional note. “Hopefully no one tries to put on airs or push their luck when it comes to their expectations involving the service. Then again, I can’t imagine that anyone would try to pick a fight with our staff.”

 

Lady Shalltear flipped through to the next page of the notepad, which was entirely blank. It appeared that they had completed what they had set out to accomplish for the day. Ludmila began to gather the loose documents on the table.

 

“This gives me quite a lot to study,” she said. “I will send word for my household to investigate the cargo rates in E-Rantel while I slip in what I can between my duties here. When I’m in the city, I will see what I can learn from Liane about how the transportation business works.”

 

“Are you not interested in including Warden’s Vale as a destination for the Frost Dragons?” Lady Shalltear asked.

 

Ludmila’s hands slowed as she rolled up the extra maps that Lady Shalltear had provided for her.

 

“I’m too small for that, aren’t I?”

 

“You’re planning quite a lot of expansion, weren’t you?” Lady Shalltear tilted her head, “How many per village was it again?”

 

“Roughly 200 to 250 people per village. It will be no more than 1250 between the five villages planned…the golems I’ve requested won’t be free for a little while, though, so it will probably take until the end of the year before we can clear all the space and structure the terraces and foundations. Construction will be completed in the winter while the fields are being prepared at the same time.”

 

“What about your port town? I recall that most of your ambitions lie here.”

 

“I’m uncertain how quickly that will progress, to be honest. My hope is an additional 1000 tenants by this time next year.”

 

“It’s on the small side for a town, but that should be more than enough to include Warden’s Vale as a destination. Though having the river is quite a boon, you’re still isolated for the time being having only a single ship – if anything happens to it, you’ll be sunk.”

 

“Are you certain, my lady?” Ludmila frowned, “Wouldn’t that seem like I’m taking advantage of my position as part of the staff for this project?”

 

“They might harbour some feelings on the matter,” Lady Shalltear shrugged, “but considering that you’re basically one hundred percent of my tax revenue and those taxes are going straight into the transportation network, I hardly think such complaints would be justified. Also, the idea that you are considered important enough to include as part of the major transport routes will help you attract people faster, no?”

 

“It might,” Ludmila admitted. “You are correct, I think – the misplaced humility you mentioned is a lot harder to keep in check than it seems.”

 

“As long as you’re learning what is appropriate. The faster your demesne grows, the more of your taxes I can put to work on this project…speaking of which, you never did specify just how much these taxes were. ”

 

Ludmila realized that she hadn’t, and reorganized the thoughts she had originally put together for the proposal. Taking a sip of tea, she launched into a summary of the state of her finances.

 

“Tenant shares, Undead labour, Undead security and various costs involving administration, maintenance and fees will take up forty percent of my total revenues. If you don’t mind, I would like to ask for a tax rate of ten percent for the time being: the remaining half of my revenues can be turned directly towards further development of industries in my fief. My revenues are purely from commodities that are directly affected by the existence of Undead Labour, so next season I imagine they will be significantly diminished due to the abundance of it throughout the Sorcerous Kingdom.”

 

“I have no idea what these numbers mean,” Lady Shalltear stated flatly. “I haven’t ever received taxes before. Is ten percent a small amount?”

 

“If it was one of the more developed territories, yes,” Ludmila said. “A twenty to forty percent tax on demesne revenues is more along the lines of what the other nobles see; this is in addition to trade taxes, tolls and any additional measures raised by their liege. As a border territory, we actually received a small stipend rather than a tax: to maintain security along our part of the frontier. This security is, for the most part, maintained by His Majesty’s armies which are leased by every noble now – though their organization is still mostly up to each noble to handle. I determined that I should be paying at least some taxes with this being the case.”

 

“I see…so you want to stay ahead of the falling prices for your goods by investing into industries that will not be adversely affected by the markets being flooded by Undead labour. I believe you mentioned this some time ago?”

 

“That’s exactly correct,” Ludmila nodded. “If I don’t have the capital to invest in new industries, I will be at the mercy of the plummeting price of basic commodities over the next few years. Revenues will collapse in line with the markets for these goods, so taxes will similarly become poor if nothing is done.”

 

“Mmh…this is something you’re better at than I am, so I’ll leave it to you.”

 

“Thank you, my lady. Hopefully I’m able to manage things well and bring prosperity to my fief…though I should at least build something to accommodate visiting Frost Dragons.”

 

“They’d probably be perfectly happy lairing up in these mountains somewhere,” Lady Shalltear said. “The main thing they seem to complain about is the lack of space in the city. You might want to make sure they are somewhere your ability can reach them when they’re resting, just in case. I will send one of my Vampire Brides over once they are done working up north with the Dwarven migration.”

 

Rather than relying on the Elder Liches who reported to the central administration, Lady Shalltear had opted to post her Vampire Brides in the offices of the transportation network instead. Ludmila had no idea how many she actually had, but her liege assured her that there were enough for what was planned so far.

 

“I’m not sure what sort of accommodations are appropriate for one of your handmaidens,” Ludmila said. “My labourers will still be busy with the farming village so there’s little in the way of construction going on in the port, but I have two extra beds here in my manor if she doesn’t mind.”

 

“It’s not as if they need to sleep,” Lady Shalltear turned her head to look at the four beds tightly arranged to the side. “A small desk and room to organize parcels is fine until you can set up a proper office for her.”

 

“I can place a desk in front of the manor, then. She can use my hall to store parcels…does that sound alright?”

 

“It should do.”

 

“What about food?”

 

“There won’t be a need for any. She’ll have something brought from home if she feels like having something.”

 

“The arrangements will be seen to before her arrival,” Ludmila said. “There won’t be any friction between your servants and those of the administration, will there? It’s not unheard of for Human political factions to experience such things…”

 

“I don’t think it’s likely to happen,” Lady Shalltear replied, “but if anything does, it will be from Albedo’s side – maybe something along the lines of petty administrative harassment. The Vampire Bride will be instructed to keep to her own business with the transportation service. She’ll also know who you are so she will heed what you say in matters related to your duties. I’ll be counting on you to keep things in order if anything does happen.”

 

“I will do my best to keep the peace, my lady,” Ludmila nodded.

 

“Ah – don’t kill her though: the new one won’t have the same training, so we’d be losing all of her work experience from the Dwarven migration.”

 

“It would be difficult for me to justify such a thing if she’s just working as a logistics officer…I don’t think I could harm her anyways.”

 

“That’s a good point. Still, other things can happen, and she’ll be in your care.”

 

“Of course, my lady,” Ludmila said. “Was there anything else you could think of for this evening?”

 

“Not particularly,” Lady Shalltear tapped her lip lightly with a finger. “It’s late enough that I’ve dodged all of the banal events Albedo has probably organized. I will speak to a few people on some of the things we’ve discussed today and see if I can come up with anything to improve on what’s already planned.”

 

Ludmila escorted Lady Shalltear through the hall of the manor and back outdoors. Night blanketed the barony in a canopy of stars, and no signs of activity could be seen or heard over the village. The Death Knight with its Squire Zombie standing guard at the door stood at attention as Lady Shalltear stepped out and onto the lane.

 

“Hanzo,” Lady Shalltear said.

 

A familiar, lithe, figure wrapped in some sort of black uniform stepped out of the shadows. Ludmila did not have even an inkling of its presence before it revealed itself.

 

“Gather the others,” her liege instructed, “we’re headed home.”

 

The Hanzo dashed away, its form wavering in her sight as it used some unknown ability that was foiled by her Talent. It was less than a second before it disappeared around the hill. Ludmila turned back to address Lady Shalltear as they waited.

 

“When will we next meet?” She asked.

 

“I will return the day after tomorrow, two hours before noon. I have to check up on a few things in the meanwhile, and I believe you said you had some catching up to do here. Cocytus should be back at the lake by then so I’ll see if I can arrange the meeting that he wanted....”

 

“Should I be making any preparations for this meeting?” Ludmila asked.

 

“Hmm...not that I can think of,” Lady Shalltear answered. “I still have no idea what he wants: only that he is interested in meeting you specifically. Given his nature, I can’t imagine it’s anything bad – he may just be curious what Human warrior vassals are like, as he is a warrior vassal himself.”

 

“I hope I do not disappoint him. I will see what I can do about preparing a presentable appearance, at least.”

 

The Hanzo returned, lining up along the village lane with four more of its fellows. Lady Shalltear opened a Gate and looked around one last time.

 

“I’ll be off, now,” Lady Shalltear said. “I will contact you if anything comes up, Lady Zahradnik.”

 

Ludmila spread her skirts and dipped her head in a curtsey.

 

“Have a pleasant night, my lady.”

 

Lady Shalltear disappeared into the portal, followed by her escorts. The Gate over the village lane closed silently, and Ludmila was left standing in the cool wind with Aemilia at her side. They returned into the manor to prepare for the night, and it was only until after they both lay in their respective beds that Ludmila spoke.

 

“Thank you for your hard work today, Aemilia.”

 

“I-it wasn’t a problem, my lady,” Aemilia replied. “I am your lady’s maid, after all.”

 

“We were at it for hours; it must have been tiring for you. Having a member of the Royal Court suddenly appear and all.”

 

The sound of rustling sheets came from the side before her maid turned in her bed to respond.

 

“Just a little bit, perhaps. Kept worrying about a thousand little things, and then there was the village stew – not that it’s bad, I think it’s better than most of the food served in the city, actually.”

 

“I understand what you mean,” Ludmila smiled. “I was worrying about all those same things as well.”

 

“Really? It didn’t actually seem that way, my lady. I mean…you’ve gotten so much closer with Lady Shalltear.”

 

“...I have, haven’t I? I guess most of the difference is from my end – she’s never displayed the same level of formality when we’re not in a public setting, and I’ve always felt like she’s been trying to draw me closer to her for some reason.”

 

“Why is that?”

 

“I think you’ve heard a part of it this evening: in at least some ways, she feels that we are somewhat alike. When she interacts with those she feels familiar with, she barely seems a powerful member of the Royal Court at all – especially when she is with Lady Aura or Lord Mare. Whenever I see them together it feels like they are like a boisterous family more than anything else. They are nothing like the haughty, cold, highlords that I imagined those in their position would be. While she may appear to act the part to those who look in from the outside, Lady Shalltear is actually possessed of a pure and passionate character, embracing the intimacy of those she becomes comfortable with.”

 

That same character also meant that those on the wrong end of her convictions were met with a decisive outcome, but Ludmila thought this an admirable quality as well.

 

The sound of sheets rustling came from the side again, followed by a long sigh. Ludmila turned her head to see Aemilia staring up at the rough stone ceiling.

 

“What’s wrong?” Ludmila asked.

 

“I didn’t know,” Aemilia muttered.

 

“You didn’t know what?”

 

“They’re Undead!” Aemilia moaned, “I didn’t even realize it until today. Lady Shalltear and her handmaidens, they’re all Vampires, aren’t they?”

 

“Yes,” Ludmila replied. “Though I figured with all the time you spent together with them that day you’d have noticed.”

 

“Ughhhhh…” Aemilia continued in pained tones, “You know, on the day when we first went out into the city, I kept cowering away from all the Death Knights and things that were obviously Undead, but I felt perfectly fine around them. Then, when we started riding around, I talked about how frightening all the Undead were around the city: I thought that they must have felt the same way. How can I bring myself to face them now? I must have sounded terrible.”

 

“Did they say anything about it?”

 

“They didn’t reply to that at all, but they did eventually open up as we found things of common interest to talk about. While you were away out west, I saw one of them on the street and just happily called out to her. When I mentioned that I was going around visiting the boutiques of the city she seemed interested in what sort of fashions were on offer, so we just went around all day planning out your wardrobe. At least a quarter of the ideas must have been from her.”

 

Ludmila recalled the sheer fabrics of the Vampire Brides’ scant garments.

 

“I hope I’m going to be able to wear these outfits without needing to hide under a box.”

 

“There shouldn’t be anything to worry about. They’re all very tasteful, and the touches she made were quite light. Mmh…they have the glowy red eyes and everything too – I didn’t want to inadvertently insult them by bringing it up, and then I just ended up assuming it was Darkvision or something. How should I apologize, my lady?”

 

“Lady Shalltear never mentioned any grievances from her handmaidens…”

 

“They don’t seem the type to complain,” Aemilia said, “and it’s not uncommon for servants to hold in a lot of things…maybe I can offer them some clothing…maybe blood?”

 

“That might not be a good idea,” Ludmila replied. “Don’t you get turned into a Vampire if one bites you?”

 

“What about a bottle then? I could just collect some and…”

 

“It will clot and dry up. While I am not a Vampire, that doesn’t sound very appetizing at all.”

 

A dissatisfied sound rose from Aemilia, and she tossed about again.

 

“I will ask Lady Shalltear what they might like as gifts,” Ludmila said. “Until then, please don’t do anything crazy. I’m not sure how the migrants would feel if they saw a manor painted with blood. We should get some rest: we’ll be having another long day tomorrow.”

 

“Yes, my lady,” Aemilia replied. “The Undead…they’re not so bad, are they?”

 

“Those of the Sorcerous Kingdom are not; some of them I even prefer over a lot of what we Humans have to offer. Just don’t run around trying to get along with the ones that pop up on their own, though: they’ll still just try to kill you on the spot.”