\chapter{Ludmila Zahradnik}

The sounds of someone working at the back counter nearby stirred Ludmila from her rest. She stretched her laziness away and, in doing so, her head poked out part way from under her covers. In the main living space of the manor, she saw Aemilia working to prepare breakfast. The rich aroma of breakfast filled the air, and the grey light of dawn cast dim shadows from the hall around the corner.

 

“When since have you been up?” She asked her maid.

 

“Hmm...two hours or so, I think?” Aemilia answered, “When I went out to draw water, Wiluvien was already out in front of their place next door. They’re still learning their way around here, so I made some breakfast for them.”

 

“You early risers are all crazy,” Ludmila muttered as she watched her maid lay out bowls of warm stew. “Make sure you are getting enough rest. I am usually late to bed and late to rise, but you always try to keep up with me at night. Once the Linum sisters get used to things around here, you should let them handle their share of the work.”

 

“I will, my lady,” Aemilia said. “Thank you for your consideration. It might be just a little bit hard to stay in bed with them moving around in here though.”

 

Ludmila winced. She knew her maid did not mean poorly by it, but the comment still brought with it the fresh memory of hosting a member of the Royal Court in a hole in the ground. Her ‘manor’ was essentially a combination hall/kitchen/sleeping space that was not that much larger than the other dwellings in the hill. The granite walls, ceilings and floors were hewn straight into the stone.

 

“If Lady Shalltear had said anything about this place,” Ludmila said, “I would have curled up and died right on the spot.”

 

“I’m sorry, my lady,” Aemilia turned contrite. “I didn’t mean that.”

 

“Oh you certainly did. Even I feel that way when outsiders come in.”

 

“You’re right, my lady…I’m still sorry, though.”

 

Ludmila threw back her covers and swung her legs off of the bed, feeling the cool stone of the floor under her feet.

 

“There is no need to be,” she said. “I’ve lived here all my life, and I won’t deny it for what it is. All of the labour I can pull into the demesne is being focused on developing that strip of farmland, so please bear with me until next year when we can finally start working on the port town.”

 

“I have little to complain about,” Aemilia replied as she completed arranging the last of the meals, “and none of it is truly serious. Just three months ago I was desperately trying to enter even some insignificant household as a scullery maid with little but a hope and a prayer, and now I’m the lady’s maid of a frontier lord. I’m pleased beyond belief to live out what I thought could only be a dream: to play my small part in a grand tale that only ever continues to unfold before my very eyes.”

 

Ludmila shuffled to a stop on the way to the chest of clothes at the foot of her bed.

 

“That’s, uh…wow. I hope that I am not slaying any Dragons in these dreams of yours – the only ones I know of are on our side.”

 

“You never seem to disappoint, my lady,” Aemilia smiled. “I’m always excited about what will happen next.”

 

With that, she picked up the first meal and headed to deliver it next door.

 

Ludmila shook her head wordlessly before changing into fresh clothing. She thought that the passage of time would have the effect of dampening the fantastically lofty expectations of her maid, but they only seemed to grow instead. After moving over to unlock her cabinet and withdraw several folders, she went over to the counter, tossed a roll of bread into her stew bowl and walked everything out. She peeked out of the hall window before sitting at her desk to review the day’s tasks.

 

After completing the morning’s preparations, she would head out to the farming village and get all of the petitions that had piled up over the last few weeks out of the way. Following this, she would head out to the logging camp to check on their progress with land clearance. On the way back, she would take a look around to inspect the progress on the village’s construction before returning to the port for the evening. It was a deceptively short list that would probably keep her busy until the evening.

 

The door opened, and she looked up.

 

“How is the Linum family doing?” Ludmila asked.

 

“Much the same, it seems,” Aemilia replied, tapping her boots on the doormat. “I don’t understand, my lady – Ilwé seems perfectly healthy in body, yet she’s so listless. Lluluvien and Wiluvien received their training under Miss Veyron around the same time I did, and they were in nowhere near as bad a shape even after their ordeals. When they came into your service, I could see them get better by the day.”

 

“As far as I understand,” Ludmila said, “their mother was with House Fassett even before they were granted the county by House Vaiself. That would mean that she has been a slave for at least 150 years. I would guess being a slave for what basically amounts to two Human lifetimes has left quite a mark on her life. Maybe she just needs to slowly recover...or maybe she will never fully return to who she used to be, if she even remembers. Not even her own daughters know who she truly is, or where she is from.”

 

Aemilia clutched her apron tightly in her fingers as she scowled down at the floor. Clearly, she did not like Ludmila’s assessment.

 

“There must be something we can do for them, my lady,” she said. “She must have suffered so much…it’s not right that even after she’s free, she remains chained to her past.”

 

“I do not find it a satisfactory answer either,” Ludmila looked back down to her work, “but I am just a Noble, and I know next to nothing about Elves. Perhaps the answer will present itself in time.”

 

The sound of her maid’s steps receded into the back of the manor, and Aemilia paced out again with another meal. After delivering breakfast, she came up to the desk with a hairbrush in hand.

 

“Shall I accompany you today, my lady?” Aemilia said as she stepped in behind her and started straightening Ludmila’s appearance.

 

“Most of it should be receiving petitions in the village,” Ludmila said, “and going around to make sure everything is proceeding smoothly. It is probably best that you remain here – I will send word if I need anything.”

 

“You’ll be gone for the entire day?”

 

“I should be home in time for supper,” Ludmila replied. “About a dozen households have been furnished so, rather than dealing with the petitions themselves, most of my time will be spent trying to ensure that the people have a clearer idea of what’s going on for the short term. I will also have to keep an eye out for any potential problems along that vein, especially: these migrants from the interior seem to keep their heads down when it comes to dealing with authority instead of just speaking up properly.”

 

“As far as I understand, my lady,” Aemilia said, “most people are used to dealing with their own village chiefs, and it’s those leaders that bring forward problems to the next level of administration. A regular tenant doesn’t expect to suddenly appear in front of a noble. The gap is just too wide: all the newer people that came in yesterday were shocked at the realization, and half of them could barely put their sentences together.”

 

“Well, their ‘village chief’ is going to be an Elder Lich, so if they cannot even speak to another Human I cannot imagine how they will fare with the Undead.”

 

“I imagine they will do just fine,” Aemilia said, “once they become used to it. It’s more a matter of hierarchy rather than any personal problem with you, my lady. It would be as if I had a question about your wardrobe and found myself asking the Sorcerer King instead. It just feels awkward and entirely out of place, leaving you wondering if you should really be there or not wasting an important person’s time.”

 

“I still want to knock them out of this docile nature of theirs,” Ludmila muttered. “Frontier citizens should not be so timid. If there are problems, they should communicate them; it is not as if they are enemies.”

 

“This attitude you desire for your people might be beneficial for frontier life, my lady,” Aemilia admitted, “but what happens when the demesne has more people? A household is kept in order because the junior staff report to the senior staff, and those senior staff will only approach the head of the household if an issue requires their attention. I can’t imagine everyone directly coming to you with their problems when there are thousands of families in the fief.”

 

“We will have enough administrative assistants to handle that by the time it gets to that point – I just meant that they shouldn’t fear communicating any problems they might have. Speaking of which, have you noticed anything in the village here that needs to be addressed, Aemilia?”

 

“Not much to be honest. Most of the people just seem to be waiting to be called to move into their new homes. The children around the village keep finding strange things to do with the Skeletons, though.”

 

“Strange things?”

 

“Yes...just this morning before you woke up they were making them dance in a circle – they had a small crowd watching by the time I came across them.”

 

Recalling the request to be allowed to paint the Undead labourers, the odd image of colourful Skeletons dancing in a circle arose in her mind. She waved the ridiculous thought away.

 

“As long as they aren’t doing anything dangerous, I suppose,” Ludmila told her. “The more comfortable they are with the Undead labourers, the better…who knows, they may figure out some useful things along the way.”

 

“I will let the people in the harbour know your intentions, my lady,” Aemilia said, then paused in thought. “You know, it’s only a matter of time before the boys start using them as soldiers to have battles with.”

 

“…you are absolutely right about that. They should hold off until I can investigate how safe it is myself. Something like that seems like it could go any number of ways.”

 

Ludmila didn’t actually think it was a bad thing: it meant that the next generation might possibly produce commanders who could assist with the security of the demesne, or even find a place in the Sorcerous Kingdom’s armies. She already had loose plans to raise new Rangers for both purposes, but if she could train an officer corps that could increase the performance of the nation’s Undead armies, the vague idea that the town could support an institution which carried forward the militant traditions of Warden’s Vale made the possibility that much closer to grasp.

 

In addition, it would further increase her fief’s value to the Sorcerous Kingdom, creating yet another unique industry; maybe it was even possible to secure a portion of the national budget to develop it if she could prove her own usefulness to the Royal Court.

 

“Is something the matter, my lady?” Aemilia asked after several moments of silence.

 

“Not particularly: I was just thinking about something,” Ludmila answered. “Do you think that most of the children you’ve seen will follow in the footsteps of their parents?”

 

“I’m probably not the best person to ask about that, considering my own path,” Aemilia frowned. “I suppose that it would depend on what their family does, and whether there’s room for opportunity. Since you’re planning on developing five farming villages in total, I would imagine that not everyone would be able to become a farmer when the Undead labour reduces the need for manpower so drastically. Those people would have to move into the town you’re planning here…I think that was the idea, anyways?”

 

“That was the basic idea. It should still take a while to populate all the villages, but I am trying to figure out whether I need to develop the town more rapidly than expected. I will have a population with basic education entering the town, but aside from their journeymen, I will still need ways to train the ones who are not. I still have not figured out what sort of industries would be best suited for this port.”

 

“I’m just a weaver’s daughter, my lady,” Aemilia apologised. “The fibres extracted from the marsh plants are quite sturdy, but, while they are exceedingly abundant, they’re only suited for plain textiles at best so I’m uncertain whether they are worth exporting. That’s the only thing I can really think of in terms of what can be done here. Ah, please stand when it is convenient for you: I need to check over your dress.”

 

Ludmila rose and absently stepped out into the open area of the hall as she mulled over things. She still had no real exports aside from excess agricultural produce every harvest: commodities that were bound to collapse in value over the next few years, if not all at once. There were many ideas that were promising, but still none that she could yet consider a solid anchor for the fief’s economy. Her saving grace was that they were mostly self-sufficient now, meaning that she had some leeway in experimentation using her available tax revenues.

 

Aemilia’s hands moved lightly over Ludmila’s outfit as her maid continued her work. The dress was one of the first that her lady’s maid had ordered from the city: she had actually located the shop that had designed last year’s outfit and had them recreate it with slight changes. It had been adjusted to fit her slender proportions better, and the materials were more suited to the rough conditions that they would be exposed to in Warden’s Vale.

 

The overall image it presented, as well as how the various parts of it worked, had also been ‘improved’ upon: altered to match the strange image that Aemilia always seemed to attribute to her – it felt like she could literally fight in the thing. The effect was striking; even in the city when she had wandered around to test it out briefly, she was clearly recognizable in the crowded streets of the city as some sort of gallant noble figure. It felt that starry-eyed looks followed her wherever she went and, being trained to not attract attention as a Ranger, it was awkward in more ways than one.

 

“Alright, it looks like we’re good here…”

 

Aemilia rose and circled around Ludmila one more time, peering carefully over her form. She stopped with her hands on her hips and nodded to herself with a satisfied look.

 

“Will there be anything else, my lady?”

 

“No, I should really get going if I want to come back while dinner is still fresh,” Ludmila said. “If anything happens, let me know right away.”

 

Gathering all of her work on the desk into a bag, she slung it over her shoulder and made her way towards the door.

 

“I will, my lady,” Aemilia curtseyed. “Have a safe journey.”