\chapter{Ludmila Zahradnik}

Lyndon Roscoe removed his hat before bowing roughly. He stayed that way, until Ludmila had to wave him away so he could rejoin his son. Ludmila and Jelena remained long enough to watch the tall pine crash to the ground with small frowns on their faces before turning to continue along the way along the edge of the forest.

 

Progress in clearing was proceeding according to schedule, but Ludmila felt things were going far too slowly. Clearing the strip of farmland was a crucial stage in her plans, yet it was only the first. She still needed to build the town, expand the harbour and figure out how to improve her capacity for transport. While doing so, she lost crucial time in securing the ever-shrinking pool of skilled labour that was still loose in the duchy. While the other territories were more than happy to let go of tenants who could be replaced by cheaper Undead labour, the exact opposite was true for those industries that Undead labour could not impact so easily.

 

She required the revenues generated from the farming villages to begin investing in the town’s industries but, with every passing week, she felt that the time it would take to complete the terraces and the farming outposts – roughly eighteen months – would leave her at the mercy of changing economic conditions. Thus, she had decided to lease the six golems from the central administration to speed things along.

 

In addition, Lord Mare’s unexpected interest in her plans was a great boon and her projections improved considerably as a result. In the end, the time required to finish this stage of development had been reduced to six months. Even so, Ludmila still felt time and opportunity continuing to slip through her fingers as the days went by – compared to Clara’s progress in Corelyn County, the development in Warden’s Vale was like a molehill beside a mountain.

 

Not that they were competing. Clara always happily snapped up the timber sent downriver to supply her own development, and Ludmila could trust her to pay fairly and on time. Clara would be purchasing all of her grain exports to keep up with the demands of her greatly expanded demesne, which specialized in vineyards, orchards and crops of various low-growing fruits and vegetables, as well as the culinary and medicinal herbs that grew in the same space.

 

She had apiaries in great abundance as well; her entire demesne was a land overflowing in luxuries: spices and herbs; oils and perfumes; wines, mead, fruity beverages and deserts – all of which the existence of Undead labour had minimal impact upon. If anything, the burgeoning population that resulted from the abundance of food in the future would drive up the prices of her goods, making her even wealthier than before.

 

One could not help but envy her position, yet Clara did not rest idly in her advantage. Her entire territory continued to improve in leaps and bounds as she pursued what nearly anyone would consider a nigh-impossible vision for her realm.

 

Ludmila, on the other hand, was barely started. She and Jelena walked slowly through the dried piles of cleared undergrowth while they watched the next woodcutter team. A Death Knight stood watch over the treeline, yet she continued to scan her surroundings. As with most of the Sorcerous Kingdom’s Undead forces, the towering sentry was not actually entirely suited for being, well, a sentry.

 

They were excellent in defending against threats in plain view, which made them ideal for guarding cities and towns. Out here, however, she had to combine them with the Bone Vultures overhead to keep even modestly sneaky threats at bay. The woodcutters were made aware of this as well – if they felt that something was amiss, they were instructed to run to the nearest Death Knight and make it aware of the situation.

 

She continued to note the changes since her last visit, until a casual glance towards the western slope of the valley stopped her in her tracks.

 

There was a grey something making its way through the undergrowth along the edge of the clearing. It was certainly nowhere near as large as the feline Demihuman that was encountered several days ago: going by the trees and bushes it was traversing through, it was not even a metre high.

 

“Do you see that?” She asked Jelena.

 

The girl peered in the direction Ludmila indicated for a while, then shook her head. Since an untrained village girl could not detect it, despite her natural aptitudes, she thought that the creature might at least have some inherent skill at concealment. That didn’t make it an immediate threat, however: many animals were naturally stealthy.

 

“I’m going to take a closer look,” she told Jelena. “Head back to the Death Knight and wait there.”

 

Jelena immediately turned around and retraced their steps. Looking to the sky, Ludmila called over two Bone Vultures patrolling overhead and stalked towards the slope. She was keenly aware that she had no armament, so she would need to rely on the Undead under her command if her quarry turned out to be hostile.

 

The grey colour appeared to be from some sort of hide or coat, giving the creature a roughly sheep-like appearance. Except this sheep appeared to have a set of branched antlers extending from its head and over its back. A tail with a spaded point twitched back and forth as it continued through the trees in a strange, loping fashion. It stopped, and Ludmila froze in place as it reared up on its hooved hind legs, grasping at a nearby trunk with one of its three-toed forelegs. It sniffed at the air cautiously, but did not seem to be aware of her presence.

 

It continued standing there and, after a few seconds, Ludmila realized that, unlike a sheep or a deer or whatever strange mix of animals it appeared to be, this creature did not have two eyes: it had three. The third eye was set on its forehead, and it was staring straight up at the sky overhead.

 

Ludmila looked up and silently instructed the Bone Vultures to fly away to safety. Before they could wheel back around, two bolts of silver light streaked down from the sky and drove them violently into the debris of the cleared field. Masses of unpleasantly familiar vines snaked out of the ground to bind the two flailing Undead before they could right themselves again.

 

The creature turned its attention in her direction, and Ludmila heard the rapid approach of metal-shod boots. The Death Knight sentry darted by her with a roar, plowing through the debris with its shield leading the way and flamberge held high. It didn’t quite make it halfway between them, though, as another set of vines whipped out and anchored it to the ground. Ludmila half-expected Jelena to appear but, thankfully, the girl hadn’t doggedly tried to follow her instructions to stay with the Death Knight.

 

The creature returned to all fours, loping out from the trees. It sized up the Death Knight with an unconcerned air even as the powerful Undead being glared back at it from merely twenty metres away. Its apparent composure caused Ludmila to be uncertain of the outcome, and she turned and called out towards the farming village.

 

『Nonna, I need you out here now.』

 

She felt the drain as she cast her voice to the village roughly four kilometres distant. The ability still gave no indication as to whether it succeeded or not, but, hopefully, it reached its intended target. The sight that greeted her when she turned her attention back to the standoff continued to build on her uneasy feelings: the creature was now floating in the air, roughly ten metres from the ground and rising. It stared down at the Death Knight with the same, unruffled attitude. The Death Knight, its legs still bound by the entangling vines, bent over to lift a boulder the size of Ludmila’s torso out of the ground before it.

 

“「Eye of the Storm」.”

 

With a voice that sounded oddly exactly how Ludmila thought a sheep would if one could talk, the creature cast a spell. The Death Knight hurled the boulder but, when the projectile came within three lengths of its intended target, it was cast aside like a piece of straw. Leaves and debris were being swept up from below, slowly forming into a swirling sphere surrounding the creature at roughly the distance that the boulder had been so easily deflected. A gnarled branch and a smaller stone flew up from the Death Knight as it attempted to hit the creature again and again to no avail.

 

The creature continued to look down from it’s barrier of wind; its sheep-like voice sounded over the roar of the frustrated Death Knight.

 

“「Inferno」.”

 

The Death Knight exploded into flames. Its restraints instantly burned away, and it ran forward all alight, leaping from below its tormentor in a vain attempt to reach it. The Death Knight finally threw its flamberge and its arm came off at the shoulder, still holding the hilt of the weapon. The flaming limb grasping the massive blade was flicked away with no more difficulty than any other projectile that had come before.

 

Ludmila finally rose from her concealed position, quickly coming forward in an attempt to salvage the situation.

 

“Stop!” She called up to the creature, “Why are you picking on my sentries?”

 

The creature looked down at her – or rather, it tilted its head to focus its central eye on her. The rectangular pupils of its other eyes kept watch on its surroundings.

 

“You come to the defence of the Undead, Ranger. Why?”

 

“How do you know I am a Ranger?”

 

“It is Druids and Rangers that can traverse over rough terrain so effortlessly. You do not have the sense of being a spellcaster.”

 

It was nice to be immediately recognized as a Ranger, for once. The Death Knight’s other arm burned off.

 

“You have entered my territory,” Ludmila said. “Is it your intent to challenge us for it?”

 

“The Undead carry risks to the living,” it stated. “This is simple to understand, yes?”

 

“These Undead are under my command.”

 

“Ridiculous. A Ranger professes to manage Undead?”

 

“It stopped when I said so, did it not? If aggression is not your intent, then why are you here? Your kind is unfamiliar to this place.”

 

A brief silence passed as the eye seemed to measure her. There was a rustle on the ground as one of the Bone Vultures was released from the entangling vines, and it took wing to resume its watch overhead. Its companion soon followed, and the flames consuming the Death Knight receded. Ludmila stepped forward slowly to examine the remains of her sentry: all of its limbs had been burned away – its head as well. An Undead being capable of destroying entire countries had been reduced to little more than a torso in a half-melted breastplate on the ground. It still rocked and twisted an effort to right itself.

 

“Good work holding out there,” she said, and the Death Knight ceased its movements, “Nonna should be able to fix you up.”

 

She reached down to pat the Death Knight’s breastplate, but stopped upon feeling the waves of heat emanating from the dark metal. The winds around the being overhead vanished, and it floated to the ground in front of her. Now that she was able to gauge it properly, she could not tell how strong it actually was…and that made it incredibly strong. By appearance alone, it was deceptively weak-looking for something that had disabled a Death Knight so easily.

 

It stood at about half a metre when on all fours; the long antlers that extended halfway over the thick, grey, wool covering its body added perhaps another third to that. Unlike the rectangular-pupils of its two other eyes, the third eye had a round one which focused on her intently. Its rear legs ended in hooves like one might expect from a sheep or a goat, but its forelegs had two stubby fingers and a thumb which she had seen grasping the tree trunk from a distance.

 

“I am Ludmila Zahradnik,” she introduced herself politely, “Baroness of Warden’s Vale.”

 

The eye peered up at her with a lidded gaze.

 

“Such a pointless introduction.”

 

“Pointless?”

 

“Yes,” the small creature at her feet replied, “pointless. Shallow. Weak. You spoke your name, yes? Your mouth moves; your voice cries – yet your heart does not sing. I hear the sound of your name, yet it means nothing. A hollow declaration. Do you fear? Or is it shame? Or are you such a pitiful existence that you do not even know who you are?”

 

Ludmila looked down in confusion at the string of questions. Was it referring to the mysterious way in which the world allowed communication between different peoples, conveying language and concepts to those who could understand them? The being at her feet let out a breath that she thought was probably a sigh.

 

“You struggle to comprehend,” it said. “Then allow me to introduce myself.”

 

It gave a short bleat, and a long string of ideas accompanied it. Rather than being composed of any coherent sentences, meaning came in a single, condensed bundle. While Ludmila understood that all it had done was issue the brief sound, what unspooled before her perception was a collection of associations that painted an identity in her mind. After absorbing the name, Ludmila understood who he was…and she had no idea how one could convey their identity in that manner.

 

“My people don’t speak like that,” Ludmila explained. “I am uncertain if any race or creature I have encountered around here does.”

 

“All can speak like this,” it replied. “It is unfortunate that your kind seems to have lost the how, or maybe never knew. Yet, I sense that you are able: I hear the faint echoes of it in your words; you knew me when I named myself. Perhaps you simply do not know that you can.”

 

With that, he turned around and headed back towards the trees.

 

“Wait,” Ludmila asked. “Where are you going?”

 

“Away. I cannot know you, so we can never truly understand one another. Your soul is closed to me, and so I shall move on.”

 

Ludmila thought over their brief exchange, and she wracked her mind for a suitable answer. All words and names had associations, but, in the languages that she knew, they only meant what they meant and meaning could change or be lost to time. Certainly, some words carried a certain intangible weight when expressed in various ways, but she did not feel that they fully manifested what he wished to know.

 

The short bleat that was his name, once understood, coalesced into what she could only describe as an image perceived as a whole in her mind. It was not anything one could grasp with a single, physical sense. Every minute detail was a part of him; trying to latch onto a single element to make sense out of it made the whole lose its meaning. It was him and he just was. He had simply expressed the essence of himself, yet there was nothing simple about doing so.

 

Humans had names, and those names had meanings. Some liked to believe that names also had power. Yet these names were usually bestowed to one by their parents, who themselves might not even know their meaning. Whether one lived up to that name in the end was a whim of fate at best.

 

Lady Shalltear asked a similar question just two months ago – a question that she had been unable to answer.

 

Who are you?

 

“I am Ludmila Zahradnik,” she called out after him. “Baroness of Warden’s Vale.”

 

They were not just words this time. While Lady Shalltear used words just like her, what she conveyed did not contain any events or achievements; no transient ties or idle aspirations. Stripped of all the things that did not matter, Ludmila invested what she thought must be the essence of her being, and it felt like a piece of herself was carried away as she expressed her identity to the receding figure.

 

He immediately stopped, ears and tail twitching. After standing in place for a few minutes, he turned back around again and returned to stand before her. To Ludmila’s surprise, he closed his eyes and lowered his head.

 

“Warden of the Vale,” he said. “There is something we would ask of you.”

