\chapter{Ludmila Zahradnik}

Their journey paused when Ludmila saw the Volkhv stop at the edge of the wooden bridge to sniff around. Though greatly diminished as spring gave way to summer, the level of the Katze river was still high enough to overflow into the floodplains. After several minutes, the Volkhv returned from his sampling of the surroundings, eyeing the hill where the village stood over the harbour.

 

“There shouldn’t be any issue with this place for tonight,” the Volkhv told her. “If there are predators here, it’s probably best to warn them from trying to eat me.”

 

“The village is just Humans, Undead and the birds,” Ludmila replied. “Do you require any shelter?”

 

“No. My kind are accustomed to sleeping in the open.”

 

They made their way into the village entrance, where several of her new migrants roughly paid their respects even as they warily watched the strange creature walking alongside her. The Volkhv appeared to be able to look in nearly every direction at once, taking in the details of the settlement and its occupants while asking questions that touched on everything it saw in seemingly random order.

 

The pair stopped at the warehouse, where Jeeves was walking up and down the aisles with a stepladder. He straightened and turned after Ludmila knocked on the doorframe of the building.

 

“Good evening, Lady Zahradnik!” He said in his usual, cheery tone, “Hm…is this a new product?”

 

Ludmila glanced down at the Volkhv in alarm over his question, quickly producing a reply.

 

“His people have petitioned to migrate here,” she said. “They are composed of two races: the other is a Beastman-type Demihuman that resembles a large feline.”

 

Jeeves bowed deeply to the Volkhv, and Ludmila could not help but think the miniature Skeleton was just the right size to ride the Krkonoše Druid around. She mentally waved away the image before her mind started adding other features.

 

“My most sincere apologies,” Jeeves said. “Some of the villagers asked about livestock today, so I could not help but draw the association. Still, given the similarities…are certain products actually possible? Do you shed your coats, for instance?”

 

“We do,” the Volkhv’s ears twitched. “When the cold weather abates, we shed our coats: they grow back before winter.”

 

“What happens to your wool?” Ludmila’s interest was piqued.

 

“We rub it off on hard surfaces,” the Volkhv said. “The wind will blow it away, eventually.”

 

“It appears your hunch was correct, Jeeves,” Ludmila said. “It must be those merchant senses at work.”

 

“I have merchant senses? I suppose I must,” Jeeves looked at the Krkonoše Druid thoughtfully, “I just recognized a potential source of goods that are notably absent in our inventories and trade ledgers. Does anything else…ehm, come off?”

 

“We shed our horns around the same time as our coats,” the Volkhv’s ears twitched again. “They are left where they fall.”

 

“Another product?” Jeeves mused, “I have no knowledge of crafting recipes, so I suppose you will have to ask around about that, my lady.”

 

“Also, we cast our droppi–”

 

“Ooookay, we should move on,” Ludmila cut in. “Let Nonna know about those additional queries, Jeeves – I will get back to them in a few days.”

 

She led the Volkhv back outside before Jeeves could try picking up on another potential Krkonoše product, and continued on their way through the village terraces. Ostrik Kovalev stood over his makeshift workshop, overseeing the apprentices who were carrying loads of charcoal towards the back. One of the children stopped and stared in her direction, causing the smith to also turn his attention towards her, then down at the Volkhv.

 

“Oh, Lady Zahradnik,” he said with a slight bow. “Didn’t hear you coming. Hmm...guess we’re finally gonna get mutton around here, eh?”

 

You too?

 

Ludmila wondered if every merchant and shopkeeper saw things the same way. Perhaps she was a potential product or some sort of marketing opportunity in their eyes as well. Now that she thought about it, her friends did so as well. If an unknown object was placed before Clara, Liane and Florine, they would debate over its worth and try to figure out how it could be turned to economic advantage.

 

“This is a Volkhv of the Krkonoše,” she explained. “His people have petitioned to join us. They are composed of this race and the Demihuman from the other day.”

 

“That’s, uh…not going to be a problem, is it?”

 

“We have already discussed the matter,” Ludmila replied, and the Volkhv’s ears twitched. “They will still be moving in, pending my consultation with Lady Shalltear.”

 

“Hunh,” Ostrik grunted. “Well, that’s pretty big-hearted. You too, my lady: I thought followers of The Six were supposed to be all hateful of nonhumans.”

 

Was everyone trying to put cracks into her new relationship with the Krkonoše? Ostrik cleared his throat as Ludmila’s mood darkened.

 

“Er, anyways,” he said, “you’re just in time.”

 

“In time for what?”

 

“We’ve built a new sort of smelter – we’re just finishing loading it up right now.”

 

Ostrik motioned for her to follow, leading them to the back of the forge area. A long structure, which she assumed to be some sort of storage bin when she had seen it on previous visits, was filled with charcoal. The row of vents along the side glowed a bright orange and flames licked out from to top. Two of the smith’s apprentices watched from nearby with baskets of charcoal on hand, topping off the level of fuel as it burned and fell away.

 

“What is it?” Ludmila asked.

 

“A wind furnace,” the smith had a proud look on his face as he stared down at the contraption. “Since the winds from the north are so damn consistent and funnel right into the end of the valley here, I figured I’d give it a shot. Oh, this guy looks pretty flammable – might want to stand away a bit or you’ll turn into a ball of fire.”

 

“Our coats are not known for catching fire,” the Volkhv replied. “I cannot recall any of our recountings portraying such a thing.”

 

“Well aren’t you a little bundle of value,” Ostrik said. “Let me know if you knit an apron – I’ll be your first customer.”

 

“Knit?” The Volkhv tilted its head up at the blacksmith, and Ostrik looked to her.

 

“We have plenty of time to think over those things after the Krkonoše settle themselves,” Ludmila said. “So what are the benefits of this ‘wind furnace’? How does it work?”

 

Ostrik walked back to his portable forge, grabbing a fire iron from where it was hanging from a hook. He returned and started gesturing to various parts of the wind furnace.

 

“These are tuyères – air ducts, basically,” he pointed to the row of ports along the side. “The wind we got coming from the north all the time passed over the top of the furnace, which draws air through the tuyères and up through the fuel. It keeps the flames consistently stoked to high temperatures – high enough to produce steel inside. About half that comes out of this is iron; the other half some of the highest quality steel I’ve ever seen…at least if I got the damn thing built right.”

 

“Is this your first time using one of these?” Ludmila asked.

 

“Nah, it’s something I saw a few years ago,” Ostrik waved his fire iron vaguely in the distance. “Far to the southeast – way beyond the Theocracy, the Draconic Kingdom, and the meaner Demihuman nations around there – there’s an empire of Tiger Beastmen that are famous for their metallurgy. Hmm…that trip took me a good two years, actually. Took a ship from a port past the Draconic Kingdom, sailed for three months and ended up in some crazy hot place full of jungles and huge cities that make what we have here look like child’s play.

 

“Anyways, a few of these cities are designated as trade cities, where many races come together to do business. They’re really strict about enforcing everything there. If you’re caught outside of the designated locations, you might become a snack, heh. They have techniques for Mithril and Adamantite alloys as well, but this was as much as the smith I met was willing to show an outsider. All throughout his lessons, I got the sense that he was just doling out charity to a pitiful primitive: I can’t say he was wrong either – what they do out there is way beyond anything I’ve seen around this part of the world.”

 

The smith reached out and grabbed a flask sitting on a stump nearby, uncapping it and taking a long draught.

 

“Seeing that it’ll still be awhile before we get a regular forge set up, I went ahead and built this so we can get good steel flowing sooner rather than later. Hell, I might have a permanent one of these set up in the end anyways.”

 

“Does that mean you will not be needing the Undead labourers?” Ludmila asked.

 

“If this wind furnace works out, I’ll only have one of these clay bloomeries running just to make sure these brats know how to build and use one, so bellows work will be limited. Then they’ll be free to start learning how to work metal. Once we start turning out enough steel and iron, the apprentices will start putting out simple things in a week or two. I got some other ideas that I want to try putting to use, but that’ll have to wait until the buildings in the harbour here start coming up.”

 

“I see,” she said. “Do you have any recommendations for the steel that we produce?”

 

“Tools, definitely,” Ostrik told her. “The majority of my time is split between replacing the cast iron tools that break, and making iron nails and such for the ongoing construction work. Once we start putting out steel equipment, I’ll have a lot more time to focus on other things you might want to see done. Converting all the broken cast iron stuff that’s been piling up into even more steel will probably be the first thing.”

 

“You have my permission to go ahead with that, then. Will there be any changes to the amount of fuel or ore that you need delivered?”

 

“We haven’t even put a dent into the bog ore in the marsh – there’s so much of it built up here that I don’t expect shortages any time soon. However, since the wind furnace is much larger and burns hotter than these bloomeries we’ve been using, we’ll definitely be going through more charcoal. Seeing how much timber is building up on the flats, I figured that wouldn’t be a problem for the next little while.”

 

“Very well,” Ludmila nodded, “once you determine your new requirements, make sure Jeeves is updated.”

 

“Will do, my lady,” Ostrik bowed slightly.

 

She gave the new wind furnace one last, long, look before turning to continue on her way. The vague worries that had been tugging at her became stronger as they approached her manor where the Death Knight and its Squire Zombie continued to stand their silent vigil. Covering the remaining distance in silence, she stopped on the lane in front of the manor as the Volkhv stepped forward towards the Squire Zombie.

 

He turned his head up to look at the massive figure, then sniffed at it several times, ears twitching. A moment passed before he turned around and walked back to her.

 

“It is the likeness of my friend,” he confirmed. “This one was made by the other from her remains?”

 

“Yes,” she replied, “it is one of their abilities. Death Knights create Squire Zombies from the corpses of those that they personally slay.”

 

“I see,” his ears twitched again. “It is not unlike the ways of some other Undead beings.”

 

“Okay, before we continue, I really have to ask: what does it mean when you twitch your ears like that?”

 

“Like this?” The Volkhv twitched his ears in the same way as before.

 

“Yes, like that,” Ludmila said. “It is making me nervous because after you witness or hear something I think might be offensive to you, your ears twitch and I half expect the entire hill to explode into flames.”

 

“In this context and fashion, it is an expression signifying agreement or acceptance.”

 

“There are other meanings to your ears twitching?”

 

“Why, yes.” He replied, “Is your own body language so singular?”

 

“I guess not,” Ludmila admitted. “Then that means you are really alright with this Zombie Squire in the form of your friend? I know many of my kind have the belief that their souls are bound to undying servitude when the Undead are raised from their bodies.”

 

“That sounds quite silly,” the Volkhv bleated strangely. “The delusion of a primitive and unlearned people. Such a thing is not so commonplace. There are many sorts of Undead: most appear in a simplistic, single-minded state; a scant few may be powerful enough to manifest their own intellect and identity. There are also those who are raised to serve their summoners, usually in a temporary way. None of these do such a thing as bind the soul of another.

 

“The living may very rarely continue in this world as one of the Undead through preparations and conditions which facilitate the passing from one form to the next. There are those who return from beyond the threshold of death; where the will of the soul itself is so strong that they anchor themselves in the great cycle and the world accedes to accommodate their purpose.”

 

With the apparently well-learned Volkhv saying this, people threatening to haunt others out of spite didn’t seem like a joke or an empty promise. It was just a piece of folklore, though – she had never heard of anyone actually coming back from the dead to enact some grim vengeance or something along those lines.

 

“Your people certainly know a lot about the world,” Ludmila noted. “It is hard to imagine coming into all that knowledge dwelling in the same mountain range for countless ages.”

 

“Being in the same place for your entire life tends to have one looking beyond,” the Volkhv said. “We happen to have the magic to do so without ever leaving our homes, and our knowledge is passed on through those countless ages.”

 

“Then what about Vampires?” Ludmila asked, “The ones who they feed on will turn into Vampires themselves, do they not?”

 

“Hmm...this is a subject which is currently undergoing debate,” he answered. “It is one of a few rare cases of a victim’s soul genuinely being enslaved and turned into one of the Undead. Yet, in the case where a Vampire releases their hold on such a soul turned to unlife, those newly freed slaves tend to not immediately end themselves…so was the soul actually enslaved? Or was it willing in some small way: tempted by means through which only Vampires know how? Vampires are quite rare, but maybe one day we will come across one and find out.”

 

“Well, your people have apparently studied the Undead for a long time,” Ludmila said, looking away slightly. “What’s one more day?”