\chapter{Ludmila Zahradnik}

Tap tap. Thunk tap.

 

A strange sound issued from somewhere, and Ludmila opened her eyes to the sight of Aemilia sitting on her own bed, getting dressed. It wasn’t her, however, so she turned over to face the living area of the manor, trying to figure out what the noise was. There was no light against the table: it appeared that dawn had not broken yet.

 

Since she still had several hours until she needed to wake up and prepare for Lady Shalltear’s arrival, Ludmila decided to stay in bed. Suppressing her alert nature was a difficult thing, but, after several weeks of living with Aemilia in Warden’s Vale, she had mostly adjusted to her maid’s presence and could return to a restful sleep again.

 

Thunk thunk tap thunk. Scrape. Scrape. Tap tap tap thunk thunk. Scrape.

 

Well, she could have, if not for that noise. The events of the past day had made her sensitive to the goings-on around her again. Ludmila was almost certain it was the Krkonoše walking around on the roof of the hall. She relaxed and kept her eyes shut, but the more she tried to ignore the sound the more wakefulness returned to her.

 

“Luzi…”

 

She was too lethargic to even spare the extra two syllables.

 

“Yes, my lady?” Her maid replied as she knelt before the fireplace, getting the cookfire started and lighting the lamps.

 

“Go to the outside,” Ludmila mumbled, “and tell the Volkhv not to be stomping on my roof so damn early…”

 

“The priest…?”

 

“The…the floof on the roof…”

 

Aemilia’s footfalls left the kitchen area and receded down through the hall, and Ludmila turned back over. The door opened and the sounds of the village outside leaked in before it quietly closed again.

 

“Oh my, you really are floofy,” her maid’s voice sounded through the wall. “Excuse me, floof–er, priest?”

 

“Volkhv,” he bleated in correction.

 

“Yes, I just said that,” Aemilia said. “You are disturbing my lady’s rest by walking all over the roof at this hour.”

 

Thunk tap thunk tap thunk tap tap thunk thunk…

 

Ludmila heard the light thump as the Krkonoše Druid landed in front of the hall. She buried herself under the covers, half aware of Aemilia’s return to the kitchen. There should be at least two more precious hours of sleep left…

 

『Ludmila?』

 

Just as she dozed off, Lady Shalltear’s voice sounded in her mind.

 

『Ludmila? Hm…did I mess this up somehow? Ah – if you don’t know how all you need to do to respond is–』

 

『Just five more minutes…』

 

『F-five minutes? I’m not sure if the Message scroll lasts that long…』

 

『Lady Shalltear…you have already come? I thought–』

 

『No, no, this is a Message spell. Why do you sound so tired? Are you sick? Do you have a debuff? Should I come over and cure you? We have much to do today, so you can’t be out of form.』

 

She shifted in her bed and stretched. To her embarrassment, the sound of her voice while she did so was conveyed through the Message spell.

 

『L-Ludmila? What was that strange noise? That sounded a bit, hmm...actually, I’ll be right ther–』

 

『It was nothing, my lady. You messaged me while I was in bed – your voice popped up in my head while I was asleep.』

 

Ludmila wondered if this was what Moren Boer felt like, being assailed by so many people through Message spells. Shouldn’t there be some sort of etiquette for it?

 

『I see. What was that cute little noise, then?』

 

『…I was stretching, my lady – please forget about it. How may I be of service?』

 

『Why would I want to forget–ahem, I just thought I’d call ahead to let you know that I’ve arranged the appointment with Cocytus. It shouldn’t take more than a few hours, so we’ll do the rest of our work in the afternoon. I’ll arrive at your place at the time we agreed on.』

 

『Very well, I will begin preparations for an audience…would it be appropriate to have Luzi accompany us?』

 

『Hmm…yes, actually. There’s little to speak of in the way of civilized comforts there, so your maid might come in handy.』

 

『We will be ready, my lady.』

 

『I’ll see you then.』

 

Ludmila felt the Message spell end and she propped herself up in a seated position against the wall, rubbing the sleep out of her eyes. The spell felt very similar to her own ability, so she wondered why there was such a disparity in range.

 

“Aemilia.”

 

“Yes, my lady?”

 

“Lady Shalltear just contacted me,” Ludmila told her maid. “We will be attending an audience with Lord Cocytus after she arrives.”

 

“What shall I prepare?” Aemilia asked.

 

“I…have no idea actually,” she admitted. “Lady Shalltear mentioned something about civilized comforts – I think we will be heading to that Demihuman town in the Great Forest of Tob. We should not require much; maybe add a change of clothes just in case.”

 

“I’ll figure something out, my lady.”

 

Ludmila forced herself out of bed and threw on the robe laid out on her elder brother’s mattress. She yawned, stretched again and shuffled through the kitchen and the hall, opening the door. Greeting her outside was the sight of the Volkhv, tearing a clump of moss off of the wall with his teeth.

 

“The day’s greetings to you, Warden,” his voice was somehow perfectly clear even as he chewed on a mouthful of moss at the same time, “...is something the matter?”

 

“That clump of moss has been growing there since my father was a child,” Ludmila frowned.

 

“Oh. Were you saving it for a special occasion?”

 

He stopped chewing, and looked about to spit it out.

 

“No,” she said hurriedly. “I just never thought someone would just walk by and eat it off of the wall one day.”

 

“The flavour is quite well developed,” he resumed chewing. “You would like some, perhaps?”

 

“My race does not usually eat moss,” Ludmila told him. “Lady Shalltear will be here in a bit over an hour, but we have some business to attend to elsewhere. I would like to at least introduce you to her before we head off.”

 

“What is an hour…? Well, no matter, I will be here.”

 

Ludmila looked over the village and the valley beyond. Noting nothing amiss, Ludmila went back into the manor.

 

At the appointed time, the familiar portal of the Gate spell manifested in the manor hall and Lady Shalltear appeared. The escorting Hanzos stirred in her shadow, but they did not leave it.

 

“Good morning, Lady Shalltear,” Ludmila curtseyed in greeting.

 

“Good morning, Lady Zahradnik,” her liege replied. “Are we ready to go?”

 

“Am I presentable?” Ludmila asked as she rose.

 

Lady Shalltear’s crimson gaze ran over her, and she leaned from one side to the other in the confined space. Ludmila was wearing the same outfit that she had worn on the visit to the farming village and the logging camp – Aemilia had managed to quickly clean it up again after her encounter with the Krkonoše the previous day.

 

“There shouldn't be any problems,” Lady Shalltear told her, “unless Cocytus asks for something silly.”

 

“Something silly?” Ludmila furrowed her brow.

 

“Your guess is as good as mine,” Lady Shalltear shrugged. “Better than mine, probably – considering how alike you two are.”

 

“I see…well, I cannot imagine anything asking for anything crazy in this situation, though I suppose it depends on what he wishes to see me for.”

 

Aemilia stirred to her side, moving to pack up the preparations she had made.

 

“Before we get going, my lady,” Ludmila said, “there is someone I would like for you to meet outside.”

 

“Oh?” Her liege raised an eyebrow, “I don’t recall any mention of this during the Message.”

 

“Apologies, my lady,” she lowered her head. “I was still half-asleep at the time.”

 

“That you were,” Lady Shalltear smiled. “You sound very different in bed, by the way.”

 

“That is, uh…we should get this introduction out of the way so we can get to this audience with Lord Cocytus. I just thought you should meet him – we can discuss his business later today.”

 

Leading Lady Shalltear outside, Ludmila looked around for the Volkhv. The Krkonoše Druid had meandered over to the Linum residence, where he was grazing morsels off of their wall. Lady Shalltear looked down curiously at the small, sheep-like creature as they caught up with him.

 

“I believe this is more Aura’s specialty,” she said.

 

At the sound of Lady Shalltear’s voice, the Volkhv turned his attention towards them.

 

“Lady Shalltear,” Ludmila said, “this is a Volkhv of the Krkonoše People. Volkhv, Lady Shalltear Bloodfallen: my liege, and Minister of Transportation of the Sorcerous Kingdom.”

 

The Volkhv bobbed its head once before speaking.

 

“I had assumed your liege was another Human noble, Warden,” he said. “It appears that one more day was not so long to wait, after all. Greetings on behalf of the Krkonoše.”

 

“Do they not use names as we do?” Lady Shalltear looked up at her, “You were called by some sort of title; you used one for him as well.”

 

“They convey their identities in a very…complete manner, my lady,” Ludmila said. “A little while after we met, we settled on using titles for my own benefit. I am uncertain what they will come up with for you. The Krkonoše desire to migrate into Warden’s Vale, but, as Warden’s Vale is a territory of the Sorcerous Kingdom, several aspects of their unique culture lie at odds with our laws. It will probably be a lengthy discussion – I believed it would be best to be at least aware of their presence, just in case you recognized any immediate issues.”

 

“We have all sorts of problems getting the surrounding nations to like us,” Lady Shalltear said, “yet here you are with outsiders coming to you on their own. Rather than having any concerns, I’m curious: just what are you using to bait them in? Don’t tell me Aura let you use her Kal Kan.”

 

“I have not used any bait, as far as I know,” Ludmila had no idea what Kal Kan was. “They first arrived while we were away. As for what caused them to appear, it is yet another thing I need to discuss with you after the appointment with Lord Cocytus.”

 

The door to the manor opened, and Aemilia appeared with a light bag over her shoulder. Lady Shalltear looked over to the approaching maid.

 

“I see,” she said. “Well, if you believe that it isn’t an immediately pressing concern, it’s best to get this business with Lord Cocytus over with.”

 

“We will see you in the afternoon,” Ludmila told the Volkhv as Lady Shalltear opened a new Gate. “I have informed the Undead here of your presence, so feel free to explore a bit if you wish. Also, some children may try and pet you, but please don’t light them on fire.”

 

They stepped through the new portal; into a cavernous chamber which appeared to be fashioned out of solid stone. To her right was a window carved into the wall, under which a potted tree stretched towards the light streaming in from outdoors. Its imbalanced look bothered her a bit.

 

“Don’t move the plant,” Lady Shalltear warned as Ludmila peered down at it with a frown. “Someone turned the pot once: to have the tree grow back the other way. A few hours later, there was a Mare-sized hole in the wall.”

 

Ludmila backed away and fell into line behind Lady Shalltear. They made their way across the polished stone floor, to a long carpet that stretched between the entrance of the building and some sort of statue placed on what appeared to be an altar further inside. There were a number of nonhuman beings awaiting them: two rows of three reptilian Demihumans arranged on either side of two insectoid creatures that stood upright. Standing between them was another insectoid, distinctly different in form and massive in stature, who towered over everyone.

 

Sheathed in an exoskeleton of muted blue plates which glimmered under a fine mist that wafted off of its form, it measured their approach with a set of glistening compound eyes. Four arms extended from its shoulders and torso, ending in powerful claws – one which held a huge, silvery, halberd of incalculable quality that matched its mighty appearance. It suddenly exhaled from between the mouthparts behind its large mandibles: a hissing blast of frozen air that raised gooseflesh from where they stood over four metres away.

 

“You’ve come.”

 

The being’s voice was deep and gravelly. The air seemed to freeze and crackle with its breath as it spoke. Aemilia’s muted gasp came from behind her.

 

“Indeed,” Lady Shalltear replied as they came forward. “By your request, I’ve brought Baroness Ludmila Zahradnik. Baroness, Cocytus: member of the Royal Court and Lord of the Great Lake.”

 

Ludmila lowered her head as Lady Shalltear introduced them, spreading her skirts in a deep curtsey.

 

“It is my pleasure to finally make your acquaintance, Lord Cocytus,” she said. “Duty has kept me indisposed recently, but I have looked forward to our meeting ever since your first mention by Lady Shalltear.”

 

Throughout her greeting, she keenly felt the gazes of the Demihumans upon her, and she resisted the urge to check why they were doing so. She studied the rich carpet at her feet instead as she awaited Lord Cocytus’ response.

 

“Shalltear. This one: you trained?”

 

“Oh no,” Lady Shalltear replied lightly, “she was always this way.”

 

“Hmm…”

 

Another blast of frigid air frosted over the ground between them, and she watched it melt away as a long silence passed between them with no discernable movement. Still lowered in her greeting, Ludmila had no sense of what was going on.

 

"Welcome,” he finally said. “Raise your heads.”

 

She rose, only to see the massive ice crystals jutting from the back of Lord Cocytus as he strode away with the two insectoid creatures following alongside him. There was a small, pained, sound behind her as Aemilia straightened herself as well. They had been frozen in their curtseys for several minutes, and it must have strained her maid quite a bit. Unsure what had instigated the extended greeting, Ludmila looked to Lady Shalltear worriedly.

 

“Cocytus is quite the competitive fellow,” Lady Shalltear told her in a low voice as they left the two rows of Demihumans behind them. “He’s been trying to teach his subjects here what he considers proper protocol, with varying degrees of success.”

 

“Is that why all those Demihumans were staring at me the entire time, my lady?” Ludmila replied in an equally low voice as she made an active effort to not look over her shoulder.

 

“Perhaps. You’re far superior to any of his subjects in courtly behaviour. They’re probably in for it now after he witnessed your demonstration.”

 

“I did not realize that I was going to be used as a demonstration.”

 

“Well, Cocytus is the sort that will suddenly latch onto ideas he finds appealing,” Lady Shalltear smiled slightly. “I’d wager that if he saw those fortified villages you’re putting up, the lake would end up having castles springing up all around it within the week.”

 

“Is the Great Lake not surrounded by wetlands and forest, my lady?” Ludmila tried to accurately recall what she had written down two days previous, “There were no apparent sources of stone here mentioned in our review…”

 

“Well…there was at least one large block of stone somewhere around here,” Lady Shalltear told her, “though I think they might have used it to make this building. As for the rest of what he needs, it would hardly matter. Cocytus is very direct – he’d end up personally cutting a path straight through the hills and mountains to get what he wants.”

 

According to the maps provided in their planning for the aerial transportation network, the Great Lake over which Lord Cocytus ruled was near the foot of the Azerlisia Mountains. There were no known roads for wheeled traffic which led through the region, so moving anything by land presented severe challenges. Ludmila was unable to fathom how quickly one would need to ‘personally cut a road’ so that castles would rise around the lake within a week of doing so.

 

Ahead of them, Lord Cocytus and the two shorter insectoids were genuflecting before the large statue set on the altar at the back of the building. A variety of things – raw food, flowers, simple crafts and some other objects she was unfamiliar with – were neatly arranged around it. Lady Shalltear walked up to stand beside Lord Cocytus before she lowered herself into an elegant curtsey. Ludmila followed suit behind her liege, and there was a rustling of skirts behind Ludmila. Then there was an entirely unfamiliar sound beyond that. With the air as tense and solemn as it was, the noise seemed a bit out of place.

 

When Lady Shalltear rose, Ludmila stood and glanced behind her. Past Aemilia, she saw that the six Demihumans had followed them – they had lowered themselves into kneeling postures as well, tails laid flat against the floor. Seeing that both Lady Shalltear and Lord Cocytus had paid their respects before it, Ludmila assumed that the statue could be none other than a likeness of His Majesty: the Sorcerer King, Ainz Ooal Gown.

 

It was the first time Ludmila had any idea about the appearance of her new sovereign. Looking up at the masterfully graven image, which held an ornate staff out a grand gesture, she wondered how close of a likeness it was.

 

The sound of a massive form shifting around drew her attention away from the statue. Lord Cocytus had turned to address them.

 

“Come,” he said. “This place: I will show you.”

