\chapter{Ludmila Zahradnik}

Lord Cocytus left without awaiting their response, his heavy steps sounding over the stone floor.

 

Like so many of His Majesty’s servants, he only registered as a being of undefined power to Ludmila’s senses. As terse as his delivery was, however, Ludmila did not sense any overt hostility from him. Also, though she had never seen their species before and could not read their expressions, the weaker reptilian Demihumans did not display any clear signs of fear towards the Lord of the Great Lake.

 

Lady Shalltear’s characterization of Lord Cocytus in their past discussions had the effect of painting him as something like a warrior lord; his stern and taciturn attitude lent weight to that impression. She also suggested that Ludmila was like him in some way, though Ludmila couldn’t tell if that was actually the case based on their brief interaction so far. Rather than herself, Ludmila couldn’t help but draw parallels between Lord Cocytus and her father.

 

They followed Lord Cocytus and his escorts out of the carved entrance of the building, and the sight of a settlement constructed in the middle of a shallow wetland greeted them.

 

The building which contained the statue of His Majesty was raised over the rest of the surroundings, giving Ludmila a partial view of the settlement’s entirety. Though it was labeled as a ‘town’ on the map, seeing it from her current vantage did not give it the same sense as that of a Human town. In the place of blocks of buildings lined by streets, clusters of buildings were built on raised mounds of packed earth. Upon most of the mounds were collections of dwellings constructed from materials which were common to wetlands, framed in roughly fashioned timber and possessed of a single storey. A handful of the other mounds had larger structures erected upon them with little in the way of defining characteristics that she could recognize to set them apart.

 

Ludmila noted that there were a few buildings that bore the marks of years of weathering and habitation, while the majority of the structures looked to be relatively new. The locations with the older buildings were all set closely to one another, so Ludmila surmised they were of the original settlement which recent expansion had centred around. As they continued to follow Lord Cocytus through the low trails between the mounds, the ground squelched wetly beneath their feet and pools of still water could be seen everywhere along their meandering route.

 

There were several distinct types of Demihumans visible as they wandered about, but the majority appeared to be the reptilian sort that had awaited them near their point of arrival. Clad in scales of a variety of earthy shades and scant garments that seemed more decorative than functional, they basked in the sun near their huts, attended to various chores or gathered around the fires amidst their clusters of homes.




They regularly went back and forth from a large structure that she thought might be a granary or a warehouse, carrying woven reed baskets filled with various unprocessed goods to seemingly everywhere else. She saw some pushcarts parked near several of the buildings, but she guessed they wouldn’t do much good on the waterlogged footpaths. Given enough time, she might have figured out which buildings represented which industries and services but, for the time being, the layout of the place was a mystery.

 

For his part, Lord Cocytus appeared content to wordlessly lead them around: as if simply witnessing their surroundings was sufficient explanation for their tour. The Lizardmen – or at least Ludmila did not see any other race present resembling what she would consider Lizardmen – paid them little mind, save for the group of six from before who had fallen behind them to follow in their wake. Upon reaching the boggy beaches of the lake nearby, she discovered that two-thirds of the Lizardman town was situated in the water.

 

Beyond the edge of the shore, in the shallow marshes which appeared to cover the entire southern point of the great lake, more of the same style of buildings in similar arrangement as the ones they had passed lay on small earthen islands nearby. Others still were built on wooden platforms raised above the surface of the water on sturdy poles, and Lizardmen could be seen working to connect them with boardwalks. Those in the water moved about just as they did on land, splashing through it all indifferently as they went around delivering planks and driving posts into the ground.

 

“Lady Shalltear,” Ludmila asked when they stopped to look over the lake, “where are we placing the office for the transportation network? These Demihumans seem just as suited for the shallows as the shore, but there may be issues with keeping cargo out of the damp.”

 

“I’m not too sure yet, actually,” Lady Shalltear replied. “Frost Dragons can land on the ground or in the water, but there’s no space to do so in the middle of the village. There are small populations of other Demihumans around the lake, too, and there are no roads that lead to them.”

 

“I have not seen any boats, even though settlements ring the lake…” Ludmila said as she scanned the distant shores which eventually vanished over the horizon, “Is there anything like a harbour?”

 

Lady Shalltear looked up at Lord Cocytus, who shook his head.

 

“Before we came,” he turned his head to look down at them, “war between races: common. War between tribes. Trade. Boats. Wagons. Roads. Nonexistent.”

 

Meaning to say that each population probably existed at a subsistence level, and subject to the whims of nature. The conditions for commerce did not exist, nor had it been possible due to the belligerent nature of each population towards one another. Ludmila wondered if this had something to do with why she had been summoned. When they made their overview of the aerial transportation network, the lake had no notable exports beyond what could be hunted or foraged, resulting in an imbalance in their projected cargo flows. Her own demesne shared a few similarities in its environment, so perhaps he was looking for ideas.

 

“Is this why you requested to see my vassal?” Lady Shalltear voiced Ludmila’s unspoken question.

 

“No. A different reason.”

 

Lord Cocytus focused his attention on Ludmila and, after a moment, he shook his head.

 

“It is uncertain,” he said.

 

“What is?” Lady Shalltear turned to look at her as well.

 

“A warrior noble,” he replied. “Her reputation: by reports; by rumors. But before me…a Human noble, like the rest. I see little.”

 

Beyond the disappointed tone of his voice, Lord Cocytus was unreadable. Ludmila couldn’t tell what his body language meant, nor did she notice any more subtle cues that indicated his general disposition. This was a common problem between species that were too different: in the absence of foreknowledge or experience, assumptions associated with one’s own kind could be projected onto others and the results of doing so could lead to no end of trouble. She supposed that the opposite was true: other Humans were able to tell to one degree or another that she was a Frontier Noble at a glance, but the cultural distinction was most likely lost on Lord Cocytus.

 

“The reports come from multiple sources,” Lady Shalltear said, “and are well documented. Is this why you called us? So you could see her for yourself? This seems a frivolous reason to draw us away from our duties.”

 

“It is related,” he said after another blast of cold air. “Come. The rest awaits.”

 

He strode off again, leading them along the shore. Eventually, they came to the edge of the town where a short, wooden stockade had been raised. The wall extended into the water, and Ludmila suspected that Lord Mare had a hand in setting its foundations: there was little chance it could have been erected in the marshy soil through any other means which she knew of. Wooden guard towers were set at regular intervals, manned by Skeletons that she had never seen before. The equipment they carried appeared far superior to those she would employ on the walls of her village strongholds – they even came with powerful-looking bows.

 

The procession continued beyond the walls, Making their way through a sparse forest which followed the shore of the lake. More of the same type of well-equipped Skeletons that had been stationed in the guard towers patrolled the surroundings. When they passed them, none of the Lizardmen reacted adversely to the presence of the Undead. Ludmila wondered if there was some sort of Lizardman Lord present, reinforcing the population. Then again, as the lake was actually a part of the Sorcerous Kingdom before E-Rantel was, they might have just become accustomed to them.

 

“What sort of Skeletons are these, my lady?” Ludmila asked.

 

“They’re Nazarick Old Guarders,” Lady Shalltear replied. “Hmm…I suppose they wouldn’t be a part of the regular labour request forms. Maybe they’re on the security forms?”

 

Ludmila recalled the mentioned forms, but she was certain that she would have remembered such an odd designation.

 

“I will take a look at them again when I get the chance,” she said. “I have not used the security forms since I ordered the forces for the first village.”

 

Their entourage continued to slowly trudge through the light brush, appearing out the other side ten minutes later. There was another section of wetland before them, which had seen significant development. An array of enclosures stretched out from the shoreline, and they stopped at a point where they could observe a handful of Lizardmen tending to them.

 

Ludmila watched as one of them leaned over and dove into the water. After a brief struggle, it came back up with arms wrapped around a huge carp. Wrestling it back to the shore, the Lizardman tossed the fish onto a simple mat of reeds, rolling it up and carrying it back towards the village.

 

“Is this the fish farm mentioned in the logistical overview?” She asked Lady Shalltear.

 

The enclosure nearby, if she was to be nice about it, was crude in construction. As she looked further, however, they were larger, more sturdy looking and uniform. It was as if someone had experimented with the idea at first, then built on their success, making drastic improvements with the succeeding enclosures.

 

“Yes.” Lord Cocytus answered in Lady Shalltear’s stead, “This idea, recent to this place. This place; these people, I know – primitive, in your eyes. But their spirit; worthy of respect. The Lizardmen, sometimes, have Travellers. Go out – into the world – to see, and learn. This farm; this idea: something that returned. Lord Ainz…suggested the same, to…broaden horizons. Lizardmen, I have dispatched: to E-Rantel, to Human lands, the Empire, the Dwarves. What is good, they will see; ideas will return.”

 

As they listened intently to Lord Cocytus’ explanation, Ostrik Kovalev came to Ludmila’s mind. A travelling blacksmith, he had been to lands far beyond where most Humans would dare to go: seeing things unimaginable to a rustic border noble like herself. Due to this, he was a font of knowledge when it came to matters related to his trade so she decided that the plan had real merit.

 

Ludmila looked towards him with a tentative expression.

 

“Speak,” he said.

 

“Lord Cocytus,” she asked, “is it your purpose then to send these ‘Travellers’ to my demesne? This is the reason for your summons?”

 

“Yes,” Lord Cocytus replied, “and no. They may – like Travellers – learn. However, the reason…from Lord Ainz, also. Send them with you. Parents, with children. Families. To live.”

 

It was an order from His Majesty? Ludmila turned her head to look over at the six Lizardmen who followed them. She had felt them watching her the entire time.

 

“These Lizardmen, my lord?”

 

“Yes,” Lord Cocytus nodded. “Hunters. They go first. Investigate. Your land: like this place, reports say…this is true?”

 

Ludmila looked over the shores and the vast wetlands in the south of the lake which stretched to the surrounding forests. The vegetation was far more sparse here, and the water ever-present due to being situated in a lake. According to the new maps she had received, the Great Lake in its entirety covered roughly the same area as the floodplain in Warden’s Vale. The floodplain’s form was different, however, running along the length of the valley floor and subject to the rise and fall of the Katze River with the seasons.

 

“There are some similarities, my lord,” she replied, “but the nature of my land is distinctly different. It is a floodplain, so the water level in the marshes is dependent on the season. It will look vaguely like this when the river swells; otherwise, it looks more like an extensive, overgrown morass with many shallow bodies of water. There will most likely be differences in vegetation and wildlife as well, but, without some time to study the Great Lake, I cannot say how things will work out for the Lizardmen.”

 

“Yes,” Lord Cocytus told her. “These six will go: to survey your land. If suitable, they will report; their families will come…plus others.”

 

“How many do you plan on sending, my lord?”

 

“Enough for a…colony,” Lord Cocytus told her. “This, too, is my purpose. If war – true war – comes…entire lake: gone in a blink. All will be lost. To ensure their survival, I must send some away. To E-Rantel, to your place…others, in the future – when they are found."

 

“Lord Cocytus,” she asked, “does this mean the other races that live will be sent to my demesne as well?”

 

“Those that can, eventually,” he answered. “Others, unsuited: need lake – deep water. The Lizardmen: they come first. To pave the way.”

 

“Then what will the state of this ‘colony’ be, my lord? An enclave?”

 

“In E-Rantel, they live as citizens,” Lord Cocytus said. “I thought…to give you these, but, as mentioned…uncertain.”

 

“If they are to live on my land, my lord,” Ludmila reasoned, “things would run more smoothly if they were incorporated as my vassals. Having an enclave would introduce all sorts of needless complications for many.”

 

“Agreed,” Lord Cocytus nodded. “But first: proof.”

 

“Proof?” Ludmila frowned.

 

“Proof of lordship,” he told her, “proof of strength. Respect: must be earned. This is their way.”

 

“I see…this is something I have long understood of Demihumans, my lord,” Ludmila said, “but by what means do you intend on using to measure my suitability as their liege?”

 

She didn’t like the way this was going. It was probably going that way, anyways. Definitely.

 

Lord Cocytus’ head turned slightly to the side, and he jerked his head in a brusque gesture. One of the Lizardmen that had accompanied them since their arrival stepped forward, exuding an air of confidence.

 

Yep.

 

“Of the chosen,” Lord Cocytus gestured to the Lizardman who now stood across from her, “this one: the strongest. Proof…through combat. Prove your mettle, and they are yours.”