\chapter{Ludmila Zahradnik}

A hymn filled the air – its severe and militant themes at distinct odds with the gentle voice of its songstress.

 

Heard half a year ago, it would have surely given passers-by pause with its stormy melody...then as those people registered the lyrics of the hymn, they would have surely frowned in disapproval. It was not half a year ago, however, and the state of the realm was in no way similar to how things were before. Voice falling and rising through the hymn’s verses, Themis also knew that she was alone, in a place where no passers-by were present to hear her anyways.

 

The hymn floated out of the office, through the stone halls and into the chambers of the morgue in E-Rantel's vast cemetery. Even if she were not an adherent of Surshana, she still believed it would be her favorite. It was a call to action, a song of war. The battle hymn’s clarion call was wrought with conviction and offered devout prayer and supplication to Surshana, the god of death. It was a song she had locked away in her heart since she was a child but, now, with the population of the duchy slowly but surely returning to the faith, it indeed felt like a long, hard, battle was being won.

 

The revival of the Temples of the Six graced her voice with fresh fervour, and any heathens and apostates would have surely felt great discomfort upon hearing the hymn. It was one that one might expect to hear in the lands of the Theocracy, sung by the zealous masses in their great cathedrals; their tens of thousands of temples, monasteries and shrines. Hearing it in E-Rantel would, to those sensitive to it, signify a change that had come over the Human population – making one wonder what else the faith of the Six Great Gods would bring.

 

She glanced at the timepiece on the desk and reached out to pick up a clipboard and pen. Themis rose from her seat and walked slowly down the hall, carefully scanning the names on the documents attached to the clipboard in hand. Crime and hunger were issues that had become nonexistent in the city since the advent of the Sorcerous Kingdom, so murder and starvation were nearly unheard of. Death from accidents had also receded, but the fact of the matter was that death still came, and Surshana would have His due.

 

The majority on the list were those who had passed away from old age. The rest included those who had died instantly from various accidents, those who passed away from health problems that were not addressed in time, and those brought in from the surrounding lands who had met similar fates. The latter was a measure that came with new procedures in the processing of the dead within the Sorcerous Kingdom. Previous to its advent, the recently deceased were placed in a period of observance followed by the appropriate rites and interral. The wealthy often did so in family crypts or mausoleums, but this had been done away with. Now, regardless of social standing, all of the dead passed through the expansive city morgue.

 

These tasks were performed by members of the city priesthood and, as the majority of the citizens still worshipped The Four, their temple staff saw to most of the duties. Not too long ago, the few worshippers of The Six had rites performed individually at the request of their families. In the past few months, however, worship of The Six had increased dramatically, so one of the six chambers of the morgue – which had originally been built when the majority of the city population worshipped The Six in the past – was once again a place where their faithful rested.

 

As such, two shifts in the week were now allocated to the Temple of the Six. As an adherent of Surshana, the job fell to Themis. It was something that just happened to fit quite well with her schedule as an Adventurer. After expending her mana through training, she would assume her post in the morgue and meditate between her periodic rounds through the facility. Weak Skeletons and Zombies she could handily defeat without using any mana. If anything she couldn't handle appeared, all she needed to do was inform the sentries outside.

 

Walking up and down the rows of corpses, she updated their progress on the lists as she went. The observation period consisted of several days where the corpse was laid within the morgue. Any that showed signs of manifesting as Undead were specially noted. If a corpse started to show signs of decay, the soul was considered to have moved on and the corpse marked for relocation and interral. She had not seen anything actually get up in the short time she had been working here, but it was still a procedure long practiced in the city.

 

She stopped over a body which had reached the end of its observation period, and she marked off the person’s name on the list. After sprinkling droplets of holy water onto the resting form, she drew the incensed linen shroud over its body, unfurling the symbol of the Six Great Gods stitched into the cloth.

 

“Lord Surshana, into your merciful embrace we commend the soul of our beloved brother. May your faithful servant–”

 

Her voice broke, and she felt moisture run down her cheeks. She recalled the man’s aged face, and sobbed.

 

Themis had only graduated recently from being an Acolyte of the city cathedral; so far she had only spent a few weeks ministering to the people. She knew of him, however, and several others like him. Long-standing members of the congregation, they had personally witnessed the decline of the Temple in the city. Through generations of dwindling numbers, through all of the scorn and ridicule, these few had remained and kept the faith.

 

Though sprightly and active still in his advanced age, he somehow knew his time was coming. Some time ago he had come to her: a young Cleric of Surshana. He worried – yet his worries were not for himself: they were for his son and his family, who had been blessed with several children. They had fallen away from the faith, and his heart ached – if he was gone, he believed that no one would continue the fight for their souls.

 

The gods themselves had heard his heartfelt prayers. The people started to return to the faith, his family among them, and still yet they returned. He passed away shortly after, assured in the providence of the gods over his line. How many more were like him? How many before? How many prayers for the lost, over how long? Years? Decades? Generations? She could not even begin to imagine what they had experienced in their long lives. Surely such righteousness was of the highest order, and their faith would be rewarded in what lay after.

 

“May your faithful servant receive his deserved measure in your judgement, and be granted his rightful place in your eternity. To those who have been touched by his righteousness; his perseverance: bestow unto us a portion of your grace, that we may sustain the fruits of his faith – that we may follow his path until, in the ever after, we meet again.”

 

Her hand moved in a gesture of sanctification over the shroud, then she made a sign of the Six Great Gods over herself.

 

Themis took a few deep breaths to settle herself once again. She just couldn’t get used to this – she didn’t want to get used to this. It would mean that it didn’t mean as much to her any more, and that a piece of her faith somewhere had died inside. She would willingly go through these feelings every time, for as long as she drew breath. Straightening her clerical robes and scapular, Themis continued in her duties.

 

Nearly an hour later, she came out of the main hall and back into the front office of the morgue. An Elder Lich appeared through the entrance while she seated herself to update the morgue’s paperwork. She looked up and nodded silently to the Undead administrator, and it disappeared into the hallway. Two pairs of Skeletons walked in and out of the morgue repeatedly, carrying the corpses that she had just completed rites for, while bringing in new ones from outside.

 

Rather than bury the dead or cremate them, they were now all taken away to some unknown place by the Sorcerous Kingdom, presumably to be used as materials for the Undead labourers that had started appearing in various places. The Temples of the Four were aghast at the practice, but had no choice but to acquiesce to the change in procedure. The Temples of the Six had Surshana, who received the souls of the dead, so, to them, it didn’t really matter what happened to the corpses.

 

There was a brief exchange of documents after the Elder Lich’s tasks were complete, and it then left as quietly as it had arrived.

 

Themis finished cleaning up her desk in preparation to leave for the day. At the door of the building, she briefly exchanged pleasantries with the priest of The Four who had arrived ten minutes late. She frowned as she turned away and walked through the cemetery, where the grave markers and monuments cast their lengthening shadows in the late afternoon sun.

 

The priest taking over the shift and the Elder Lich that oversaw the delivery of corpses were supposed to arrive at the same time. She could then hitch a ride on the Soul Eater-drawn wagon that ferried the corpses out of the city through the north gate. At some point, she had mustered up the courage to ask if she could, and the Soul Eater just waited for her to get on before continuing on its way. The Undead in the city operated like clockwork, so of course the wagon was long gone and Themis let out a long sigh.

 

It took fifteen minutes just to walk back through the cemetery and to the northern entrance of the civilian sector of the city. It took an additional ten minutes to traverse the city streets to the Cathedral dormitories, and thirty minutes to change into her combat equipment. The growling of her stomach could somehow be heard through her undershirt, layered gambeson, chain mail and scapular, but, since the other priest was late and she missed her ride, she had no time to grab a bite to eat.

 

After experimenting with the timings surrounding her mana regeneration, she had devised a schedule that would have her ready for a training session with the Adventurer’s guild after a long shift in the morgue where she could meditate to full mana. It guaranteed two points in the week where her mana wasn’t constantly in flux seeing to the needs of temple supplicants, and allowed her to see to those needs without worrying about when she would have mana to train.

 

Cutting across the corner of the plaza between the cathedral and the Adventurer Guild, she peered around the hall after entering the building. It was now barely used with the guild’s transition to becoming a nationalized institution. There was no point in gathering to exchange information on the region, fill vacancies in parties or to check for new job postings. For the most part, it served as a gathering place for teams slated for training sessions, reviews of said training and an information kiosk for the bare trickle of prospective members that appeared.

 

Themis followed the women’s voices which floated over the stairs to the second floor, finding that most of her team had already assembled. All but one of the faces were familiar: Kyla, Penn and a Rogue that went by the name of Mag stood around the reception desk where Ishpen and Wina waited for the odd recruit or query from a member. The receptionists now also helped to organize the training teams and ensure they were properly prepared before setting off.

 

“I’m not late, I hope,” Themis said as she joined them.

 

“Naw,” replied Mag, “you’re safe. The other two haven’t shown their faces yet.”

 

“Who are we missing?”

 

“Henrich and Ludmila,” Ishpen answered. “Howe got himself eaten by turtles the other day, so he’s behind.”

 

Themis grimaced, and so did Kyla. They had been in the same party, and had watched as Howe fell prey to some ridiculous sequence of traps and was dropped into a moat full of giant turtles. She spent the same night awake with the sounds of his odd demise echoing in her mind.

 

“Howe was supposed to be here as well?” Themis said, “That makes it the original party we had back then, doesn’t it?”

 

“Gods, don’t remind me of that,” Kyla paled.

 

“Still…we see a couple of us at most as they shuffle members around – is there some reason why we’re back to the same combination? And why Ludmila? We haven’t seen her for weeks…”

 

“The Training Area Manager is the one that actually made the changes,” Ishpen replied. “Apparently he wants to try something out…”

 

The Adventurers exchanged worried glances. ‘Try something out’ had become known as a code phrase for pain and suffering. Before anyone could ask, however, the door to the guild hall opened and they quieted at the sound of approaching steps.

 

“Thirty.”

 

“Twenty-Five.”

 

“Ten.”

 

The robed man, who appeared around the stairs, stopped and shuffled back the way he came.

 

“I can't believe you're still doing that," Themis said incredulously.

 

“There’s no rule against it,” Ishpen smiled as she watched the defeated Adventurer slink away. “Men always complain that we’re never clear about these things anyways, right?”

 

The Adventurer Guild receptionist was leaning forward over the counter, chin propped in her left hand. Ishpen’s habit of grading men had gotten to the point of other women openly joining in. It had the effect of turning the reception counter into a fortified position when there were several women present: where men had to weather the spears and arrows that were hurled at them as they rounded the stairs to approach. Few survived. Most turned away abruptly just like the poor Silver-plate Sorcerer from a moment previous.

 

“Ishpen is as harsh as ever,” Kayla laughed. “I thought he’d at least come close to a pass if he polished himself up a bit.”

 

“How many years do you think I’ve been sizing up Adventurers for?” The receptionist sniffed dismissively, “There are just some things that no amount of polish will fix.”

 

“I swear one of these guys is going to run away crying because of you one day.”

 

“Hmph. Adventurers should be made out of sterner stuff than that. Eighty.”

 

“Eighty-Five.”

 

“Eighty-Eight?”

 

“Ninety-Five.”

 

The other women turned their heads at the score that had absently rolled out; Themis clapped a hand over her own mouth.

 

“Why?” The newcomer asked.

 

“Maybe she just fancies you that much?” Penn mused.

 

“That’s…no, I mean why? People already have a hard time seeing me as a Ranger – I can’t imagine things have gotten so bad that I’m not even recognizable as a woman.”

 

The new challenger who had just come around the stairs was Baroness Zahradnik. She tried having the other Adventurers simply address her by her first name but Themis, who knew what she meant to the Temple of The Six, could not help but defer to her social standing. Along with Countess Corelyn, the two nobles were steadfast cornerstones of the faith in the Sorcerous Kingdom and, to the Temple, their support of the faithful far overshadowed something like being an Adventurer.

 

“If you didn’t look like you just crawled out of a sewer,” Ishpen ignored her protest, “I’d have given you at least an Eighty Five.”

 

“I actually did just crawl out of a sewer,” Lady Zahradnik said. “I swear I’ve seen something like it somewhere before…since when did we have something like that?”

 

“A couple of weeks now, at least,” Themis replied. “The Training Area Manager came out to meet us at the entrance one day looking all pleased with himself. Then we were buried in giant rats, slimes and cockroaches. There was even a huge crocodile swimming around that we had to fight at the end. I swear whenever Mare gets that expression something absolutely horrifying always happens right after.”

 

“Is that so?” The noblewoman tilted her head, “I’ve seen Lord Mare happy with his work before, and nothing bad happened…”

 

Considering how Baroness Zahradnik was clearly made from something else entirely, Themis thought that events that would traumatize even veteran Adventurers would simply bounce off of her with little effect.

 

“Uh huh,” Ishpen answered dubiously. “Anyways, how did your run go?”

 

“It was completed, I believe?”

 

“‘It was completed, I believe?’” Ishpen mimicked Lady Zahradnik’s refined tones. “You just completed an exam for Silver-rank without a scratch. Did you even fight?”

 

“I walked by nearly everything – there were a few interesting traps along the way, but I skipped by those as well. The crocodile at the end didn’t want to let me by, though.”

 

Themis frowned. The giant crocodile for her silver rank exam had taken a whole group of Adventurers to take down, and they had barely squeaked by.

 

“What happened?” Kyla asked.

 

“I shot it.”

 

“And then?”

 

“That was it?”

 

Ishpen rolled her eyes.

 

“A single Iron-rank passes a Silver-rank exam meant for a group without a scratch: ‘I walked by some stuff. There were some traps. I shot a thing.’ Remind me to never put you on recruitment – even Farmers will think their own lives more exciting. Would it kill you to spice things up a bit?”

 

“…that’s all that happened, though?” Lady Zahradnik replied, “You were there when Merry sent me off to do this, saying that I was already way above Iron. It shouldn’t be a surprise.”

 

“Yes, yes,” Ishpen drummed her fingers on the counter. “Congratulations on Silver. Time for your Gold Exam. You know, it’d be one thing if you were like Momon and Nabe, who came here from some far away place with no previous guild registration, but I gave you the Copper-rank assessment personally. You did, what, a run in the Training Area, earned your Iron-plate, disappeared for a few weeks and now you’re taking the Gold Exam? Just what the hell did you do between now and then?”

 

“Paperwork in my manor…holding court with my vassals…some planning for a village? I had to travel out west for a few days, too.”

 

“What happened out west?” Kyla asked.

 

“A legal issue,” Lady Zahradnik answered.

 

Ishpen rose from her stool, placing both hands on the counter.

 

“If a few weeks of paperwork and a legal issue made nobles so strong,” she said. “Re-Estize wouldn’t have needed Adventurers. We would have just had Adamantite nobles all over the place with the mire of ‘legal issues’ constantly stewing there.”

 

“There are at least a couple, as I recall…”

 

“Right,” Ishpen snorted, “and how many nobles do you think there are in Re-Estize, even?”

 

“Hmm…there should be around forty thousand, if you include their families.”

 

“That’s my point – you must be doing something different. What else happened?”

 

“Well, I went to a Lizardman town and got into a fight. There was also a flying sheep that blew up one of my Death Knights.”

 

They all stared at Lady Zahradnik.

 

“…should I save all of us some time and just hand you an Adamantite tag right now?”

 

“It was a joke,” Baroness Zahradnik said. “The Death Knight didn’t explode.”

 

But there was a flying sheep, right? And you fought a whole town full of Demihumans?

 

Before Themis could voice her thoughts, the door of the Adventurer Guild slammed shut and heavy footfalls came from behind the stairs.

 

“Nine.”

 

“Eight.”

 

“Six.”

 

“Out of ten? Not bad, not bad…”

 

Henrich strutted up to the women at the counter and leaned upon it heavily. He flashed a broad smile at Ishpen, who had bestowed the highest of the abysmal ratings. She plainly looked like she wanted to change her score.

 

“So, miss receptionist, are you free after this?”

 

Ishpen let out an exasperated noise, turning away to walk into the back hall.

 

“Didn’t think she’d be so shy,” he chuckled and turned to Mag, who had given him the eight. “I gotta say, you’re a lot easier on the eyes than Howe.”

 

There was a creak of leather, and Wina quickly interceded before Kyla decked the oblivious Fighter.

 

“Since you’re all assembled,” the receptionist said hastily, “you should head out to the Training Area – it’s about forty five minutes before you’re scheduled to begin, and the manager still needs to brief you on what he wants to do.”