\chapter{Ludmila Zahradnik}

“「Clairaudience」.”

 

Ilyn’s voice sounded quietly over the room as she cast the spell through a Mirror of Remote Viewing.

 

“This is actually going to be worth casting this time, right?” She asked after she reseated herself, “I may as well have not used it at all for that last run.”

 

Ainzach grunted at what was probably a rhetorical question.

 

The Silver-rank exam that had preceded the current exam was nothing more than a formality by Merry’s estimation, and it had been exactly that. The Ranger examinee, Ludmila, simply stalked by everything undetected, bypassed all of the traps and killed the ‘boss’ at the end with a well-placed broadhead arrow from over a hundred metres away. The Giant Crocodile bled out within a few minutes, never knowing what had killed it.

 

It was a test meant for a group, defeated by a single, patient hunter. The only sound transmitted by the spell was at the end, after she had descended to the next floor and asked if there was anything more.

 

“It’s a group,” he told her, “so they should be communicating with one another most of the time. You’re up next, Blair.”

 

“「Life Essence」.”

 

“「Mana Essence」.”

 

Glowing auras appeared over the party members being observed, representing the relative condition of their Health and Mana. The auras were overlaid over one another, yet somehow the observers could clearly discern both at the same time. The Druid nodded over to Aura and Mare, who were standing to the side of the assembled proctors: one for each role represented in the party.

 

Except for one.

 

There was a Bard seated with them, who was one of the Gold-ranks present at their disastrous first showing outside of the city walls. After reading over the party composition – and who he was supposed to be monitoring – he looked about as confused as the others when they had gone over the briefing materials as well.

 

“Ah…ah…testing – why am I the one doing the talking, Mare?”

 

“B-because you like doing it, big sis? You’re always the one doing this kind of stuff, anyways…”

 

Aura frowned at the answer, and Mare shifted away with a timid look. After peering at her brother suspiciously for a moment, she turned back to address the figures in the mirror.

 

“A-hum,” she cleared her throat. “We’ll be trying something new today, so this’ll be a test in more ways than one. Ludmila will be in charge of the party, and uh…don’t die!”

 

The party members in the Mirror exchanged glances, except for the suddenly-in-charge Ludmila, who was trying to not make eye contact with anyone. Mag, their Rogue, looked up.

 

“Since this is an experiment,” she asked, “what happens with our points?”

 

“Even though it’s an experiment,” Aura told her, “it’s still a test so you’ll still be taking a hit to your points if you fail. Rezzes are the same deal, too. No pressure.”

 

“Ehhh…”

 

There was visible consternation between the party members. Ainzach couldn’t blame them. Failure in training runs resulted in a penalty to each participant’s running point tally. It had been worked out to roughly what a party would experience in losses of supplies and other materials if they failed a job that took a week to do. The penalty for resurrections scaled up according to rank, starting at ten percent of the cost at Silver; eventually becoming full cost at Adamantite.

 

Not that they had any tests higher than Gold yet. However, with equipment and consumables now provided through the point system, as well as the frequency of training, they found that the penalties stung enough that the trainees ended up treating each run about as seriously as could be expected.

 

“I still don’t get why I’m here,” the Bard, Vincent, said. “I mean, I get why you brought me here, but I don’t think I have anything to do with what this briefing claims.”

 

“You’re the closest thing we have,” Ainzach replied. “This branch has had noble Adventurers in the past but, beyond the ones who were Adventurers before becoming nobles, the rest were in name only. I got no clue how they work. At least a Bard with group-enhancing abilities might be able to notice things that we don’t.”

 

“Yeah, I’ll be sure to note when she does paperwork off-key,” Vincent looked down to his desk where the briefing lay spread out before him. “I have no idea how noble abilities work – hell, I didn’t even know nobles had abilities until I read this thing.”

 

Ainzach scratched his head, as Vincent still appeared unconvinced. Even he wasn’t really sure what to think of it all. Everyone had some sense that nobles had certain things they were good at, and Frontier Nobles were distinctly Frontier Nobles for some intangible, yet non-negotiable, reason. No one really explored why it was: nobles had their own things to do, and Adventurers in general didn’t really care since it wasn’t something they had to deal with directly.

 

In other places, where the spare children of nobles sometimes became full-time Adventurers, they’d participate as the common vocations that were associated with Adventuring. A Cleric; a Fighter, a Wizard. Or a Ranger, in Ludmila’s case. But you never had a noble sign up at the reception desk saying that they’d be a Noble. Well, it wasn’t actually unheard of, but those particular nobles were politely turned away, coming across as being pretentious, overbearing and obnoxious. Not to mention that it was considered suicidal. Nobles belonged in their manors, performing administrative tasks and managing their little corner of the Kingdom.

 

The examinees were also trying to figure out how things would work with the unforeseen change. All things considered, it was a confused mess.

 

“Seems like half of them didn’t take well to being told that,” Moknach remarked. “We Adventurers pick leaders ourselves – that part hasn’t changed even though a lot of other things recently have. We’re not some retinue or army where butlers or sergeants are set over us.”

 

The veteran of the E-Rantel Adventurer Guild was right, of course. Adventurers were fiercely independent and free-spirited, and having someone put over them arbitrarily was sure to invite an adverse reaction. Respect between them was not granted as a matter of course: it was earned. This was being made clear before the observers right now: with Henrich, Penn and Mag voicing their doubts over the decision rather plainly. The party had been purposely chosen because they were mostly well acquainted with one another, yet it had still become a problem.

 

Frontline combatants, who were capable of anchoring their team during a fight, tended to have the best sense of how combat was flowing around them and what shots could be called without breaking their party’s formation. As such, they more often than not were accepted as party leaders in a profession that often saw sudden, pitched, battles. Bards, too, could rise to a position of leadership as their broad set of abilities altered the dynamics of the group and could be employed to orchestrate the flow of combat.

 

It was commonly accepted, up to this point, that strikers, supporters and ranged combatants were best left to focus on performing their specific roles rather than becoming distracted by additional responsibilities. Though they were perfectly capable of melee combat, Ludmila was recognized as a Ranger, and Rangers were usually perceived as ranged combatants and scouts. With their often being too far away to communicate properly, it simply did not lend well to a leadership role in conventional Adventurer parties.

 

Much had changed with the Sorcerous Kingdom’s Adventurer Guild, yet much was very difficult to change. Party practices, taboos, preconceptions and overarching traditions would all take time to shake off – if they ever were.

 

“Well it is a trial, after all,” Josin said. “If we stubbornly stick to tried and true, we’ll never learn anything new. The Training Area Manager thinks that one of our members can be used as a Commander, and we can explore that idea in a controlled environment here.”

 

The Silver-rank party in the Mirror of Remote Viewing seemed to have reached the same general conclusion as well. They made their way inside the surface entrance and down the spiralling stairwell to reach the nexus where trials appropriate for their exam rank started. From there, the Rogue went on ahead of them to reconnoiter the crypt-like passages ahead.

 

The current exam reflected what the proctors considered a relatively light Gold-rank training session, but it was also at this point that the first major challenges to an Adventurer’s perception started. While Copper to Silver-rank training was relatively straightforward and simple: consisting of experiences and concepts that could be related to by the everyday individual, Gold marked where common sense started to make less sense.

 

Adventurers gained in strength at a pronounced rate past this point; as did their adversaries. Martial Arts became far more frequent and all sorts of things started to use extraordinary and supernatural abilities, often employing increasingly powerful spells. The level of complexity in encounters exploded as the avenues of possibility expanded in all directions. It was the first step an Adventurer took beyond the mundane world of regular people – where Adventurers learned just how far away the realm of Heroes really was, and that the histories so romantically regaled by the Bards were not as preposterous as cynics would have others believe.

 

Between all of the Adventurer Guild veterans and the Sorcerer King’s vassals that had been assigned to work with the Training Area, it was agreed upon that this would be the starting point for when their curriculum truly started to become a challenge. It was the minimum qualification for expeditionary work, so they would need to be schooled broadly. The Gold-rank exam would give them a taste of what was to come, but it was still considered manageable.

 

“I can’t help but think you really hate us scouts,” Merry said from where she was standing near Aura and Mare. “There must be some way to make this part better.”

 

“Weren’t you the one that suggested doing this?” Ainzach arched an eyebrow at her.

 

“Well, yeah,” she furrowed her brow, “but you guys agreed and I can’t help but get annoyed watching.”

 

In one Mirror – the one without additional sensory enchantments – Mag was sneaking around, covering the routes that led through the exam area. Single-route training sessions ended at Gold, and the scout would have to perform reconnaissance over several possible routes. As it was a part of each session past this point, higher rank runs took much longer to complete. The scout would ideally report back to their party, where they would together determine the best route and what methods could be used to overcome the various challenges identified.

 

The ‘dungeon’ this time split into three paths, the two side paths held chambers that gave a clear view overlooking the central path, and each of these side chambers had a dozen moderately weak Skeleton Mages in them. The central path had a large group of stronger Zombies that would tie up anyone that tried going through the middle. Immediately trying to advance through the Zombies would draw the attention of the Skeleton Mages and pelt the Adventurer party with magic from both sides. At the rank intended, no one would fall for that sort of trap as long as they scouted ahead in advance.

 

The party would have to go up the sides, to clear the ambush first. While the Skeleton Mages being used were only capable of casting spells of the First Tier, going about it recklessly would still result in taking a fair amount of damage. If one was careful–

 

“Uh…what is she doing?” Ilyn sat up in alarm, clutching the edges of her desk.

 

An arrow flew out and struck one of the Zombies in the central chamber, who turned to look in the direction of the attack with the shaft buried in its head. Ludmila and the rest of the party were out in the open, standing slightly inside the central hall, adjacent to the junction between the three paths. The Ranger loosed another arrow, and the Zombie collapsed. The noise alerted the Undead in all three chambers, and they started to converge on the party. Arrows and crossbow bolts continued to fly out from the party with the Fighters forming a defensive line, oblivious to the Skeleton Mages now running down the side halls towards them.

 

The proctors leaned forward as one at the incomprehensible action. The party knew what was waiting, yet they chose to ignore it.

 

“This is suicidal,” Josin stated. “She just made things ten times harder for them!”

 

Four more of the advancing group of Zombies fell before the small swarm reached them. Henrich and Kyla switched to their shields and melee weapons, while Mag continued to release crossbow bolts into the Zombies from behind the two Fighters.

 

“This is going to be so ugly,” Blair said. “It’s so much unnecessary damage.”

 

The two groups of Skeleton Mages started to round their respective corners at the same time, and Themis raised her holy symbol high above her head.

 

“My Lord Surshana, god of death,” her voice rang out, “return our foes to your embrace!”

 

A wave of divine power washed out from the Cleric of Surshana, and two dozen Skeleton Mages were reduced to ash in an instant. The remaining Zombies turned around and shuffled away. The two Fighters set upon them, cleaning up the fleeing Undead in short order.

 

“Turn Undead is such bullshit,” Blair muttered sourly to the side.

 

The Rogue headed out again while the group recovered their spent ammunition, and the assembled proctors exchanged looks with the action abruptly ended.

 

“That’s our bad, I guess?” Moknach seemed amused, “The Adventurer Guild only has two Clerics, and Themis is the most powerful one we have at the moment. Just an oversight, yeah?”

 

“Gotta admit,” Merry said, “that was pretty neat. It’s not often that you get to see that many Undead go poof at once…actually, why was that even a surprise? I didn’t hear anything until the fight started – did your spell go wonky?”

 

“My spells don’t go ‘wonky’,” Ilya sniffed. “I’ve been maintaining Clairaudience ever since we started. We didn’t hear any of their planning because they didn’t say anything after the Rogue reported her findings: they all just stood around that Ranger and nodded once in a while, then they all set up for the fight.”

 

“Can you do anything like that?” Ainzach asked Vincent.

 

“Uh…I can do something that resembles a Message spell,” the Bard answered, “but that requires a spellsong, and I’m fairly certain she doesn’t use those. Ventriloquism still requires me to say something, so Clairaudience would pick it up. There are a lot of oratory abilities – it may be something along those lines, but I’m hard pressed to think of anything else that lets you say something without saying anything.”

 

“Maybe they were being really paranoid and had the Cleric set up a Silence spell before discussing their plans?” Josin presented a possibility.

 

“No, that doesn’t make sense,” Moknach shook his head. “We’ve done that before, too, but why would they only do it after Mag reported her findings? It didn’t look like their mouths were moving either.”

 

“We’ll just have to ask after they’re done,” Ainzach said while jotting down the mysterious ability on the page sitting on the desk in front of him. “Looks like the Rogue is back.”

 

“That was fast,” Josin said. “Did she miss something? Hidden doors?”

 

“N-no,” Mare shook his head, “there’s nothing like that this time.”

 

“She just went through all the passages and disarmed the traps like it was nothing,” Merry noted. “That was a lot faster than the first set…it was about the same amount to cover, and I’m pretty sure I set them all to be around the same difficulty.”

 

The proctors frowned at the anomaly. Being able to watch the goings-on during the training sessions made many things obvious that would have not been otherwise. Having something genuinely mysterious or unknown occurring was actually quite rare.

 

“Ah, I get it,” Vincent said.

 

“Get what?” Ainzach glanced at the Bard.

 

“The difference between Bards and Commanders,” Vincent told them. “Bards use a sort of magic that can bolster their allies and afflict their enemies, as well as a whole lot of other things. The same can be said for any other sort of similar support magic: you cast it on your group or your target and it works. Commanders – Sergeants, Generals, and the like – don’t use magic. It’s more like an ability or an aura or maybe Martial Arts? Anyways, it affects a lot more people – armies, literally – but the kicker is that only subordinates receive the benefits of a Commander.”

 

“Uh…okay?” Blair said, “That doesn’t seem to matter here: they didn’t sign up for her army or anything.”

 

“But they did!” Vincent said excitedly, “Well, kinda. That fight just now was what did it. She coordinated a stunt that all of us thought was suicidal, and they breezed through it without a single scratch. They barely used anything: no potions, no mana – just a single Turn Undead. Before that fight, half of them probably didn’t care for being told to let her lead, but now she’s shown that she knows what she’s doing, they’re willing to follow – at least for the time being. That’s why the Rogue is breezing through everything: Mag’s getting benefits from her ‘Commander’ now, where she wasn’t before.”

 

“And somehow, this isn’t a spell,” Ilyn scoffed.

 

“It’s not a spell like you’d have in tier magic,” Vincent said, “but it is something like magic, just like how Martial Arts are considered a Warrior’s magic. I suppose you might say the successful ploy just now was a spell of sorts: once successfully cast, those who fall under her influence receive all of her benefits. As a Bard, I can move my audience to tears or laughter or feats of valour with a song. As a Commander, she can move those who subordinate themselves to her to greater levels of performance or coordination or whatever they’re getting from her. Similarly, though, it is double-edged: if I mess up a performance I can possibly lose my audience, so may she lose the faith of her subordinates if she falls short somehow.”

 

“Are you really sure?” Ainzach peered at him, “I’ve dealt with nobles before, and, while some might be charismatic, none of them do anything like this.”

 

Vincent’s gaze turned inwards, and he tapped a finger on his desk in thought. Several moments passed before he replied.

 

“It makes a certain amount of sense to me,” he said. “Consider the old tales, from before Re-Estize, after the lands were ruined by the Demon Gods – a wilderness savage and untamed. Who was it that drove back the races of that frontier? The heroes of those days were not Adventurers or mercenaries, but nobles: who led their retinues and armies, heading the charge and pioneering the foundations of the nation: what is now the heartlands of Re-Estize and the Empire. That is why most of the Great Houses in Re-Estize and Baharuth are styled in the manner of Marcher Lords.”

 

“I’ve seen some of those ‘Marcher Lords’ at the annual conflicts between Re-Estize and the Empire,” Moknach snorted, “they might talk big and wear a shiny sword, but there’s no way you can convince me that they’re fighting men.”

 

“That’s besides the point, really,” Vincent said. “What matters is that, at one point, these nobles did exist in that capacity: commonly enough to enter into our cultural memory. Baroness Zahradnik is a Frontier Noble: her house never stopped being those nobles from the early days – she is a song made flesh; one that continues its lonely tune to this day, significance forgotten even as she walks amongst us…save for the intangible sense that she is different somehow.”

 

The Bard was really beginning to wax poetic, but Ainzach still made a note of it. The world was certainly mysterious when it came to many things, but maybe this particular mystery could actually be tracked down in some rational manner. Still, the idea that Humans could be naturally influenced by a noble in similar fashion to a Demihuman Lord influencing their tribe was hard to swallow – especially since Adventurers commonly considered Demihumans uncivilized savages. Were Humans really not as different as they thought? Perhaps this was one of the reasons why the Sorcerer King did not consider Humans particularly special.

 

“I didn’t hear anything again,” Merry noted as the party set off.

 

“It probably doesn’t matter, whatever they decide,” Josin shrugged. “That first half was supposed to take up a lot more time and resources than they actually used. Now they’re effectively going into this next part beyond full strength if what Vincent says is what’s going on.”

 

Ainzach nodded in agreement. The opening fight had specifically been structured to force the party to use a certain amount of their resources, even if they played things as carefully as possible. They hadn’t expected that the party would, instead, crush it as aggressively as possible and render their calculations useless.

 

The second part of the test had the crypt turning into a crisscrossing network of caves that eventually led to a grotto, where several Ogres had volunteered to act as the final encounter. The caves had traps installed everywhere, and were guarded at intervals by various animals and monsters a Gold-ranked party would expect to commonly encounter throughout their work. Even if they straightforwardly cleared a way through the caves, going into them with their enhanced strength meant that they should handily make their way through with more leeway than intended.

 

Watching their mostly silent progress, the tactics seemed quite conservative – at least at first. As more of the passages were cleared, the team became so efficient that it almost seemed like play to them. Monsters were whittled away at range to be finished off by the Fighters, lured into ambushes or cornered and systematically taken apart with little excitement or flair. Traps meant for the Adventurers were used against their opponents instead to devastating effect. By the time they reached the exit of the cave system, they had perhaps used two healing potions and still hadn’t cast a single spell.

 

“I don’t think those Ogres are going to get what they signed up for…” Ilyn said in tones of pity. “Penn and Themis are just going to dump all of their mana on them once the front line ties them down. They’re three and three too – Mag’s going to have a field day.”

 

The Ogres were part of the Demihuman forces residing in the area around Carne Village. There were always a few of them around E-Rantel, who came to fight in the Adventurer Training Area to better themselves – or just have fun, depending who you asked. There were four in the grotto: three Ogre Berserkers and one Ogre Shaman. They were not the same as the ones that had fought the Adventurer Guild some weeks before during the battle outside of the city walls – those ones had already grown stronger – but a new batch that were each individually about as strong as a Gold-rank Adventurer themselves.

 

The Demihumans that came from Carne to participate always seemed stronger than they should have been, but, after witnessing firsthand the effects of a Commander over their subordinates, Ainzach decided that their extra strength must come from being under the Bloody General. It would be one mystery solved, at least.

 

Even so, he didn’t think they would fare too well: they were supposed to be a challenging final fight for a battered Adventurer party that was larger than them. As Ilyn had predicted, the Ranger – or was it the Commander? He wasn’t sure what to consider her any more – put away her bow and pulled out a spear from somewhere. With their respective frontlines occupied, the sheer magical power between Penn and Themis would come down like a hammer on the unsuspecting Ogre group. Mag had already slunk out of sight as well, crawling along the ledge below where the Ogres stood to position herself for sneak attacks.

 

Ainzach crossed his arms, awaiting the inevitable outcome as the two groups closed in on one another. The Ogre Shaman started casting a spell, but a sneak attack from Mag with her crossbow interrupted it. She ducked back under the ledge to reload while the Shaman turned about trying to figure out where the bolt had come from. Meanwhile, the three Ogre Berserkers and the three Adventurers occupied each other while Penn and Themis positioned themselves.

 

Clubs battered shields and counter-blows from the two fighters returned the favour. The Ogre facing Ludmila found itself pierced three times before it could reach her with a powerful overhead attack. She backed away with the incoming strike, positioning her polearm to receive the large club.

 

“「Smash」!”

 

The Ogre’s club snapped the spear like a toothpick, and the auras surrounding Ludmila winked out.

 

“Aiiieee!!!”

 

“Huh?”

 

“What!”

 

“Uh…”

 

“How the…”

 

“Ah, lucky~”

 

At his cheery words, all heads in the room turned to Mare.

 

“Mare…” Aura said with a frown, “What do you mean by that?”

 

“Um…didn’t big sis say that her build might be messed up? Now we can–ow! Owowoh! Hihter, whaus–”

 

Aura’s hands came in from both sides, fingers pinching Mare’s cheeks. Merry started to make fretful motions from the side.

 

“You…” Aura growled at her brother, and she stretched out his face, “You!”

 

“Uh! Wuh? Wha?”

 

“Just because you started getting along with a girl doesn’t mean you can just force her like that! Ah…how did my little brother become like this? It must be those women that keep spoiling you. I’m going to go and–”

 

“Awawa! Ih wahet ee!”

 

“What? Speak properly!”

 

“Uuuuu…”

 

Aura released her brother’s cheeks, but continued glaring at him.

 

“It,” Mare sniffed, “i-it wasn’t me. I didn’t do anything!”

 

“Haah?” Aura pointed to the mirror, where the party was wrapping up the fight, “They’re not supposed to go squoosh like that! Explain!”

 

“I-I don’t know! Everything should be normal…”

 

Mare looked around the room with watery eyes that begged for someone to come to his defence. Ainzach cleared his throat.

 

“I can safely say that that wasn’t normal,” he said. “This one was planned out with extra care since we were testing something out, so there shouldn’t have been anything amiss. If anything, everything went beyond perfectly until, uh, that.”

 

In the mirror, a Gate opened and Pestonya stepped out. After healing the subdued Ogres, she walked over to where Ludmila’s corpse lay.

 

“「Raise Dead」.”

 

After a moment, the noblewoman stirred.

 

Ainzach regretted that he hadn’t contacted them before the spell was cast. Raise Dead had been agreed on beforehand as the spell to be used to recover Silver and Gold-ranked Adventurers. According to Pestonya, those revived through Raise Dead lost ‘four levels’ or, in a more recognizable measure, roughly twelve difficulty ratings’ worth. The Training Area made it so that recovering from the loss in strength was relatively quick – as long as one participated earnestly. This being the case, they had decided on using the cheapest spell possible to free up more of their budget for crucial magical item purchases now that trade was flowing again.

 

The way Ludmila had died, however, was annoyingly unsatisfying and completely strange. If they had used a spell that restored her closer to her previous condition, a reasonably accurate assessment could have been made as to why she had died to what, by all appearances, should have been an easy attack to deal with. Her smoothly prepared defence indicated that she knew exactly how to handle it.

 

Now, he wasn’t sure if she was strong enough to keep her Silver plate. Ainzach let out a sigh, wondering if she could now even do anything that they had noted through the exam.

