\chapter{Ludmila Zahradnik}

The characteristic north wind and the uncharacteristically blazing afternoon sun greeted her outside, and Ludmila shifted in her mantle to part the front slightly. The magically-induced clear skies had the side effect of turning the flooded valley significantly warmer and more humid for the spring months, and she started to wonder if maintaining such ‘perfect’ weather indefinitely would produce adverse effects over the land. In addition to the accelerated growth of all manner of crops and wild vegetation, the insects were out in force far in advance of when they would usually appear in their summer swarms.

 

Skirting around a cloud of bugs that hovered over the lane, she hoped that the conditions wouldn’t become horrific by the end of the season. The normally muddy stretches of village paths, too, were caked and dry. The song of the forge sounded dimly in the air as she made her way down to the flats where the two tents with their small campfire stood against the backdrop of harvested timber.

 

Though Ludmila had noted more on her way into the harbour, only two men and a woman now tended to the fire. As far as she knew, they had not really done anything beyond collecting the scraps of cloth for their makeshift shelters and bits of wood for the fire. How or where they procured food and other supplies was unknown, though she suspected that they were poaching from the river and her surrounding lands. The three rose to their feet upon registering her approach; one of the men pulled a thick staff from the tent behind them. All wore suspicious frowns as she came forward, and the man without the staff spoke.

 

“Don’t come no closer,” he said. “We’ve had it up to here with you people comin’ to gawk at us like some sideshow.”

 

The crunch of boots on gravel ceased as Ludmila stopped a fair distance away from the trio. Despite Aemilia’s protests, she had decided to come out plainly dressed, without an escort or any indication of who she was. She sensed that they were no stronger than most of the villagers on the way in, and the manner in which the migrants on the trip to Warden’s Vale opened up to who they thought was a future fellow villager encouraged her to find out why these three had arrived on their own in a similar fashion. The rude reception was entirely unexpected, and she glanced up to count the Bone Vultures circling in the skies nearby.

 

Were they mistreated in some fashion by the villagers before she had arrived? Or maybe they were put off by Nonna – though Ludmila had not ever actually received any complaints about the Elder Lich from anyone in all of her time here.

 

“Why are you here?” Ludmila asked.

 

The man looked to his companions before replying with a scoff.

 

“Why’re we here? We moved here’s what.”

 

“All of the migrants here come by way of the river,” Ludmila said, “by the invitation of the local lord.”

 

“Invitation?” He sneered, “Lords don’t go inviting no one. We’re freedmen, y’know. We ain’t some stupid serfs bein’ shipped in on a boat. We can go wherever we please. Heard there’s plenty of land ‘ere, so we’ll be staking a claim when we find us a nice patch, eh?”

 

The strange mess of twisted understanding that came out of the man’s mouth struck Ludmila silent for a moment – it took a conscious effort to keep a straight face.

 

“I think you are confused about how things work,” she explained. “This land is a fief managed by the local administration.”

 

The three only offered her blank looks over the fire in response.

 

“A noble house rules these lands – it is someone’s property,” Ludmila explained. “It is not just some piece of unclaimed wilderness that you can decide to settle without permission.”

 

“Nah, yer the one that’s confused,” the man crinkled his nose at her. “This here’s the Sorcerous Kingdom now, and we’re it’s citizens. No noble’s gonna give us a hard time, just ask ‘ol Fassett.”

 

“…what does Fassett have to do with this?”

 

The man looked to his companions again and gave a short bark of a laugh.

 

“‘Ey now, looks like these swamp hicks really do live underground,” he said, and the two others chuckled. “The Sorcerous Kingdom don’t like it when you mess with its citizens. They found out what Count Fassett was up to and now he ain’t there no more. If th’ lord here messes with us, they’ll send someone out to off ‘im as well.”

 

“You’re from Fassett County?” She didn’t think it was possible for Lady Aura to miss anyone in their sweep of the territory.

 

“Naw, Crosston next door,” he said. “Place was being turned upside-down: some new guy got put in charge. Made ourselves scarce...not like it was any good there anyways. Now we’ll get some nice land to ourselves, then we’ll be the lords and no one’ll tell us what to do.”

 

Ludmila was at a loss as to what she could say. Not only was the man entirely oblivious to how the lands were managed, he had also concocted some sort of nonsensical worldview that only served to fuel his cocksure manner.

 

“Didn’t I tell you we don’t like being stared at?”

 

The man scowled as Ludmila stood pondering, and the man with the quarterstaff stepped forward threateningly.

 

“If y’ain’t got anythin’ fer us, get the hell out of our faces.”

 

Ludmila turned around and walked off back the way she came. The loud sound of someone clearing his throat caused her to glance over her shoulder, and the man spat in an exaggerated way into the campfire.

 

“Stupid bog bitch,” he said, “come out all this way fer nothin’.”

 

She turned her head back to face forward. On a whim, she focused her senses. An unmistakable sensation emanated from the group behind her, a lighter feeling than what she had perceived while she tracked down her quarry in Fassett County: indicating that they were indeed undesirable elements, though nowhere near as bad. They had not run afoul of any laws in her territory, either, so she could not act...well, she technically had the right, but it would be like she was lashing out against the group simply for being rude to a stranger.

 

Releasing the ability, she calmed herself down. At first – once she had explored its use in helping to clear out Fassett County – she thought it would make her life much easier when it came to sifting out problematic elements in the realm. After testing it several times after returning from the west, however, she discovered that, while it helped her track down what might be problems within the greater scope of order in the Sorcerous Kingdom, the severity gauged had many degrees and never provided any insight as to why such elements existed.

 

The sense associated with specific individuals could vanish the next day without any sort of intervention; and trying to do something about the problems she encountered sometimes actually made things worse. It could mean anything from a lack of direction in the general populace to individual swells of emotion manifesting into a temporary disposition that would shortly dissipate into nothing the next day. Findings that turned out to be rebellion, severe crime or heavy corruption were practically nonexistent – at least in the places where she had been.

 

In the end, the most use she could normally make out of her ability was the loose idea of whether things were going in the right direction or not, and employing it in crowded places like E-Rantel overwhelmed her entirely. From the brief period that she had tried while she was in the city, though, nothing appeared to be anywhere near the severity that she experienced in Fassett County.

 

Reentering the manor hall, she found that Nonna and Aemilia were still inside.

 

“Was there something that we missed, my lady?” Aemilia asked, glancing around the small space that was the manor.

 

“No,” Ludmila replied, “I just returned from speaking with the group that pitched those tents out on the flats.”

 

“Already? They didn’t attack you or anything, did they? The bunch of them seemed quite dubious, even from a distance.”

 

“No, they didn’t go so far as to physically attack me,” Ludmila said. “Nonna, have them put on the next ship out: tie them up if necessary.”

 

“What are they to be charged with?” The Elder Lich opened her book and looked at her.

 

“If you are required to provide a charge to the administration, then I suppose that they are technically trespassing on my territory. That isn’t the reason why I am sending them away though: I simply don’t wish for people with the sort of behaviour that they demonstrated living in my fief. The last thing I want is their spitefully using a charge laid against them as the basis for malicious rumours about my territory not accepting immigrants. Well, they may end up doing it anyway, but I’m not about to give them any ideas.”

 

Ludmila put her mantle aside, accepting a fresh cup of tea offered by Aemilia as the scratching of Nonna’s pen filled the silence.

 

“Let the captain know that they’re to be delivered to Corelyn Harbour – I’ll have to warn Clara about them as well.”

 

“Should they be detained until then?” Nonna asked.

 

“Not unless they look like they’re about to go somewhere,” Ludmila pointed in the general direction of the flats. “Set a Bone Vulture to specifically watch over them from overhead. I don’t care if they loiter around outside without bothering anyone, but I want them out–”

 

“You haven’t even invited me in yet,” a light voice chimed from the door, “never mind throwing me out. I think I’m hurt.”

 

Nonna bowed in front of her and Ludmila spun around, curtseying deeply towards the narrow doorway as soon as she confirmed the owner of the new voice.

 

“I am dreadfully sorry!” She cried in a horrified voice, “My words were meant for some other people. You are, of course, always welcome in my home, Lady Shalltear.”

 

The lightly-frilled hem of Lady Shalltear’s black ballroom gown filled her downcast gaze as her liege stepped over the threshold of the manor. Ludmila was made painfully aware of the dust from the road that she had just tracked in being swept up by the exquisite and incalculably valuable dress.

 

“You may raise your heads.”

 

With a bit of hesitation, Ludmila rose to face Lady Shalltear. Her silhouette filled the entryway, and her glowing crimson eyes were laid upon her in some bemusement.

 

“While it’s fun to find opportunities to tease you,” she said with a small smile, “your skill at groveling is decidedly lacking. I suppose I shall have to find other ways to derive my pleasure from you, Lady Zahradnik. So what was this about throwing people out?”

 

Ludmila guided Lady Shalltear to the rear of her home, taking a seat across the small dining table from her. Aemilia attended to them near the table.

 

“Do you take tea, my lady?” Ludmila asked.

 

“I can drink tea, yes,” Lady Shalltear replied.

 

Aemilia turned away to prepare what little hospitality they had to offer as Ludmila explained what had occurred.

 

“The capital has bylaws that address this sort of behaviour,” Lady Shalltear noted, “do they not exist in your fief as well?”

 

“Not as such, no,” Ludmila answered. “Laws against rowdy and belligerent behaviour short of inflicting grievous injury and committing murder have never existed in Warden’s Vale. To be frank, my lady, it has always been a place where the people are rough, rowdy and rude…but not that kind of rude. My people knew where the boundaries of respect were drawn, so there was never any need for such measures.”

 

Populations in territories charged with the defence of the realm had a distinct culture of their own, which stemmed from their principal duties. Unlike inland territories that generally had docile tendencies encouraged in their populations, frontier regions had a martial culture that harnessed aggression and the skills required to defend their homes. Children and adults alike were allowed to wrestle, roughhouse and fight and, in doing so, also developed a code of behaviour that understood where the lines of such conduct lay.

 

Dealing with ‘militant’ individuals from the inland territories was always a vaguely annoying thing. Be they a fresh member of the militia or an Adventurer, it was like interacting with people that only recently came into ownership of a weapon and didn’t know how and when it was to be used, or what it could do. From what she had seen, brawls and domestic conflicts in the city were also like this: one had to break up altercations because the people involved often fought without reserve. They just acted like their lives were being threatened, or acted with deadly intent – even over ridiculously minor things. Though the inland nobles seemed to equate the borderlands with brutal militancy and savage conduct, the populations of border territories might consider inlanders undisciplined and soft.

 

“Well these people are here now,” Lady Shalltear looked up at her, “and your new migrants are not the same villagers that you grew up with.”

 

“It is as you say, my lady,” Ludmila admitted. “Even so, I was hoping to carry my own culture forward with the new migrants. They do not seem to share the same proud, independent spirit of my people and it seems that they are floundering about when left to their own devices. Whether I can instill them with the same ideals as before, I am uncertain…but at the least I would like to see roughly the same freedoms enjoyed.”

 

“Then I suppose we will see where your path leads you,” Lady Shalltear said after taking a sip out of the cup of tea laid before her. “I have no worries about you personally, but keep in mind that you are a rarity amongst your kind. Your experiences beyond the borders of your fief should have provided you with ample evidence of that.”

 

“Thank you, my lady,” Ludmila lowered her head. “I will keep that well in mind. So what is it that brings you personally all the way to my humble fief?”

 

“Those Frost Dragons are finally behaving properly for the capital’s grand opening, so I came over here to see what was going on. I was curious about the Demihuman intrusion that was reported, but I suppose all that’s left of it is standing outside of your door…”

 

“There have been no further incidents beyond the first one, my lady,” Ludmila said. “Unfortunately I have no way of knowing why they even appeared.”

 

“Is there even a point to knowing this?” Lady Shalltear looked at her curiously, “Your role as a Frontier Noble was always to keep intruders out, yes? The result here seems a satisfactory conclusion.”

 

“I suppose when dealing from a position of power that might be the case, my lady,” Ludmila said. “I suppose it is a vestige of our ways of thinking when House Zahradnik had limited strength and numbers. You are correct that our duty was to keep the borders as clear of hostile intruders as possible, but it rarely resorted to facing our neighbors directly in combat. When you only have a hundred or so villagers and there are potentially thousands of Demihumans in the wilderness nearby, understanding when deterrence is sufficient and when force is required is essential.”

 

Lady Shalltear nursed her drink in both hands, frowning down at the surface of the table. It was probably not something she would have to consider: her liege was an extraordinarily powerful Cleric, and leveling entire towns with a single spell was well within her capabilities.

 

“Then…what were you hoping to discover?” Lady Shalltear asked.

 

“No two Demihuman species are the same,” Ludmila answered, “and the Squire Zombie outside of the door is of one that I have never seen before. As imposing as it appears, it is no guarantee of its actual behaviour. Some vicious-looking Demihumans are perfectly benign, while the opposite is true for others. If it was a part of an envoy, and a series of misunderstandings is in progress, it could very well culminate into a full scale reprisal. Even the last time someone fought with the Undead here, it was a Human who thought he was saving me from them.”

 

“How often do Demihumans send you envoys?”

 

“Most would only resort to diplomacy if they respect the other side’s strength…or if dire circumstances arise that force them into it. Around here, it is extraordinarily rare, as we keep our borders well-defined. The Theocracy is not very far away, either, so the local Demihumans tend to stay away from Humans, and understand that Human reprisals are extraordinarily deadly.”

 

“Well, if it’s any comfort, they wouldn’t get very far even if they did come by,” Lady Shalltear took another sip of tea. “The reports on the local Demihuman tribes during our initial sweeps over the area indicated no substantial threats.”

 

“Please forgive my saying so, my lady, but that is not the point. I still consider it imperative to understand as much as is possible, to have the most complete picture of the situation so that I may make sound judgements.”

 

Lady Shalltear looked up from the table, and Ludmila shifted slightly under the scrutiny of her gaze.

 

“Your outlook is genuinely surprising,” Lady Shalltear said, “and not only because of your apparent duty to exterminate invaders. Do the teachings of your gods also not promote such behaviour?”

 

“The faith of the Six Great Gods does promote the agenda of Humanity first and foremost: it is a religion for Humans, after all. The faithful in the Theocracy are reported to be as zealous as you suggest, but in Re-Estize and the other northern Human nations, our faith is in the minority and we have a degree of temperance when it comes to such things by necessity. The faithful inland are even far more mild, from what I have seen…if anything, frontier populations may be the most extreme in their outlook beyond the borders of our neighbor to the south, as we do experience periodic hostilities with nonhuman races.”

 

“I think your definition of ‘extreme’ differs slightly from mine…”

 

“Perhaps,” Ludmila smiled slightly, “but my desire for information is not the product of some benevolent and optimistic outlook: it is to make the best decisions possible in any given situation. If that decision happens to be the extermination of hostile invaders, then the understanding that I have developed will help me come up with the best ways by which to do so.”

 

“Yes, I suppose that’s more like you,” Lady Shalltear’s eyes gleamed. “If that’s the case, then maybe you should resurrect the fellow outside and ask directly.”

 

“You would do this, my lady?”

 

“No,” her liege’s lips turned down in a small frown. “The budget that has been allocated to me is scarce enough as it is – I swear Albedo is giving me a hard time on purpose. Speaking of which, this brings me to another reason I came to visit you.”

 

Lady Shalltear turned her head to the figure standing nearby in the hall.

 

“Hm…Nonna, yes?”

 

“It is an honour that Lady Shalltear would remember this one’s designation,” the Elder Lich bowed.

 

“Return to your duties,” she told the Elder Lich. “You do not need to be here.”

 

Nonna once again bowed respectfully before leaving the manor. After the door shut quietly, Lady Shalltear turned her attention back to Ludmila.

 

“Now where was I…ah, yes – the reason why I came.”

 

“It wasn’t to investigate the report of intrusion, my lady?” Ludmila asked.

 

“I suppose that was something like a reasonable excuse,” Lady Shalltear answered. “I have enlisted you to aid me in my new duties: it is as good a time as any to begin.”