\chapter{Ludmila Zahradnik}

Lady Shalltear’s lips parted to speak again; then she stopped and scanned the room carefully.

 

“「Silence」.”

 

The dim sounds of the village leaking through the thin walls of the manor hall abruptly ceased, leaving an eerie stillness in the air. In the corner of her vision, Ludmila saw Aemilia glance about nervously. Going by the still-audible shuffle of her maid’s feet, it seemed that Lady Shalltear had cast the same enchantment from the night she had visited Ludmila’s solar in E-Rantel.

 

“My lady?”

 

“「All Appraisal Magic Item」.”

 

Taking one last look around the room, Lady Shalltear nodded in satisfaction before answering.

 

“I doubt you’ve forgotten that your attaché is one of Albedo’s creatures,” she said. “Since the Prime Minister seemingly wishes to abandon me to my own devices in the pursuit of my task, then I will keep her big nose out of my matters entirely. Do keep this in mind, Ludmila: she’s been gleaning the fruit of your own efforts as well.”

 

“I understand, my lady,” Ludmila replied. “I will keep information regarding this separate from my other work…will we be headed somewhere later? If so, I’d like to ask for some time; I’ve not completely caught up to all of my duties here – it should take another day or two provided nothing unexpected occurs that pushes things back.”

 

“We’ll just be conducting an overview today,” Lady Shalltear dismissed her concerns with an absent wave of her hand, “there are also several other things…I believe you mentioned wanting to discuss something to do with our contract the last time we parted?”

 

“Yes, that’s right, my lady,” Ludmila nodded. “I need to discuss my taxes with you.”

 

“The taxes of the Sorcerous Kingdom should go to the Sorcerer King, should they not?”

 

“As far as I know, the tax laws have not been changed. Nobles have the right to collect revenues from their holdings independently, and their liege similarly collects revenues from their vassals in addition to what is garnered from the holdings that they administer directly. Land taxes are of course separate from customs duties, tolls, fines and such, but, as you are my liege, you are who receives my taxes…is this not something you normally practice?”

 

“It’s not,” Lady Shalltear said. “We don’t pay taxes to His Majesty – though there have been occasions where we’ve offered personal tributes to him. His Majesty even offered to provide us with a salary at one point, but since all of our needs are provided by him in the first place, one thing led to another and the notion was abandoned.”

 

“I’ve heard of subsidies and stipends being provided to fund various projects or address security concerns, my lady, but I’ve never heard of vassals being compensated simply for being vassals…”

 

Ludmila wondered what sort of salary Lady Shalltear would command. Surely it was some fabulous amount, and the proceeds would go into something equally so.

 

“Then what would you do with the taxes I paid you?” Ludmila asked.

 

“Hmm…there’s at least one thing I would like to do: how many years of taxes do you think it would take to come up with one billion gold coins?”

 

Ludmila mouthed the amount silently while Lady Shalltear looked on in expectation. What in the world would one do with so much currency? More to the point: did so much coinage even exist?

 

“Er, well…I don’t expect prices for commodities produced by Undead labour to maintain their current levels, but even so I don’t think that’s something my demesne could produce in my entire lifetime…”

 

“But your descendants will serve me as well, yes?”

 

“I do indeed desire this to be the case, my lady, but I’ve no confidence in making such long range economic projections.”

 

“That’s a shame. I suppose that in the end the full amount would go to His Majesty, though…every little bit counts, yes?”

 

The unfathomable nature of the Sorcerous Kingdom once again made itself plainly clear to Ludmila. Even the plans that she had wrought for her demesne and its resulting productivity seemed less than a mote in comparison. She needed to find some way for her contributions to have more meaning than simply being an indistinguishable drop in an ocean.

 

“You mentioned some budgetary constraints and the Prime Minister…what was that about?”

 

“Ah, yes,” Lady Shalltear said. “As you know, the Ministry of Transportation is establishing an aerial transportation network, using the Frost Dragons as the backbone for the project. The Prime Minister has allocated, well, nothing to the project, so I’ve been using my own resources for it.”

 

“The Prime Minister has allocated none of the nation’s budget to a national project? That doesn’t make much sense…”

 

“To be honest, I technically do have everything needed to make things run, which is ultimately His Majesty’s anyways…the reasoning should be somewhere along those lines…”

 

“If that’s the reasoning, then perhaps the Prime Minister considered the matter of my taxes as well. Regardless, I believe it would be a productive way to put the resources to use. Once we’ve developed this network into a workable form, the revenues from the nation’s effective monopoly over aerial transportation will be well worth the investment.”

 

“The revenues?” Lady Shalltear tilted her head curiously.

 

“Even transporting goods over land has associated costs, yes? My vessel needs to be maintained, plus I need to pay harbour fees and such. Then I have to hire a wagon to transport my goods from the harbour to the city for sale. I’m not sure how much the Frost Dragons cost to maintain, but we’ll have to balance the service’s expenses, at least.”

 

Lady Shalltear tilted her head the other way, and Ludmila held her words in check. Considering what Lady Shalltear had said about the arrangement of her own resources, she might have been approaching the challenge from an entirely different angle.

 

“Apologies, my lady – I’ve only been considering things from my own limited understanding,” Ludmila said. “Rather than getting ahead of myself, I should have made sure that I was on the same page first. We should start from the beginning to avoid misunderstandings.”

 

“I agree,” Lady Shalltear said. “I’ve made a great study of these Frost Dragons in the past few weeks, and I believe I’ve come up with a number of ideas to best put them to use. Let’s see…”

 

Lady Shalltear’s voice trailed off as she reached into a hole in the air in front of her. Ludmila and Aemilia watched as her arm made rummaging motions as she muttered to herself.

 

“No not that one…

 

“It should be somewhere around here…

 

“Hm…I thought I left that at home…

 

“Oops, I forgot to turn this off.

 

“Ah, here it is.”

 

Her hand reappeared, holding a light blue notepad with an expensive-looking pen clipped onto it. After she placed the item on the table between them, her gown shimmered briefly before being replaced by an entirely different outfit. Ludmila could only see the portion of it above the table: her liege now wore a white silken blouse with long sleeves; a rich crimson tie at her collar. Over the blouse was a sleeveless black vest with grey pinstripes: fastened by three large, glistening, buttons.

 

Oval half-rimmed spectacles with dark frames appeared on her face, while the bow and bonnet on her head disappeared, releasing the lustrous waves of her silver hair to spill over her shoulders and down her back. Lady Shalltear reached up to loosen the tie and unbuttoned her collar to expose the slender lines of her pale neck and collarbone. A moment passed before a small furrow appeared on her brow and a large clip appeared in one hand; a brush in the other.

 

“I guess the quick swap crystal in the clip won’t work so conveniently,” she murmured, then looked towards her. “Fix my hair, Ludmila.”

 

Ludmila stared blankly after the sudden request, blinking several times.

 

“Noblewomen here are trained to be Ladies-in-Waiting, yes?” Lady Shalltear asked as she pulled out a ghostly-looking hair band.

 

“Yes, my lady,” Ludmila replied. “Just one moment.”

 

She stepped away to make sure her hands were clean, wondering how things had gone from planning an aerial transportation network to arranging her lady’s hair. Returning to stand behind Lady Shalltear, she knelt down and held out her hands, clasping and unclasping her fingers nervously. Aemilia had surreptitiously inched over to closely watch – somehow the entire affair had become a trial.

 

“How would you like your hair arranged, my lady?” She forced out a calm and even voice.

 

“Just keeping it up and off the floor is fine,” Lady Shalltear replied lightly. “There’s no need to be so nervous…”

 

“Is this…invisible?” Ludmila asked as she picked up the strange hair band.

 

“Yes, it’s an invisible hair band. Usually my Vampire Brides deactivate the invisibility before using it, but I suppose that’s not a problem for you.”

 

Even Lady Shalltear’s hair ties were magic items. Ludmila hoped she didn’t accidentally break anything.

 

The first challenge Ludmila thought she would have was confusion over which hair was currently her hair, but her concerns eased as she was able to accurately work with the hair that was actually there. Her shoulders loosened, and her stiff movements grew more fluid; the light aroma of her lady’s sweet, cinnamon perfume drifted up with each stroke of the brush. It was only after Lady Shalltear’s hair had taken a soft sheen in the light of the lamp overhead that she gathered it into her hands, twisting it up into a large bun over the nape of her neck and fastening it with the clip. Stepping from one side to the other, she teased out strands to lightly frame her face with lazy curls that fell in front of her shoulders.

 

Ludmila stepped back and waited anxiously while Lady Shalltear examined her work with an ornate hand mirror produced from somewhere. She turned her head this way and that, tilting both her head and the mirror in several angles before a hole opened up in the air again and she put the mirror and the brush away.

 

“This is quite nice,” she smiled. “It seems that you’re adept at organizing all sorts of things.”

 

“You honour me, my lady,” Ludmila said. “I suppose I should be thankful to Clara for dragging me into these things all the time. Speaking of which…Clara and the others would help greatly in envisioning this transportation network – Liane, especially. Their background as merchant houses would be an advantage here. Should I see about enlisting their talents as well?”

 

“As tempting as this might be,” Lady Shalltear replied, “they still report directly to Albedo as His Majesty’s direct vassals, so I’ll not risk their direct participation. Perhaps in the future I will have the confidence that I can bring them in under me as well but, for the time being, I dare not request more than what His Majesty has already provided me. Our work will have to earn recognition beyond the shadow of a doubt if you wish to have your friends join you.”

 

“The fact that it is possible is encouraging, my lady. I look forward to our future success.”

 

“Oh my...filled with conviction now, aren’t we?”

 

“Well they are my friends, so yes. I would very much like to be able to work more closely with them.”

 

“Friends, hmm…” Lady Shalltear repeated absently, “well, that will most likely be far in the future. Now that we’re in the spirit of things, let’s see what you can make out of my notes.”

 

Ludmila reached out and took the light blue notepad in her hands, flipping open the cover. Within...were notes in some language that she had never seen before. Continuing to flip through page after page, she saw a multitude of diagrams, maps and dense blocks of the same elegant, yet unknown, text throughout. After her reaction to the initial report on Fassett County, Ludmila thought her liege might be averse to lengthy and meticulous documentation, but going through her notes it seemed like it might not be the case.

 

“I’m sorry, my lady,” she said as she looked back up, “I’m unable to read this…what are you doing?”

 

In front of her, Lady Shalltear was holding a dark green notepad, writing something within.

 

“Taking notes,” she said.

 

On what? Ludmila wondered.

 

“Er, anyways...if you’d be so kind as to provide a translation, I’ll scribe a copy for myself. Aemilia, how much paper do we have left lying around?”

 

Before her maid could reply, Lady Shalltear’s hand disappeared into a hole in the air again, withdrawing a stack of expensive-looking paper.

 

“I have plenty to use,” she said. “Feel free.”

 

She kept piling up more and more stacks of paper until Ludmila thought there should be several thousand sheets towering on the table. Just how many platinum coins was this worth? Aemilia circled around to start storing them away before they toppled over.

 

Placing the first sheet over a hard writing surface, Ludmila took pen in hand.

 

“By the way, my lady,” she asked, “is this your native language? I’ve never seen such script before.”

 

“It is,” Lady Shalltear replied. “And If you do encounter it somewhere, you are to report your findings to me as soon as possible. Consider it a matter of utmost importance.”

 

“…is this language dangerous?”

 

“Not in the way that you probably mean, but those who use it are. In all likelihood, your trying to fight such a person is about as futile as trying to fight me – your best chance of survival would lie with us, though escaping such an individual is unlikely should you provoke them.”

 

There was a stern tone to her liege’s voice: a hard edge bordering on hostility that she had never heard Lady Shalltear express before.

 

“Understood, my lady,” Ludmila nodded. “Though I hope to never meet someone like that. I will avoid confrontation and report to you immediately if I do.”

 

As they settled down into translating Lady Shalltear’s notes, Ludmila could not help but marvel at her attention to detail. After several hours, they had only gotten a third of the way into them; the majority of what was completed being a meticulous breakdown of characteristics and behaviours of the Frost Dragons. Everything from their natural habits, abilities and the known personality traits, performance and tendencies of each individual Dragon under her management. From just the notes, she could understand why they were so suited to serve in their role as the core of the nation’s aerial logistics.

 

A Frost Dragon could cover vast distances through the air: a day’s travel for a mundane and laden caravan in good conditions and paved roads would amount to less than an hour of unhurried flight. They never forgot what they experienced, making them ideal for navigating even the furthest reaches of the world – they would never get lost, as long as they had been there before. Very little in the world could catch one in the air, never mind defeat one, so security for cargo was similarly low on the list of concerns.

 

“These Frost Dragons,” Ludmila said while stretching between sections of notes, “how did they come to join the Sorcerous Kingdom?”

 

“They were a bonus, I suppose,” Lady Shalltear shrugged. “His Majesty was negotiating with the Dwarf Kingdom for various things and the topic of their old capital, Feoh Berkana, came up.”

 

“I suppose that part had something to do with the Dragons?”

 

Lady Shalltear leaned forward, putting her elbows on the table and cupping her chin in her hands.

 

“Yes,” she replied. “The Dwarves had one of their other cities destroyed by a clash between two Frost Dragons, and the Dragons that ended up joining us were the ones that had turned Feoh Berkana into their lair. Hm…how did it go again? We broke a siege by the Quagoa on the final Dwarf stronghold, then one thing led to another and His Majesty promised to liberate Feoh Berkana in exchange for amicable trade relations, technical assistance and one of their ancestral crafts.”

 

“What about these Quagoa you mentioned?” Ludmila asked, “It sounds like the Dwarf Nation was at war with them.”

 

“You could say that they were rivals over the same territory,” Lady Shalltear answered. “They’re hairy, rodent-like Demihumans that stand around my own height. I guess if the Frost Dragons were a bonus, then the Quagoa were a bonus of a bonus? They were servants of the Frost Dragons, so after the Frost Dragon leader was defeated the Quagoa were given the option to submit or die.”

 

“What happened to them?”

 

“They asked for us to prove our strength, so they died for a while. Then they submitted. Those who remained after everything was said and done were transported away, along with their intact dead. Hm...I wonder what that shorty did with the rest of their pieces? She had better still not be carrying it all around with her – that would take forever to air out.”

 

“Ah, I guess they were that sort of Demihuman then.”

 

“That sort? What do you mean?”

 

“I mentioned something along those lines earlier, I think,” Ludmila said. “Many Demihumans will only negotiate if they respect the other side’s strength, so something like a skirmish or contest to prove this is often required before they are willing to resort to diplomacy.”

 

“Ah, that you did,” Lady Shalltear nodded. “Yes, that’s precisely what happened. As expected of someone accustomed to dealing with Demihumans. Ah–I’m glad I managed to get things right, finally…”

 

Her voice trailed off, and Lady Shalltear sat silently in her seat. Ludmila straightened in alarm as her liege’s lip started to tremble, and tears gathered in her shining crimson eyes. Rising from her chair, Ludmila circled around the table as she fished a handkerchief from a pocket. She lowered herself down beside Lady Shalltear, offering the folded linen cloth to her.

 

At first, Lady Shalltear looked down at it wordlessly, trying to contain her emotions. Then a tear escaped and she quickly took the handkerchief to catch it. She stared at the damp spot on the cloth for a moment before her composure collapsed completely. Ludmila laid her hand soothingly between Lady Shalltear’s shuddering shoulders as she sobbed quietly into the handkerchief.

 

“I’m sho glad,” she said in a muffled voice. “Lord Ainzsch…”

 

Ludmila remained beside her, and Lady Shalltear sniffed loudly.

 

“I…I should stop,” she sniffed again, trying to regain control of herself, “He shaid – he said I can’t waste my face on tears.”

 

“Tears of happiness are not a waste, my lady,” Ludmila said gently.

 

Lady Shalltear’s sobs started anew.

 

A long while later, Lady Shalltear finally settled down and Ludmila returned to her seat after helping to fix up her appearance again. Her liege blew her nose into the handkerchief and looked back down at the sheets on the table.

 

“The Quagoa…Demihumans…” She murmured between sniffles, “That reminds me: Cocytus wanted to speak to you about something.”

 

“Lord Cocytus? I’m surprised he would mention me at all.”

 

“Well,” Lady Shalltear sniffed again, “he’s been aware of your existence for as long as I have, and your name has come up several times since. Though he is a man of few words, it does seem like he has some sort of request for you.”

 

Ludmila set the pen down on the untouched page in front of her.

 

“Should we see to this immediately?” She asked, “How long has it been since he asked?”

 

“It’s not an urgent matter,” Lady Shalltear answered. “He’s busy with security arrangements for the events in the capital at the moment anyways. We’ll arrange a visit in advance at some point. For now, let’s continue with these notes, hm?”

