\chapter{Ludmila Zahradnik}

Beyond the documentation of the Frost Dragons and their characteristics, Lady Shalltear’s notes consisted of a variety of ideas and concepts that she had come up with regarding how the Frost Dragons could be utilized and how the transportation network would work. As a result, their progress slowed down considerably since Ludmila needed to often expand on their ongoing transcription to understand what her liege was attempting to convey. While the idea of air transport was something she had grasped on a minor level with the Bone Vultures, many other things, such as ideas revolving around magic and magical items were far outside of her personal experience.

 

“Are these items so readily available for purchase?” She stopped to ask at one point, “Even one such as myself understands the implications of such items being used. Surely someone must have thought of something like this for other forms of transportation at some point, and the concept would’ve become widespread. There’s no way I can think of that can compete with this aside from the spells that you use for transport: you could even use these items in conjunction with those spells and it would become even more ludicrous.”

 

“We do – it’s an everyday thing for us,” Lady Shalltear answered. “Also, when we went on our trip to the north, there was at least one Dwarf that used a similar item to carry the ores that he was mining…he didn’t appear to be a well-off fellow either, compared with some others we encountered later.”

 

“Alright…suppose we use these Infinite Haversacks that are described here,” Ludmila said. “What prevents a Frost Dragon from strapping on any number of these, effectively allowing them to fly all over the place with the capacity of a large ship?”

 

“Being able to fly does not make one immune to encumbrance,” Lady Shalltear told her. “The Infinite Haversacks do weigh enough on their own that the burdens of carrying multiples will add up. I’ve determined that four is the maximum that an average Adult Frost Dragon can manage without affecting the consistency of their long-distance performance. They become larger and more powerful as they age, so an Old or Ancient Frost Dragon will be able to handle more.”

 

“Then what if we put an Infinite Haversack inside of another Infinite Haversack?”

 

“I wouldn’t recommend that. The results would be…unfortunate.”

 

“Alright,” Ludmila said. “But the question still stands…are such items so freely available? Something like these Infinite Haversacks must be exorbitantly expensive, even if they were. The profits a merchant could garner from even a single wagon loaded with these would be enormous, and the demand for them equally so.”

 

Lady Shalltear was silent for a moment at the question, then her hand disappeared into the mysterious hole in the air again. After withdrawing a rolled vellum parchment, a small frown appeared on her face.

 

“What’s that?” Ludmila asked.

 

“It’s a Message scroll,” Lady Shalltear replied. “When I use it, it casts a Message spell which allows me to converse with a single target over long distances. I haven’t had to use one before, so I’m just making sure that I remember what to do.”

 

The described function of the spell seemed conspicuously similar to Ludmila’s own ability. Had she been using magic all along?

 

“Are there limits to its use? Range and such.”

 

“Hmm…I haven’t heard any reports of range limitations – it’s used quite often over hundreds of kilometres. It can be interfered with, though.”

 

“Oh.”

 

“That sounded suspiciously like disappointment.”

 

“It’s just…well, it sounded like one of my own abilities, but the spell appears to be far superior by comparison.”

 

“You have the ability to use Message?” Lady Shalltear eyed her curiously.

 

“I don’t think it works the same way,” Ludmila said. “I’m fairly certain it has to do with my command abilities: Clara and the others can do it as well, but what they do seems slightly different as far as we can tell. Going by my own experience there doesn’t seem to be a limitation on range, but distances beyond a few kilometres take a fair bit out of me. Hearing that Message can contact others hundreds of kilometres away makes my own ability seem unremarkable.”

 

“Well, if it’s not the same thing, there must be other advantages. What else can you do with it?”

 

“You mentioned that Message reaches a single target, but this ability can be heard by multiple individuals if desired…as long as I know roughly where they are. It’s the same ability that you witnessed me use when sending out the first batch of Undead labourers ordered at the administrative office in the city. We’ve found some rather useful applications, but the range is very short in comparison to this spell you’re using.”

 

“Are you able to do it right now? It doesn’t take any mana or components or anything special does it?”

 

“Just a little bit of concentration – next to nothing when we’re this close.”

 

“Ah, then give it a try! I want to hear.”

 

『Hello, Lady Shalltear.』

 

“Oh, I heard it!” Lady Shalltear perked up in her seat, “Okay, how do I reply?”

 

“As far as I know, it’s one-way only,” Ludmila said.

 

“Oh.”

 

Lady Shalltear’s voice fell in disappointment. Ludmila tried thinking of some benefits to the ability.

 

“The four of us – Clara, Liane, Florine and I – are able to freely communicate in complete silence as long as we are within range of one another and we know where each one of us is,” Ludmila said. “Group conversations are also possible. It’s unknown whether the other nobles here have learned how to harness this ability, but it doesn’t seem to be the case…they are keeping it a well-guarded secret otherwise. Between ourselves, we’ve decided not to spread the knowledge of this ability outside of our own little circle.”

 

“Do you know if it can be interfered with?” Lady Shalltear asked, “Or if the communication can be intercepted?”

 

“We have no way to find out, really. At the least, no one has been able to interfere with the ability…but it could simply mean that no one has cared to try. The idea that someone might be able to listen in on our discussions is unsettling, though at that point I suppose it would be no different than eavesdropping on a regular conversation.”

 

“We should find out one of these days,” Lady Shalltear said, “this ability is quite intriguing. Your decision to keep it to yourselves is prudent as well: Lord Ainz has expressed similar sentiments over what knowledge should be promoted, and what should be restricted.”

 

“His Majesty is wise,” Ludmila agreed. “Just the idea of this ability being utilized by corrupt nobles or those with harmful designs against us seems like it would be a nightmare to deal with.”

 

Lady Shalltear tapped the roll of vellum several times on the table. Then she took a deep breath and released it.

 

“Well, here I go,” she said after resolving herself. “Wish me luck.”

 

“Good luck.”

 

“「Message」.”

 

Lady Shalltear released the scroll, which unfurled itself and floated into the air between them before being consumed by azure flames. Raising a hand, she held it to an ear. After a moment, her look of concentration turned to one of success, and she smiled at Ludmila while excitedly gesturing with her free hand. Ludmila smiled back, and Lady Shalltear went through a range of expressions as she silently conversed with the recipient of the spell.

 

“It worked,” Lady Shalltear said in relief as she lowered her hand. “That was a good thing too: I only brought one to try out.”

 

Looking around the manor, Lady Shalltear’s gaze settled on an open section of the hall near the manor entrance.

 

“You won’t mind if I bring them here, yes?” She asked.

 

“My land is yours, but I don’t mind if you trust them,” Ludmila answered. “Who is it?”

 

“You’ve met them before: I’m sure you’ll recognize them immediately.”

 

Stretching her hand towards the empty area, Lady Shalltear cast a spell.

 

“「Gate」.”

 

The familiar black portal opened in the hall and a familiar figure, clad in black plate armour, stepped into the manor. Ludmila rose from her seat and turned to greet him.

 

“Welcome back to Warden’s Vale, Momon,” she said with a warm smile. “I’ve never had the opportunity to express my gratitude for everything that you’ve done for me.”

 

“Umu,” he replied as he stood before them. Ludmila still did not know what it meant.

 

The Adamantite Adventurer looked over her for a moment before walking over to pull out a chair and seat himself to her left. Ludmila reseated herself as well, folding her hands over her lap. Momon’s visored gaze continued to scrutinize her for a long while, and it took an active effort not to shift in her seat. Finally, a long sigh escaped from beneath his helm.

 

“Is something the matter?” Lady Shalltear asked.

 

“Ah, no,” Momon said as Ludmila continued to feel his intense gaze upon her. “If anything, being here in this home sets my mind at ease.”

 

Huh?

 

“Wow~” Lady Shalltear’s mouth slowly formed into a smile.

 

Ludmila felt warmth creeping up her neck and blooming over her cheeks. She turned her gaze away from the Adventurer, and out of the corner of her vision she could see Aemilia covering her mouth with both hands.

 

Why now? It was an ambush against which she had been entirely unprepared. Lady Shalltear was sitting right across from her as well…if anything, shouldn’t she be the one who would normally receive such compliments? The notion that he was paying more attention to her than Lady Shalltear sent several more fragments of Ludmila’s composure tumbling into the abyss.

 

Fighting to wrest back her peace of mind, she couldn’t quite look at him before she found a thread of reason to cling onto.

 

“I-I am…quite flattered,” she struggled to force coherent words out of her mouth, “but I do not wish to come between you and Nabe.”

 

“Eh?”

 

“You are a…couple, yes? You two seem so close, so this must be the case. It is said that you came here from some far away place, pursuing some great cause around the world together…I feel it quite romantic.”

 

Ludmila did feel that it was quite romantic: something that one might only expect out of fanciful tales. The reliance and commitment in one another that would surely blossom into genuine love and respect over the course of their many trials…

 

Perhaps the old saying is true, that all men are wolves.

 

“Though there is one thing I am curious about,” she was finally able to turn back to face him. “Do you plan on settling down somewhere once you start a family together?”

 

Momon planted his face in his gauntlet. It seemed like she had successfully fended him off.

 

“Yes, that’s right,” Lady Shalltear added. “I had expected that Nabe would be with you. She would have surely loved to hear this.”

 

Momon jerked suddenly and went into a fit of coughing. Maybe it wasn’t the first time Lady Shalltear had seen him attempt this.

 

“Ahem,” he cleared his throat. “Ah, ehm. Nabe is with the magic ite–I mean, Nabe is at the exhibition set up by the Imperial Ministry of Magic in E-Rantel. We were about to start cataloguing the magic items they have on display there. You mentioned that you wanted to consult with me on the subject of magic items – is that an office lady suit you’re wearing?”

 

Momon finally turned his attention away from her to speak with Lady Shalltear, and Ludmila stared down at her hands while she resettled herself. Eyeing the inert Ring of Mental Fortitude on her finger, she wished that it would protect her from mind-affecting attacks of that nature as well.

 

“Yes, it gives off just the right image for desk work, doesn’t it?” Lady Shalltear replied. “Lady Zahradnik here arranged my hair…not bad, yes?”

 

“More to the point,” Momon said, “you two seem to have become quite close…”

 

“Human noblewomen are trained to serve as handmaidens, and my Vampire Brides are all busy making preparations for the new transportation network. Which brings me to the reason I called: we wanted your feedback on the magical items I’ve proposed should be standard to each Frost Dragon for their transportation duties. Lady Zahradnik – show him what we were just talking about.”

 

“Yes, my lady,” Ludmila replied.

 

Ludmila looked up and reached over to pull an open folder filled with sheets of paper in front of her. Leafing through the pages, she withdrew the dozen which outlined the subject of their discussion. Placing them in front of Momon, they waited quietly as he scanned over the details.

 

“Hmm…two Infinite Haversacks for Juveniles, four for Adults, six for Old, eight for Elder and twelve for Ancient Dragons. Periapt of Health, Ring of Sustenance, Ring of Regeneration, Greater Ring of Fire Resistance – three rings?

 

“The one Lord Ainz gave to Aura had his own spectacles, so we started seeing what else they could wear. Barring body armour, it appears that they can equip nearly everything – including a band for their tails.”

 

“That’s...rather interesting,” Momon said. “I follow the general idea so far: they won’t get sick, you’ll save on the costs of feeding them, they’ll regenerate injuries that they might receive while on the job, and you’re reinforcing them against their primary weakness.”

 

“Yes, this is the basic equipment I was thinking of to start off with,” Lady Shalltear nodded. “The set should keep them working and prevent the most likely of maintenance issues. Lord Ainz told Aura and Mare that they should rest and eat since they are still growing, so I’ve scheduled time for the Dragons to do so as well to eventually improve our cargo capacity: they’re free to hunt game in the Azerlisia Mountains and the Great Forest of Tob.”

 

“What about these other pages?”

 

“They are optional equipment loadouts that I’ve been considering, though I am leaning towards providing Message scrolls as part of the basic provisions just in case they encounter unforeseen events and emergencies that need to be relayed to us. They’ll be able to report anything suspicious that they notice as they fly around as well.”

 

“Optional, huh…” Momon murmured as he continued reading through. “Why do some of these look like you’re equipping them for war instead of cargo shipments?”

 

“That’s just in case the Sorcerous Kingdom becomes involved in some conflict. If the risks involved with their work increases or they are called in for some reason to fight or deliver our forces somewhere, then they should be suitably prepared, yes?”

 

“Some of these suitable preparations would make some of these Dragons you have capable of destroying small nations single-handedly…perhaps you should stick to something simple for now. There is also the fact that they are Dragons, so being inundated with so many items at once could trigger undesirable behaviours.”

 

“Is that so? Then would it be possible to secure the first set of accessories for all of the Dragons? The Infinite Haversacks as well, of course.”

 

“I will ask around and find out whether it’s possible or not,” Momon replied. “The Adventurer Guild has been clamouring for magic items as well, but the Ministry of Transportation would most likely take priority for practical reasons. The Message scrolls are a prudent addition as well: I’m certain that there should be no problem with those.”

 

“Excellent,” Lady Shalltear smiled brightly. “Please let me know once you have a definitive answer for me.”

 

Momon flipped through the pages quickly one last time before returning them to the table and rising from his seat. Ludmila rose as well, to see him away.

 

“I should get back to E-Rantel,” he said. “Nabe is probably still waiting for me at the Imperial Ministry of Magic’s exhibition. I will send word once I have an answer for you, Minister. Still, though...I had no idea that you had such an eye for coordinating magic items.”

 

“Well, I do have quite an expansive wardrobe of magical equipment,” Lady Shalltear replied, “so this much should be natural, no? Though I suppose I found out how addictive it could be while I was figuring out what might best suit Lady Zahradnik. The hours simply seem to vanish when one has so many magic items to mix and match.”

 

“Indeed…” Momon chuckled, “It is somewhat surprising that you would part so readily with your own precious possessions, however.”

 

“Well, after seeing the others being so free-handed with their own subordinates, I decided that my own should not be so easily overshadowed. She has proven herself a faithful servant thus far, and much has changed since I claimed her as my vassal, don’t you agree?”

 

“This is very true, in many ways. Much has changed for the better since I first encountered her in this place. So what did you end up bestowing Baroness Zahradnik with?”

 

“I’ve only been able to get her to take a ring so far,” Lady Shalltear held up a hand in a helpless gesture. “She is quite stubborn even after I told her that I considered such refusals foolish. As pragmatic as she usually is, like Cocytus she believes that everything one receives from their liege must be earned through merit or come with some important duty. Though she is a noble, she also has that same, obstinate warrior spirit – can you imagine what would happen if you put the two of them together?”

 

“Hmm…I do wonder how such a meeting would play out: either they would hit it off spectacularly or they would barely say anything to one another at all. Speaking of which, you remember he was asking after you two?”

 

“Yes, we’ll be visiting him after he’s seen to organizing his part in E-Rantel’s events.”

 

“I see,” Momon turned away from the table and walked out into the hall. “Well, I should be on my way…if you please.”