\chapter{Ludmila Zahradnik}


Ludmila turned around as Momon left and the Gate closed in on itself. Upon doing so, she found Aemilia reaching above the dining table towards the oil lamp hanging from above.

 

“Please excuse me, Lady Shalltear,” her maid apologised for the imposition. “This lamp needs to be refilled.”

 

Facing back away, Ludmila worked off the neutral expression she had frozen onto her face as the two members of the Royal Court conversed with one another. As she had not been called upon to speak, she could only remain silent without a reason to interrupt their discourse. She felt a presence at her arm and looked down to see that Lady Shalltear had come out to stand beside her.

 

“You went from hot to cold quite quickly there,” she said as they looked out the manor window. “I believe most of the women around E-Rantel would have flung themselves bodily at Momon if they sensed even the hint of a proposition from him.”

 

“I had no expectations at all,” Ludmila replied, “so I was caught completely by surprise. My mind has been on everything else but, recently. I think it’s been that way for all of my friends as well – too much has changed: there’s just so much to do, and never enough time…even if there was, the pool of suitable consorts is sparse.”

 

“It’s not as if the land is completely bereft of men,” Lady Shalltear looked up at her. “Being in your position, you should have plenty of options.”

 

“If it were only that simple. Liane and Florine might be more open to certain matches, but Clara and I are far more selective…I guess it boils down to our respective religions. I hope you don’t mind my bringing it up, as you are a Cleric yourself, my lady.”

 

“You are speaking of Human religions, yes? I’m a bit curious, actually.”

 

“In that case…”

 

Ludmila paused for a moment, thinking on how to best explain.

 

“The faith of the Six Great Gods once dominated these northern lands but, at some point in the past, a heresy took root – a schism, if you will – and the faith of The Four rose to prominence, supplanting the tenets and much of the culture promoted by the faith of The Six. The great cathedrals that were founded long ago alongside the cities became quiet, and only a few strongholds remain: such as Warden’s Vale and the territories that now form Corelyn County. There were many differences that caused this schism, but, by and large, the central tenets of the faith of The Four are far more convenient for the northern nations, if I were to describe it. Their paths are not as straight and narrow as ours, and how each faith views family and marriage is an example of that.”

 

“I see,” Lady Shalltear said. “So the Humans that are picky are followers of your faith, and the ones I see rubbing themselves all over one another on the city streets belong to the others.”

 

“That’s a bit too general of a statement, I think,” Ludmila frowned at the mental image. “But if you observe Clara and I alongside Liane and Florine, the difference in behaviour is distinct enough that it doesn’t need to be stated directly. For lack of a better term, Clara and I are more reserved. The faith of the Six encourages its followers to evaluate potential partners based on their strength and ability with the hope that our children and their descendents will, too, become stronger with each generation through this practice. The institution of marriage is sacred, and faithful relationships are not only prized: they are expected.”

 

“Ah, that explains why you started to bristle after you recovered from Momon’s words.”

 

“I…bristled?” Ludmila didn’t think she did, “I didn’t mean to openly, but I did feel that way inside. As a follower of The Six, those are the values I was raised with. In the northern nations, where the faith of The Four holds sway over the vast majority, our tenets that harness the truths of the world have been cast aside and forgotten. Partners are often chosen using frivolous criteria, bloodlines are thinned to the point where they might as well not exist at all, and the potential of entire generations is left to the winds of fate. All sorts of wrongheaded ideas manifest, such as one’s worth being judged on the basis of inherited wealth and social status, which only serves to make the problem even worse.”

 

“Then,” Lady Shalltear asked, “as a noble, you do not believe yourself above your fellow Humans?”

 

“As a noble,” Ludmila answered, “I understand that I have the education and training invested in me to do what I am supposed to be doing, just as a professional in any other vocation. I do not believe in any inherent sense of superiority conferred simply by occupying my station: the expectations and trust placed in me are components of duty, not privilege.

 

“Also, as my house has remained faithful, I understand that my lineage is more reliable when it comes to producing individuals of higher calibre. It is simply a fact proven in every generation that members of our house are martially superior compared to the average individual. House Corelyn is the same: they consistently produce excellent administrators every generation, and are in a position to harness that potential. Both Clara and I are a product of the tenets of the Six Great Gods – born and raised to excel at what our bloodlines demonstrate aptitude in. We do not run around with the idea in our heads that we are wholly self-made. By the same token, we tend to respect others for what they are born into, be they a farmer, smith or merchant.”

 

“…I didn’t realize there was so much behind your reaction,” Lady Shalltear lightly scratched her cheek with a finger. “I suppose Momon should resign himself to his fate.”

 

“Not only are both Momon and Nabe strong,” Ludmila said, “they have such a close history together…I guess the very idea of his infidelity was offensive. Besides, since they are like that…he should be the same as Nabe, yes?”

 

A small sound issued from Lady Shalltear’s nose. She struggled to control herself for a moment before giving up and laughing outright.

 

“My lady?”

 

“This is too much!” Lady Shalltear said as the light chime of her laughter filled the manor, “Of all the things that could…cheating on Nabe! Bahaha!”

 

A few minutes went by before Lady Shalltear finally reined in her mirth. She wrapped her hand around Ludmila’s elbow, drawing her close.

 

“「Silence」.”

 

The sounds of Aemilia working deeper inside ceased once her liege cast the spell. She felt a cool touch as Lady Shalltear reached around to hold her other hand, pulling Ludmila lightly to face her.

 

“You’re not angry?” Lady Shalltear asked.

 

“What about, my lady?”

 

“Through your perception,” Lady Shalltear told her, “you have discerned that Momon is the same as Nabe. That the Hero of E-Rantel is not who the people believe he is – a champion of humanity: the legend that lifts their spirits as subjects of the Sorcerous Kingdom. Does that not bother you?”

 

“I knew that Nabe wasn’t Human when I first met her,” Ludmila said. “It didn’t change my recognition of her as an Adamantite Adventurer – Adventurers are not solely Human anyways. When we first met, Momon asked me what I saw. His reaction to my answer told me that, at the least, he knew as well. After learning bits and pieces of Darkness’ tale from the Adventurer Guild, I guess I naturally came to that conclusion. That he isn’t what others might expect does not change the fact that he willingly took on a burden that was not his own, and continues to shoulder that burden to this day.”

 

“I know you to be an even-handed individual,” Lady Shalltear noted, “with a perspective far more broad than most of your kind. Do you really think other Humans would share the same sentiments?”

 

Ludmila withdrew her hands from Lady Shalltear’s light grip, turning back to look out past the river to the distant north.

 

“Though it would not be prudent to announce it at this point, I do not believe the majority would care all that much. Nonhumans are becoming more and more commonplace in the Sorcerous Kingdom and, sooner or later, it will just probably be received as nothing more than an odd bit of news. Many are coming to the realization that the future of our people is bright in the Sorcerous Kingdom, and it was Momon who was there to lift them up and help stir them to action. He is still the Hero of E-Rantel and, in a way, he is still also a champion of humanity.”

 

“…so that’s how you see things,” Lady Shalltear said. “Well, since you already seem to be keeping it to yourself, I don’t believe I have to tell you to keep your lips sealed on this matter.”

 

“Yes, my lady,” Ludmila nodded. “Momon suggested that I do the same when we first arrived in E-Rantel – it is not really my place to say anything anyways.”

 

“It’s good that you’re so accommodating,” Lady Shalltear said as the sounds from the rear of the manor resumed, “on some things, at least. If you plan on being so selective, what will you do about a consort?”

 

“Eh…we’re continuing from there? If it comes down to it, I can always consult with the cathedral.”

 

“Are you saying that your temples are also matchmaking agencies?”

 

“It should be expected, considering everything that I’ve mentioned. The temples keep track of lineages and such and, in certain scenarios, there are allowances for polygamy.”

 

“Didn’t you just say that faithful relationships are expected?” Lady Shalltear raised an eyebrow.

 

“I did, but the faith of The Six is not simply made out of lofty ideals: unexpected things can happen: war, raids, famine or disease that decimate populations. If anything, it’s the faith of The Four that–never mind.”

 

“I guess that makes sense. So what happens after you apply for polygamy? Do several men just appear at your door one day?”

 

In the back of the manor, Aemilia suddenly froze.

 

“T-that’s probably not how it works,” Ludmila replied. “Anyways, I have time aplenty to see to that end of things later…we should get back to the Frost Dragons, yes?”

 

“Of course,” Lady Shalltear said with a slight smile before they made their way back to the table.

 

As they seated themselves again, Aemilia came forward and exchanged glances with Ludmila.

 

“Will you be having dinner with us, my lady?” Ludmila asked.

 

“This should take us until tonight some time…did you need me to leave?”

 

“You may stay if you wish, of course. I was more concerned about the council meeting that usually happens around this time…”

 

“Ah, that. His Majesty is currently in the city during the grand opening of the capital, so most of the evening functions revolve around entertaining dignitaries from the Empire.”

 

“Should you not be there as a member of the Royal Council and as the Minister of Transportation?”

 

A displeased expression appeared on Lady Shalltear’s face.

 

“The venues have all been arranged by Albedo,” she said in dubious tones, “so I suspect that she’s planned something along the lines of dumping me into the midst of a swarm of Imperial Nobles to distract them while she looks down from beside the high seat smugly. Rather than needing to politely suffer their attentions, I would much rather be here: seeing to my newly assigned duties. Should I do well, I will have more meaningful audiences with His Majesty in the future.”

 

“I can’t imagine I’d do well in that sort of setting either,” Ludmila said. “I would much rather do as you’ve chosen. Hmm…I’m not sure if our food would suit you: is there anything you can’t take?”

 

“I don’t require food, but I wouldn’t mind trying a little of what you’re having.”

 

Aemilia lowered her head before turning around to begin her preparations. Ludmila sifted through the papers on the table, looking for the page where they had left off.

 

“Should we continue under the assumption that the equipment will be available?” She asked.

 

“Yes, let’s,” Lady Shalltear answered. “I can’t imagine it being any less than the basic set that he agreed was appropriate. We should put together our projections based on this equipment – if there are substantial changes, we’ll be able to see how much the overall picture would change as a result.”

 

It seemed reasonable enough: if the alterations had too pronounced of an effect on their projections, they would have a base to argue from in favour of meeting their requirements for equipment and securing the means to do so. Ludmila had no idea how expensive one set of these magic items would be, however…each seemed to eliminate an aspect of maintenance in transportation, so the practical value of each was readily apparent even to her. Finally finding the half-filled page that she was looking for, she picked up her pen and looked up to Lady Shalltear.

 

“Alright, the last part we left off was arrangements in E-Rantel…please continue with your notes, my lady.”

 

Rather than continuing right away, Lady Shalltear stood from her seat and moved over to sit on the chair to Ludmila’s left. She placed her notepad on the table.

 

“There are diagrams and such,” she explained, “so it will be easier this way.”

 

Looking down at the pad of paper, Ludmila could still not puzzle out anything about the language the notes were written in.

 

“The Frost Dragons are being put up along the northeastern wall of the Central District, overlooking the new Demihuman Quarter. They naturally cool the area with their presence, so the places below the wall will be cooler as well.”

 

“How much cooler is it going to become?”

 

“The top of the wall where they live is completely frozen over and a thin mist often rolls off of the walls. They’ve just moved in so I don’t know how cold it might eventually get.”

 

“Won’t that be a problem?” Ludmila asked. “Lord Mare manages the weather around the agricultural areas of the duchy, so E-Rantel is almost always sunny with the harvest on its way. This has the effect of making the areas of the central district along the north wall feel like standing in an oven, so the cooling from the Frost Dragons should be welcome – at least during the day. The other side, however, is perpetually in the shadow of the wall, so they won’t have the sun warming them up to counteract the cold.”

 

“Yes, that was one of the reasons behind placing them there,” Lady Shalltear answered. “In addition to providing cooling for the central district, the cold, damp area along the wall on the Demihuman side will be used to accommodate the races that prefer cool temperatures, while the opposite wall of the quarter will have the reverse arrangement.”

 

“It sounds like the new Demihuman Quarter will look completely different from what it was before. I thought they would just be building homes for the various races coming to live in E-Rantel that Human homes aren’t suited for.”

 

“It no longer resembles any part of E-Rantel,” Lady Shalltear told her. “The first phase of construction is mostly complete – Mare is quite proud of the design; the Dwarves and Quagoa are assisting in the finer adjustments now. Yuri set up her orphanage there too…it’s a lot bigger than anyone expected it would be.”

 

“Miss Alpha founded her orphanage in the Demihuman Quarter? Aren’t most of the orphans she’s taking in Human children from around the duchy?”

 

“Most of them are, yes,” Lady Shalltear said. “Lord Ainz has granted her his full support for the project, so she chose a place in the city with a lot of room to build. Yuri also believes that having the orphanage there will result in the children becoming used to seeing and interacting with nonhuman species, and vice versa. She and a few others have put quite a lot of thought into it – the complex is very expansive.”

 

“I should really take a look at the new quarter when I have the chance,” Ludmila said. “It must be full of ideas that I’ve never considered before.”

 

“I’m sure you’ll have plenty of opportunities to do so,” Lady Shalltear flipped to the next page. “We’ll be dropping by at some point soon so I can show you around the Dragon area anyways. This is what it looks like, roughly.”

 

Looking down to the notepad, Ludmila saw a diagram of the wall. While the curtain walls of E-Rantel were massive by Human standards, they were too narrow to accommodate the Frost Dragons which currently measured up to eighteen metres in length. In an earlier portion of Lady Shalltear’s notes, their slain leader was estimated to be twenty metres from the tip of his tail to the end of his snout. Their wingspan was as wide as they were long, though it was only a consideration for spaces where they were expected to take off and fly through. Dragons reportedly grew throughout their lives, so the hoardings that had been built for them on the wall would become too small for their occupants eventually.

 

“Are these hoardings not cramped?” Ludmila asked as she copied the diagrams, “For a Human these would seem quite large, but the Dragons barely fit. They’re almost like pens for livestock.”

 

“It’s the best that the Dwarven architects could devise given the smaller size of the inner wall,” Lady Shalltear answered. “Once we’ve determined where the highest areas of demand for the network will be, the Dragons will have their lairs redistributed to match – then we can knock down some of the divisions between the pens in the city for more space. The arrangement is temporary for now and I’ve let them know that it is, but they certainly like to complain to one another about it when I’m not around.”

 

“What does a whining Dragon even sound like?”

 

“You’ll inevitably hear it one of these days, as much as they do. As long as it doesn’t affect their work, they can complain all they want – they’ve directly witnessed what happened to their patriarch and one of the stronger ones in the younger generation that challenged Lord Ainz, so the price of disobedience has been burned into their minds.”

 

“Would you actually kill one?”

 

“Mmh…not unless they did something absolutely unforgivable. Since their recollection of their own experiences is so excellent, they are easy to train and correct if they pick up undesirable behaviours. They also aren’t like Adventurers that will be certain to take resurrections after an incident, either – a Frost Dragon might decide to reject a resurrection out of spite and then we’ll be short one until new offspring can be raised. It would take over a century to replace a lost Adult Frost Dragon.”

 

“If that’s the case,” Ludmila said, “shouldn’t treating them well be the best course of action? That way there’s a lower risk of rejection should resurrection be required.”

 

“Yes, well, figuring out what ‘treating them well’ is is the question, isn’t it?” Lady Shalltear told her, “You might know what Humans desire and perhaps draw some similarities between Humans and Demihumans, but these are Dragons. Their minds operate much differently than yours – even the way they perceive the world is entirely alien to you. You will have to understand them first before thinking about how to manage them; in the meanwhile, fear is a more reliable motivator than respect or loyalty.”

 

Ludmila glanced to the side where the piles of translated notes continued to accumulate. She thought the subject quite interesting, but it would probably still take weeks of study to develop what she might consider a basic understanding. At least out in her demesne, her daily tasks were grouped by location so she would have blocks of time to read in between.

 

The quiet sounds of work from the nearby counter stopped, and Aemilia appeared carrying the first portion of dinner. Ludmila put down her pen to clear away space for their meal.

 

“It seems like we’re making good time,” Ludmila said. “Shall we take a quick break for dinner?”