\chapter{Ludmila Zahradnik}

Aemilia appeared with a second bowl, followed by tea. Dinner was the customary village stew which Ludmila had taught her maid how to make. A roll of bread accompanied each bowl, and a rich aroma wafted up to tempt the appetite. She waited as Lady Shalltear studied the dish in front of her.

 

“I hope it’s to your liking,” Ludmila said. “I remembered you eating a biscuit the first night, and you can drink tea but, as you might imagine, we don’t have any experience in serving meals for the Undead.”

 

“Our cooks were in the midst of experimenting with recipes that night,” Lady Shalltear told her, “so I ended up being a sort of test subject – you were as well, as I recall. I think most of them were a failure: there were no unexpected findings, and they confirmed that you simply can’t substitute one thing for another in a recipe, regardless of similarities.”

 

“It did seem like Miss Alpha was expecting something when she asked me how I felt about the meal,” Ludmila said. “I guess I should have tried to figure out a way to provide you with something suitable. Are the tales true that Vampires drink blood?”

 

“Blood has a wide variety of flavours and sensations just like any other sort of food but, broadly speaking, it is what we normally consume. Other Undead have different diets: Ghouls eat flesh, Zombies eat…actually, I haven’t seen Yuri eat anything beyond Human-style food.”

 

“…Miss Alpha is a Zombie?” Ludmila stared at Lady Shalltear.

 

“Yuri is a Dullahan,” Lady Shalltear replied. “She’s using mundane means to conceal any hints of it, so your Talent isn’t of any use with her. She looks exactly the way she looks: there isn’t much to hide, really.”

 

The E-Rantel Orphanage is being run by the Undead.

 

Clara said she would be leaving the four children from Fassett County at the Orphanage; Ludmila wondered how they would feel about this.

 

“Anyways, you shouldn’t worry so much,” Lady Shalltear said as she stirred the bowl with her wooden spoon. “Though our tastes might differ in various things, we can still eat. Itadakimasu.”

 

Lady Shalltear put a spoonful of the village stew into her mouth, rolling it around for a while before swallowing to speak again.

 

“This is more substantial than it looks – what the nobles seem to eat in the city is meagre by comparison. Is this why you’re taller than the other noblewomen?”

 

“Clara is only a bit shorter than I am,” Ludmila said, “and she dines on the same cuisine as the city nobles. It should be more along the lines of what I mentioned earlier concerning the cultivation of bloodlines. You said something at the end just now that I didn’t quite get…what does it mean?”

 

The spoon returned to its bowl, idly stirring as Lady Shalltear furrowed her brow. After a handful of seconds, she turned to Ludmila with a questioning look.

 

“What did I say?”

 

“Itada-something…”

 

“Ah, it’s a ritual of sorts,” Lady Shalltear turned back to her bowl, “If I were to paraphrase it, it’s a consideration for all the elements that went into the meal: from what was grown and raised, to the efforts of all those involved in its preparation.”

 

“By ritual, you mean it’s one of your faith? I hope I’m not being rude by prying.”

 

“Not at all. The saying is a part of the culture of where I’m from. It’s simply a respectful mannerism – there’s nothing directly magical about it.”

 

Lady Shalltear resumed eating and Ludmila began on her own meal, relieved that her liege found nothing offensive about it. They continued in silence until she wiped up the remaining bits of stew with her last piece of bread.

 

“Do Frost Dragons eat a lot?” She asked as Aemilia carried away their dishes.

 

“By their own explanation,” Lady Shalltear replied, “it depends on how active they are. An Adult would require roughly one large game animal every four or five days if they flew around making deliveries like I plan on having them.”

 

“That would require a tremendous hunting range for eighteen Dragons…is the territory you’ve designated as their feeding grounds sufficient? The Azerlisia Mountains and its surrounding foothills extend all the way north to the sea, but if the bulk of the deliveries are in the area of E-Rantel, it limits their hunting grounds to the southern parts of the Great Forest of Tob.”

 

“They’ll still have their Rings of Sustenance, so they won’t starve. I just wanted them to continue eating so they would eventually grow to increase their carrying capacity.”

 

“Still…having that many Dragons feeding in the area might have some undesirable side effects. I’m not actually certain what is in that part of the Great Forest of Tob, but if there are citizens living there, it may result in some ill will.”

 

“I see,” Lady Shalltear looked up thoughtfully at her. “You always seem to have this broad consideration for things.”

 

“Understanding relationships in nature is a part of being a Ranger,” Ludmila said, “and, with a little bit of thought, that understanding may provide perspective on other aspects of the world around me…though I can’t say it always results in a sensible or useful outcome.”

 

“Hmm…so what would be your solution to this problem?”

 

“You mentioned that they would eventually be based in different locations depending on route demand, so the problem may actually take care of itself. At the least, it would require fewer adjustments once we have a clearer picture of how this network will be laid out.”

 

Reaching out to where their work had been piled off to the side, she found the place where they had left off. Lady Shalltear took the notepad and flipped through until they reached the page past the diagrams for E-Rantel. In addition, she produced a map from the hole in the air, along with several measuring instruments.

 

“I’ve been wondering…what exactly happens when you reach into that hole in the air?”

 

“I’m pulling things out from my personal inventory – probably the easiest way to understand it is equating it to reaching into a much larger Infinite Haversack.”

 

“I’ve never seen an Infinite Haversack before. Today is the first time I’ve even heard of it.”

 

“Oh.” Lady Shalltear reached into her inventory again, “Where is it...no, not that one...ah, here it is.”

 

A modestly-sized satchel appeared, and Lady Shalltear placed it on the table. Considering that the notes mentioned one such container could hold five hundred kilograms, it was much smaller than what Ludmila had expected.

 

“Didn’t you say that placing an Infinite Haversack inside another such container would have unfortunate results?”

 

“An inventory is not the same,” Lady Shalltear replied. “What I was referring to were other similar enchanted containers like this.”

 

After looking towards Lady Shalltear, who nodded, Ludmila reached out to lift the bag. It was far heavier than it looked, but the weight was only a small fraction of its full capacity. Placing it back on the table, she reached into the dark void of the container.

 

“Is there anything inside of this one?” She asked as she felt around inside of it blindly.

 

“That was the one that was holding most of the paper,” Lady Shalltear said. “There should be a few other things as well…try thinking of the clipboard that you saw one of my Vampire Brides holding in the alley when we met.”

 

Ludmila recalled the item from her memory, and she felt an object in her hand. She pulled it out: it was a clipboard similar to the one that she had envisioned. The item was wider than the neck of the container, but she was able to withdraw it smoothly somehow and deposit it again the same way.

 

“What if one doesn’t know what’s inside?”

 

“You could always pour everything out,” Lady Shalltear said as she returned the container to her inventory. “I’d advise caution, as the contents would be unknown. Someone dumping five hundred kilograms of objects onto their own feet will probably be in for some pain. You can even store liquids in them so you may end up with quite a mess.”

 

Several ideas that she had been nursing ever since she had read of the Infinite Haversack floated to the forefront of her mind again.

 

“I think I’ve known you long enough to understand what that look means…” Lady Shalltear said.

 

“I was just revisiting my thoughts from before about these containers,” Ludmila started slowly as she solidified her thoughts. “If a common Dwarf can get their hands on something like this, then why is it that we don’t see more of them being used? I’ve become well aware that Re-Estize is behind when it comes to the utilization of magic and magical items across many fields, but merchant companies who travel the world are not constrained to our local ways of thinking and would certainly take advantage of such wondrous items. You could haul thousands of these containers in a caravan, transporting the wealth of entire cities.”

 

“Have you considered the idea that nations may see these as dangerous?” Lady Shalltear offered, “As you say, the implications of such items cast a shadow over your ideas of mundane transport. A nation which collects these would have distinct logistical advantages, be they intended for commercial or military use. It may be that they are simply snapped up by such interests, or the crafters of these items are well guarded and restricted from openly selling their wares.”

 

“If that is the case,” Ludmila sighed, “would Momon even have a chance of locating a source of them? As you’ve said, the planning of this network hinges greatly on the availability of these items. Without them, our freight capacities are drastically reduced.”

 

“We’ll have to see, won’t we?” Lady Shalltear smiled.

 

“To be honest, my lady,” Ludmila said. “I’m surprised that you called Momon here rather than someone like the Royal Treasurer for something of this nature. Though the Royal Treasurer seems to be active around E-Rantel, I haven’t actually met this person before.”

 

“The Royal Treasurer has his own set of duties to attend to,” Lady Shalltear said. “If the situation calls for it, I will personally pay him a visit.”

 

“I understand,” Ludmila said. “Someone in his position is bound to be a busy person, and Darkness should have any number of useful connections with how well-traveled they are.”

 

Thinking about the Infinite Haversacks again, Ludmila absently stared down at the sheets laid before her.

 

“I suppose you’d want one for yourself.”

 

“I’d want as many as I could purchase, but I have the feeling that these would be far beyond my budget considering their utility.” Ludmila sighed, “It seems like anything goes when you have magic.”

 

She glowered at the empty space that the Infinite Haversack formerly occupied. Maybe Liane would know more.

 

“Is there some personal use you had in mind for one?” Lady Shalltear asked.

 

“There’s an…old problem,” Ludmila said. “As members of my family grew stronger in…levels, was it? We could use more powerful bows. I suppose that would lead to powerful, enchanted bows but we never got our hands on any…anyways, even supposing that we could find a powerful, enchanted bow, we wouldn’t be able to realize the full potential of our weapons because taking advantage of the power of such bows meant that we would need to use arrows capable of delivering the incredible force to our targets with power far greater than what a mundane warbow can achieve.”

 

“What about enchanted arrows?”

 

“The construction of the arrow still matters,” Ludmila shook her head. “If anything, you want durable arrows that won’t shatter like regular ones if you plan on using enchantments on them: that way you can recover them after use. Even then, they are only a part of the arsenal that an archer can bring to bear, and this wide variety of ammunition is a part of the problem. There are arrows designed to deliver alchemical compounds and simple mechanisms, those with special material properties to counteract the damage resistance of various species and exploit their weaknesses. A multitude of mundane options exist as well, and all of this adds up.

 

“The founder of House Zahradnik was said to have been able to knock a Troll clean off their feet using the same type of bow and arrows that I use today. They say if he had managed to find a powerful magical bow with arrows to match, he would have been able to take even Dragons out of the sky.”

 

“You’re not supposed to be shooting our Dragons out of the sky,” Lady Shalltear frowned.

 

“...it was just an example. The point is that obtaining a powerful bow is only one part of the problem. Having a selection of arrows that can take full advantage of a powerful bow is not a problem beyond their cost if you are defending a position where you can store them, but their weight becomes an issue if the supply of these arrows is restricted to what you can carry. Without something like an Infinite Haversack, I need to balance issues of encumbrance and flexibility when I’m out ranging or on patrol. With one, I would be able to bring thousands...well, not that I could afford thousands. At the least, I wouldn’t have to worry about storage issues. That in itself would ensure I’d have the bare minimum on hand to deal with any given situation.”

 

“Well, maybe if you’re lucky we’ll have some to spare, hm? If Momon secures a supply of them, I will most certainly be taking extras – I wouldn’t mind if you wanted one or two for your personal use.”

 

Ludmila remained silent as she deliberated over Lady Shalltear’s offer.

 

“If you refuse me after all this trouble,” Lady Shalltear said as a frown started to form on Ludmila’s face, “I will most certainly get annoyed. I know you’re a practical person, and this is about as practical as it gets. If you really must, you may consider this a reward for your continued assistance in managing all this.”

 

“Yes, my lady,” Ludmila lowered her head. “Thank you for your consideration.”

 

“Let’s continue, shall we?” Lady Shalltear said, unfurling the large map she had taken out earlier, “All that remains is examining our routes and making some initial projections for them.”

 

The map was centred on the Sorcerous Kingdom, but included an extended area around its borders. There were many places without details or labels, but those with them were exceptionally intricate. It was immeasurably superior to the one that Momon showed to her when they first travelled to E-Rantel – she wondered why that was…perhaps it was recently made.

 

“Who produced this map?” Ludmila asked, “The ones that Re-Estize have are nowhere near as good.”

 

“That would be Aura,” Lady Shalltear answered. “This is the most recent update of her local surveys.”

 

“As expected of such a talented Ranger,” Ludmila continued to marvel over its craftsmanship. “If I were even half as good I would be satisfied.”

 

“Well, I wouldn’t get ahead of myself there: ‘half as good’ is probably a lot further than you think.”

